### 2017-10-10 Regeneron Paper.tex
Initial commit

\documentclass{article}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{enumitem}
\usepackage{hyperref}

\algnewcommand{\LineComment}[1]{
	\State \(\triangleright\) #1
}

\algrenewcommand
\textproc{}

\hypersetup{
	colorlinks=true,
	linkcolor=blue
}

\setlist{nolistsep}
\setlength{\parskip}{1em}

\begin{document}
	\begin{abstract}
		This paper introduces the \textit{fragmented list} data structure, which implements the list abstract data type. A fragmented list consists of multiple arrays, or \textit{buffers}, that store its elements. Fragmented lists do not make copies or throw away old buffers while resizing. As a result, they perform significantly better than dynamic arrays when a large number of elements are added to them. However, this is provided the final size of the list (or a close upper bound on it) is not known beforehand. If it is, a buffer of that size can be pre-allocated and resizing can be avoided, making fragmented lists redundant.
	\end{abstract}

	\section{Introduction}
	\label{Introduction}

	% TODO: This isn't being indented
	Often, node-based structures receive the most attention in a course on data structures. Although it is simpler to implement everything with arrays\footnote{}, node-based structures are favored because they have better time complexity for operations such as insertion and deletion.\par

	However, arrays have their own performance advantages over such structures, including:\par

	\begin{itemize}
		\item Better locality when iterating: elements of an array live next to each other in memory.
		\item Less memory overhead: memory does not need to be allocated for nodes.
		\item Fast random access: since arrays are just pointers, indexing them takes a few instructions and runs in $O(1)$ time.
	\end{itemize}

	When an abstract data type (which I will refer to as \textit{data type}) can be implemented easily with arrays, they are often used. One such data type is the \textit{list}\footnote{}, which is usually implemented with a dynamic array.\par

	Dynamic arrays perform reasonably well with respect to their most common operations. Adding an item runs in amortized $O(1)$ time, indexing them runs in $O(1)$ time, and they can be iterated in $O(n)$ time.\par

	However, when a dynamic array is \textit{full} (that is, its size equals its capacity) and an item is added, it must resize its buffer to fit the new item. Its behavior here is less than optimal: it allocates a new buffer larger than the current one, copies over the items, and discards the current buffer.\par

	Instead of throwing away buffers once they're filled up, \textit{fragmented lists} store references to them in a two-dimensional array. During a resize, a new buffer is still allocated; however, for a sufficiently large number of items, it is always half the size of the buffer that a dynamic array would allocate.\par

	In addition, no items are copied to the front of the new buffer. This is because no buffer represents the entire content of the list; each buffer holds just a \textit{fragment} of the items. To get back the items that were added to the fragmented list, one needs to traverse each of the buffers and copy their share of the items.\par

	% TODO: ToC or not?

	\section{Terminology}
	\label{Terminology}

	\begin{description}
		\item[buffer] % TODO
		\item[capacity] % TODO
		\item[full/filled] % TODO
		\item[growth factor]
		\item[list] % TODO
		\item[resize]
		\item[threshold sizes] The set of sizes for which adding one more item will cause the list to resize. This is the same as the set of all capacities the list takes on. [prove]
	\end{description}

	\section{Predefined Functions}
	\label{Predefined Functions}

	I assume the following functions are provided by the runtime environment, so that I may use them without defining them beforehand.\par

	\begin{algorithm}\begin{algorithmic}
			\LineComment{Adds \textit{item} to dynamic array \textit{dynamic}}
			\State $add(dynamic, item)$
			\\
			\LineComment{Allocates and returns an array of length \textit{len}}
			\State $array(len)$
			\\
			\LineComment{Returns the length of array \textit{array}}
			\State $len(array)$
		\end{algorithmic}\end{algorithm}

	\section{Fragmented List Structure}
	\label{Fragmented List Structure}

	Each fragmented list, denoted by $\ell$, is given four \textit{fields}: $h(\ell)$, $t(\ell)$, $size(\ell)$, and $hsize(\ell)$. These fields may be read from and assigned to.\par

	\begin{itemize}
		\item $h$ stands for the \textit{head} of the fragmented list. It returns the buffer we are currently adding items to.
		\item $t$ stands for the \textit{tail} of the list. It returns a list of buffers that have already been filled.
		\item $size$ returns the number of items in $\ell$.
		\item $hsize$ stands for \textit{head size}. It returns the number of items in $h(\ell)$. This is \textit{not} the same as $len(h(\ell))$; that is the head's capacity.
	\end{itemize}

	Below, I also define some auxiliary functions on $\ell$ (which cannot be assigned to). $:=$ denotes a definition, as opposed to $=$ which checks equivalence. Functions that return boolean values are suffixed with ?.

	\begin{algorithm}\begin{algorithmic}
			\LineComment{Returns the capacity of $\ell$}
			\State $cap(\ell) := size(\ell) + \left(hcap(\ell) - hsize(\ell)\right)$
			\\
			\LineComment{Returns whether $\ell$ is empty}
			\State $empty?(\ell) := size(\ell) = 0$
			\\
			\LineComment{Returns whether $\ell$ is full}
			\State $full?(\ell) := size(\ell) = cap(\ell)$
			\\
			\LineComment{Returns the capacity of $h(\ell)$}
			\State $hcap(\ell) := len(h(\ell))$
		\end{algorithmic}\end{algorithm}

	\section{Fragmented List Operations}
	\label{Fragmented List Operations}

	\subsection{Adding an Element}

	I begin with the implementation for \textit{add} since it is the most common list operation [cite]. Its algorithm is very similar to that of a dynamic array: it resizes the list if it's full, then stores the item and increments the size. The head's size is also incremented since an item is added to it.

	\begin{algorithm}\begin{algorithmic}[1]
			\Procedure{\textit{add}}{$\ell, item$}
				\If{$full?(\ell)$}
					\State $resize(\ell)$
				\EndIf

				\State $h(\ell)[hsize(\ell)] \gets item$
				\State $size(\ell) \gets size(\ell) + 1$
				\State $hsize(\ell) \gets hsize(\ell) + 1$
			\EndProcedure
		\end{algorithmic}\end{algorithm}

	A fragmented list is resized quite a bit differently from a dynamic array, however. % TODO

	\begin{algorithm}\begin{algorithmic}[1]
			\Procedure{\textit{resize}}{$\ell$}
				\Require
					\Statex $full?(\ell)$
				\If{$empty?(\ell)$}
					\State $h(\ell) \gets array(4)$
					\State $cap(\ell) \gets 4$
					\State \Return
				\EndIf

				\State $add(tail(\ell), head(\ell))$
				\State $newcap \gets g(hcap(\ell))$
				\State $h(\ell) \gets array(newcap)$
				\State $hsize(\ell) \gets 0$
				\State $cap(\ell) \gets cap(\ell) + newcap$
			\EndProcedure
		\end{algorithmic}\end{algorithm}

	\begin{algorithm}\begin{algorithmic}[1]
			\LineComment{\textit{g} is the \textit{growth function}.}
			\LineComment{It decides the capacity of the next buffer based on the current buffer's capacity.}
			\Function{\textit{g}}{$cap$}
			\Require
			\Statex $cap \geq 4 \land \log_2{cap} \in \mathbb{N}$
			\State \Return $\begin{cases}
			4 & cap = 4\\
			2 * cap & cap \neq 4
			\end{cases}$
			\EndFunction
		\end{algorithmic}\end{algorithm}

	\subsubsection{Time Analysis}

	$$
	T[add] = T_{2,6} = T_{2,3} + T_{4, 6}
	$$

	When $\ell$ is not full:

	$$
	T_{2,3} + T_{4,6} = T_{4,6} = C
	$$

	When $\ell$ is full:

	$$
	T_{2,3} + T_{4,6} = T_[full?] + T_[resize] + T_{4,6} = T[resize] + C
	$$

	Now we must analyze $resize$.

	When $\ell$ is empty:

	$$
	T[resize] = T_{2,5} = T[empty?] + T_alloc(4) + T_5 = T_alloc(4) + C
	$$

	When $\ell$ is non-empty:

	$$
	T[resize] = T[empty?] + 
	$$

	\subsubsection{Space Analysis}

	\subsection{Indexing}

	\begin{algorithm}\begin{algorithmic}[1]
			\Function{\textit{item at index}}{$\ell, index$}
	 			\Require
	 				\Statex $0 \leq index < size(\ell)$
	 			\State $i \gets index$
	 			\ForAll{$buf \in t(\ell)$}
	 				\If{$i < len(buf)$}
	 					\State \Return $buf[i]$
	 				\EndIf
	 				\State $i \gets i - len(buf)$
	 			\EndFor

	 			\Return $h(\ell)[i]$
 			\EndFunction
		\end{algorithmic}\end{algorithm}

	A function to set an item at a particular index can be implemented in a similar fashion.

	\subsection{Inserting an Element}

	\subsection{Deleting the Last Element}

	\subsection{Deleting an Element}

	\subsection{Copying to an Array}

	\subsection{Iterating}

	\subsection{Searching}

	\subsection{In-Place Sorting}

	\section{Implementations}
	\label{Implementations}

	\section{Benchmarks}
	\label{Benchmarks}

	\section{Closing Remarks}
	\label{Closing Remarks}

	% TODO: May need to ask something about how the pseudocode is only valid for GC'd languages.

\end{document}

### 2017-10-13 Regeneron Paper.tex
Add _dyn suffix
Plenty of changes

@@
 \usepackage{enumitem}
-\usepackage{hyperref}
 
 \algnewcommand{\LineComment}[1]{
-	\State \(\triangleright\) #1
+	\Statex \(\triangleright\) #1
 }
 
-\algrenewcommand
-\textproc{}
-
-\hypersetup{
-	colorlinks=true,
-	linkcolor=blue
+\newcommand{\head}{
+	\ensuremath{Head_L}
+}
+\newcommand{\tail}{
+	\ensuremath{Tail_L}
+}
+\newcommand{\size}{
+	\ensuremath{Size_L}
+}
+\newcommand{\capacity}{
+	\ensuremath{Cap_L}
 }
 
+\newcommand{\headsize}{
+	\ensuremath{Hsize_L}
+}
+\newcommand{\headcapacity}{
+	\ensuremath{Hcap_L}
+}
+\newcommand{\isempty}{
+	\ensuremath{Empty?_L}
+}
+\newcommand{\isfull}{
+	\ensuremath{Full?_L}
+}
+
+\newcommand{\addfn}{
+	\ensuremath{Add_L}
+}
+\newcommand{\resizefn}{
+	\ensuremath{Resize_L}
+}
+
+\newcommand{\timeof}[1]{
+	\ensuremath{T\big[#1\big]}
+}
+\newcommand{\spaceof}[1]{
+\ensuremath{S\big[#1\big]}
+}
+\newcommand{\capacities}{
+	\ensuremath{Caps_L}
+}
+
+\algrenewcommand{\textproc}{
+}
+
+\setlength{\parskip}{1em}
 \setlist{nolistsep}
-\setlength{\parskip}{1em}
 
@@
 	Often, node-based structures receive the most attention in a course on data structures.
-Although it is simpler to implement everything with arrays\footnote{}, node-based structures are favored because they have better time complexity for operations such as insertion and deletion.\par
+Although it is simpler to implement everything with arrays\footnote{}, node-based structures are favored because they have better time complexity for operations such as insertion and deletion.
 
-	However, arrays have their own performance advantages over such structures, including:\par
+	However, arrays have their own performance advantages over such structures, including:
 
@@
 	When an abstract data type (which I will refer to as \textit{data type}) can be implemented easily with arrays, they are often used.
-One such data type is the \textit{list}\footnote{}, which is usually implemented with a dynamic array.\par
+One such data type is the \textit{list}\footnote{}, which is usually implemented with a dynamic array.
 
 	Dynamic arrays perform reasonably well with respect to their most common operations.
-Adding an item runs in amortized $O(1)$ time, indexing them runs in $O(1)$ time, and they can be iterated in $O(n)$ time.\par
+Adding an item runs in amortized $O(1)$ time, indexing them runs in $O(1)$ time, and they can be iterated in $O(n)$ time.
 
 	However, when a dynamic array is \textit{full} (that is, its size equals its capacity) and an item is added, it must resize its buffer to fit the new item.
-Its behavior here is less than optimal: it allocates a new buffer larger than the current one, copies over the items, and discards the current buffer.\par
+Its behavior here is less than optimal: it allocates a new buffer larger than the current one, copies over the items, and discards the current buffer.
 
 	Instead of throwing away buffers once they're filled up, \textit{fragmented lists} store references to them in a two-dimensional array.
-During a resize, a new buffer is still allocated; however, for a sufficiently large number of items, it is always half the size of the buffer that a dynamic array would allocate.\par
+During a resize, a new buffer is still allocated; however, for a sufficiently large number of items, it is always half the size of the buffer that a dynamic array would allocate.
 
@@
 This is because no buffer represents the entire content of the list; each buffer holds just a \textit{fragment} of the items.
-To get back the items that were added to the fragmented list, one needs to traverse each of the buffers and copy their share of the items.\par
+To get back the items that were added to the fragmented list, one needs to traverse each of the buffers and copy their share of the items.
 
@@
 
-	\section{Terminology}
-	\label{Terminology}
+	\section{Definitions}
+	\label{Definitions}
+
+	\subsection{Terminology}
 
 	\begin{description}
-		\item[buffer] % TODO
-		\item[capacity] % TODO
-		\item[full/filled] % TODO
-		\item[growth factor]
-		\item[list] % TODO
-		\item[resize]
-		\item[threshold sizes] The set of sizes for which adding one more item will cause the list to resize. This is the same as the set of all capacities the list takes on. [prove]
+		\item[buffer] An array that holds a portion of the items in a fragmented list.
+		\item[capacity] The maximum amount of items a list can hold without resizing.
+		\item[full, filled] A list is full iff its size equals its capacity, meaning it must resize if another item is added.
+		\item[growth factor] The factor by which the capacity grows when the list is resized, if the current capacity is nonzero.
+		\item[list] The list data type. This term does not refer to a particular implementation of the data type, only the "interface."
+		\item[resize] To increase a list's capacity once it is full.
+		\item[threshold sizes] The set of sizes for which the list is full.
 	\end{description}
 
-	\section{Predefined Functions}
-	\label{Predefined Functions}
+	% TODO: Prove that the set of threshold sizes equals the set of capacities. Superset/subset argument.
+
+	\subsection{Runtime-Provided Functions}
 
@@
 	\begin{algorithm}\begin{algorithmic}
-			\LineComment{Adds \textit{item} to dynamic array \textit{dynamic}}
-			\State $add(dynamic, item)$
+			\LineComment{Adds \textit{item} to dynamic array \textit{d}}
+			\State $Add\ dyn_{d}(item)$
 			\\
 			\LineComment{Allocates and returns an array of length \textit{len}}
-			\State $array(len)$
+			\State $Array(len)$
 			\\
-			\LineComment{Returns the length of array \textit{array}}
-			\State $len(array)$
+			\LineComment{Allocates and returns an empty dynamic array}
+			\State $Dynamic()$
+			\\
+			\LineComment{Returns the length of array \textit{a}}
+			\State $Len_a$
 		\end{algorithmic}\end{algorithm}
+
+	\subsection{Mathematical Notation}
+
+	\begin{description}
+		\item[$T_m(n)$] Time it takes to allocate memory for an array of size $n$
+	\end{description}
 
@@
 
-	Each fragmented list, denoted by $\ell$, is given four \textit{fields}: $h(\ell)$, $t(\ell)$, $size(\ell)$, and $hsize(\ell)$. These fields may be read from and assigned to.\par
+	Each fragmented list, denoted by $L$, is given four \textit{fields}: \head, \tail, \size, and \capacity. These fields may be read from and assigned to.
 
 	\begin{itemize}
-		\item $h$ stands for the \textit{head} of the fragmented list. It returns the buffer we are currently adding items to.
-		\item $t$ stands for the \textit{tail} of the list. It returns a list of buffers that have already been filled.
-		\item $size$ returns the number of items in $\ell$.
-		\item $hsize$ stands for \textit{head size}. It returns the number of items in $h(\ell)$. This is \textit{not} the same as $len(h(\ell))$; that is the head's capacity.
+		\item \head is the \textit{head} of the fragmented list. It returns the buffer we are currently adding items to.
+		\item \tail is the \textit{tail} of the list. It returns a list of buffers that have already been filled.
+		\item \size is the list's \textit{size}. It returns the number of items in $L$.
+		\item \capacity is the list's \textit{capacity}. It returns the maximum number of items $L$ can hold without resizing.
 	\end{itemize}
 
-	Below, I also define some auxiliary functions on $\ell$ (which cannot be assigned to).
+	Below, I also define some auxiliary functions on $L$ (which may not be assigned to).
 $:=$ denotes a definition, as opposed to $=$ which checks equivalence.
@@
 	\begin{algorithm}\begin{algorithmic}
-			\LineComment{Returns the capacity of $\ell$}
-			\State $cap(\ell) := size(\ell) + \left(hcap(\ell) - hsize(\ell)\right)$
+			\LineComment{Returns whether $L$ is empty}
+			\State $\isempty := \size = 0$
 			\\
-			\LineComment{Returns whether $\ell$ is empty}
-			\State $empty?(\ell) := size(\ell) = 0$
+			\LineComment{Returns whether $L$ is full}
+			\State $\isfull := \size = \capacity$
 			\\
-			\LineComment{Returns whether $\ell$ is full}
-			\State $full?(\ell) := size(\ell) = cap(\ell)$
+			\LineComment{Returns the capacity of \head}
+			\State $\headcapacity := Len_{\head}$
 			\\
-			\LineComment{Returns the capacity of $h(\ell)$}
-			\State $hcap(\ell) := len(h(\ell))$
+			\LineComment{Returns the size of \head}
+			\State $\headsize := \size - \left(\capacity - \headcapacity\right)$
+		\end{algorithmic}\end{algorithm}
+
+	Before we call any functions with $L$, we need to make sure that it is properly initialized. (In an object-oriented language, this code would go in the constructor.)
+
+	\begin{algorithm}\begin{algorithmic}
+			\State $\head \gets Array(0)$
+			\State $\tail \gets Dynamic()$
 		\end{algorithmic}\end{algorithm}
@@
 
-	I begin with the implementation for \textit{add} since it is the most common list operation [cite].
+	I begin with the implementation for \textit{Add} since it is the most common list operation\footnote{}.
 Its algorithm is very similar to that of a dynamic array: it resizes the list if it's full, then stores the item and increments the size.
@@
 	\begin{algorithm}\begin{algorithmic}[1]
-			\Procedure{\textit{add}}{$\ell, item$}
-				\If{$full?(\ell)$}
-					\State $resize(\ell)$
+			\Procedure{$Add_L$}{$item$}
+				\If{$\isfull$}
+					\State $Resize_L()$
 				\EndIf
 
-				\State $h(\ell)[hsize(\ell)] \gets item$
-				\State $size(\ell) \gets size(\ell) + 1$
-				\State $hsize(\ell) \gets hsize(\ell) + 1$
+				\State $\head[\headsize] \gets item$
+				\State $\size \gets \size + 1$
 			\EndProcedure
@@
 	\begin{algorithm}\begin{algorithmic}[1]
-			\Procedure{\textit{resize}}{$\ell$}
+			\Procedure{$Resize_L$}{}
 				\Require
-					\Statex $full?(\ell)$
-				\If{$empty?(\ell)$}
-					\State $h(\ell) \gets array(4)$
-					\State $cap(\ell) \gets 4$
+					\Statex $\isfull$
+				\If{$\isempty$}
+					\State $\head \gets Array(4)$
+					\State $\capacity \gets 4$
 					\State \Return
@@
 
-				\State $add(tail(\ell), head(\ell))$
-				\State $newcap \gets g(hcap(\ell))$
-				\State $h(\ell) \gets array(newcap)$
-				\State $hsize(\ell) \gets 0$
-				\State $cap(\ell) \gets cap(\ell) + newcap$
+				\State $Add\ dyn_{\tail}(\head)$
+				\State $new\ cap \gets G(\headcapacity)$
+				\State $\head \gets Array(new\ cap)$
+				\State $\headsize \gets 0$
+				\State $\capacity \gets \capacity + new\ cap$
 			\EndProcedure
@@
 	\begin{algorithm}\begin{algorithmic}[1]
-			\LineComment{\textit{g} is the \textit{growth function}.}
+			\LineComment{\textit{G} is the \textit{growth function}.}
 			\LineComment{It decides the capacity of the next buffer based on the current buffer's capacity.}
-			\Function{\textit{g}}{$cap$}
+			\Function{\textit{G}}{$cap$}
 			\Require
@@
 
+	In each "Time Analysis" section, I derive not just the time complexity of the operation, but a complete formula that approximates the actual (amortized) amount of time it takes.
+In order to do this in a clean fashion, I use the following notation:
+
+	\begin{description}
+		\item[$\timeof{F}$] The amortized amount of time it takes for function $F$ to run.
+		\item[$T_A$] The amortized amount of time it takes for the code at line to run.
+		\item[$T_{A,B}$] The amortized amount of time it takes for code between lines $A$ and $B$ to run, inclusive.
+		\item[$T(k)$] The amount of time it takes for $T$ to run, where $T$ is any time expression, when $\size = k$.
+		% TODO: T_m should go here?
+	\end{description}
+
+	Since the first three definitions represent \textit{amortized} time, which is the average amount of time it takes for an operation to run, I can expand them to
+
+	\begin{align*}
+	\timeof{F} &= \frac {\sum_{i = 0}^{n - 1} F(i)} n\\
+	T_A &= \frac {\sum_{i = 0}^{n - 1} T_A(i)} n\\
+	T_{A,B} &= \frac {\sum_{i = 0}^{n - 1} T_{A,B}(i)} n
+	\end{align*}
+
+	% TODO: Where n is an arbitrarily large integer? Since that's true, we may ignore 0 in the below sigmas.
+
+	These definitions will be used frequently when a piece of code takes longer to run for some sizes than others.
+
+	Now, I begin analyzing the amortized amount of time for \addfn. The expression we want to find is \timeof{\addfn}. In order to do this, I will need a few lemmas:
+
+	Lemma.
+Let \capacities be the set of all values assigned to \capacity as \size increases indefinitely.
+Let $\capacities(n)$ be the subset of \capacities less than $n$.
+I show that $capacities(n)$ is the set
+
+	\begin{align*}
+	\capacities(n) = \{0\} \cup \{2^i | 1 < i \leq lgc(n) \}
+	\end{align*}
+
+	where $lgc(n) = \lfloor \log_2{(n - 1)} \rfloor$, the base 2 \textit{logarithm of the greatest capacity} less than $n$.
+
+	% TODO: Proof
+
+	We define $\overline{\capacities(n)}$ as $\{0, 1, ... n - 1\} \char`\\ \capacities(n)$.
+
+	\begin{align*}
+	\timeof{\addfn} &= T_{2,6} = T_2 + T_3 + T_{4,6}\\
+	&= T_3 + C\\
+	&= \frac {\sum_{i = 0}^n T_3(i)} n + C\\
+	&= \frac {\sum_{i \in \capacities(n)} T_3(i) + \sum_{i \in \overline{\capacities(n)}} T_3(i)} n + C
+	\end{align*}
+
+	Since $|\capacities(n)| = lgc(n) - 1$ and $|\overline{\capacities(n)}| = n - |\capacities(n)| = n + 1 - lgc(n)$, this resolves to
+
+	\begin{align*}
+	\frac {(lgc(n) - 1)\timeof{\resizefn}} n + C
+	\end{align*}
+
+	Now we have to determine the complexity of \resizefn.
+
+	\begin{align*}
+	\timeof{\resizefn} &= T_{2, 10} = T{6,10}
+	\end{align*}
+
+	When $L$ is not full:
+
 	$$
-	T[add] = T_{2,6} = T_{2,3} + T_{4, 6}
+	T_{2,3} + T_{4,6} = \timeof{full?} + T_{4,6} = C
 	$$
 
-	When $\ell$ is not full:
+	When $L$ is full:
 
 	$$
-	T_{2,3} + T_{4,6} = T_{4,6} = C
-	$$
-
-	When $\ell$ is full:
-
-	$$
-	T_{2,3} + T_{4,6} = T_[full?] + T_[resize] + T_{4,6} = T[resize] + C
+	T_{2,3} + T_{4,6} = \timeof{full?} + T_[resize] + T_{4,6} = T[resize] + C
 	$$
@@
 
-	When $\ell$ is empty:
+	When $L$ is empty:
 
@@
 
-	When $\ell$ is non-empty:
+	When $L$ is non-empty:
 
@@
 	\begin{algorithm}\begin{algorithmic}[1]
-			\Function{\textit{item at index}}{$\ell, index$}
+			\Function{\textit{item at index}}{$L, index$}
 	 			\Require
-	 				\Statex $0 \leq index < size(\ell)$
+	 				\Statex $0 \leq index < \size$
 	 			\State $i \gets index$
-	 			\ForAll{$buf \in t(\ell)$}
-	 				\If{$i < len(buf)$}
+	 			\ForAll{$buf \in \tail$}
+	 				\If{$i < Len_{buf}$}
 	 					\State \Return $buf[i]$
 	 				\EndIf
-	 				\State $i \gets i - len(buf)$
+	 				\State $i \gets i - Len_{buf}$
 	 			\EndFor
 
-	 			\Return $h(\ell)[i]$
+	 			\Return $\head[i]$
  			\EndFunction

### 2017-10-13 Regeneron Paper.tex
Remove gibberish

@@
 		\item[resize] To increase a list's capacity once it is full.
+		\item[time proportion] The average ratio of the time spent on particular part(s) of a method, to the time spent on the method.
 		\item[threshold sizes] The set of sizes for which the list is full.
@@
 
-	In each "Time Analysis" section, I derive not just the time complexity of the operation, but a complete formula that approximates the actual (amortized) amount of time it takes.
-In order to do this in a clean fashion, I use the following notation:
-
-	\begin{description}
-		\item[$\timeof{F}$] The amortized amount of time it takes for function $F$ to run.
-		\item[$T_A$] The amortized amount of time it takes for the code at line to run.
-		\item[$T_{A,B}$] The amortized amount of time it takes for code between lines $A$ and $B$ to run, inclusive.
-		\item[$T(k)$] The amount of time it takes for $T$ to run, where $T$ is any time expression, when $\size = k$.
-		% TODO: T_m should go here?
-	\end{description}
-
-	Since the first three definitions represent \textit{amortized} time, which is the average amount of time it takes for an operation to run, I can expand them to
-
-	\begin{align*}
-	\timeof{F} &= \frac {\sum_{i = 0}^{n - 1} F(i)} n\\
-	T_A &= \frac {\sum_{i = 0}^{n - 1} T_A(i)} n\\
-	T_{A,B} &= \frac {\sum_{i = 0}^{n - 1} T_{A,B}(i)} n
-	\end{align*}
-
-	% TODO: Where n is an arbitrarily large integer? Since that's true, we may ignore 0 in the below sigmas.
-
-	These definitions will be used frequently when a piece of code takes longer to run for some sizes than others.
-
-	Now, I begin analyzing the amortized amount of time for \addfn. The expression we want to find is \timeof{\addfn}. In order to do this, I will need a few lemmas:
-
-	Lemma.
-Let \capacities be the set of all values assigned to \capacity as \size increases indefinitely.
-Let $\capacities(n)$ be the subset of \capacities less than $n$.
-I show that $capacities(n)$ is the set
-
-	\begin{align*}
-	\capacities(n) = \{0\} \cup \{2^i | 1 < i \leq lgc(n) \}
-	\end{align*}
-
-	where $lgc(n) = \lfloor \log_2{(n - 1)} \rfloor$, the base 2 \textit{logarithm of the greatest capacity} less than $n$.
-
-	% TODO: Proof
-
-	We define $\overline{\capacities(n)}$ as $\{0, 1, ... n - 1\} \char`\\ \capacities(n)$.
-
-	\begin{align*}
-	\timeof{\addfn} &= T_{2,6} = T_2 + T_3 + T_{4,6}\\
-	&= T_3 + C\\
-	&= \frac {\sum_{i = 0}^n T_3(i)} n + C\\
-	&= \frac {\sum_{i \in \capacities(n)} T_3(i) + \sum_{i \in \overline{\capacities(n)}} T_3(i)} n + C
-	\end{align*}
-
-	Since $|\capacities(n)| = lgc(n) - 1$ and $|\overline{\capacities(n)}| = n - |\capacities(n)| = n + 1 - lgc(n)$, this resolves to
-
-	\begin{align*}
-	\frac {(lgc(n) - 1)\timeof{\resizefn}} n + C
-	\end{align*}
-
-	Now we have to determine the complexity of \resizefn.
-
-	\begin{align*}
-	\timeof{\resizefn} &= T_{2, 10} = T{6,10}
-	\end{align*}
-
-	When $L$ is not full:
-
-	$$
-	T_{2,3} + T_{4,6} = \timeof{full?} + T_{4,6} = C
-	$$
-
-	When $L$ is full:
-
-	$$
-	T_{2,3} + T_{4,6} = \timeof{full?} + T_[resize] + T_{4,6} = T[resize] + C
-	$$
-
-	Now we must analyze $resize$.
-
-	When $L$ is empty:
-
-	$$
-	T[resize] = T_{2,5} = T[empty?] + T_alloc(4) + T_5 = T_alloc(4) + C
-	$$
-
-	When $L$ is non-empty:
-
-	$$
-	T[resize] = T[empty?] + 
-	$$
-
 	\subsubsection{Space Analysis}

### 2017-10-13 Regeneron Paper.tex
Fix thing
Fixes

@@
 
-	I assume the following functions are provided by the runtime environment, so that I may use them without defining them beforehand.\par
+	I assume the following functions are provided by the runtime environment, so that I may use them without defining them beforehand.
 
+	% TODO: Why is this appearing in the wrong place?
 	\begin{algorithm}\begin{algorithmic}
@@
 		\end{algorithmic}\end{algorithm}
-
-	\subsection{Mathematical Notation}
-
-	\begin{description}
-		\item[$T_m(n)$] Time it takes to allocate memory for an array of size $n$
-	\end{description}
 
@@
 
-	I begin with the implementation for \textit{Add} since it is the most common list operation\footnote{}.
+	I begin with the implementation for \addfn since it is the most common list operation\footnote{}.
 Its algorithm is very similar to that of a dynamic array: it resizes the list if it's full, then stores the item and increments the size.
@@
 			\Statex $cap \geq 4 \land \log_2{cap} \in \mathbb{N}$
-			\State \Return $\begin{cases}
-			4 & cap = 4\\
-			2 * cap & cap \neq 4
-			\end{cases}$
+			\If{$cap = 4$}
+				\State \Return $4$
+			\EndIf
+			\State \Return $2 \cdot cap$
 			\EndFunction
@@
 
+	\begin{align*}
+	W(n) &= n + R(n) - 1\right)\\
+	R(n) &= \begin{cases}
+	0 & n = 0\\
+	1 & 1 \leq n \leq 4\\
+	\lfloor \log_2{(n - 1)} \rfloor & n > 4
+	\end{cases}\\
+	W(n) &= O(n)
+	\end{align*}
+
+	\begin{align*}
+	T_n &= P_W \left(T_W W(n) \right)
+	\end{align*}
+
 	\subsubsection{Space Analysis}
+
+	\begin{align*}
+	S(n) = O(2^{\lceil \log_2 n \rceil})
+	% For dynamic arrays, it's this O(2^{\lceil \log_2 n \rceil}).
+	\end{align*}
 

### 2017-10-13 Draft2.tex
Progress significantly on Section 5, Draft 2

\documentclass{article}
\usepackage{amsmath}

\newcommand{\tcomplex}{\textbf{Time complexity}}
\newcommand{\scomplex}{\textbf{Space complexity}}

\newcommand{\timefn}{T}
\newcommand{\spacefn}{S}
\newcommand{\nwritesfn}{W}

\newcommand{\bigo}{O}
\newcommand{\biggo}{P}
\newcommand{\varnitems}{n}

\setlength{\parskip}{1em}

\begin{document}
	\begin{abstract}
	\end{abstract}

	\section{Introduction}

	\section{Definitions}

	\section{Predefined Functions}

	\section{Fields and Properties}

	In this section, I define \textbf{fields} and \textbf{properties} on dynamic arrays and resize lists. These will be used later to implement operations on them in pseudocode.

	\section{Common Resize List Operations}

	In this section, I implement common operations for dynamic arrays, then resize lists, in pseudocode. Then, I analyze and compare the time complexities of the implementations. If the operation allocates memory, I also compare their space complexities.

	\subsection{Adding}

	Adding is the most common operation done on a dynamic array\footnote{}. Resize lists improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.

	% <dynamic array implementation>

	\tcomplex

	\begin{align*}
	\nwritesfn(\varnitems) = \biggo(2\varnitems)
	\end{align*}

	\scomplex

	\begin{align*}
	\spacefn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil + 1}) = \bigo(\varnitems)
	\end{align*}

	% <resize list implementation>

	\tcomplex

	\begin{align*}
	\nwritesfn(\varnitems) = \biggo(\varnitems)
	\end{align*}

	\scomplex

	\begin{align*}
	\spacefn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
	\end{align*}

	\subsection{Indexing}

	\subsection{Iterating}

	\subsection{Copying to an array}

	\section{Other Resize List Operations}

	\subsection{Inserting}

	\subsection{Deleting}

	\subsection{Searching}

	\subsection{In-place sorting}

	\section{Implementations}

	\section{Benchmarks}

	\section{Closing Remarks}

\end{document}

### 2017-10-13 Draft2.tex
Finish the skeleton of "Adding"
Add more skeletons
Add primes to the resize list fns
More variables
Add description of big-P notation

@@
 \newcommand{\scomplex}{\textbf{Space complexity}}
+\newcommand{\tcomplexcmp}{\textbf{Time complexity comparison}}
+\newcommand{\scomplexcmp}{\textbf{Space complexity comparison}}
 
@@
 \newcommand{\nwritesfn}{W}
+
+\newcommand{\timenewfn}{\timefn'}
+\newcommand{\spacenewfn}{\spacefn'}
+\newcommand{\nwritesnewfn}{\nwritesfn'}
+
+\newcommand{\timeratio}{r_\timefn}
+\newcommand{\spaceratio}{r_\spacefn}
 
@@
 
+	The following mathematical definitions will be used while analyzing time and space complexity:
+
+	\begin{description}
+		\item[$\biggo(f(n))$] This is an alternative to big-O notation for time complexity; I will call it \textbf{big-P notation}.
+			\subitem The main purpose of big-P notation is to preserve the constant coefficient of the fastest-growing term in $f(n)$, while still maintaining many properties of big-O.
+For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
+This makes it possible to compare time complexities whose ratio converges to a constant as $n$ becomes larger.
+			\subitem More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
+	\end{description}
+
 	\subsection{Adding}
@@
 	\begin{align*}
-	\nwritesfn(\varnitems) = \biggo(\varnitems)
+	\nwritesnewfn(\varnitems) = \biggo(\varnitems)
 	\end{align*}
@@
 	\begin{align*}
-	\spacefn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
+	\spacenewfn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
+	\end{align*}
+
+	\tcomplexcmp
+
+	\begin{align*}
+	\end{align*}
+
+	\scomplexcmp
+
+	\begin{align*}
+	\spaceratio = \frac {\biggo(2^{\lceil \log_2 \varnitems \rceil})} {\biggo(2^{\lceil \log_2 \varnitems \rceil + 1})} = \frac{1}{2}
 	\end{align*}
@@
 
+	% <dynamic array implementation>
+
+	\tcomplex
+
+	$\timefn(\varnitems) = \bigo(1)$
+
+	% <resize list implementation>
+
+	\tcomplex
+
+	$\timenewfn(\varnitems) = \bigo(1)$
+
+	\tcomplexcmp
+
 	\subsection{Iterating}
+
+	% <dynamic array implementation>
+
+	\tcomplex
+
+	$\timefn(\varnitems) = \bigo(\varnitems)$
+
+	% <resize list implementation>
+
+	\tcomplex
+
+	$\timenewfn(\varnitems) = \bigo(\varnitems)$
+
+	\tcomplexcmp
 

### 2017-10-14 Draft2.tex
Rename to funnel array

@@
 
-	In this section, I define \textbf{fields} and \textbf{properties} on dynamic arrays and resize lists. These will be used later to implement operations on them in pseudocode.
+	In this section, I define \textbf{fields} and \textbf{properties} on dynamic and funnel arrays. These will be used later to implement operations on them in pseudocode.
 
-	\section{Common Resize List Operations}
+	\section{Common Funnel Array Operations}
 
-	In this section, I implement common operations for dynamic arrays, then resize lists, in pseudocode.
+	In this section, I implement common operations for dynamic arrays, then funnel arrays, in pseudocode.
 Then, I analyze and compare the time complexities of the implementations.
@@
 
-	Adding is the most common operation done on a dynamic array\footnote{}. Resize lists improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
+	Adding is the most common operation done on a dynamic array\footnote{}. Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
 
@@
 
-	% <resize list implementation>
+	% <funnel array implementation>
 
@@
 
-	\section{Other Resize List Operations}
+	\section{Other Funnel Array Operations}
 

### 2017-10-15 Draft2.tex
Lots of stuff

@@
 
+\newcommand{\descriptn}{\textbf{Description}}
+\newcommand{\dynarrayimpl}{\textbf{Dynamic array implementation}}
+\newcommand{\funarrayimpl}{\textbf{Funnel array implementation}}
+\newcommand{\commimpltext}{Common implementation}
+\newcommand{\commimpl}{\textbf{\commimpltext}}
 \newcommand{\tcomplex}{\textbf{Time complexity}}
@@
 \newcommand{\varnitems}{n}
+\newcommand{\indexertime}{I}
+
+\newcommand{\listname}{L}
 
@@
 
+	\begin{description}
+		\item[field] A variable associated with an object that may be read from or written to.\\
+			It is assumed that fields can be read from and written to in constant time.
+		\item[get indexer] A method that gets an item at a specified index in a list.
+		\item[indexer] Refers to a get indexer or set indexer.
+		\item[property] A function of an object that returns a value, runs in constant time, and does not mutate any state (i.e. by assigning new values to fields).
+		\item[set indexer] A method that sets an item at a specified index in a list.
+		\item[trivial member] A field or property of an object.
+	\end{description}
+
 	\section{Predefined Functions}
 
-	\section{Fields and Properties}
+	\section{Trivial Members}
 
@@
 
-	In this section, I implement common operations for dynamic arrays, then funnel arrays, in pseudocode.
+	In this section, I implement common operations for dynamic and funnel arrays in pseudocode.
 Then, I analyze and compare the time complexities of the implementations.
@@
 
+	\descriptn
+
 	Adding is the most common operation done on a dynamic array\footnote{}. Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
 
-	% <dynamic array implementation>
+	\dynarrayimpl
 
@@
 
-	% <funnel array implementation>
+	\funarrayimpl
 
@@
 
-	% <dynamic array implementation>
+	\descriptn
+
+	Indexing is another very common operation on a list. An \textbf{indexer} gets or sets an item at a specified index in a list.
+
+	\dynarrayimpl
 
@@
 
+	For the rest of this paper, I will not assume the indexer's time complexity is $\bigo(1)$ nor $\bigo(\log \varnitems)$.
+Instead, I will denote it by the function $\indexertime(\varnitems)$, where $\indexertime(\varnitems)$ is either $1$ or $\log \varnitems$.
+
+	Since many list operations I detail can be implemented using the indexer in a loop, I make the following useful claim:
+
+	Let $\listname$ be a list.
+Suppose $LC$ is a loop construct that runs $N$ times, where $N$ is a fixed number.
+If the body of the loop contains only the indexer of $\listname$ and statements that run in constant time, and the loop does not contain nested loops, then the time complexity of the loop is $\bigo(N \cdot \indexertime(\varnitems))$.
+
+	To see this, note that the time complexity of the body of the loop is $\bigo(\indexertime(\varnitems)) + \bigo(1) = \bigo(\indexertime(\varnitems))$.
+Since the body is run $N$ times, the total time complexity is $N \cdot \bigo(\indexertime(\varnitems)) = \bigo(N \cdot \indexertime(\varnitems))$.
+
 	\tcomplexcmp
@@
 
-	% <dynamic array implementation>
+	\descriptn
+
+	\textbf{Iteration} of a list is the process of performing some action on each of its elements.
+The standard implementation of iteration for dynamic arrays is also applicable to funnel arrays.
+When this happens in this and subsequent sections, the second heading will be titled "\commimpltext".
+
+	\commimpl
 
@@
 
-	$\timefn(\varnitems) = \bigo(\varnitems)$
+	By , the time complexity of this operation is $\bigo(\varnitems)$ for dynamic arrays.
 
-	% <funnel array implementation>
+	By , the time complexity of this operation is $\bigo(\varnitems \cdot \indexertime(\varnitems))$ for funnel arrays.
+However, I demonstrate an alternative implementation for funnel arrays below that is $\bigo(\varnitems)$ independent of $\indexertime(\varnitems)$:
+
+	\funarrayimpl
 

### 2017-10-15 Draft2.tex
Revert some things from previous commit

--- 2017-10-14 Draft2.tex
@@
 
+\newcommand{\descriptn}{\textbf{Description}}
+\newcommand{\dynarrayimpl}{\textbf{Dynamic array implementation}}
+\newcommand{\funarrayimpl}{\textbf{Funnel array implementation}}
 \newcommand{\tcomplex}{\textbf{Time complexity}}
@@
 
-	\section{Predefined Functions}
+	\begin{description}
+		\item[field] A variable associated with an object that may be read from or written to.\\
+			It is assumed that fields can be read from and written to in constant time.
+		\item[get indexer] A method that gets an item at a specified index in a list.
+		\item[indexer] Refers to a get indexer or set indexer.
+		\item[property] A function of an object that returns a value, runs in constant time, and does not mutate any state (i.e. by assigning new values to fields).
+		\item[set indexer] A method that sets an item at a specified index in a list.
+		\item[trivial member] A field or property of an object.
+	\end{description}
 
-	\section{Fields and Properties}
+	\section{Runtime-Defined Functions}
+
+	\section{Trivial Members of Dynamic and Funnel Arrays}
 
@@
 
-	% <dynamic array implementation>
+	\descriptn
+
+	\textbf{Iteration} of a list is the process of performing some action on each of its elements.
+
+	\dynarrayimpl
 
@@
 
-	$\timefn(\varnitems) = \bigo(\varnitems)$
+	Ignoring the arbitrary code run after getting each element, the time complexity of this method is $\bigo(\varnitems)$.
 
-	% <funnel array implementation>
+	\funarrayimpl
 

### 2017-10-15 Draft2.tex
Add descriptions

@@
 	\begin{description}
+		\item[decrement, increment] Decreasing or increasing (respectively) the value of an integer variable by one.
 		\item[field] A variable associated with an object that may be read from or written to.\\
 			It is assumed that fields can be read from and written to in constant time.
-		\item[get indexer] A method that gets an item at a specified index in a list.
+		\item[get indexer, set indexer] A method that gets or sets (respectively) an item at a specified index in a list.
 		\item[indexer] Refers to a get indexer or set indexer.
 		\item[property] A function of an object that returns a value, runs in constant time, and does not mutate any state (i.e. by assigning new values to fields).
-		\item[set indexer] A method that sets an item at a specified index in a list.
 		\item[trivial member] A field or property of an object.
@@
 
+	\descriptn
+
+	Users often want to take list structures, such as dynamic arrays, and convert them into plain arrays.
+There are multiple reasons why someone would want to do this after they are done adding to the list:
+
+	\begin{itemize}
+		\item Plain arrays hold on to exactly the amount of memory needed to hold their elements. However, dynamic and funnel arrays allocate more space than necessary to optimize adding new items.
+		\item The user wants to call a function in third-party code that takes a plain array as an argument.
+		\item
+		\item Plain arrays are contiguous, while funnel arrays are fragmented and have worse locality.
+		\item The indexer of funnel arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
+	\end{itemize}
+
+	\dynarrayimpl
+
+	\tcomplex
+
+	\funarrayimpl
+
+	\tcomplex
+
 	\section{Other Funnel Array Operations}
@@
 
+	\descriptn
+
+	\textbf{Inserting} an element places it at a specified index within the list, and increments the list's count.
+If the index equals the size of the list, the effect is the same as adding the element.
+Otherwise, the elements at indices greater than or equal to the specified index are moved to the next index, then the element is placed at the specified index.
+
 	\subsection{Deleting}
+
+	\descriptn
+
+	\textbf{Deleting} the element at a specified index moves the elements at indices greater than the specified index to the previous index. The count of the list is decremented.
 
@@
 
+	\descriptn
+
+	\textbf{Searching} for an element returns the first or last index within the list where the item can be found. If the user knows the items of the lists are sorted, \textbf{binary search} can be used.
+
 	\subsection{In-place sorting}
+
+	\descriptn
+
+	Given a strict ordering $<$, we say a list $\listname$ is \textbf{sorted} by $<$ iff $\left(a, b \in \listname \land a < b\right) \leftrightarrow I_M(a) < I_m(b)$.
+$I_M(a)$ is the last (maximum) index of $a$ in $L$, and $I_m(b)$ is the first (minimum) index of $b$ in $L$.
+Note that the use of $<$ on the right-hand side compares integers and not elements of $L$, so this is not a recursive definition.
 

### 2017-10-15 Draft2.tex
:tada:

@@
 
+\newcommand{\initcapacity}{C_f}
+\newcommand{\growthfactor}{G}
+\newcommand{\capacityfn}{C}
+
 \setlength{\parskip}{1em}
@@
 
-	\section{Definitions}
+	\section{Fields and Properties}
 
-	\begin{description}
-		\item[decrement, increment] Decreasing or increasing (respectively) the value of an integer variable by one.
-		\item[field] A variable associated with an object that may be read from or written to.\\
-			It is assumed that fields can be read from and written to in constant time.
-		\item[get indexer, set indexer] A method that gets or sets (respectively) an item at a specified index in a list.
-		\item[indexer] Refers to a get indexer or set indexer.
-		\item[property] A function of an object that returns a value, runs in constant time, and does not mutate any state (i.e. by assigning new values to fields).
-		\item[trivial member] A field or property of an object.
-	\end{description}
+	I define some \textbf{fields} and \textbf{properties} (constant time methods that do not change state) for both types of arrays, so I may use them later to implement non-trivial methods.
 
-	\section{Runtime-Defined Functions}
+	\section{Common Operations}
 
-	\section{Trivial Members of Dynamic and Funnel Arrays}
-
-	In this section, I define \textbf{fields} and \textbf{properties} on dynamic and funnel arrays. These will be used later to implement operations on them in pseudocode.
-
-	\section{Common Funnel Array Operations}
-
-	In this section, I implement common operations for dynamic and funnel arrays in pseudocode.
-Then, I analyze and compare the time complexities of the implementations.
-If the operation allocates memory, I also compare their space complexities.
+	In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
 
@@
 	\begin{description}
-		\item[$\biggo(f(n))$] This is an alternative to big-O notation for time complexity; I will call it \textbf{big-P notation}.
-			\subitem The main purpose of big-P notation is to preserve the constant coefficient of the fastest-growing term in $f(n)$, while still maintaining many properties of big-O.
+		\item[$\biggo(f(n))$] This is an alternative to big-O notation that I will name "big-P notation".
+It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
 For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
-This makes it possible to compare time complexities whose ratio converges to a constant as $n$ becomes larger.
-			\subitem More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
+This makes it possible to compare two time complexities, if their ratio tends to a constant for large $n$.\\
+		More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
 	\end{description}
@@
 
-	Adding is the most common operation done on a dynamic array\footnote{}. Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
+	Adding is the most common operation done on dynamic arrays\footnote{}.
+Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
+We begin with the implementation for dynamic arrays.
 
-	\dynarrayimpl
+	I will first implement and analyze adding for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
 
-	\tcomplex
+	\begin{description}
+		\item[initial capacity] The capacity of a dynamic a array when one item is added to it. I denote this $\initcapacity$.\\
+		(The capacity of any dynamic array with size zero should be zero.)
+		\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\listname$ is resized. I denote this with $\growthfactor$.
+	\end{description}
+
+	% impl.
+
+	Before I analyze the time complexity of [add], I consider a different method for measuring its cost.
+Suppose I start with an empty list and $\varnitems$ elements are added.
+How many times is an element stored in an array?
+I will term the answer to this question the \textbf{write cost} of $\varnitems$ adds, and denote it $\nwritesfn(n)$.
+
+	In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ adds.
+However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$ I need to analyze when [resize] is called.
+Consider the following lemma:
+
+	[lemma]
+	Let $\listname$ by a dynamic array.
+As $\varnitems$ are added, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
+
+	[proof]
+	The capacity starts out at zero and becomes $\initcapacity$ once one element is added.
+From then on, it can only grow by a factor of $\growthfactor$ via [resize], so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
+By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$.
+Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$.
+Using this property, we now derive $k$.
+
+	\begin{align*}
+	\growthfactor^k\initcapacity &\geq \varnitems\\
+	\growthfactor^k &\geq \frac{\varnitems}{\initcapacity}\\
+	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity\\
+	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity > k - 1\\
+	k &= \big\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \big\rceil
+	\end{align*}
+
+	Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.
+
+	Now, consider that to grow by $\growthfactor$ we have to call [resize].
+So $\growthfactor^k\initcapacity$ being present in $S_C$ means we once called [resize] at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
+Then we must have called [resize] at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
+
+	Each time [resize] is called, we copy $i$ items where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ adds is
+
+	\begin{align*}
+	0 + \initcapacity + \growthfactor\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity &= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+	\end{align*}
+
+	Finally, adding the writes made for every item in [add], I finally find an explicit formula for $\nwritesfn(\varnitems)$.
+
+	$$
+	\nwritesfn(\varnitems) = n + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+	$$
 
@@
 
-	Indexing is another very common operation on a list. An \textbf{indexer} gets or sets an item at a specified index in a list.
+	Indexing is another very common operation on a list. I will call methods that get or set an item at a specified index \textbf{get indexer} and \textit{set indexers}, respectively.
 
@@
 
-	\section{Other Funnel Array Operations}
+	\section{Other Operations}
 

### 2017-10-15 Draft2.tex
[Nightmarish] Finish P-analysis of adding to dynamic arrays

@@
 	$$
-	\nwritesfn(\varnitems) = n + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+	\nwritesfn(\varnitems) = \varnitems + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
 	$$
 
+	To make this expression easier to work with, I will write it in big-P notation to approximate it for large $\varnitems$.
+First I note that $\log_{\growthfactor} k \leq \lceil \log_{\growthfactor} k \rceil < \left( \log_{\growthfactor} k \right) + 1$ for any $k > 0$, so $k \leq \growthfactor^{\lceil \log_{\growthfactor} k \rceil} < \growthfactor{k}$ and $\exists r \in {[1, \growthfactor)} : rk = \growthfactor^{\lceil \log_{\growthfactor} k \rceil}$.
+Then
+
 	\begin{align*}
-	\nwritesfn(\varnitems) = \biggo(2\varnitems)
+	\nwritesfn(\varnitems) &= \varnitems + \left( \frac{\growthfactor^{\big\lceil \log_{\growthfactor} \left( \frac {\varnitems} {\initcapacity} \right) \big\rceil} - 1}{\growthfactor - 1} \right) \initcapacity\\
+	\varnitems + \left( \frac{\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
+	\varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right)\\
+	\biggo\left( \varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right) \right)\\
+	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo(\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \left( \frac{2\growthfactor - 1}{\growthfactor - 1} \right) \varnitems \right)
 	\end{align*}

### 2017-10-15 Draft2.tex
Madness

@@
 
+\newcommand{\nwritesresizefn}{W_R}
+
 \newcommand{\timeratio}{r_\timefn}
@@
 \newcommand{\capacityfn}{C}
+
+\newcommand{\initcapacitynew}{\initcapacity'}
+\newcommand{\growthfactornew}{\growthfactor'}
 
@@
 
+	\tcomplex
+
 	Before I analyze the time complexity of [add], I consider a different method for measuring its cost.
@@
 
+	[make lemma]
 	Now, consider that to grow by $\growthfactor$ we have to call [resize].
@@
 	\tcomplex
+
+	I again start off by finding the write cost when $\varnitems$ are added.
+I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so we can compare it to $\nwritesfn(\varnitems)$ later.
+I also use $\growthfactornew$ and $\initcapacitynew$ instead of $\growthfactor$ and $\initcapacity$ for the growth factor and initial capacity, respectively.
+
+	[That lemma] still holds, since all of the assumptions made there are also true for funnel arrays.
+In particular, although funnel arrays resize slightly differently than dynamic arrays, the following claim is still true:
+
+	[lemma]
+	The capacity of a funnel array grows by a constant factor $\growthfactornew$ after the first time it is called.
+
+	[proof]
+	I prove that the algorithm ensures this using induction.
+
+	For the base case, consider the second time [resize] is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
+Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be added, and that is what the algorithm does.
+
+	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time.
+From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\growthfactornew^i\initcapacitynew$ and the head capacity is $(\growthfactornew^i - \growthfactornew^{i - 1})\initcapacitynew$.
+The next (total) capacity should be $\growthfactornew^{i + 1}\initcapacitynew$, and the next head capacity should be $(\growthfactornew^{i + 1} - \growthfactornew^i)\initcapacitynew$, which is $\growthfactornew$ times the current head capacity.
+The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
+
+	Now I wish to find the number of writes [resize] performs.
+From [make lemma], I know that [resize] is called at the sizes $$S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew$$
+
+	Unlike dynamic arrays, however, the number of writes performed does not equal $i$ if the current size is $i$.
+It is a function of $i$, however, so I will denote it $\nwritesresizefn(i)$.
+A formula for $\nwritesnewfn(\varnitems)$ can be expressed in terms of $\nwritesresizefn(i)$:
+
+	$$
+	\nwritesnewfn(\varnitems) = n + \sum_{i \in S_R} \nwritesresizefn(i)
+	$$
+
+	so the goal is now to find a formula for $\nwritesresizefn(i)$.
+First note that all of the writing in [resize] comes from the call to [add] on a dynamic array.
+Let the initial capacity of the dynamic array be $\initcapacity$ and its growth factor be $\growthfactor$.
+We showed before that
 

### 2017-10-15 Draft2.tex
Apex of madness

@@
 
+	[ref1]
 	$$
@@
 First note that all of the writing in [resize] comes from the call to [add] on a dynamic array.
-Let the initial capacity of the dynamic array be $\initcapacity$ and its growth factor be $\growthfactor$.
-We showed before that
+Let the initial capacity of the dynamic array be $\initcapacity$, its growth factor be $\growthfactor$, and its write cost function be $\nwritesfn(k)$.
+In [ref1] we derived a formula for $\nwritesfn(k)$,
 

### 2017-10-15 Draft2.tex
Not the apex

--- 2017-10-15 Draft2.tex
@@
 
-	Now I wish to find the number of writes [resize] performs.
-From [make lemma], I know that [resize] is called at the sizes $$S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew$$
+	Now I take a look at [resize].
+Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$.
+No items are being copied; the only source of writes is adding a buffer to the tail.
+The goal is to find the number of writes that causes.
 
-	Unlike dynamic arrays, however, the number of writes performed does not equal $i$ if the current size is $i$.
-It is a function of $i$, however, so I will denote it $\nwritesresizefn(i)$.
-A formula for $\nwritesnewfn(\varnitems)$ can be expressed in terms of $\nwritesresizefn(i)$:
+	Let $\nwritesresizefn(n)$ denote the total number of writes made by [resize]. From [make lemma], I know that [resize] is called at the sizes
 
 	$$
-	\nwritesnewfn(\varnitems) = n + \sum_{i \in S_R} \nwritesresizefn(i)
+	S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew
 	$$
 
-	so the goal is now to find a formula for $\nwritesresizefn(i)$.
-First note that all of the writing in [resize] comes from the call to [add] on a dynamic array.
-Let the initial capacity of the dynamic array be $\initcapacity$ and its growth factor be $\growthfactor$.
-We showed before that
+	Let $k$ be the number of times the tail is added to.
+Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
+Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+Then the formula for $\nwritesresizefn(n)$ is
+
+	$$
+	\nwritesresizefn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+	$$
+
+	where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the funnel array). I finally conclude that
+
+	$$
+	\nwritesnewfn(n) = n + k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+	$$
+
+	Now I wish to find the number of writes [resize] performs.
 

### 2017-10-15 Draft2.tex
Big-P complexity of adding for funnel array impl

@@
 Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
 Then the formula for $\nwritesresizefn(n)$ is
@@
 
-	Now I wish to find the number of writes [resize] performs.
+	I now approximate this expression with big-P notation. First, I establish an approximation for $k$ using big-O:
 
 	\begin{align*}
-	\nwritesnewfn(\varnitems) = \biggo(\varnitems)
+	k &= \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil\\
+	\bigo(k) &= \bigo(\log \varnitems)
+	\end{align*}
+
+	Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\nwritesnewfn(\varnitems)$, leaving just $\biggo(\varnitems)$:
+
+	\begin{align*}
+	\biggo(\nwritesnewfn(\varnitems)) &= \biggo(\varnitems + \nwritesfn(k))\\
+	&= \biggo(\varnitems) + \biggo(\nwritesfn(k))\\
+	&= \biggo(\varnitems) + \bigo(\log \varnitems)\\
+	&= \biggo(\varnitems)
 	\end{align*}
@@
 	\tcomplexcmp
-
-	\begin{align*}
-	\end{align*}
 

### 2017-10-16 Draft2.tex
More madness

@@
 Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
-We begin with the implementation for dynamic arrays.
+I begin with the implementation of adding for dynamic arrays.
 
@@
 Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$.
-Using this property, we now derive $k$.
+Using this property, I now derive $k$.
 
@@
 	[make lemma]
-	Now, consider that to grow by $\growthfactor$ we have to call [resize].
-So $\growthfactor^k\initcapacity$ being present in $S_C$ means we once called [resize] at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
-Then we must have called [resize] at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
+	Now, consider that to grow by $\growthfactor$ [resize] must be called.
+So $\growthfactor^k\initcapacity$ being present in $S_C$ means [resize] was called at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
+Then [resize] was called at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
 
-	Each time [resize] is called, we copy $i$ items where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ adds is
+	Each time [resize] is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ adds is
 
@@
 
+	[ref2]
 	To make this expression easier to work with, I will write it in big-P notation to approximate it for large $\varnitems$.
-First I note that $\log_{\growthfactor} k \leq \lceil \log_{\growthfactor} k \rceil < \left( \log_{\growthfactor} k \right) + 1$ for any $k > 0$, so $k \leq \growthfactor^{\lceil \log_{\growthfactor} k \rceil} < \growthfactor{k}$ and $\exists r \in {[1, \growthfactor)} : rk = \growthfactor^{\lceil \log_{\growthfactor} k \rceil}$.
+First I note that $\log_{\growthfactor} k \leq \lceil \log_{\growthfactor} k \rceil < \left( \log_{\growthfactor} k \right) + 1$ for any $k > 0$, so $k \leq \growthfactor^{\lceil \log_{\growthfactor} k \rceil} < \growthfactor{k}$.
 Then
@@
 	\biggo\left( \varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right) \right)\\
-	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo(\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \left( \frac{2\growthfactor - 1}{\growthfactor - 1} \right) \varnitems \right)
+	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \left( \frac{2\growthfactor - 1}{\growthfactor - 1} \right) \varnitems \right)
 	\end{align*}
@@
 
+	I wish to find the space allocated while adding $\varnitems$ items to a dynamic array.
+I denote this quantity $\spacefn(\varnitems)$, and define it as the total length of all arrays allocated during $\varnitems$ [add] calls.
+I now derive a formula for $\spacefn(\varnitems)$.
+
+	From [lemma] I know the exact capacities $\listname$ takes on as $\varnitems$ items are added.
+Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.
+Then the total length of arrays allocated is
+
 	\begin{align*}
-	\spacefn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil + 1}) = \bigo(\varnitems)
+	\spacefn(\varnitems) &= \sum_{i \in S_C} i\\
+	&= 0 + \initcapacity + \growthfactor\initcapacity + \growthfactor^2\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity\\
+	&= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil + 1} - 1}{\growthfactor - 1} \right) \initcapacity
+	\end{align*}
+
+	Using the identity in [ref2] again, I bound its big-P complexity:
+
+	\begin{align*}
+	\left( \frac{\growthfactor \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \spacefn(\varnitems) &< \left( \frac{\growthfactor^2 \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
+	\biggo\left( \left( \frac{\growthfactor \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \right) \leq \biggo\left( \spacefn(\varnitems) \right) &< \biggo\left( \left( \frac{\growthfactor^2 \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \right)\\
+	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo\left( \spacefn(\varnitems) \right) &< \biggo\left( \left( \frac{\growthfactor^2}{\growthfactor - 1} \right) \varnitems \right)
 	\end{align*}
@@
 	I again start off by finding the write cost when $\varnitems$ are added.
-I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so we can compare it to $\nwritesfn(\varnitems)$ later.
+I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so I can compare it to $\nwritesfn(\varnitems)$ later.
 I also use $\growthfactornew$ and $\initcapacitynew$ instead of $\growthfactor$ and $\initcapacity$ for the growth factor and initial capacity, respectively.
@@
 
-	[lemma]
+	[other lemma]
 	The capacity of a funnel array grows by a constant factor $\growthfactornew$ after the first time it is called.
@@
 Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+Since [resize] is called $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
 Then the formula for $\nwritesresizefn(n)$ is
@@
 
+	% Should this be C(n) instead of C?
+	The space function for $\varnitems$ [add] calls on a funnel array is denoted $\spacenewfn(\varnitems)$.
+Since funnel arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.
+$\spacenewfn(\varnitems)$ is usually greater than $C$, however; this is because funnel arrays not only allocate item buffers, but stores references to them in the tail.
+Thus the space the tail allocates must also be determined.
+
+	I determined in [...] that if $\varnitems$ are added then the tail is added to $k$ times, where $k = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+Since the tail is a dynamic array, it allocates $\spacefn(k)$ space, where $\spacefn$ is the space function of the tail.
+Through a similar method to [...] it can be shown $\bigo(\spacefn(k)) = \bigo(k) = \bigo(\log \varnitems)$.
+Then % TODO: P-analysis should come after the explicit formula.
+
 	\begin{align*}
@@
 
-	Indexing is another very common operation on a list. I will call methods that get or set an item at a specified index \textbf{get indexer} and \textit{set indexers}, respectively.
+	Indexing is another very common operation on a list. I will call methods that get or set an item at a specified index \textbf{get} and \textbf{set indexers}, respectively.
 
@@
 
-	Given a strict ordering $<$, we say a list $\listname$ is \textbf{sorted} by $<$ iff $\left(a, b \in \listname \land a < b\right) \leftrightarrow I_M(a) < I_m(b)$.
+	Given a strict ordering $<$, I say a list $\listname$ is \textbf{sorted} by $<$ iff $\left(a, b \in \listname \land a < b\right) \leftrightarrow I_M(a) < I_m(b)$.
 $I_M(a)$ is the last (maximum) index of $a$ in $L$, and $I_m(b)$ is the first (minimum) index of $b$ in $L$.

### 2017-10-16 Draft2/Appending.Dynamic.tex
Modularize things

--- 2017-10-16 Draft2.tex
@@
-\documentclass{article}
-\usepackage{amsmath}
+\dynarrayimpl
 
-\newcommand{\descriptn}{\textbf{Description}}
-\newcommand{\dynarrayimpl}{\textbf{Dynamic array implementation}}
-\newcommand{\funarrayimpl}{\textbf{Funnel array implementation}}
-\newcommand{\tcomplex}{\textbf{Time complexity}}
-\newcommand{\scomplex}{\textbf{Space complexity}}
-\newcommand{\tcomplexcmp}{\textbf{Time complexity comparison}}
-\newcommand{\scomplexcmp}{\textbf{Space complexity comparison}}
-
-\newcommand{\timefn}{T}
-\newcommand{\spacefn}{S}
-\newcommand{\nwritesfn}{W}
-
-\newcommand{\timenewfn}{\timefn'}
-\newcommand{\spacenewfn}{\spacefn'}
-\newcommand{\nwritesnewfn}{\nwritesfn'}
-
-\newcommand{\nwritesresizefn}{W_R}
-
-\newcommand{\timeratio}{r_\timefn}
-\newcommand{\spaceratio}{r_\spacefn}
-
-\newcommand{\bigo}{O}
-\newcommand{\biggo}{P}
-\newcommand{\varnitems}{n}
-\newcommand{\indexertime}{I}
-
-\newcommand{\listname}{L}
-
-\newcommand{\initcapacity}{C_f}
-\newcommand{\growthfactor}{G}
-\newcommand{\capacityfn}{C}
-
-\newcommand{\initcapacitynew}{\initcapacity'}
-\newcommand{\growthfactornew}{\growthfactor'}
-
-\setlength{\parskip}{1em}
-
-\begin{document}
-	\begin{abstract}
-	\end{abstract}
-
-	\section{Introduction}
-
-	\section{Fields and Properties}
-
-	I define some \textbf{fields} and \textbf{properties} (constant time methods that do not change state) for both types of arrays, so I may use them later to implement non-trivial methods.
-
-	\section{Common Operations}
-
-	In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
-
-	The following mathematical definitions will be used while analyzing time and space complexity:
-
-	\begin{description}
-		\item[$\biggo(f(n))$] This is an alternative to big-O notation that I will name "big-P notation".
-It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
-For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
-This makes it possible to compare two time complexities, if their ratio tends to a constant for large $n$.\\
-		More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
-	\end{description}
-
-	\subsection{Adding}
-
-	\descriptn
-
-	Adding is the most common operation done on dynamic arrays\footnote{}.
-Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
-I begin with the implementation of adding for dynamic arrays.
-
-	I will first implement and analyze adding for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
+I will first implement adding for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
 
@@
 \end{align*}
-
-	\funarrayimpl
-
-	\tcomplex
-
-	I again start off by finding the write cost when $\varnitems$ are added.
-I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so I can compare it to $\nwritesfn(\varnitems)$ later.
-I also use $\growthfactornew$ and $\initcapacitynew$ instead of $\growthfactor$ and $\initcapacity$ for the growth factor and initial capacity, respectively.
-
-	[That lemma] still holds, since all of the assumptions made there are also true for funnel arrays.
-In particular, although funnel arrays resize slightly differently than dynamic arrays, the following claim is still true:
-
-	[other lemma]
-	The capacity of a funnel array grows by a constant factor $\growthfactornew$ after the first time it is called.
-
-	[proof]
-	I prove that the algorithm ensures this using induction.
-
-	For the base case, consider the second time [resize] is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
-Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be added, and that is what the algorithm does.
-
-	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time.
-From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\growthfactornew^i\initcapacitynew$ and the head capacity is $(\growthfactornew^i - \growthfactornew^{i - 1})\initcapacitynew$.
-The next (total) capacity should be $\growthfactornew^{i + 1}\initcapacitynew$, and the next head capacity should be $(\growthfactornew^{i + 1} - \growthfactornew^i)\initcapacitynew$, which is $\growthfactornew$ times the current head capacity.
-The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
-
-	Now I take a look at [resize].
-Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$.
-No items are being copied; the only source of writes is adding a buffer to the tail.
-The goal is to find the number of writes that causes.
-
-	Let $\nwritesresizefn(n)$ denote the total number of writes made by [resize]. From [make lemma], I know that [resize] is called at the sizes
-
-	$$
-	S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew
-	$$
-
-	Let $k$ be the number of times the tail is added to.
-Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since [resize] is called $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
-Then the formula for $\nwritesresizefn(n)$ is
-
-	$$
-	\nwritesresizefn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the funnel array). I finally conclude that
-
-	$$
-	\nwritesnewfn(n) = n + k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	I now approximate this expression with big-P notation. First, I establish an approximation for $k$ using big-O:
-
-	\begin{align*}
-	k &= \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil\\
-	\bigo(k) &= \bigo(\log \varnitems)
-	\end{align*}
-
-	Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\nwritesnewfn(\varnitems)$, leaving just $\biggo(\varnitems)$:
-
-	\begin{align*}
-	\biggo(\nwritesnewfn(\varnitems)) &= \biggo(\varnitems + \nwritesfn(k))\\
-	&= \biggo(\varnitems) + \biggo(\nwritesfn(k))\\
-	&= \biggo(\varnitems) + \bigo(\log \varnitems)\\
-	&= \biggo(\varnitems)
-	\end{align*}
-
-	\scomplex
-
-	% Should this be C(n) instead of C?
-	The space function for $\varnitems$ [add] calls on a funnel array is denoted $\spacenewfn(\varnitems)$.
-Since funnel arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.
-$\spacenewfn(\varnitems)$ is usually greater than $C$, however; this is because funnel arrays not only allocate item buffers, but stores references to them in the tail.
-Thus the space the tail allocates must also be determined.
-
-	I determined in [...] that if $\varnitems$ are added then the tail is added to $k$ times, where $k = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
-Since the tail is a dynamic array, it allocates $\spacefn(k)$ space, where $\spacefn$ is the space function of the tail.
-Through a similar method to [...] it can be shown $\bigo(\spacefn(k)) = \bigo(k) = \bigo(\log \varnitems)$.
-Then % TODO: P-analysis should come after the explicit formula.
-
-	\begin{align*}
-	\spacenewfn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
-	\end{align*}
-
-	\tcomplexcmp
-
-	\scomplexcmp
-
-	\begin{align*}
-	\spaceratio = \frac {\biggo(2^{\lceil \log_2 \varnitems \rceil})} {\biggo(2^{\lceil \log_2 \varnitems \rceil + 1})} = \frac{1}{2}
-	\end{align*}
-
-	\subsection{Indexing}
-
-	\descriptn
-
-	Indexing is another very common operation on a list. I will call methods that get or set an item at a specified index \textbf{get} and \textbf{set indexers}, respectively.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	$\timefn(\varnitems) = \bigo(1)$
-
-	% <funnel array implementation>
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(1)$
-
-	\tcomplexcmp
-
-	\subsection{Iterating}
-
-	\descriptn
-
-	\textbf{Iteration} of a list is the process of performing some action on each of its elements.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	Ignoring the arbitrary code run after getting each element, the time complexity of this method is $\bigo(\varnitems)$.
-
-	\funarrayimpl
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(\varnitems)$
-
-	\tcomplexcmp
-
-	\subsection{Copying to an array}
-
-	\descriptn
-
-	Users often want to take list structures, such as dynamic arrays, and convert them into plain arrays.
-There are multiple reasons why someone would want to do this after they are done adding to the list:
-
-	\begin{itemize}
-		\item Plain arrays hold on to exactly the amount of memory needed to hold their elements. However, dynamic and funnel arrays allocate more space than necessary to optimize adding new items.
-		\item The user wants to call a function in third-party code that takes a plain array as an argument.
-		\item
-		\item Plain arrays are contiguous, while funnel arrays are fragmented and have worse locality.
-		\item The indexer of funnel arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
-	\end{itemize}
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	\funarrayimpl
-
-	\tcomplex
-
-	\section{Other Operations}
-
-	\subsection{Inserting}
-
-	\descriptn
-
-	\textbf{Inserting} an element places it at a specified index within the list, and increments the list's count.
-If the index equals the size of the list, the effect is the same as adding the element.
-Otherwise, the elements at indices greater than or equal to the specified index are moved to the next index, then the element is placed at the specified index.
-
-	\subsection{Deleting}
-
-	\descriptn
-
-	\textbf{Deleting} the element at a specified index moves the elements at indices greater than the specified index to the previous index. The count of the list is decremented.
-
-	\subsection{Searching}
-
-	\descriptn
-
-	\textbf{Searching} for an element returns the first or last index within the list where the item can be found. If the user knows the items of the lists are sorted, \textbf{binary search} can be used.
-
-	\subsection{In-place sorting}
-
-	\descriptn
-
-	Given a strict ordering $<$, I say a list $\listname$ is \textbf{sorted} by $<$ iff $\left(a, b \in \listname \land a < b\right) \leftrightarrow I_M(a) < I_m(b)$.
-$I_M(a)$ is the last (maximum) index of $a$ in $L$, and $I_m(b)$ is the first (minimum) index of $b$ in $L$.
-Note that the use of $<$ on the right-hand side compares integers and not elements of $L$, so this is not a recursive definition.
-
-	\section{Implementations}
-
-	\section{Benchmarks}
-
-	\section{Closing Remarks}
-
-\end{document}

### 2017-10-16 Draft2/Appending.Growth.tex
Modularize things

--- 2017-10-16 Draft2.tex
@@
-\documentclass{article}
-\usepackage{amsmath}
-
-\newcommand{\descriptn}{\textbf{Description}}
-\newcommand{\dynarrayimpl}{\textbf{Dynamic array implementation}}
-\newcommand{\funarrayimpl}{\textbf{Funnel array implementation}}
-\newcommand{\tcomplex}{\textbf{Time complexity}}
-\newcommand{\scomplex}{\textbf{Space complexity}}
-\newcommand{\tcomplexcmp}{\textbf{Time complexity comparison}}
-\newcommand{\scomplexcmp}{\textbf{Space complexity comparison}}
-
-\newcommand{\timefn}{T}
-\newcommand{\spacefn}{S}
-\newcommand{\nwritesfn}{W}
-
-\newcommand{\timenewfn}{\timefn'}
-\newcommand{\spacenewfn}{\spacefn'}
-\newcommand{\nwritesnewfn}{\nwritesfn'}
-
-\newcommand{\nwritesresizefn}{W_R}
-
-\newcommand{\timeratio}{r_\timefn}
-\newcommand{\spaceratio}{r_\spacefn}
-
-\newcommand{\bigo}{O}
-\newcommand{\biggo}{P}
-\newcommand{\varnitems}{n}
-\newcommand{\indexertime}{I}
-
-\newcommand{\listname}{L}
-
-\newcommand{\initcapacity}{C_f}
-\newcommand{\growthfactor}{G}
-\newcommand{\capacityfn}{C}
-
-\newcommand{\initcapacitynew}{\initcapacity'}
-\newcommand{\growthfactornew}{\growthfactor'}
-
-\setlength{\parskip}{1em}
-
-\begin{document}
-	\begin{abstract}
-	\end{abstract}
-
-	\section{Introduction}
-
-	\section{Fields and Properties}
-
-	I define some \textbf{fields} and \textbf{properties} (constant time methods that do not change state) for both types of arrays, so I may use them later to implement non-trivial methods.
-
-	\section{Common Operations}
-
-	In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
-
-	The following mathematical definitions will be used while analyzing time and space complexity:
-
-	\begin{description}
-		\item[$\biggo(f(n))$] This is an alternative to big-O notation that I will name "big-P notation".
-It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
-For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
-This makes it possible to compare two time complexities, if their ratio tends to a constant for large $n$.\\
-		More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
-	\end{description}
-
-	\subsection{Adding}
-
-	\descriptn
-
-	Adding is the most common operation done on dynamic arrays\footnote{}.
-Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
-I begin with the implementation of adding for dynamic arrays.
-
-	I will first implement and analyze adding for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
-
-	\begin{description}
-		\item[initial capacity] The capacity of a dynamic a array when one item is added to it. I denote this $\initcapacity$.\\
-		(The capacity of any dynamic array with size zero should be zero.)
-		\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\listname$ is resized. I denote this with $\growthfactor$.
-	\end{description}
-
-	% impl.
-
-	\tcomplex
-
-	Before I analyze the time complexity of [add], I consider a different method for measuring its cost.
-Suppose I start with an empty list and $\varnitems$ elements are added.
-How many times is an element stored in an array?
-I will term the answer to this question the \textbf{write cost} of $\varnitems$ adds, and denote it $\nwritesfn(n)$.
-
-	In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ adds.
-However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$ I need to analyze when [resize] is called.
-Consider the following lemma:
-
-	[lemma]
-	Let $\listname$ by a dynamic array.
-As $\varnitems$ are added, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
-
-	[proof]
-	The capacity starts out at zero and becomes $\initcapacity$ once one element is added.
-From then on, it can only grow by a factor of $\growthfactor$ via [resize], so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
-By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$.
-Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$.
-Using this property, I now derive $k$.
-
-	\begin{align*}
-	\growthfactor^k\initcapacity &\geq \varnitems\\
-	\growthfactor^k &\geq \frac{\varnitems}{\initcapacity}\\
-	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity\\
-	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity > k - 1\\
-	k &= \big\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \big\rceil
-	\end{align*}
-
-	Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.
-
-	[make lemma]
-	Now, consider that to grow by $\growthfactor$ [resize] must be called.
-So $\growthfactor^k\initcapacity$ being present in $S_C$ means [resize] was called at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
-Then [resize] was called at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
-
-	Each time [resize] is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ adds is
-
-	\begin{align*}
-	0 + \initcapacity + \growthfactor\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity &= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	\end{align*}
-
-	Finally, adding the writes made for every item in [add], I finally find an explicit formula for $\nwritesfn(\varnitems)$.
-
-	[ref1]
-	$$
-	\nwritesfn(\varnitems) = \varnitems + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	[ref2]
-	To make this expression easier to work with, I will write it in big-P notation to approximate it for large $\varnitems$.
-First I note that $\log_{\growthfactor} k \leq \lceil \log_{\growthfactor} k \rceil < \left( \log_{\growthfactor} k \right) + 1$ for any $k > 0$, so $k \leq \growthfactor^{\lceil \log_{\growthfactor} k \rceil} < \growthfactor{k}$.
-Then
-
-	\begin{align*}
-	\nwritesfn(\varnitems) &= \varnitems + \left( \frac{\growthfactor^{\big\lceil \log_{\growthfactor} \left( \frac {\varnitems} {\initcapacity} \right) \big\rceil} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\varnitems + \left( \frac{\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right)\\
-	\biggo\left( \varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right) \right)\\
-	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \left( \frac{2\growthfactor - 1}{\growthfactor - 1} \right) \varnitems \right)
-	\end{align*}
-
-	\scomplex
-
-	I wish to find the space allocated while adding $\varnitems$ items to a dynamic array.
-I denote this quantity $\spacefn(\varnitems)$, and define it as the total length of all arrays allocated during $\varnitems$ [add] calls.
-I now derive a formula for $\spacefn(\varnitems)$.
-
-	From [lemma] I know the exact capacities $\listname$ takes on as $\varnitems$ items are added.
-Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.
-Then the total length of arrays allocated is
-
-	\begin{align*}
-	\spacefn(\varnitems) &= \sum_{i \in S_C} i\\
-	&= 0 + \initcapacity + \growthfactor\initcapacity + \growthfactor^2\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity\\
-	&= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil + 1} - 1}{\growthfactor - 1} \right) \initcapacity
-	\end{align*}
-
-	Using the identity in [ref2] again, I bound its big-P complexity:
-
-	\begin{align*}
-	\left( \frac{\growthfactor \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \spacefn(\varnitems) &< \left( \frac{\growthfactor^2 \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\biggo\left( \left( \frac{\growthfactor \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \right) \leq \biggo\left( \spacefn(\varnitems) \right) &< \biggo\left( \left( \frac{\growthfactor^2 \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \right)\\
-	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo\left( \spacefn(\varnitems) \right) &< \biggo\left( \left( \frac{\growthfactor^2}{\growthfactor - 1} \right) \varnitems \right)
-	\end{align*}
-
 \funarrayimpl
@@
 \end{align*}
-
-	\tcomplexcmp
-
-	\scomplexcmp
-
-	\begin{align*}
-	\spaceratio = \frac {\biggo(2^{\lceil \log_2 \varnitems \rceil})} {\biggo(2^{\lceil \log_2 \varnitems \rceil + 1})} = \frac{1}{2}
-	\end{align*}
-
-	\subsection{Indexing}
-
-	\descriptn
-
-	Indexing is another very common operation on a list. I will call methods that get or set an item at a specified index \textbf{get} and \textbf{set indexers}, respectively.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	$\timefn(\varnitems) = \bigo(1)$
-
-	% <funnel array implementation>
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(1)$
-
-	\tcomplexcmp
-
-	\subsection{Iterating}
-
-	\descriptn
-
-	\textbf{Iteration} of a list is the process of performing some action on each of its elements.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	Ignoring the arbitrary code run after getting each element, the time complexity of this method is $\bigo(\varnitems)$.
-
-	\funarrayimpl
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(\varnitems)$
-
-	\tcomplexcmp
-
-	\subsection{Copying to an array}
-
-	\descriptn
-
-	Users often want to take list structures, such as dynamic arrays, and convert them into plain arrays.
-There are multiple reasons why someone would want to do this after they are done adding to the list:
-
-	\begin{itemize}
-		\item Plain arrays hold on to exactly the amount of memory needed to hold their elements. However, dynamic and funnel arrays allocate more space than necessary to optimize adding new items.
-		\item The user wants to call a function in third-party code that takes a plain array as an argument.
-		\item
-		\item Plain arrays are contiguous, while funnel arrays are fragmented and have worse locality.
-		\item The indexer of funnel arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
-	\end{itemize}
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	\funarrayimpl
-
-	\tcomplex
-
-	\section{Other Operations}
-
-	\subsection{Inserting}
-
-	\descriptn
-
-	\textbf{Inserting} an element places it at a specified index within the list, and increments the list's count.
-If the index equals the size of the list, the effect is the same as adding the element.
-Otherwise, the elements at indices greater than or equal to the specified index are moved to the next index, then the element is placed at the specified index.
-
-	\subsection{Deleting}
-
-	\descriptn
-
-	\textbf{Deleting} the element at a specified index moves the elements at indices greater than the specified index to the previous index. The count of the list is decremented.
-
-	\subsection{Searching}
-
-	\descriptn
-
-	\textbf{Searching} for an element returns the first or last index within the list where the item can be found. If the user knows the items of the lists are sorted, \textbf{binary search} can be used.
-
-	\subsection{In-place sorting}
-
-	\descriptn
-
-	Given a strict ordering $<$, I say a list $\listname$ is \textbf{sorted} by $<$ iff $\left(a, b \in \listname \land a < b\right) \leftrightarrow I_M(a) < I_m(b)$.
-$I_M(a)$ is the last (maximum) index of $a$ in $L$, and $I_m(b)$ is the first (minimum) index of $b$ in $L$.
-Note that the use of $<$ on the right-hand side compares integers and not elements of $L$, so this is not a recursive definition.
-
-	\section{Implementations}
-
-	\section{Benchmarks}
-
-	\section{Closing Remarks}
-
-\end{document}

### 2017-10-16 Draft2/FieldsProperties.tex
Modularize even more

--- 2017-10-15 Draft2.tex
@@
-\documentclass{article}
-\usepackage{amsmath}
-
-\newcommand{\descriptn}{\textbf{Description}}
-\newcommand{\dynarrayimpl}{\textbf{Dynamic array implementation}}
-\newcommand{\funarrayimpl}{\textbf{Funnel array implementation}}
-\newcommand{\tcomplex}{\textbf{Time complexity}}
-\newcommand{\scomplex}{\textbf{Space complexity}}
-\newcommand{\tcomplexcmp}{\textbf{Time complexity comparison}}
-\newcommand{\scomplexcmp}{\textbf{Space complexity comparison}}
-
-\newcommand{\timefn}{T}
-\newcommand{\spacefn}{S}
-\newcommand{\nwritesfn}{W}
-
-\newcommand{\timenewfn}{\timefn'}
-\newcommand{\spacenewfn}{\spacefn'}
-\newcommand{\nwritesnewfn}{\nwritesfn'}
-
-\newcommand{\nwritesresizefn}{W_R}
-
-\newcommand{\timeratio}{r_\timefn}
-\newcommand{\spaceratio}{r_\spacefn}
-
-\newcommand{\bigo}{O}
-\newcommand{\biggo}{P}
-\newcommand{\varnitems}{n}
-\newcommand{\indexertime}{I}
-
-\newcommand{\listname}{L}
-
-\newcommand{\initcapacity}{C_f}
-\newcommand{\growthfactor}{G}
-\newcommand{\capacityfn}{C}
-
-\newcommand{\initcapacitynew}{\initcapacity'}
-\newcommand{\growthfactornew}{\growthfactor'}
-
-\setlength{\parskip}{1em}
-
-\begin{document}
-	\begin{abstract}
-	\end{abstract}
-
-	\section{Introduction}
-
-	\section{Fields and Properties}
-
 I define some \textbf{fields} and \textbf{properties} (constant time methods that do not change state) for both types of arrays, so I may use them later to implement non-trivial methods.
-
-	\section{Common Operations}
-
-	In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
-
-	The following mathematical definitions will be used while analyzing time and space complexity:
-
-	\begin{description}
-		\item[$\biggo(f(n))$] This is an alternative to big-O notation that I will name "big-P notation".
-It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
-For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
-This makes it possible to compare two time complexities, if their ratio tends to a constant for large $n$.\\
-		More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
-	\end{description}
-
-	\subsection{Adding}
-
-	\descriptn
-
-	Adding is the most common operation done on dynamic arrays\footnote{}.
-Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
-We begin with the implementation for dynamic arrays.
-
-	I will first implement and analyze adding for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
-
-	\begin{description}
-		\item[initial capacity] The capacity of a dynamic a array when one item is added to it. I denote this $\initcapacity$.\\
-		(The capacity of any dynamic array with size zero should be zero.)
-		\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\listname$ is resized. I denote this with $\growthfactor$.
-	\end{description}
-
-	% impl.
-
-	\tcomplex
-
-	Before I analyze the time complexity of [add], I consider a different method for measuring its cost.
-Suppose I start with an empty list and $\varnitems$ elements are added.
-How many times is an element stored in an array?
-I will term the answer to this question the \textbf{write cost} of $\varnitems$ adds, and denote it $\nwritesfn(n)$.
-
-	In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ adds.
-However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$ I need to analyze when [resize] is called.
-Consider the following lemma:
-
-	[lemma]
-	Let $\listname$ by a dynamic array.
-As $\varnitems$ are added, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
-
-	[proof]
-	The capacity starts out at zero and becomes $\initcapacity$ once one element is added.
-From then on, it can only grow by a factor of $\growthfactor$ via [resize], so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
-By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$.
-Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$.
-Using this property, we now derive $k$.
-
-	\begin{align*}
-	\growthfactor^k\initcapacity &\geq \varnitems\\
-	\growthfactor^k &\geq \frac{\varnitems}{\initcapacity}\\
-	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity\\
-	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity > k - 1\\
-	k &= \big\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \big\rceil
-	\end{align*}
-
-	Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.
-
-	[make lemma]
-	Now, consider that to grow by $\growthfactor$ we have to call [resize].
-So $\growthfactor^k\initcapacity$ being present in $S_C$ means we once called [resize] at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
-Then we must have called [resize] at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
-
-	Each time [resize] is called, we copy $i$ items where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ adds is
-
-	\begin{align*}
-	0 + \initcapacity + \growthfactor\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity &= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	\end{align*}
-
-	Finally, adding the writes made for every item in [add], I finally find an explicit formula for $\nwritesfn(\varnitems)$.
-
-	[ref1]
-	$$
-	\nwritesfn(\varnitems) = \varnitems + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	To make this expression easier to work with, I will write it in big-P notation to approximate it for large $\varnitems$.
-First I note that $\log_{\growthfactor} k \leq \lceil \log_{\growthfactor} k \rceil < \left( \log_{\growthfactor} k \right) + 1$ for any $k > 0$, so $k \leq \growthfactor^{\lceil \log_{\growthfactor} k \rceil} < \growthfactor{k}$ and $\exists r \in {[1, \growthfactor)} : rk = \growthfactor^{\lceil \log_{\growthfactor} k \rceil}$.
-Then
-
-	\begin{align*}
-	\nwritesfn(\varnitems) &= \varnitems + \left( \frac{\growthfactor^{\big\lceil \log_{\growthfactor} \left( \frac {\varnitems} {\initcapacity} \right) \big\rceil} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\varnitems + \left( \frac{\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right)\\
-	\biggo\left( \varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right) \right)\\
-	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo(\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \left( \frac{2\growthfactor - 1}{\growthfactor - 1} \right) \varnitems \right)
-	\end{align*}
-
-	\scomplex
-
-	\begin{align*}
-	\spacefn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil + 1}) = \bigo(\varnitems)
-	\end{align*}
-
-	\funarrayimpl
-
-	\tcomplex
-
-	I again start off by finding the write cost when $\varnitems$ are added.
-I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so we can compare it to $\nwritesfn(\varnitems)$ later.
-I also use $\growthfactornew$ and $\initcapacitynew$ instead of $\growthfactor$ and $\initcapacity$ for the growth factor and initial capacity, respectively.
-
-	[That lemma] still holds, since all of the assumptions made there are also true for funnel arrays.
-In particular, although funnel arrays resize slightly differently than dynamic arrays, the following claim is still true:
-
-	[lemma]
-	The capacity of a funnel array grows by a constant factor $\growthfactornew$ after the first time it is called.
-
-	[proof]
-	I prove that the algorithm ensures this using induction.
-
-	For the base case, consider the second time [resize] is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
-Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be added, and that is what the algorithm does.
-
-	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time.
-From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\growthfactornew^i\initcapacitynew$ and the head capacity is $(\growthfactornew^i - \growthfactornew^{i - 1})\initcapacitynew$.
-The next (total) capacity should be $\growthfactornew^{i + 1}\initcapacitynew$, and the next head capacity should be $(\growthfactornew^{i + 1} - \growthfactornew^i)\initcapacitynew$, which is $\growthfactornew$ times the current head capacity.
-The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
-
-	Now I take a look at [resize].
-Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$.
-No items are being copied; the only source of writes is adding a buffer to the tail.
-The goal is to find the number of writes that causes.
-
-	Let $\nwritesresizefn(n)$ denote the total number of writes made by [resize]. From [make lemma], I know that [resize] is called at the sizes
-
-	$$
-	S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew
-	$$
-
-	Let $k$ be the number of times the tail is added to.
-Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
-Then the formula for $\nwritesresizefn(n)$ is
-
-	$$
-	\nwritesresizefn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the funnel array). I finally conclude that
-
-	$$
-	\nwritesnewfn(n) = n + k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	Now I wish to find the number of writes [resize] performs.
-
-	\begin{align*}
-	\nwritesnewfn(\varnitems) = \biggo(\varnitems)
-	\end{align*}
-
-	\scomplex
-
-	\begin{align*}
-	\spacenewfn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
-	\end{align*}
-
-	\tcomplexcmp
-
-	\begin{align*}
-	\end{align*}
-
-	\scomplexcmp
-
-	\begin{align*}
-	\spaceratio = \frac {\biggo(2^{\lceil \log_2 \varnitems \rceil})} {\biggo(2^{\lceil \log_2 \varnitems \rceil + 1})} = \frac{1}{2}
-	\end{align*}
-
-	\subsection{Indexing}
-
-	\descriptn
-
-	Indexing is another very common operation on a list. I will call methods that get or set an item at a specified index \textbf{get indexer} and \textit{set indexers}, respectively.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	$\timefn(\varnitems) = \bigo(1)$
-
-	% <funnel array implementation>
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(1)$
-
-	\tcomplexcmp
-
-	\subsection{Iterating}
-
-	\descriptn
-
-	\textbf{Iteration} of a list is the process of performing some action on each of its elements.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	Ignoring the arbitrary code run after getting each element, the time complexity of this method is $\bigo(\varnitems)$.
-
-	\funarrayimpl
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(\varnitems)$
-
-	\tcomplexcmp
-
-	\subsection{Copying to an array}
-
-	\descriptn
-
-	Users often want to take list structures, such as dynamic arrays, and convert them into plain arrays.
-There are multiple reasons why someone would want to do this after they are done adding to the list:
-
-	\begin{itemize}
-		\item Plain arrays hold on to exactly the amount of memory needed to hold their elements. However, dynamic and funnel arrays allocate more space than necessary to optimize adding new items.
-		\item The user wants to call a function in third-party code that takes a plain array as an argument.
-		\item
-		\item Plain arrays are contiguous, while funnel arrays are fragmented and have worse locality.
-		\item The indexer of funnel arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
-	\end{itemize}
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	\funarrayimpl
-
-	\tcomplex
-
-	\section{Other Operations}
-
-	\subsection{Inserting}
-
-	\descriptn
-
-	\textbf{Inserting} an element places it at a specified index within the list, and increments the list's count.
-If the index equals the size of the list, the effect is the same as adding the element.
-Otherwise, the elements at indices greater than or equal to the specified index are moved to the next index, then the element is placed at the specified index.
-
-	\subsection{Deleting}
-
-	\descriptn
-
-	\textbf{Deleting} the element at a specified index moves the elements at indices greater than the specified index to the previous index. The count of the list is decremented.
-
-	\subsection{Searching}
-
-	\descriptn
-
-	\textbf{Searching} for an element returns the first or last index within the list where the item can be found. If the user knows the items of the lists are sorted, \textbf{binary search} can be used.
-
-	\subsection{In-place sorting}
-
-	\descriptn
-
-	Given a strict ordering $<$, we say a list $\listname$ is \textbf{sorted} by $<$ iff $\left(a, b \in \listname \land a < b\right) \leftrightarrow I_M(a) < I_m(b)$.
-$I_M(a)$ is the last (maximum) index of $a$ in $L$, and $I_m(b)$ is the first (minimum) index of $b$ in $L$.
-Note that the use of $<$ on the right-hand side compares integers and not elements of $L$, so this is not a recursive definition.
-
-	\section{Implementations}
-
-	\section{Benchmarks}
-
-	\section{Closing Remarks}
-
-\end{document}

### 2017-10-16 Draft2/CommonOperations.Blurb.tex
Modularize even momre

--- 2017-10-15 Draft2.tex
@@
-\documentclass{article}
-\usepackage{amsmath}
-
-\newcommand{\descriptn}{\textbf{Description}}
-\newcommand{\dynarrayimpl}{\textbf{Dynamic array implementation}}
-\newcommand{\funarrayimpl}{\textbf{Funnel array implementation}}
-\newcommand{\tcomplex}{\textbf{Time complexity}}
-\newcommand{\scomplex}{\textbf{Space complexity}}
-\newcommand{\tcomplexcmp}{\textbf{Time complexity comparison}}
-\newcommand{\scomplexcmp}{\textbf{Space complexity comparison}}
-
-\newcommand{\timefn}{T}
-\newcommand{\spacefn}{S}
-\newcommand{\nwritesfn}{W}
-
-\newcommand{\timenewfn}{\timefn'}
-\newcommand{\spacenewfn}{\spacefn'}
-\newcommand{\nwritesnewfn}{\nwritesfn'}
-
-\newcommand{\nwritesresizefn}{W_R}
-
-\newcommand{\timeratio}{r_\timefn}
-\newcommand{\spaceratio}{r_\spacefn}
-
-\newcommand{\bigo}{O}
-\newcommand{\biggo}{P}
-\newcommand{\varnitems}{n}
-\newcommand{\indexertime}{I}
-
-\newcommand{\listname}{L}
-
-\newcommand{\initcapacity}{C_f}
-\newcommand{\growthfactor}{G}
-\newcommand{\capacityfn}{C}
-
-\newcommand{\initcapacitynew}{\initcapacity'}
-\newcommand{\growthfactornew}{\growthfactor'}
-
-\setlength{\parskip}{1em}
-
-\begin{document}
-	\begin{abstract}
-	\end{abstract}
-
-	\section{Introduction}
-
-	\section{Fields and Properties}
-
-	I define some \textbf{fields} and \textbf{properties} (constant time methods that do not change state) for both types of arrays, so I may use them later to implement non-trivial methods.
-
-	\section{Common Operations}
-
 In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
@@
 \end{description}
-
-	\subsection{Adding}
-
-	\descriptn
-
-	Adding is the most common operation done on dynamic arrays\footnote{}.
-Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
-We begin with the implementation for dynamic arrays.
-
-	I will first implement and analyze adding for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
-
-	\begin{description}
-		\item[initial capacity] The capacity of a dynamic a array when one item is added to it. I denote this $\initcapacity$.\\
-		(The capacity of any dynamic array with size zero should be zero.)
-		\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\listname$ is resized. I denote this with $\growthfactor$.
-	\end{description}
-
-	% impl.
-
-	\tcomplex
-
-	Before I analyze the time complexity of [add], I consider a different method for measuring its cost.
-Suppose I start with an empty list and $\varnitems$ elements are added.
-How many times is an element stored in an array?
-I will term the answer to this question the \textbf{write cost} of $\varnitems$ adds, and denote it $\nwritesfn(n)$.
-
-	In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ adds.
-However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$ I need to analyze when [resize] is called.
-Consider the following lemma:
-
-	[lemma]
-	Let $\listname$ by a dynamic array.
-As $\varnitems$ are added, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
-
-	[proof]
-	The capacity starts out at zero and becomes $\initcapacity$ once one element is added.
-From then on, it can only grow by a factor of $\growthfactor$ via [resize], so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
-By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$.
-Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$.
-Using this property, we now derive $k$.
-
-	\begin{align*}
-	\growthfactor^k\initcapacity &\geq \varnitems\\
-	\growthfactor^k &\geq \frac{\varnitems}{\initcapacity}\\
-	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity\\
-	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity > k - 1\\
-	k &= \big\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \big\rceil
-	\end{align*}
-
-	Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.
-
-	[make lemma]
-	Now, consider that to grow by $\growthfactor$ we have to call [resize].
-So $\growthfactor^k\initcapacity$ being present in $S_C$ means we once called [resize] at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
-Then we must have called [resize] at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
-
-	Each time [resize] is called, we copy $i$ items where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ adds is
-
-	\begin{align*}
-	0 + \initcapacity + \growthfactor\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity &= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	\end{align*}
-
-	Finally, adding the writes made for every item in [add], I finally find an explicit formula for $\nwritesfn(\varnitems)$.
-
-	[ref1]
-	$$
-	\nwritesfn(\varnitems) = \varnitems + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	To make this expression easier to work with, I will write it in big-P notation to approximate it for large $\varnitems$.
-First I note that $\log_{\growthfactor} k \leq \lceil \log_{\growthfactor} k \rceil < \left( \log_{\growthfactor} k \right) + 1$ for any $k > 0$, so $k \leq \growthfactor^{\lceil \log_{\growthfactor} k \rceil} < \growthfactor{k}$ and $\exists r \in {[1, \growthfactor)} : rk = \growthfactor^{\lceil \log_{\growthfactor} k \rceil}$.
-Then
-
-	\begin{align*}
-	\nwritesfn(\varnitems) &= \varnitems + \left( \frac{\growthfactor^{\big\lceil \log_{\growthfactor} \left( \frac {\varnitems} {\initcapacity} \right) \big\rceil} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\varnitems + \left( \frac{\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right)\\
-	\biggo\left( \varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right) \right)\\
-	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo(\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \left( \frac{2\growthfactor - 1}{\growthfactor - 1} \right) \varnitems \right)
-	\end{align*}
-
-	\scomplex
-
-	\begin{align*}
-	\spacefn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil + 1}) = \bigo(\varnitems)
-	\end{align*}
-
-	\funarrayimpl
-
-	\tcomplex
-
-	I again start off by finding the write cost when $\varnitems$ are added.
-I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so we can compare it to $\nwritesfn(\varnitems)$ later.
-I also use $\growthfactornew$ and $\initcapacitynew$ instead of $\growthfactor$ and $\initcapacity$ for the growth factor and initial capacity, respectively.
-
-	[That lemma] still holds, since all of the assumptions made there are also true for funnel arrays.
-In particular, although funnel arrays resize slightly differently than dynamic arrays, the following claim is still true:
-
-	[lemma]
-	The capacity of a funnel array grows by a constant factor $\growthfactornew$ after the first time it is called.
-
-	[proof]
-	I prove that the algorithm ensures this using induction.
-
-	For the base case, consider the second time [resize] is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
-Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be added, and that is what the algorithm does.
-
-	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time.
-From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\growthfactornew^i\initcapacitynew$ and the head capacity is $(\growthfactornew^i - \growthfactornew^{i - 1})\initcapacitynew$.
-The next (total) capacity should be $\growthfactornew^{i + 1}\initcapacitynew$, and the next head capacity should be $(\growthfactornew^{i + 1} - \growthfactornew^i)\initcapacitynew$, which is $\growthfactornew$ times the current head capacity.
-The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
-
-	Now I take a look at [resize].
-Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$.
-No items are being copied; the only source of writes is adding a buffer to the tail.
-The goal is to find the number of writes that causes.
-
-	Let $\nwritesresizefn(n)$ denote the total number of writes made by [resize]. From [make lemma], I know that [resize] is called at the sizes
-
-	$$
-	S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew
-	$$
-
-	Let $k$ be the number of times the tail is added to.
-Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
-Then the formula for $\nwritesresizefn(n)$ is
-
-	$$
-	\nwritesresizefn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the funnel array). I finally conclude that
-
-	$$
-	\nwritesnewfn(n) = n + k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	Now I wish to find the number of writes [resize] performs.
-
-	\begin{align*}
-	\nwritesnewfn(\varnitems) = \biggo(\varnitems)
-	\end{align*}
-
-	\scomplex
-
-	\begin{align*}
-	\spacenewfn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
-	\end{align*}
-
-	\tcomplexcmp
-
-	\begin{align*}
-	\end{align*}
-
-	\scomplexcmp
-
-	\begin{align*}
-	\spaceratio = \frac {\biggo(2^{\lceil \log_2 \varnitems \rceil})} {\biggo(2^{\lceil \log_2 \varnitems \rceil + 1})} = \frac{1}{2}
-	\end{align*}
-
-	\subsection{Indexing}
-
-	\descriptn
-
-	Indexing is another very common operation on a list. I will call methods that get or set an item at a specified index \textbf{get indexer} and \textit{set indexers}, respectively.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	$\timefn(\varnitems) = \bigo(1)$
-
-	% <funnel array implementation>
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(1)$
-
-	\tcomplexcmp
-
-	\subsection{Iterating}
-
-	\descriptn
-
-	\textbf{Iteration} of a list is the process of performing some action on each of its elements.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	Ignoring the arbitrary code run after getting each element, the time complexity of this method is $\bigo(\varnitems)$.
-
-	\funarrayimpl
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(\varnitems)$
-
-	\tcomplexcmp
-
-	\subsection{Copying to an array}
-
-	\descriptn
-
-	Users often want to take list structures, such as dynamic arrays, and convert them into plain arrays.
-There are multiple reasons why someone would want to do this after they are done adding to the list:
-
-	\begin{itemize}
-		\item Plain arrays hold on to exactly the amount of memory needed to hold their elements. However, dynamic and funnel arrays allocate more space than necessary to optimize adding new items.
-		\item The user wants to call a function in third-party code that takes a plain array as an argument.
-		\item
-		\item Plain arrays are contiguous, while funnel arrays are fragmented and have worse locality.
-		\item The indexer of funnel arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
-	\end{itemize}
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	\funarrayimpl
-
-	\tcomplex
-
-	\section{Other Operations}
-
-	\subsection{Inserting}
-
-	\descriptn
-
-	\textbf{Inserting} an element places it at a specified index within the list, and increments the list's count.
-If the index equals the size of the list, the effect is the same as adding the element.
-Otherwise, the elements at indices greater than or equal to the specified index are moved to the next index, then the element is placed at the specified index.
-
-	\subsection{Deleting}
-
-	\descriptn
-
-	\textbf{Deleting} the element at a specified index moves the elements at indices greater than the specified index to the previous index. The count of the list is decremented.
-
-	\subsection{Searching}
-
-	\descriptn
-
-	\textbf{Searching} for an element returns the first or last index within the list where the item can be found. If the user knows the items of the lists are sorted, \textbf{binary search} can be used.
-
-	\subsection{In-place sorting}
-
-	\descriptn
-
-	Given a strict ordering $<$, we say a list $\listname$ is \textbf{sorted} by $<$ iff $\left(a, b \in \listname \land a < b\right) \leftrightarrow I_M(a) < I_m(b)$.
-$I_M(a)$ is the last (maximum) index of $a$ in $L$, and $I_m(b)$ is the first (minimum) index of $b$ in $L$.
-Note that the use of $<$ on the right-hand side compares integers and not elements of $L$, so this is not a recursive definition.
-
-	\section{Implementations}
-
-	\section{Benchmarks}
-
-	\section{Closing Remarks}
-
-\end{document}

### 2017-10-16 Draft2/CopyArray.Blurb.tex
Modularize even momre

--- 2017-10-15 Draft2.tex
@@
-\documentclass{article}
-\usepackage{amsmath}
-
-\newcommand{\descriptn}{\textbf{Description}}
-\newcommand{\dynarrayimpl}{\textbf{Dynamic array implementation}}
-\newcommand{\funarrayimpl}{\textbf{Funnel array implementation}}
-\newcommand{\tcomplex}{\textbf{Time complexity}}
-\newcommand{\scomplex}{\textbf{Space complexity}}
-\newcommand{\tcomplexcmp}{\textbf{Time complexity comparison}}
-\newcommand{\scomplexcmp}{\textbf{Space complexity comparison}}
-
-\newcommand{\timefn}{T}
-\newcommand{\spacefn}{S}
-\newcommand{\nwritesfn}{W}
-
-\newcommand{\timenewfn}{\timefn'}
-\newcommand{\spacenewfn}{\spacefn'}
-\newcommand{\nwritesnewfn}{\nwritesfn'}
-
-\newcommand{\nwritesresizefn}{W_R}
-
-\newcommand{\timeratio}{r_\timefn}
-\newcommand{\spaceratio}{r_\spacefn}
-
-\newcommand{\bigo}{O}
-\newcommand{\biggo}{P}
-\newcommand{\varnitems}{n}
-\newcommand{\indexertime}{I}
-
-\newcommand{\listname}{L}
-
-\newcommand{\initcapacity}{C_f}
-\newcommand{\growthfactor}{G}
-\newcommand{\capacityfn}{C}
-
-\newcommand{\initcapacitynew}{\initcapacity'}
-\newcommand{\growthfactornew}{\growthfactor'}
-
-\setlength{\parskip}{1em}
-
-\begin{document}
-	\begin{abstract}
-	\end{abstract}
-
-	\section{Introduction}
-
-	\section{Fields and Properties}
-
-	I define some \textbf{fields} and \textbf{properties} (constant time methods that do not change state) for both types of arrays, so I may use them later to implement non-trivial methods.
-
-	\section{Common Operations}
-
-	In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
-
-	The following mathematical definitions will be used while analyzing time and space complexity:
-
-	\begin{description}
-		\item[$\biggo(f(n))$] This is an alternative to big-O notation that I will name "big-P notation".
-It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
-For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
-This makes it possible to compare two time complexities, if their ratio tends to a constant for large $n$.\\
-		More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
-	\end{description}
-
-	\subsection{Adding}
-
-	\descriptn
-
-	Adding is the most common operation done on dynamic arrays\footnote{}.
-Funnel arrays improve the performance of adding in two ways: by allocating less memory, and reducing the amount of copying.
-We begin with the implementation for dynamic arrays.
-
-	I will first implement and analyze adding for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
-
-	\begin{description}
-		\item[initial capacity] The capacity of a dynamic a array when one item is added to it. I denote this $\initcapacity$.\\
-		(The capacity of any dynamic array with size zero should be zero.)
-		\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\listname$ is resized. I denote this with $\growthfactor$.
-	\end{description}
-
-	% impl.
-
-	\tcomplex
-
-	Before I analyze the time complexity of [add], I consider a different method for measuring its cost.
-Suppose I start with an empty list and $\varnitems$ elements are added.
-How many times is an element stored in an array?
-I will term the answer to this question the \textbf{write cost} of $\varnitems$ adds, and denote it $\nwritesfn(n)$.
-
-	In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ adds.
-However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$ I need to analyze when [resize] is called.
-Consider the following lemma:
-
-	[lemma]
-	Let $\listname$ by a dynamic array.
-As $\varnitems$ are added, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
-
-	[proof]
-	The capacity starts out at zero and becomes $\initcapacity$ once one element is added.
-From then on, it can only grow by a factor of $\growthfactor$ via [resize], so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
-By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$.
-Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$.
-Using this property, we now derive $k$.
-
-	\begin{align*}
-	\growthfactor^k\initcapacity &\geq \varnitems\\
-	\growthfactor^k &\geq \frac{\varnitems}{\initcapacity}\\
-	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity\\
-	k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity > k - 1\\
-	k &= \big\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \big\rceil
-	\end{align*}
-
-	Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.
-
-	[make lemma]
-	Now, consider that to grow by $\growthfactor$ we have to call [resize].
-So $\growthfactor^k\initcapacity$ being present in $S_C$ means we once called [resize] at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
-Then we must have called [resize] at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
-
-	Each time [resize] is called, we copy $i$ items where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ adds is
-
-	\begin{align*}
-	0 + \initcapacity + \growthfactor\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity &= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	\end{align*}
-
-	Finally, adding the writes made for every item in [add], I finally find an explicit formula for $\nwritesfn(\varnitems)$.
-
-	[ref1]
-	$$
-	\nwritesfn(\varnitems) = \varnitems + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	To make this expression easier to work with, I will write it in big-P notation to approximate it for large $\varnitems$.
-First I note that $\log_{\growthfactor} k \leq \lceil \log_{\growthfactor} k \rceil < \left( \log_{\growthfactor} k \right) + 1$ for any $k > 0$, so $k \leq \growthfactor^{\lceil \log_{\growthfactor} k \rceil} < \growthfactor{k}$ and $\exists r \in {[1, \growthfactor)} : rk = \growthfactor^{\lceil \log_{\growthfactor} k \rceil}$.
-Then
-
-	\begin{align*}
-	\nwritesfn(\varnitems) &= \varnitems + \left( \frac{\growthfactor^{\big\lceil \log_{\growthfactor} \left( \frac {\varnitems} {\initcapacity} \right) \big\rceil} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\varnitems + \left( \frac{\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
-	\varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right)\\
-	\biggo\left( \varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right) \right)\\
-	\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo(\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \left( \frac{2\growthfactor - 1}{\growthfactor - 1} \right) \varnitems \right)
-	\end{align*}
-
-	\scomplex
-
-	\begin{align*}
-	\spacefn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil + 1}) = \bigo(\varnitems)
-	\end{align*}
-
-	\funarrayimpl
-
-	\tcomplex
-
-	I again start off by finding the write cost when $\varnitems$ are added.
-I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so we can compare it to $\nwritesfn(\varnitems)$ later.
-I also use $\growthfactornew$ and $\initcapacitynew$ instead of $\growthfactor$ and $\initcapacity$ for the growth factor and initial capacity, respectively.
-
-	[That lemma] still holds, since all of the assumptions made there are also true for funnel arrays.
-In particular, although funnel arrays resize slightly differently than dynamic arrays, the following claim is still true:
-
-	[lemma]
-	The capacity of a funnel array grows by a constant factor $\growthfactornew$ after the first time it is called.
-
-	[proof]
-	I prove that the algorithm ensures this using induction.
-
-	For the base case, consider the second time [resize] is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
-Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be added, and that is what the algorithm does.
-
-	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time.
-From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\growthfactornew^i\initcapacitynew$ and the head capacity is $(\growthfactornew^i - \growthfactornew^{i - 1})\initcapacitynew$.
-The next (total) capacity should be $\growthfactornew^{i + 1}\initcapacitynew$, and the next head capacity should be $(\growthfactornew^{i + 1} - \growthfactornew^i)\initcapacitynew$, which is $\growthfactornew$ times the current head capacity.
-The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
-
-	Now I take a look at [resize].
-Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$.
-No items are being copied; the only source of writes is adding a buffer to the tail.
-The goal is to find the number of writes that causes.
-
-	Let $\nwritesresizefn(n)$ denote the total number of writes made by [resize]. From [make lemma], I know that [resize] is called at the sizes
-
-	$$
-	S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew
-	$$
-
-	Let $k$ be the number of times the tail is added to.
-Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
-Then the formula for $\nwritesresizefn(n)$ is
-
-	$$
-	\nwritesresizefn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the funnel array). I finally conclude that
-
-	$$
-	\nwritesnewfn(n) = n + k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
-	$$
-
-	Now I wish to find the number of writes [resize] performs.
-
-	\begin{align*}
-	\nwritesnewfn(\varnitems) = \biggo(\varnitems)
-	\end{align*}
-
-	\scomplex
-
-	\begin{align*}
-	\spacenewfn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
-	\end{align*}
-
-	\tcomplexcmp
-
-	\begin{align*}
-	\end{align*}
-
-	\scomplexcmp
-
-	\begin{align*}
-	\spaceratio = \frac {\biggo(2^{\lceil \log_2 \varnitems \rceil})} {\biggo(2^{\lceil \log_2 \varnitems \rceil + 1})} = \frac{1}{2}
-	\end{align*}
-
-	\subsection{Indexing}
-
-	\descriptn
-
-	Indexing is another very common operation on a list. I will call methods that get or set an item at a specified index \textbf{get indexer} and \textit{set indexers}, respectively.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	$\timefn(\varnitems) = \bigo(1)$
-
-	% <funnel array implementation>
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(1)$
-
-	\tcomplexcmp
-
-	\subsection{Iterating}
-
-	\descriptn
-
-	\textbf{Iteration} of a list is the process of performing some action on each of its elements.
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	Ignoring the arbitrary code run after getting each element, the time complexity of this method is $\bigo(\varnitems)$.
-
-	\funarrayimpl
-
-	\tcomplex
-
-	$\timenewfn(\varnitems) = \bigo(\varnitems)$
-
-	\tcomplexcmp
-
-	\subsection{Copying to an array}
-
 \descriptn
@@
 \end{itemize}
-
-	\dynarrayimpl
-
-	\tcomplex
-
-	\funarrayimpl
-
-	\tcomplex
-
-	\section{Other Operations}
-
-	\subsection{Inserting}
-
-	\descriptn
-
-	\textbf{Inserting} an element places it at a specified index within the list, and increments the list's count.
-If the index equals the size of the list, the effect is the same as adding the element.
-Otherwise, the elements at indices greater than or equal to the specified index are moved to the next index, then the element is placed at the specified index.
-
-	\subsection{Deleting}
-
-	\descriptn
-
-	\textbf{Deleting} the element at a specified index moves the elements at indices greater than the specified index to the previous index. The count of the list is decremented.
-
-	\subsection{Searching}
-
-	\descriptn
-
-	\textbf{Searching} for an element returns the first or last index within the list where the item can be found. If the user knows the items of the lists are sorted, \textbf{binary search} can be used.
-
-	\subsection{In-place sorting}
-
-	\descriptn
-
-	Given a strict ordering $<$, we say a list $\listname$ is \textbf{sorted} by $<$ iff $\left(a, b \in \listname \land a < b\right) \leftrightarrow I_M(a) < I_m(b)$.
-$I_M(a)$ is the last (maximum) index of $a$ in $L$, and $I_m(b)$ is the first (minimum) index of $b$ in $L$.
-Note that the use of $<$ on the right-hand side compares integers and not elements of $L$, so this is not a recursive definition.
-
-	\section{Implementations}
-
-	\section{Benchmarks}
-
-	\section{Closing Remarks}
-
-\end{document}

### 2017-10-16 Draft2/Appending.Dynamic.tex
Rename some stuff

@@
 
-I will first implement adding for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
+I will first implement appending for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
 
 \begin{description}
-	\item[initial capacity] The capacity of a dynamic a array when one item is added to it. I denote this $\initcapacity$.\\
+	\item[initial capacity] The capacity of a dynamic a array when one item is appended to it. I denote this $\initcapacity$.\\
 	(The capacity of any dynamic array with size zero should be zero.)
@@
 
-Before I analyze the time complexity of [add], I consider a different method for measuring its cost.
-Suppose I start with an empty list and $\varnitems$ elements are added.
+Before I analyze the time complexity of [append], I consider a different method for measuring its cost.
+Suppose I start with an empty list and $\varnitems$ elements are appended.
 How many times is an element stored in an array?
-I will term the answer to this question the \textbf{write cost} of $\varnitems$ adds, and denote it $\nwritesfn(n)$.
+I will term the answer to this question the \textbf{write cost} of $\varnitems$ appends, and denote it $\nwritesfn(n)$.
 
-In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ adds.
+In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ appends.
 However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$ I need to analyze when [resize] is called.
@@
 Let $\listname$ by a dynamic array.
-As $\varnitems$ are added, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
+As $\varnitems$ are appended, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
 
 [proof]
-The capacity starts out at zero and becomes $\initcapacity$ once one element is added.
+The capacity starts out at zero and becomes $\initcapacity$ once one element is appended.
 From then on, it can only grow by a factor of $\growthfactor$ via [resize], so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
@@
 
-Each time [resize] is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ adds is
+Each time [resize] is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ appends is
 
@@
 
-Finally, adding the writes made for every item in [add], I finally find an explicit formula for $\nwritesfn(\varnitems)$.
+Finally, appending the writes made for every item in [append], I finally find an explicit formula for $\nwritesfn(\varnitems)$.
 
@@
 
-I wish to find the space allocated while adding $\varnitems$ items to a dynamic array.
-I denote this quantity $\spacefn(\varnitems)$, and define it as the total length of all arrays allocated during $\varnitems$ [add] calls.
+I wish to find the space allocated while appending $\varnitems$ items to a dynamic array.
+I denote this quantity $\spacefn(\varnitems)$, and define it as the total length of all arrays allocated during $\varnitems$ [append] calls.
 I now derive a formula for $\spacefn(\varnitems)$.
 
-From [lemma] I know the exact capacities $\listname$ takes on as $\varnitems$ items are added.
+From [lemma] I know the exact capacities $\listname$ takes on as $\varnitems$ items are appended.
 Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.

### 2017-10-16 Draft2/Appending.Growth.tex
Rename some stuff

@@
-\funarrayimpl
+\groarrayimpl
 
@@
 
-I again start off by finding the write cost when $\varnitems$ are added.
+I again start off by finding the write cost when $\varnitems$ are appended.
 I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so I can compare it to $\nwritesfn(\varnitems)$ later.
@@
 
-[That lemma] still holds, since all of the assumptions made there are also true for funnel arrays.
-In particular, although funnel arrays resize slightly differently than dynamic arrays, the following claim is still true:
+[That lemma] still holds, since all of the assumptions made there are also true for growth arrays.
+In particular, although growth arrays resize slightly differently than dynamic arrays, the following claim is still true:
 
 [other lemma]
-The capacity of a funnel array grows by a constant factor $\growthfactornew$ after the first time it is called.
+The capacity of a growth array grows by a constant factor $\growthfactornew$ after the first time it is called.
 
@@
 For the base case, consider the second time [resize] is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
-Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be added, and that is what the algorithm does.
+Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be appended, and that is what the algorithm does.
 
@@
 Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$.
-No items are being copied; the only source of writes is adding a buffer to the tail.
+No items are being copied; the only source of writes is appending a buffer to the tail.
 The goal is to find the number of writes that causes.
@@
 
-Let $k$ be the number of times the tail is added to.
+Let $k$ be the number of times the tail is appended to.
 Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since [resize] is called $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+Since [resize] is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
 Then the formula for $\nwritesresizefn(n)$ is
@@
 
-where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the funnel array). I finally conclude that
+where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the growth array). I finally conclude that
 
@@
 % Should this be C(n) instead of C?
-The space function for $\varnitems$ [add] calls on a funnel array is denoted $\spacenewfn(\varnitems)$.
-Since funnel arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.
-$\spacenewfn(\varnitems)$ is usually greater than $C$, however; this is because funnel arrays not only allocate item buffers, but stores references to them in the tail.
+The space function for $\varnitems$ [append] calls on a growth array is denoted $\spacenewfn(\varnitems)$.
+Since growth arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.
+$\spacenewfn(\varnitems)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail.
 Thus the space the tail allocates must also be determined.
 
-I determined in [...] that if $\varnitems$ are added then the tail is added to $k$ times, where $k = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+I determined in [...] that if $\varnitems$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
 Since the tail is a dynamic array, it allocates $\spacefn(k)$ space, where $\spacefn$ is the space function of the tail.

### 2017-10-16 Draft2/CopyArray.Blurb.tex
Rename some stuff

@@
 Users often want to take list structures, such as dynamic arrays, and convert them into plain arrays.
-There are multiple reasons why someone would want to do this after they are done adding to the list:
+There are multiple reasons why someone would want to do this after they are done appending to the list:
 
 \begin{itemize}
-	\item Plain arrays hold on to exactly the amount of memory needed to hold their elements. However, dynamic and funnel arrays allocate more space than necessary to optimize adding new items.
+	\item Plain arrays hold on to exactly the amount of memory needed to hold their elements. However, dynamic and growth arrays allocate more space than necessary to optimize appending new items.
 	\item The user wants to call a function in third-party code that takes a plain array as an argument.
 	\item
-	\item Plain arrays are contiguous, while funnel arrays are fragmented and have worse locality.
-	\item The indexer of funnel arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
+	\item Plain arrays are contiguous, while growth arrays are fragmented and have worse locality.
+	\item The indexer of growth arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
 \end{itemize}

### 2017-10-17 Draft2/Appending.Dynamic.tex
Fields and Properties

@@
 In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ appends.
-However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$ I need to analyze when [resize] is called.
+However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$, I need to analyze when [resize] is called.
 Consider the following lemma:

### 2017-10-17 Draft2/FieldsProperties.tex
Fields and Properties

@@
-I define some \textbf{fields} and \textbf{properties} (constant time methods that do not change state) for both types of arrays, so I may use them later to implement non-trivial methods.
+In subsequent sections, I will implement algorithms for both dynamic and growth arrays.
+In this section, I define the \textbf{fields} and \textbf{properties} these data structures are assumed to have for those algorithms.
+\textbf{Fields} are variables associated with an object that may be read from or written to.
+\textbf{Properties} are trivial, constant-time methods that do not change state.
+
+If $\listname$ is a dynamic array, then it is assumed to have the following fields:
+
+\begin{itemize}
+	\item $\listname.\FieldBuffer$ - The \textbf{buffer}, or raw array, that $\listname$ stores its items in.
+	\item $\listname.\FieldSize$ - The number of items in $\listname$.
+\end{itemize}
+
+As a dynamic array, $\listname$ is also given the following properties. $:=$ denotes a definition, as opposed to $=$ which checks equivalence. Functions that return boolean values are suffixed with ?.
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\LineComment{Returns the capacity of $\listname$}
+		\State $\listname.\FieldCapacity := \listname.\FieldBuffer.\FieldLength$
+		\State
+		\LineComment{Returns whether $\listname$ is full}
+		\State $\listname.\FieldFull := \listname.\FieldSize = \listname.\FieldCapacity$
+	\end{algorithmic}
+\end{algorithm}
+
+If $\listname$ is a growth array, then it is assumed to have the following fields:
+
+\begin{itemize}
+	\item $\listname.\FieldHead$ - The \textbf{head} of $\listname$. It returns the buffer we are currently adding items to.
+	\item $\listname.\FieldTail$ - The \textbf{tail} of $\listname$. It returns a dynamic array of buffers that have already been filled. This can be thought of as a two-dimensional array.
+	\item $\listname.\FieldSize$ - The number of items in $\listname$.
+	\item $\listname.\FieldCapacity$ - The \textbf{capacity} of $\listname$. It returns the maximum number of items $\listname$ can hold without resizing.
+\end{itemize}
+
+As a growth array, $\listname$ is also given the following properties:
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\LineComment{Returns whether $\listname$ is empty}
+		\State $\listname.\FieldEmpty := \listname.\FieldSize = 0$
+		\State
+		\LineComment{Returns whether $\listname$ is full}
+		\State $\listname.\FieldFull := \listname.\FieldSize = \listname.\FieldCapacity$
+		\State
+		\LineComment{Returns the capacity of $\FieldHead$}
+		\State $\listname.\FieldHeadCapacity := \listname.\FieldHead.\FieldLength$
+		\State
+		\LineComment{Returns the size of $\FieldHead$}
+		\LineComment{\textbf{Rationale:} $\FieldCapacity - \FieldHeadCapacity$ is the total capacity of the buffers in $\FieldTail$.}
+		\LineComment{Then, $\FieldSize - \left( \FieldCapacity - \FieldHeadCapacity \right)$ is the number of items that were added}
+		\LineComment{after depleting the buffers in $\FieldTail$.}
+		\State $\listname.\FieldHeadSize := \listname.\FieldSize - \left(\listname.\FieldCapacity - \listname.\FieldHeadCapacity\right)$
+	\end{algorithmic}
+\end{algorithm}

### 2017-10-17 Draft2/CommonOperations.Blurb.tex
Rename some stuff
[Madness] Rigorous proofs about P(f(n))

@@
-In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
+In this section, I implement common operations for dynamic and growth arrays, and analyze their time complexity. I also analyze space complexity of operations that allocate memory.
+
+In order to highlight the benefit of growth arrays, I must define a new notation for time complexity.
+The reason for this is, for certain operations, growth arrays are only better than dynamic arrays by a constant factor.
+For example, dynamic arrays might allocate roughly $2\varnitems$ memory for appending $\varnitems$ items, while growth arrays would allocate roughly $\varnitems$ memory.
+Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $\bigo(\varnitems)$.
+
+My goal is to be able to compare the coefficients of the highest-order terms in both expressions.
+For example, I would like to take the ratio $\frac{2\varnitems}{\varnitems}$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $\varnitems$.
+
+To do this, I define an alternative to big-O, which I will call "big-P notation". I define $\biggo(f(n))$ to be the class of functions $g$ such that $g(n) \to f(n)$ for large $n$. Formally,
+
+$$
+g \in \biggo(f(n)) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
+$$
+
+Like $\bigo$, $\biggo$ can be distributed and "un-distributed" over arithmetic operations. I define
+
+\begin{align*}
+\biggo(f(n)) + \biggo(g(n)) &:= \biggo(f(n) + g(n))\\
+\biggo(f(n)) - \biggo(g(n)) &:= \biggo(f(n) - g(n))\\
+\biggo(f(n)) \cdot \biggo(g(n)) &:= \biggo(f(n) \cdot g(n))\\
+\frac {\biggo(f(n))} {\biggo(g(n))} &:= \biggo\left(\frac{f(n)} {g(n)}\right)
+\end{align*}
+
+Notice that while $\bigo(2\varnitems) = \bigo(\varnitems)$, $\biggo(2\varnitems) \neq \biggo(\varnitems)$.
+However, $\biggo$ still retains some nice properties of $\bigo$.
+In particular, it eliminates lower-order terms from consideration: $\biggo(n) = \biggo(n + \log_2 n)$, for example.
+This is stated formally in the following theorem:
+
+\begin{theorem}
+\label{ScrubsLowerOrderTerms}
+	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $\biggo(f(n) + g(n)) = \biggo(f(n))$.
+\end{theorem}
+
+To prove this, we will need the following lemma.
+
+\begin{lemma}
+\label{UniqueClassOfFunctions}
+	Each function $f(n)$ has a unique class of functions under $\biggo$. That is, suppose $f \in \biggo(g(n))$ and $f \in \biggo(h(n))$. Then $\biggo(g(n)) = \biggo(h(n))$.
+\end{lemma}
+
+\begin{proof}
+	By definition, $\lim_{n \to \infty} \frac{f(n)}{g(n)} = 1$ and $\lim_{n \to \infty} \frac{f(n)}{h(n)} = 1$. Flipping the first equation and multiplying, we receive
+
+	\begin{align*}
+	\left( \lim_{n \to \infty} \frac {g(n)} {f(n)} \right) \left( \lim_{n \to \infty} \frac {f(n)} {h(n)} \right) &= 1\\
+	\lim_{n \to \infty} \frac {g(n)} {h(n)} &= 1\\
+	g &\in \biggo(h(n))
+	\end{align*}
+
+	Now, consider any $g' \in \biggo(g(n))$. Since
+
+	\begin{align*}
+	\lim_{n \to \infty} \frac {g'(n)} {g(n)} &= 1\\
+	\left( \lim_{n \to \infty} \frac {g'(n)} {g(n)} \right) \left( \lim_{n \to \infty} \frac{g(n)}{h(n)} \right) &= 1\\
+	\lim_{n \to \infty} \frac{g'(n)}{h(n)} &= 1
+	\end{align*}
+
+	it follows that $g' \in \biggo(h(n))$, and thus $\biggo(g(n)) \subseteq \biggo(h(n))$.
+By a similar argument, it can be shown $\biggo(h(n)) \subseteq \biggo(g(n))$.
+Thus it must be true that $\biggo(g(n)) = \biggo(h(n))$.
+\end{proof}
+
+Now \ref{ScrubsLowerOrderTerms} can be proved as follows:
+
+\begin{proof}
+	\begin{align*}
+		\lim_{n \to \infty} \frac{f(n) + g(n)}{f(n)} &= \lim_{n \to \infty} \frac{f(n)}{f(n)} + \lim_{n \to \infty}\\ \frac{g(n)}{f(n)}\\
+		&= 1 + 0\\
+		&= 1
+	\end{align*}
+
+	Then $f(n) + g(n) \in \biggo(f(n))$. Since it is also true that $f(n) + g(n) \in \biggo(f(n) + g(n))$, it follows from \ref{UniqueClassOfFunctions} that $\biggo(f(n)) = \biggo(f(n) + g(n))$.
+\end{proof}
 
@@
 
-\begin{description}
-	\item[$\biggo(f(n))$] This is an alternative to big-O notation that I will name "big-P notation".
+\begin{itemize}
+	\item $\biggo(f(n))$ - This is an alternative to big-O notation that I will name "big-P notation".
 It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
@@
 	More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
-\end{description}
+\end{itemize}

### 2017-10-17 Draft2/CommonOperations.Blurb.tex
Remove stuff

@@
 \end{proof}
-
-The following mathematical definitions will be used while analyzing time and space complexity:
-
-\begin{itemize}
-	\item $\biggo(f(n))$ - This is an alternative to big-O notation that I will name "big-P notation".
-It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
-For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
-This makes it possible to compare two time complexities, if their ratio tends to a constant for large $n$.\\
-	More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
-\end{itemize}

### 2017-10-17 Draft2/Abstract.tex
Add the abstract

This paper introduces the \textbf{growth array}, an array-like data structure designed to be efficient at appending elements. They offer substantial time and memory savings over dynamic arrays when a large number of elements are appended. Growth arrays also support other list operations, such as random access, iteration, and insertion/deletion at an index. However, they perform no better, or slightly worse, than dynamic arrays for those methods. Also, if the size of the data is known beforehand, allocating a raw array with that size and appending to it is faster than appending to a growth array.

### 2017-10-17 Draft2/Intro.tex
Add the intro

In imperative languages, the dynamic array is the most common data structure used by programs\footnote{}. People often want to add multiple items to a list and then iterate it, which dynamic arrays make simple and efficient. But can it be said dynamic arrays have the \textit{most} efficient algorithm for this pattern?

In this paper, I introduce an alternative data structure to the dynamic array, called the \textbf{growth array}. It is more efficient than the dynamic array at appending, particularly for large numbers of items. This is due to how it 'grows' once it cannot fit any more items in its buffer.

When dynamic arrays run out of space, they allocate a new buffer, copy the contents of the old one into it, and throw the old one away. However, growth arrays are less wasteful. Instead of throwing away the filled buffer, they keep it a part of the data structure. The new buffer they allocate represents a continuation of the items from the old buffer. For example, if the old buffer contained items $0-31$, the new buffer would contain items $32$ and beyond. Because of this, growth arrays allocate less memory to store the same number of items, and they do not need to copy items from the old buffer to the new one.

Growth arrays have some caveats, however. They perform no better, or slightly worse, than dynamic arrays with respect to other operations. In particular, random access involves significantly more instructions than it does for dynamic arrays. Additionally, since growth arrays are not contiguous in memory, they may have poorer locality than dynamic arrays, and cannot be passed to external code that accepts contiguous buffers.

It is also worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are completely unnecessary. A raw array could simply be allocated with the known size, and items could be appended more quickly to it. Thus, growth arrays are only advantageous for scenarios where an unknown amount of data will be appended.

### 2017-10-18 Draft2/Appendix.tex
Add an appendix, a new section

--- 2017-10-16 Draft2/CommonOperations.Blurb.tex
@@
-In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
+\appendix
+\appendixpage
 
-The following mathematical definitions will be used while analyzing time and space complexity:
+\section{Proofs of Properties of Big-P Notation}
 
-\begin{description}
-	\item[$\biggo(f(n))$] This is an alternative to big-O notation that I will name "big-P notation".
-It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
-For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
-This makes it possible to compare two time complexities, if their ratio tends to a constant for large $n$.\\
-	More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
-\end{description}
+\subsection{Merging over Arithmetic Operations}
+\label{MergingOverArithmetic}
+
+\begin{theorem}
+	$\biggo$ merges over addition and subtraction. That is,
+	\begin{align*}
+	\biggo(f(n)) + \biggo(g(n)) &= \biggo(f(n) + g(n))\\
+	\biggo(f(n)) - \biggo(g(n)) &= \biggo(f(n) - g(n))
+	\end{align*}
+\end{theorem}
+
+\begin{theorem}
+	$\biggo$ merges over multiplication and division. That is,
+	\begin{align*}
+	\biggo(f(n)) \cdot \biggo(g(n)) &= \biggo(f(n) \cdot g(n))\\
+	\frac {\biggo(f(n))} {\biggo(g(n))} &= \biggo\left(\frac{f(n)} {g(n)}\right)
+	\end{align*}
+\end{theorem}
+
+\subsection{Unique Class Lemma}
+\label{UniqueClassOfFunctions}
+
+\begin{lemma}
+	Each function $f(n)$ has a unique class of functions under $\biggo$. That is, suppose $f \in \biggo(g(n))$ and $f \in \biggo(h(n))$. Then $\biggo(g(n)) = \biggo(h(n))$.
+\end{lemma}
+
+\begin{proof}
+	By definition, $\lim_{n \to \infty} \frac{f(n)}{g(n)} = 1$ and $\lim_{n \to \infty} \frac{f(n)}{h(n)} = 1$. Flipping the first equation and multiplying, we receive
+
+	\begin{align*}
+	\left( \lim_{n \to \infty} \frac {g(n)} {f(n)} \right) \left( \lim_{n \to \infty} \frac {f(n)} {h(n)} \right) &= 1\\
+	\lim_{n \to \infty} \frac {g(n)} {h(n)} &= 1\\
+	g &\in \biggo(h(n))
+	\end{align*}
+
+	Now, consider any $g' \in \biggo(g(n))$. Since
+
+	\begin{align*}
+	\lim_{n \to \infty} \frac {g'(n)} {g(n)} &= 1\\
+	\left( \lim_{n \to \infty} \frac {g'(n)} {g(n)} \right) \left( \lim_{n \to \infty} \frac{g(n)}{h(n)} \right) &= 1\\
+	\lim_{n \to \infty} \frac{g'(n)}{h(n)} &= 1
+	\end{align*}
+
+	it follows that $g' \in \biggo(h(n))$, and thus $\biggo(g(n)) \subseteq \biggo(h(n))$.
+By a similar argument, it can be shown $\biggo(h(n)) \subseteq \biggo(g(n))$.
+Thus it must be true that $\biggo(g(n)) = \biggo(h(n))$.
+\end{proof}
+
+\subsection{Removal of Lower-Order Terms}
+\label{ScrubsLowerOrderTerms}
+
+\begin{theorem}
+	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $\biggo(f(n) + g(n)) = \biggo(f(n))$.
+\end{theorem}
+
+\begin{proof}
+	\begin{align*}
+	\lim_{n \to \infty} \left( \frac{f(n) + g(n)}{f(n)} \right) &= \lim_{n \to \infty} \frac{f(n)}{f(n)} + \lim_{n \to \infty} \frac{g(n)}{f(n)}\\
+	&= 1 + 0\\
+	&= 1
+	\end{align*}
+
+	Then $f(n) + g(n) \in \biggo(f(n))$. Since it is also true that $f(n) + g(n) \in \biggo(f(n) + g(n))$, it follows from \ref{UniqueClassOfFunctions} that $\biggo(f(n)) = \biggo(f(n) + g(n))$.
+\end{proof}

### 2017-10-18 Draft2/BigPNotation.tex
Add an appendix, a new section

\subsection{Motivation}

In order to highlight the benefit of growth arrays, I will define a new notation for time complexity. The reason for this is, for certain operations, growth arrays are only better than dynamic arrays by a constant factor. For example, dynamic arrays might allocate roughly $2\varnitems$ memory for appending $\varnitems$ items, while growth arrays would allocate roughly $\varnitems$ memory. Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $\bigo(\varnitems)$.

My goal is to be able to compare the coefficients of the highest-order terms in both expressions. For example, I would like to take the ratio $\frac{2\varnitems}{\varnitems}$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $\varnitems$. However, big-O notation does not support this.

\subsection{Definition}

I define an alternative to big-O notation, which I will call \textbf{big-P notation}. I define $\biggo(f(n))$ to be the class of functions $g$ such that $g(n) \to f(n)$ for large $n$. Formally,

$$
g \in \biggo(f(n)) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
$$

Notice that while $\bigo(2\varnitems) = \bigo(\varnitems)$, $\biggo(2\varnitems) \neq \biggo(\varnitems)$. Thus, $\biggo$ makes it possible to distinguish between a function that uses $\varnitems$ space and one that uses $2\varnitems$ space. \textbf{Note:} A consequence of this is that bases for logarithms must be specified in big-P notation.

\subsection{Properties}

\textbf{Note:} Throughout this paper, when $\biggo(f(n))$ or $\bigo(f(n))$ is used in an arithmetic expression, I am referring to a function in the set and not the set itself. For example, the verbal equivalent of $\frac{\biggo(2n)}{\biggo(n)} = \biggo(2)$ states "the quotient of a function in $\biggo(2n)$ and a function in $\biggo(n)$ is equal to a function in $\biggo(2)$."

A useful property $\biggo$ shares with $\bigo$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{MergingOverArithmetic}.

\begin{theorem}
	$\biggo$ merges over addition and subtraction. That is,
	\begin{align*}
	\biggo(f(n)) + \biggo(g(n)) &= \biggo(f(n) + g(n))\\
	\biggo(f(n)) - \biggo(g(n)) &= \biggo(f(n) - g(n))
	\end{align*}
\end{theorem}

\begin{theorem}
	$\biggo$ merges over multiplication and division. That is,
	\begin{align*}
	\biggo(f(n)) \cdot \biggo(g(n)) &= \biggo(f(n) \cdot g(n))\\
	\frac {\biggo(f(n))} {\biggo(g(n))} &= \biggo\left(\frac{f(n)} {g(n)}\right)
	\end{align*}
\end{theorem}

Another nice property $\biggo$ and $\bigo$ have in common is that lower-order terms are removed from consideration. For example, $\biggo(n) = \biggo(n + \log_2 n)$. This is stated by the below theorem, which is proved in \ref{ScrubsLowerOrderTerms}.

\begin{theorem}
	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $\biggo(f(n) + g(n)) = \biggo(f(n))$.
\end{theorem}

### 2017-10-18 Draft2/CommonOperations.Blurb.tex
Add an appendix, a new section

--- 2017-10-16 Draft2/CommonOperations.Blurb.tex
@@
-In this section, I implement and analyze common operations for dynamic and funnel arrays. I compare both implementations' time complexities, and space complexities if the operation allocates memory.
-
-The following mathematical definitions will be used while analyzing time and space complexity:
-
-\begin{description}
-	\item[$\biggo(f(n))$] This is an alternative to big-O notation that I will name "big-P notation".
-It is similar to big-O, but it preserves the coefficient of the fastest-growing term in $f(n)$.
-For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$.
-This makes it possible to compare two time complexities, if their ratio tends to a constant for large $n$.\\
-	More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
-\end{description}
+In this section, I implement common operations for dynamic and growth arrays, and analyze their time complexity. I also analyze space complexity of operations that allocate memory.

### 2017-10-18 Draft2/Appendix.tex
Add proofs for big-P properties

@@
 
+\begin{proof}
+	We will consider the statement about addition first. Recall from the note at \ref{BigPProperties} that this statement is equivalent to:
+
+	\textit{Let $f' \in \biggo(f(n))$ and $g' \in \biggo(g(n))$. Then $f' + g' \in \biggo(f(n) + g(n))$.}
+
+	We can show this by using the limit definition of $\biggo$. For brevity, we will omit the parameter $n$ to each function. Since
+
+	\begin{align*}
+	\lim_{n \to \infty} \left( \frac{f' + g'}{f + g} \right) &= \lim_{n \to \infty} \left( \frac{f'}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g'}{f + g} \right)\\
+	&= \left( \lim_{n \to \infty} \frac{f'}{f} \right) \left( \lim_{n \to \infty} \left( \frac{f}{f + g} \right) \right) +\\
+	&\ \ \ \ \left( \lim_{n \to \infty} \frac{g'}{g} \right) \left( \lim_{n \to \infty} \left( \frac{g}{f + g} \right) \right)\\
+	&= \lim_{n \to \infty} \left( \frac{f}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g}{f + g} \right)\\
+	&= \lim_{n \to \infty} \left( \frac{f + g}{f + g} \right)\\
+	&= 1
+	\end{align*}
+
+	it follows that $f' + g' \in \biggo(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
+\end{proof}
+
 \begin{theorem}
@@
 	\begin{align*}
-	\biggo(f(n)) \cdot \biggo(g(n)) &= \biggo(f(n) \cdot g(n))\\
+	\biggo(f(n))\biggo(g(n)) &= \biggo(f(n)g(n))\\
 	\frac {\biggo(f(n))} {\biggo(g(n))} &= \biggo\left(\frac{f(n)} {g(n)}\right)
@@
 \end{theorem}
+
+\begin{proof}
+	We will consider the statement about multiplication first. Recall from the note at \ref{BigPProperties} that this statement is equivalent to:
+
+	\textit{Let $f' \in \biggo(f(n))$ and $g' \in \biggo(g(n))$. Then $f'g' \in \biggo(f(n)g(n))$.}
+
+	We can show this easily by multiplying the limits corresponding to $f'$ and $g'$:
+
+	\begin{align*}
+	\lim_{n \to \infty} \frac{f'(n)}{f(n)} &= 1\\
+	\lim_{n \to \infty} \frac{g'(n)}{g(n)} &= 1\\
+	\left( \lim_{n \to \infty} \frac{f'(n)}{f(n)} \right) \left( \lim_{n \to \infty} \frac{g'(n)}{g(n)} \right) &= 1 \cdot 1\\
+	\lim_{n \to \infty} \frac{f'(n)g'(n)}{f(n)g(n)} &= 1
+	\end{align*}
+
+	it follows that $f'g' \in \biggo(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $g'$ before multiplying, resulting in
+
+	\begin{align*}
+	\lim_{n \to \infty} \frac{f'(n) / g'(n)}{f(n) / g(n)} = 1
+	\end{align*}
+
+	This implies $f' / g' \in \biggo(f(n) / g(n))$.
+\end{proof}
 

### 2017-10-18 Draft2/FieldsProperties.tex
Wording
Add constructor code

@@
 In subsequent sections, I will implement algorithms for both dynamic and growth arrays.
-In this section, I define the \textbf{fields} and \textbf{properties} these data structures are assumed to have for those algorithms.
+In this section, I define fields and properties for these data structures which the algorithms will use.
 \textbf{Fields} are variables associated with an object that may be read from or written to.
@@
 		\State $\listname.\FieldFull := \listname.\FieldSize = \listname.\FieldCapacity$
+	\end{algorithmic}
+\end{algorithm}
+
+When a dynamic array is instantiated, the following code should run:
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\State $\listname.\FieldBuffer \gets \FuncNewArray(0)$
+		\State $\listname.\FieldSize \gets 0$
 	\end{algorithmic}
@@
 \end{algorithm}
+
+When a growth array is instantiated, the following code should run:
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\State $\listname.\FieldHead \gets \FuncNewArray(0)$
+		\State $\listname.\FieldTail \gets \FuncNewDynamicArray()$
+		\State $\listname.\FieldSize \gets 0$
+		\State $\listname.\FieldCapacity \gets 0$
+	\end{algorithmic}
+\end{algorithm}

### 2017-10-18 Draft2/Appending.Dynamic.tex
Add constructor code
Algorithm for Append
Initial Grow impl
Rename some things and remove some brackets

--- 2017-10-16 Draft2/Appending.Dynamic.tex
@@
 	(The capacity of any dynamic array with size zero should be zero.)
-	\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\listname$ is resized. I denote this with $\growthfactor$.
+	\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\listname$ grows. I denote this with $\growthfactor$.
 \end{description}
 
-% impl.
+\begin{algorithm}
+	\begin{algorithmic}[1]
+		\Procedure{$\FuncAppend$}{$L, item$}
+			\If{$\listname.\FieldFull$}
+				\State $\listname.\FuncGrow()$
+			\EndIf
+
+			\State $\listname.\FieldHead[\listname.\FieldHeadSize] \gets item$
+			\State $\listname.\FieldSize \gets \listname.\FieldSize + 1$
+		\EndProcedure
+		\Statex
+		\Procedure{$\FuncGrow$}{$L$}
+			\If{$\listname.\FieldEmpty$}
+				\State $\listname.\FieldBuffer \gets \FuncNewArray(\initcapacity)$
+			\Else
+				\State $new\ buf \gets \FuncNewArray(\listname.\FieldSize \cdot \growthfactor)$
+				\State $\FuncArrayCopy(source: \listname.\FieldBuffer, dest: new\ buf, len: \listname.\FieldSize)$
+				\State $\listname.\FieldBuffer \gets new\ buf$
+			\EndIf
+		\EndProcedure
+	\end{algorithmic}
+\end{algorithm}
 
@@
 
-Before I analyze the time complexity of [append], I consider a different method for measuring its cost.
+Before I analyze the time complexity of $\FuncAppend$, I consider a different method for measuring its cost.
 Suppose I start with an empty list and $\varnitems$ elements are appended.
@@
 In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ appends.
-However, [resize] also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$ I need to analyze when [resize] is called.
+However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$, I need to analyze when $\FuncGrow$ is called.
 Consider the following lemma:
@@
 The capacity starts out at zero and becomes $\initcapacity$ once one element is appended.
-From then on, it can only grow by a factor of $\growthfactor$ via [resize], so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
+From then on, it can only grow by a factor of $\growthfactor$ via $\FuncGrow$, so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
 By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$.
@@
 [make lemma]
-Now, consider that to grow by $\growthfactor$ [resize] must be called.
-So $\growthfactor^k\initcapacity$ being present in $S_C$ means [resize] was called at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
-Then [resize] was called at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
+Now, consider that to grow by $\growthfactor$, $\FuncGrow$ must be called.
+So $\growthfactor^k\initcapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
+Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
 
-Each time [resize] is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ appends is
+Each time $\FuncGrow$ is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ appends is
 
@@
 
-Finally, appending the writes made for every item in [append], I finally find an explicit formula for $\nwritesfn(\varnitems)$.
+Finally, appending the writes made for every item in $\FuncAppend$, I finally find an explicit formula for $\nwritesfn(\varnitems)$.
 
@@
 I wish to find the space allocated while appending $\varnitems$ items to a dynamic array.
-I denote this quantity $\spacefn(\varnitems)$, and define it as the total length of all arrays allocated during $\varnitems$ [append] calls.
+I denote this quantity $\spacefn(\varnitems)$, and define it as the total length of all arrays allocated during $\varnitems$ $\FuncAppend$ calls.
 I now derive a formula for $\spacefn(\varnitems)$.

### 2017-10-18 Draft2/Appending.Growth.tex
Rename some things and remove some brackets

@@
 [That lemma] still holds, since all of the assumptions made there are also true for growth arrays.
-In particular, although growth arrays resize slightly differently than dynamic arrays, the following claim is still true:
+In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:
 
@@
 
-For the base case, consider the second time [resize] is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
+For the base case, consider the second time $\FuncGrow$ is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
 Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be appended, and that is what the algorithm does.
@@
 
-Now I take a look at [resize].
+Now I take a look at $\FuncGrow$.
 Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$.
@@
 
-Let $\nwritesresizefn(n)$ denote the total number of writes made by [resize]. From [make lemma], I know that [resize] is called at the sizes
+Let $\nwritesgrowfn(n)$ denote the total number of writes made by $\FuncGrow$. From [make lemma], I know that $\FuncGrow$ is called at the sizes
 
@@
 Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since [resize] is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
-Then the formula for $\nwritesresizefn(n)$ is
+Since $\FuncGrow$ is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+Then the formula for $\nwritesgrowfn(n)$ is
 
 $$
-\nwritesresizefn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+\nwritesgrowfn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
 $$
@@
 % Should this be C(n) instead of C?
-The space function for $\varnitems$ [append] calls on a growth array is denoted $\spacenewfn(\varnitems)$.
+The space function for $\varnitems$ $\FuncAppend$ calls on a growth array is denoted $\spacenewfn(\varnitems)$.
 Since growth arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.

### 2017-10-18 Draft2/Appending.Dynamic.tex
Proof-ize some things

@@
 
-[lemma]
+\begin{lemma}
+\label{CapacitySequence}
 	Let $\listname$ by a dynamic array.
-As $\varnitems$ are appended, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
+As $\varnitems$ items are appended, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
+\end{lemma}
 
-[proof]
+\begin{proof}
 	The capacity starts out at zero and becomes $\initcapacity$ once one element is appended.
@@
 	Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.
+\end{proof}
 
@@
 
-From [lemma] I know the exact capacities $\listname$ takes on as $\varnitems$ items are appended.
+From \ref{CapacitySequence} I know the exact capacities $\listname$ takes on as $\varnitems$ items are appended.
 Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.

### 2017-10-18 Draft2/Appending.Growth.tex
Proof-ize some things

@@
 
-[That lemma] still holds, since all of the assumptions made there are also true for growth arrays.
+\ref{CapacitySequence} still holds, since all of the assumptions made there are also true for growth arrays.
 In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:
 
-[other lemma]
+\begin{lemma}
 	The capacity of a growth array grows by a constant factor $\growthfactornew$ after the first time it is called.
+\end{lemma}
 
-[proof]
+\begin{proof}
 	I prove that the algorithm ensures this using induction.
@@
 The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
+\end{proof}
 

### 2017-10-18 Draft2/Appending.Growth.tex
Rename some commands to PascalCase
More casing
Hard-code O and P

@@
-\groarrayimpl
+\HdrGrowthArrayImpl
 
-\tcomplex
+\HdrTimeComplex
 
@@
 k &= \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil\\
-\bigo(k) &= \bigo(\log \varnitems)
+O(k) &= O(\log \varnitems)
 \end{align*}
 
-Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\nwritesnewfn(\varnitems)$, leaving just $\biggo(\varnitems)$:
+Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\nwritesnewfn(\varnitems)$, leaving just $P(\varnitems)$:
 
 \begin{align*}
-\biggo(\nwritesnewfn(\varnitems)) &= \biggo(\varnitems + \nwritesfn(k))\\
-&= \biggo(\varnitems) + \biggo(\nwritesfn(k))\\
-&= \biggo(\varnitems) + \bigo(\log \varnitems)\\
-&= \biggo(\varnitems)
+P(\nwritesnewfn(\varnitems)) &= P(\varnitems + \nwritesfn(k))\\
+&= P(\varnitems) + P(\nwritesfn(k))\\
+&= P(\varnitems) + O(\log \varnitems)\\
+&= P(\varnitems)
 \end{align*}
 
-\scomplex
+\HdrSpaceComplex
 
@@
 Since the tail is a dynamic array, it allocates $\spacefn(k)$ space, where $\spacefn$ is the space function of the tail.
-Through a similar method to [...] it can be shown $\bigo(\spacefn(k)) = \bigo(k) = \bigo(\log \varnitems)$.
+Through a similar method to [...] it can be shown $O(\spacefn(k)) = O(k) = O(\log \varnitems)$.
 Then % TODO: P-analysis should come after the explicit formula.
@@
 \begin{align*}
-\spacenewfn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
+\spacenewfn(\varnitems) = P(2^{\lceil \log_2 \varnitems \rceil}) = O(\varnitems)
 \end{align*}

### 2017-10-18 Draft2/Appendix.tex
Hard-code O and P

@@
 \begin{theorem}
-	$\biggo$ merges over addition and subtraction. That is,
+	$P$ merges over addition and subtraction. That is,
 	\begin{align*}
-	\biggo(f(n)) + \biggo(g(n)) &= \biggo(f(n) + g(n))\\
-	\biggo(f(n)) - \biggo(g(n)) &= \biggo(f(n) - g(n))
+	P(f(n)) + P(g(n)) &= P(f(n) + g(n))\\
+	P(f(n)) - P(g(n)) &= P(f(n) - g(n))
 	\end{align*}
@@
 
-	\textit{Let $f' \in \biggo(f(n))$ and $g' \in \biggo(g(n))$. Then $f' + g' \in \biggo(f(n) + g(n))$.}
+	\textit{Let $f' \in P(f(n))$ and $g' \in P(g(n))$. Then $f' + g' \in P(f(n) + g(n))$.}
 
-	We can show this by using the limit definition of $\biggo$. For brevity, we will omit the parameter $n$ to each function. Since
+	We can show this by using the limit definition of $P$. For brevity, we will omit the parameter $n$ to each function. Since
 
@@
 
-	it follows that $f' + g' \in \biggo(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
+	it follows that $f' + g' \in P(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
 \end{proof}
@@
 \begin{theorem}
-	$\biggo$ merges over multiplication and division. That is,
+	$P$ merges over multiplication and division. That is,
 	\begin{align*}
-	\biggo(f(n))\biggo(g(n)) &= \biggo(f(n)g(n))\\
-	\frac {\biggo(f(n))} {\biggo(g(n))} &= \biggo\left(\frac{f(n)} {g(n)}\right)
+	P(f(n))P(g(n)) &= P(f(n)g(n))\\
+	\frac {P(f(n))} {P(g(n))} &= P\left(\frac{f(n)} {g(n)}\right)
 	\end{align*}
@@
 
-	\textit{Let $f' \in \biggo(f(n))$ and $g' \in \biggo(g(n))$. Then $f'g' \in \biggo(f(n)g(n))$.}
+	\textit{Let $f' \in P(f(n))$ and $g' \in P(g(n))$. Then $f'g' \in P(f(n)g(n))$.}
 
@@
 
-	it follows that $f'g' \in \biggo(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $g'$ before multiplying, resulting in
+	it follows that $f'g' \in P(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $g'$ before multiplying, resulting in
 
@@
 
-	This implies $f' / g' \in \biggo(f(n) / g(n))$.
+	This implies $f' / g' \in P(f(n) / g(n))$.
 \end{proof}
@@
 \begin{lemma}
-	Each function $f(n)$ has a unique class of functions under $\biggo$. That is, suppose $f \in \biggo(g(n))$ and $f \in \biggo(h(n))$. Then $\biggo(g(n)) = \biggo(h(n))$.
+	Each function $f(n)$ has a unique class of functions under $P$. That is, suppose $f \in P(g(n))$ and $f \in P(h(n))$. Then $P(g(n)) = P(h(n))$.
 \end{lemma}
@@
 	\lim_{n \to \infty} \frac {g(n)} {h(n)} &= 1\\
-	g &\in \biggo(h(n))
+	g &\in P(h(n))
 	\end{align*}
 
-	Now, consider any $g' \in \biggo(g(n))$. Since
+	Now, consider any $g' \in P(g(n))$. Since
 
@@
 
-	it follows that $g' \in \biggo(h(n))$, and thus $\biggo(g(n)) \subseteq \biggo(h(n))$.
-By a similar argument, it can be shown $\biggo(h(n)) \subseteq \biggo(g(n))$.
-Thus it must be true that $\biggo(g(n)) = \biggo(h(n))$.
+	it follows that $g' \in P(h(n))$, and thus $P(g(n)) \subseteq P(h(n))$. By a similar argument, it can be shown $P(h(n)) \subseteq P(g(n))$. Thus it must be true that $P(g(n)) = P(h(n))$.
 \end{proof}
@@
 \begin{theorem}
-	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $\biggo(f(n) + g(n)) = \biggo(f(n))$.
+	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $P(f(n) + g(n)) = P(f(n))$.
 \end{theorem}
@@
 
-	Then $f(n) + g(n) \in \biggo(f(n))$. Since it is also true that $f(n) + g(n) \in \biggo(f(n) + g(n))$, it follows from \ref{UniqueClassOfFunctions} that $\biggo(f(n)) = \biggo(f(n) + g(n))$.
+	Then $f(n) + g(n) \in P(f(n))$. Since it is also true that $f(n) + g(n) \in P(f(n) + g(n))$, it follows from \ref{UniqueClassOfFunctions} that $P(f(n)) = P(f(n) + g(n))$.
 \end{proof}

### 2017-10-18 Draft2/BigPNotation.tex
Add proofs for big-P properties
Hard-code O and P

@@
 For example, dynamic arrays might allocate roughly $2\varnitems$ memory for appending $\varnitems$ items, while growth arrays would allocate roughly $\varnitems$ memory.
-Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $\bigo(\varnitems)$.
+Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $O(\varnitems)$.
 
@@
 
-I define an alternative to big-O notation, which I will call \textbf{big-P notation}. I define $\biggo(f(n))$ to be the class of functions $g$ such that $g(n) \to f(n)$ for large $n$. Formally,
+I define an alternative to big-O notation, which I will call \textbf{big-P notation}. I define $P(f(n))$ to be the class of functions $g$ such that $g(n) \to f(n)$ for large $n$. Formally,
 
 $$
-g \in \biggo(f(n)) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
+g \in P(f(n)) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
 $$
 
-Notice that while $\bigo(2\varnitems) = \bigo(\varnitems)$, $\biggo(2\varnitems) \neq \biggo(\varnitems)$.
-Thus, $\biggo$ makes it possible to distinguish between a function that uses $\varnitems$ space and one that uses $2\varnitems$ space.
+Notice that while $O(2\varnitems) = O(\varnitems)$, $P(2\varnitems) \neq P(\varnitems)$.
+Thus, $P$ makes it possible to distinguish between a function that uses $\varnitems$ space and one that uses $2\varnitems$ space.
 \textbf{Note:} A consequence of this is that bases for logarithms must be specified in big-P notation.
@@
 \subsection{Properties}
+\label{BigPProperties}
 
-\textbf{Note:} Throughout this paper, when $\biggo(f(n))$ or $\bigo(f(n))$ is used in an arithmetic expression, I am referring to a function in the set and not the set itself.
-For example, the verbal equivalent of $\frac{\biggo(2n)}{\biggo(n)} = \biggo(2)$ states "the quotient of a function in $\biggo(2n)$ and a function in $\biggo(n)$ is equal to a function in $\biggo(2)$."
+\textbf{Note:} Throughout this paper, when $P(f(n))$ or $O(f(n))$ is used in an arithmetic expression, I am referring to a function in the set and not the set itself.
+For example, the verbal equivalent of $\frac{P(2n)}{P(n)} = P(2)$ states "the quotient of a function in $P(2n)$ and a function in $P(n)$ is equal to a function in $P(2)$."
 
-A useful property $\biggo$ shares with $\bigo$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{MergingOverArithmetic}.
+A useful property $P$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{MergingOverArithmetic}.
 
 \begin{theorem}
-	$\biggo$ merges over addition and subtraction. That is,
+	$P$ merges over addition and subtraction. That is,
 	\begin{align*}
-	\biggo(f(n)) + \biggo(g(n)) &= \biggo(f(n) + g(n))\\
-	\biggo(f(n)) - \biggo(g(n)) &= \biggo(f(n) - g(n))
+	P(f(n)) + P(g(n)) &= P(f(n) + g(n))\\
+	P(f(n)) - P(g(n)) &= P(f(n) - g(n))
 	\end{align*}
@@
 \begin{theorem}
-	$\biggo$ merges over multiplication and division. That is,
+	$P$ merges over multiplication and division. That is,
 	\begin{align*}
-	\biggo(f(n)) \cdot \biggo(g(n)) &= \biggo(f(n) \cdot g(n))\\
-	\frac {\biggo(f(n))} {\biggo(g(n))} &= \biggo\left(\frac{f(n)} {g(n)}\right)
+	P(f(n))P(g(n)) &= P(f(n)g(n))\\
+	\frac {P(f(n))} {P(g(n))} &= P\left(\frac{f(n)} {g(n)}\right)
 	\end{align*}
@@
 
-Another nice property $\biggo$ and $\bigo$ have in common is that lower-order terms are removed from consideration.
-For example, $\biggo(n) = \biggo(n + \log_2 n)$.
+Another nice property $P$ and $O$ have in common is that lower-order terms are removed from consideration.
+For example, $P(n) = P(n + \log_2 n)$.
 This is stated by the below theorem, which is proved in \ref{ScrubsLowerOrderTerms}.

### 2017-10-18 Draft2/CopyArray.Blurb.tex
Rename some commands to PascalCase
Hard-code O and P

@@
-\descriptn
+\HdrDescription
 
@@
 	\item Plain arrays are contiguous, while growth arrays are fragmented and have worse locality.
-	\item The indexer of growth arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
+	\item The indexer of growth arrays is several times slower than that of plain arrays, whether the $O(1)$ or $O(\log \varnitems)$ implementation is chosen.
 \end{itemize}

### 2017-10-18 Draft2/Appending.Dynamic.tex
Rename some commands to PascalCase
More casing
Hard-code O and P
Renaming variables

--- 2017-10-18 Draft2/Appending.Dynamic.tex
@@
-\dynarrayimpl
+\HdrDynArrayImpl
 
-I will first implement appending for dynamic arrays. Let $\listname$ be a dynamic array. The following definitions are used in the code:
+I will first implement appending for dynamic arrays. Let $\ListName$ be a dynamic array. The following definitions are used in the code:
 
 \begin{description}
-	\item[initial capacity] The capacity of a dynamic a array when one item is appended to it. I denote this $\initcapacity$.\\
+	\item[initial capacity] The capacity of a dynamic a array when one item is appended to it. I denote this $\InitCapacity$.\\
 	(The capacity of any dynamic array with size zero should be zero.)
-	\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\listname$ grows. I denote this with $\growthfactor$.
+	\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\ListName$ grows. I denote this with $\GrowthFactor$.
 \end{description}
@@
 		\Procedure{$\FuncAppend$}{$L, item$}
-			\If{$\listname.\FieldFull$}
-				\State $\listname.\FuncGrow()$
+			\If{$\ListName.\FieldFull$}
+				\State $\ListName.\FuncGrow()$
 			\EndIf
 
-			\State $\listname.\FieldHead[\listname.\FieldHeadSize] \gets item$
-			\State $\listname.\FieldSize \gets \listname.\FieldSize + 1$
+			\State $\ListName.\FieldHead[\ListName.\FieldHeadSize] \gets item$
+			\State $\ListName.\FieldSize \gets \ListName.\FieldSize + 1$
 		\EndProcedure
@@
 		\Procedure{$\FuncGrow$}{$L$}
-			\If{$\listname.\FieldEmpty$}
-				\State $\listname.\FieldBuffer \gets \FuncNewArray(\initcapacity)$
+			\If{$\ListName.\FieldEmpty$}
+				\State $\ListName.\FieldBuffer \gets \FuncNewArray(\InitCapacity)$
 			\Else
-				\State $new\ buf \gets \FuncNewArray(\listname.\FieldSize \cdot \growthfactor)$
-				\State $\FuncArrayCopy(source: \listname.\FieldBuffer, dest: new\ buf, len: \listname.\FieldSize)$
-				\State $\listname.\FieldBuffer \gets new\ buf$
+				\State $new\ buf \gets \FuncNewArray(\ListName.\FieldSize \cdot \GrowthFactor)$
+				\State $\FuncArrayCopy(source: \ListName.\FieldBuffer, dest: new\ buf, len: \ListName.\FieldSize)$
+				\State $\ListName.\FieldBuffer \gets new\ buf$
 			\EndIf
@@
 
-\tcomplex
+\HdrTimeComplex
 
@@
 
-[lemma]
-Let $\listname$ by a dynamic array.
-As $\varnitems$ are appended, the sequence of capacities $\listname$ takes on is $$S_C = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$$.
+\begin{lemma}
+\label{CapacitySequence}
+	Let $\ListName$ by a dynamic array.
+As $\varnitems$ items are appended, the sequence of capacities $\ListName$ takes on is $$S_C = 0,\ \InitCapacity,\ \GrowthFactor\InitCapacity,\ \GrowthFactor^2\InitCapacity,\ \ldots\ \GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity$$.
+\end{lemma}
 
-[proof]
-The capacity starts out at zero and becomes $\initcapacity$ once one element is appended.
-From then on, it can only grow by a factor of $\growthfactor$ via $\FuncGrow$, so if $\growthfactor^i\initcapacity$ is the current capacity then $\growthfactor^{i + 1}\initcapacity$ must be the next capacity.
-By induction, the rest of the sequence is $$\left\{ \growthfactor^i\initcapacity \right\}_{i = 1}^k$$ for some $k$.
-Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\growthfactor^k\initcapacity \geq \varnitems$.
+\begin{proof}
+	The capacity starts out at zero and becomes $\InitCapacity$ once one element is appended.
+From then on, it can only grow by a factor of $\GrowthFactor$ via $\FuncGrow$, so if $\GrowthFactor^i\InitCapacity$ is the current capacity then $\GrowthFactor^{i + 1}\InitCapacity$ must be the next capacity.
+By induction, the rest of the sequence is $$\left\{ \GrowthFactor^i\InitCapacity \right\}_{i = 1}^k$$ for some $k$.
+Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\GrowthFactor^k\InitCapacity \geq \varnitems$.
 Using this property, I now derive $k$.
@@
 	\begin{align*}
-\growthfactor^k\initcapacity &\geq \varnitems\\
-\growthfactor^k &\geq \frac{\varnitems}{\initcapacity}\\
-k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity\\
-k &\geq \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity > k - 1\\
-k &= \big\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \big\rceil
+	\GrowthFactor^k\InitCapacity &\geq \varnitems\\
+	\GrowthFactor^k &\geq \frac{\varnitems}{\InitCapacity}\\
+	k &\geq \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity\\
+	k &\geq \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity > k - 1\\
+	k &= \big\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \big\rceil
 	\end{align*}
 
-Then the final term in the sequence is $\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity$, completing the proof.
+	Then the final term in the sequence is $\GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity$, completing the proof.
+\end{proof}
 
 [make lemma]
-Now, consider that to grow by $\growthfactor$, $\FuncGrow$ must be called.
-So $\growthfactor^k\initcapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\growthfactor^{k - 1}\initcapacity$ for $k \geq 1$.
-Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \initcapacity,\ \growthfactor\initcapacity,\ \growthfactor^2\initcapacity,\ \ldots\ \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity$$
+Now, consider that to grow by $\GrowthFactor$, $\FuncGrow$ must be called.
+So $\GrowthFactor^k\InitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\GrowthFactor^{k - 1}\InitCapacity$ for $k \geq 1$.
+Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \InitCapacity,\ \GrowthFactor\InitCapacity,\ \GrowthFactor^2\InitCapacity,\ \ldots\ \GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil - 1}\InitCapacity$$
 
@@
 \begin{align*}
-0 + \initcapacity + \growthfactor\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil - 1}\initcapacity &= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+0 + \InitCapacity + \GrowthFactor\InitCapacity + \ldots + \GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil - 1}\InitCapacity &= \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
 \end{align*}
@@
 $$
-\nwritesfn(\varnitems) = \varnitems + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+\nwritesfn(\varnitems) = \varnitems + \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
 $$
@@
 To make this expression easier to work with, I will write it in big-P notation to approximate it for large $\varnitems$.
-First I note that $\log_{\growthfactor} k \leq \lceil \log_{\growthfactor} k \rceil < \left( \log_{\growthfactor} k \right) + 1$ for any $k > 0$, so $k \leq \growthfactor^{\lceil \log_{\growthfactor} k \rceil} < \growthfactor{k}$.
+First I note that $\log_{\GrowthFactor} k \leq \lceil \log_{\GrowthFactor} k \rceil < \left( \log_{\GrowthFactor} k \right) + 1$ for any $k > 0$, so $k \leq \GrowthFactor^{\lceil \log_{\GrowthFactor} k \rceil} < \GrowthFactor{k}$.
 Then
@@
 \begin{align*}
-\nwritesfn(\varnitems) &= \varnitems + \left( \frac{\growthfactor^{\big\lceil \log_{\growthfactor} \left( \frac {\varnitems} {\initcapacity} \right) \big\rceil} - 1}{\growthfactor - 1} \right) \initcapacity\\
-\varnitems + \left( \frac{\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
-\varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right)\\
-\biggo\left( \varnitems + \left( \frac{\varnitems - \initcapacity}{\growthfactor - 1} \right) \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \varnitems + \left( \frac{\growthfactor\varnitems - \initcapacity}{\growthfactor - 1} \right) \right)\\
-\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo\left( \nwritesfn(\varnitems) \right) &< \biggo\left( \left( \frac{2\growthfactor - 1}{\growthfactor - 1} \right) \varnitems \right)
+\nwritesfn(\varnitems) &= \varnitems + \left( \frac{\GrowthFactor^{\big\lceil \log_{\GrowthFactor} \left( \frac {\varnitems} {\InitCapacity} \right) \big\rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
+\varnitems + \left( \frac{\frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\GrowthFactor\frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
+\varnitems + \left( \frac{\varnitems - \InitCapacity}{\GrowthFactor - 1} \right) \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\GrowthFactor\varnitems - \InitCapacity}{\GrowthFactor - 1} \right)\\
+P\left( \varnitems + \left( \frac{\varnitems - \InitCapacity}{\GrowthFactor - 1} \right) \right) \leq P\left( \nwritesfn(\varnitems) \right) &< P\left( \varnitems + \left( \frac{\GrowthFactor\varnitems - \InitCapacity}{\GrowthFactor - 1} \right) \right)\\
+P\left( \left( \frac{\GrowthFactor}{\GrowthFactor - 1} \right) \varnitems \right) \leq P\left( \nwritesfn(\varnitems) \right) &< P\left( \left( \frac{2\GrowthFactor - 1}{\GrowthFactor - 1} \right) \varnitems \right)
 \end{align*}
 
-\scomplex
+\HdrSpaceComplex
 
@@
 
-From [lemma] I know the exact capacities $\listname$ takes on as $\varnitems$ items are appended.
+From \ref{CapacitySequence} I know the exact capacities $\ListName$ takes on as $\varnitems$ items are appended.
 Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.
@@
 \spacefn(\varnitems) &= \sum_{i \in S_C} i\\
-&= 0 + \initcapacity + \growthfactor\initcapacity + \growthfactor^2\initcapacity + \ldots + \growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil}\initcapacity\\
-&= \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} \varnitems - \log_{\growthfactor} \initcapacity \rceil + 1} - 1}{\growthfactor - 1} \right) \initcapacity
+&= 0 + \InitCapacity + \GrowthFactor\InitCapacity + \GrowthFactor^2\InitCapacity + \ldots + \GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity\\
+&= \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil + 1} - 1}{\GrowthFactor - 1} \right) \InitCapacity
 \end{align*}
@@
 \begin{align*}
-\left( \frac{\growthfactor \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \leq \spacefn(\varnitems) &< \left( \frac{\growthfactor^2 \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity\\
-\biggo\left( \left( \frac{\growthfactor \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \right) \leq \biggo\left( \spacefn(\varnitems) \right) &< \biggo\left( \left( \frac{\growthfactor^2 \frac{\varnitems}{\initcapacity} - 1}{\growthfactor - 1} \right) \initcapacity \right)\\
-\biggo\left( \left( \frac{\growthfactor}{\growthfactor - 1} \right) \varnitems \right) \leq \biggo\left( \spacefn(\varnitems) \right) &< \biggo\left( \left( \frac{\growthfactor^2}{\growthfactor - 1} \right) \varnitems \right)
+\left( \frac{\GrowthFactor \frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \leq \spacefn(\varnitems) &< \left( \frac{\GrowthFactor^2 \frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
+P\left( \left( \frac{\GrowthFactor \frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \right) \leq P\left( \spacefn(\varnitems) \right) &< P\left( \left( \frac{\GrowthFactor^2 \frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \right)\\
+P\left( \left( \frac{\GrowthFactor}{\GrowthFactor - 1} \right) \varnitems \right) \leq P\left( \spacefn(\varnitems) \right) &< P\left( \left( \frac{\GrowthFactor^2}{\GrowthFactor - 1} \right) \varnitems \right)
 \end{align*}

### 2017-10-18 Draft2/Appending.Growth.tex
Renaming variables

@@
 I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so I can compare it to $\nwritesfn(\varnitems)$ later.
-I also use $\growthfactornew$ and $\initcapacitynew$ instead of $\growthfactor$ and $\initcapacity$ for the growth factor and initial capacity, respectively.
+I also use $\GrowthFactornew$ and $\InitCapacitynew$ instead of $\GrowthFactor$ and $\InitCapacity$ for the growth factor and initial capacity, respectively.
 
@@
 \begin{lemma}
-	The capacity of a growth array grows by a constant factor $\growthfactornew$ after the first time it is called.
+	The capacity of a growth array grows by a constant factor $\GrowthFactornew$ after the first time it is called.
 \end{lemma}
@@
 
-	For the base case, consider the second time $\FuncGrow$ is called: the current capacity is $\initcapacitynew$, and the next (total) capacity should be $\growthfactornew\initcapacitynew$.
-Then a buffer of size $(\growthfactornew - 1)\initcapacitynew$ should be appended, and that is what the algorithm does.
+	For the base case, consider the second time $\FuncGrow$ is called: the current capacity is $\InitCapacitynew$, and the next (total) capacity should be $\GrowthFactornew\InitCapacitynew$.
+Then a buffer of size $(\GrowthFactornew - 1)\InitCapacitynew$ should be appended, and that is what the algorithm does.
 
 	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time.
-From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\growthfactornew^i\initcapacitynew$ and the head capacity is $(\growthfactornew^i - \growthfactornew^{i - 1})\initcapacitynew$.
-The next (total) capacity should be $\growthfactornew^{i + 1}\initcapacitynew$, and the next head capacity should be $(\growthfactornew^{i + 1} - \growthfactornew^i)\initcapacitynew$, which is $\growthfactornew$ times the current head capacity.
+From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\GrowthFactornew^i\InitCapacitynew$ and the head capacity is $(\GrowthFactornew^i - \GrowthFactornew^{i - 1})\InitCapacitynew$.
+The next (total) capacity should be $\GrowthFactornew^{i + 1}\InitCapacitynew$, and the next head capacity should be $(\GrowthFactornew^{i + 1} - \GrowthFactornew^i)\InitCapacitynew$, which is $\GrowthFactornew$ times the current head capacity.
 The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
@@
 $$
-S_R = 0,\ \initcapacitynew,\ \growthfactornew\initcapacitynew,\ \growthfactornew^2\initcapacitynew,\ \ldots\ \growthfactornew^{\lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil - 1}\initcapacitynew
+S_R = 0,\ \InitCapacitynew,\ \GrowthFactornew\InitCapacitynew,\ \GrowthFactornew^2\InitCapacitynew,\ \ldots\ \GrowthFactornew^{\lceil \log_{\GrowthFactornew} \varnitems - \log_{\GrowthFactornew} \InitCapacitynew \rceil - 1}\InitCapacitynew
 $$
@@
 Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since $\FuncGrow$ is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+Since $\FuncGrow$ is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\GrowthFactornew} \varnitems - \log_{\GrowthFactornew} \InitCapacitynew \rceil$.
 Then the formula for $\nwritesgrowfn(n)$ is
@@
 $$
-\nwritesgrowfn(n) = k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+\nwritesgrowfn(n) = k + \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} k - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
 $$
 
-where $\initcapacity$ $\growthfactor$ are the capacity of the \textit{tail} (not the growth array). I finally conclude that
+where $\InitCapacity$ $\GrowthFactor$ are the capacity of the \textit{tail} (not the growth array). I finally conclude that
 
 $$
-\nwritesnewfn(n) = n + k + \left( \frac{\growthfactor^{\lceil \log_{\growthfactor} k - \log_{\growthfactor} \initcapacity \rceil} - 1}{\growthfactor - 1} \right) \initcapacity
+\nwritesnewfn(n) = n + k + \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} k - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
 $$
@@
 \begin{align*}
-k &= \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil\\
+k &= \lceil \log_{\GrowthFactornew} \varnitems - \log_{\GrowthFactornew} \InitCapacitynew \rceil\\
 O(k) &= O(\log \varnitems)
@@
 
-I determined in [...] that if $\varnitems$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$.
+I determined in [...] that if $\varnitems$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\GrowthFactornew} \varnitems - \log_{\GrowthFactornew} \InitCapacitynew \rceil$.
 Since the tail is a dynamic array, it allocates $\spacefn(k)$ space, where $\spacefn$ is the space function of the tail.

### 2017-10-18 Draft2/FieldsProperties.tex
Renaming variables

--- 2017-10-16 Draft2/FieldsProperties.tex
@@
-I define some \textbf{fields} and \textbf{properties} (constant time methods that do not change state) for both types of arrays, so I may use them later to implement non-trivial methods.
+In subsequent sections, I will implement algorithms for both dynamic and growth arrays.
+In this section, I define fields and properties for these data structures which the algorithms will use.
+\textbf{Fields} are variables associated with an object that may be read from or written to.
+\textbf{Properties} are trivial, constant-time methods that do not change state.
+
+If $\ListName$ is a dynamic array, then it is assumed to have the following fields:
+
+\begin{itemize}
+	\item $\ListName.\FieldBuffer$ - The \textbf{buffer}, or raw array, that $\ListName$ stores its items in.
+	\item $\ListName.\FieldSize$ - The number of items in $\ListName$.
+\end{itemize}
+
+As a dynamic array, $\ListName$ is also given the following properties. $:=$ denotes a definition, as opposed to $=$ which checks equivalence. Functions that return boolean values are suffixed with ?.
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\LineComment{Returns the capacity of $\ListName$}
+		\State $\ListName.\FieldCapacity := \ListName.\FieldBuffer.\FieldLength$
+		\State
+		\LineComment{Returns whether $\ListName$ is full}
+		\State $\ListName.\FieldFull := \ListName.\FieldSize = \ListName.\FieldCapacity$
+	\end{algorithmic}
+\end{algorithm}
+
+When a dynamic array is instantiated, the following code should run:
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\State $\ListName.\FieldBuffer \gets \FuncNewArray(0)$
+		\State $\ListName.\FieldSize \gets 0$
+	\end{algorithmic}
+\end{algorithm}
+
+If $\ListName$ is a growth array, then it is assumed to have the following fields:
+
+\begin{itemize}
+	\item $\ListName.\FieldHead$ - The \textbf{head} of $\ListName$. It returns the buffer we are currently adding items to.
+	\item $\ListName.\FieldTail$ - The \textbf{tail} of $\ListName$. It returns a dynamic array of buffers that have already been filled. This can be thought of as a two-dimensional array.
+	\item $\ListName.\FieldSize$ - The number of items in $\ListName$.
+	\item $\ListName.\FieldCapacity$ - The \textbf{capacity} of $\ListName$. It returns the maximum number of items $\ListName$ can hold without resizing.
+\end{itemize}
+
+As a growth array, $\ListName$ is also given the following properties:
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\LineComment{Returns whether $\ListName$ is empty}
+		\State $\ListName.\FieldEmpty := \ListName.\FieldSize = 0$
+		\State
+		\LineComment{Returns whether $\ListName$ is full}
+		\State $\ListName.\FieldFull := \ListName.\FieldSize = \ListName.\FieldCapacity$
+		\State
+		\LineComment{Returns the capacity of $\FieldHead$}
+		\State $\ListName.\FieldHeadCapacity := \ListName.\FieldHead.\FieldLength$
+		\State
+		\LineComment{Returns the size of $\FieldHead$}
+		\LineComment{\textbf{Rationale:} $\FieldCapacity - \FieldHeadCapacity$ is the total capacity of the buffers in $\FieldTail$.}
+		\LineComment{Then, $\FieldSize - \left( \FieldCapacity - \FieldHeadCapacity \right)$ is the number of items that were added}
+		\LineComment{after depleting the buffers in $\FieldTail$.}
+		\State $\ListName.\FieldHeadSize := \ListName.\FieldSize - \left(\ListName.\FieldCapacity - \ListName.\FieldHeadCapacity\right)$
+	\end{algorithmic}
+\end{algorithm}
+
+When a growth array is instantiated, the following code should run:
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\State $\ListName.\FieldHead \gets \FuncNewArray(0)$
+		\State $\ListName.\FieldTail \gets \FuncNewDynamicArray()$
+		\State $\ListName.\FieldSize \gets 0$
+		\State $\ListName.\FieldCapacity \gets 0$
+	\end{algorithmic}
+\end{algorithm}

### 2017-10-24 Draft2/Appending.Dynamic.tex
Remove a cdot
Language
Remove all the \varnitems stuff

@@
 			\Else
-				\State $new\ buf \gets \FuncNewArray(\ListName.\FieldSize \cdot \GrowthFactor)$
+				\State $new\ buf \gets \FuncNewArray(\ListName.\FieldSize \times \GrowthFactor)$
 				\State $\FuncArrayCopy(source: \ListName.\FieldBuffer, dest: new\ buf, len: \ListName.\FieldSize)$
@@
 Before I analyze the time complexity of $\FuncAppend$, I consider a different method for measuring its cost.
-Suppose I start with an empty list and $\varnitems$ elements are appended.
+Suppose I start with an empty list and $n$ elements are appended.
 How many times is an element stored in an array?
-I will term the answer to this question the \textbf{write cost} of $\varnitems$ appends, and denote it $\nwritesfn(n)$.
+I will term the answer to this question the \textbf{write cost} of $n$ appends, and denote it $\nwritesfn(n)$.
 
-In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(\varnitems) \geq \varnitems$ after $n$ appends.
-However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\nwritesfn(\varnitems)$, I need to analyze when $\FuncGrow$ is called.
+In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(n) \geq n$ after $n$ appends.
+However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\nwritesfn(n)$, I need to analyze when $\FuncGrow$ is called.
 Consider the following lemma:
@@
 	Let $\ListName$ by a dynamic array.
-As $\varnitems$ items are appended, the sequence of capacities $\ListName$ takes on is $$S_C = 0,\ \InitCapacity,\ \GrowthFactor\InitCapacity,\ \GrowthFactor^2\InitCapacity,\ \ldots\ \GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity$$.
+As $n$ items are appended, the sequence of capacities $\ListName$ takes on is $$S_C = 0,\ \InitCapacity,\ \GrowthFactor\InitCapacity,\ \GrowthFactor^2\InitCapacity,\ \ldots\ \GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity$$.
 \end{lemma}
@@
 By induction, the rest of the sequence is $$\left\{ \GrowthFactor^i\InitCapacity \right\}_{i = 1}^k$$ for some $k$.
-Since the capacity is only as big as is needs to be, namely greater than or equal to $\varnitems$, $k$ is the smallest integer for which $\GrowthFactor^k\InitCapacity \geq \varnitems$.
+Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $k$ is the smallest integer for which $\GrowthFactor^k\InitCapacity \geq n$.
 Using this property, I now derive $k$.
@@
 	\begin{align*}
-	\GrowthFactor^k\InitCapacity &\geq \varnitems\\
-	\GrowthFactor^k &\geq \frac{\varnitems}{\InitCapacity}\\
-	k &\geq \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity\\
-	k &\geq \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity > k - 1\\
-	k &= \big\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \big\rceil
+	\GrowthFactor^k\InitCapacity &\geq n\\
+	\GrowthFactor^k &\geq \frac{n}{\InitCapacity}\\
+	k &\geq \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity\\
+	k &\geq \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity > k - 1\\
+	k &= \big\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \big\rceil
 	\end{align*}
 
-	Then the final term in the sequence is $\GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity$, completing the proof.
+	Then the final term in the sequence is $\GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity$, completing the proof.
 \end{proof}
@@
 So $\GrowthFactor^k\InitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\GrowthFactor^{k - 1}\InitCapacity$ for $k \geq 1$.
-Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \InitCapacity,\ \GrowthFactor\InitCapacity,\ \GrowthFactor^2\InitCapacity,\ \ldots\ \GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil - 1}\InitCapacity$$
+Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \InitCapacity,\ \GrowthFactor\InitCapacity,\ \GrowthFactor^2\InitCapacity,\ \ldots\ \GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil - 1}\InitCapacity$$
 
-Each time $\FuncGrow$ is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $\varnitems$ appends is
+Each time $\FuncGrow$ is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $n$ appends is
 
 \begin{align*}
-0 + \InitCapacity + \GrowthFactor\InitCapacity + \ldots + \GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil - 1}\InitCapacity &= \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
+0 + \InitCapacity + \GrowthFactor\InitCapacity + \ldots + \GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil - 1}\InitCapacity &= \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
 \end{align*}
 
-Finally, appending the writes made for every item in $\FuncAppend$, I finally find an explicit formula for $\nwritesfn(\varnitems)$.
+Finally, counting the writes made for every item in $\FuncAppend$, I finally find an explicit formula for $\nwritesfn(n)$.
 
@@
 $$
-\nwritesfn(\varnitems) = \varnitems + \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
+\nwritesfn(n) = n + \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
 $$
@@
 [ref2]
-To make this expression easier to work with, I will write it in big-P notation to approximate it for large $\varnitems$.
+To make this expression easier to work with, I will write it in big-P notation to approximate it for large $n$.
 First I note that $\log_{\GrowthFactor} k \leq \lceil \log_{\GrowthFactor} k \rceil < \left( \log_{\GrowthFactor} k \right) + 1$ for any $k > 0$, so $k \leq \GrowthFactor^{\lceil \log_{\GrowthFactor} k \rceil} < \GrowthFactor{k}$.
@@
 \begin{align*}
-\nwritesfn(\varnitems) &= \varnitems + \left( \frac{\GrowthFactor^{\big\lceil \log_{\GrowthFactor} \left( \frac {\varnitems} {\InitCapacity} \right) \big\rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
-\varnitems + \left( \frac{\frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\GrowthFactor\frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
-\varnitems + \left( \frac{\varnitems - \InitCapacity}{\GrowthFactor - 1} \right) \leq \nwritesfn(\varnitems) &< \varnitems + \left( \frac{\GrowthFactor\varnitems - \InitCapacity}{\GrowthFactor - 1} \right)\\
-P\left( \varnitems + \left( \frac{\varnitems - \InitCapacity}{\GrowthFactor - 1} \right) \right) \leq P\left( \nwritesfn(\varnitems) \right) &< P\left( \varnitems + \left( \frac{\GrowthFactor\varnitems - \InitCapacity}{\GrowthFactor - 1} \right) \right)\\
-P\left( \left( \frac{\GrowthFactor}{\GrowthFactor - 1} \right) \varnitems \right) \leq P\left( \nwritesfn(\varnitems) \right) &< P\left( \left( \frac{2\GrowthFactor - 1}{\GrowthFactor - 1} \right) \varnitems \right)
+\nwritesfn(n) &= n + \left( \frac{\GrowthFactor^{\big\lceil \log_{\GrowthFactor} \left( \frac {n} {\InitCapacity} \right) \big\rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
+n + \left( \frac{\frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \leq \nwritesfn(n) &< n + \left( \frac{\GrowthFactor\frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
+n + \left( \frac{n - \InitCapacity}{\GrowthFactor - 1} \right) \leq \nwritesfn(n) &< n + \left( \frac{\GrowthFactorn - \InitCapacity}{\GrowthFactor - 1} \right)\\
+P\left( n + \left( \frac{n - \InitCapacity}{\GrowthFactor - 1} \right) \right) \leq P\left( \nwritesfn(n) \right) &< P\left( n + \left( \frac{\GrowthFactorn - \InitCapacity}{\GrowthFactor - 1} \right) \right)\\
+P\left( \left( \frac{\GrowthFactor}{\GrowthFactor - 1} \right) n \right) \leq P\left( \nwritesfn(n) \right) &< P\left( \left( \frac{2\GrowthFactor - 1}{\GrowthFactor - 1} \right) n \right)
 \end{align*}
@@
 
-I wish to find the space allocated while appending $\varnitems$ items to a dynamic array.
-I denote this quantity $\spacefn(\varnitems)$, and define it as the total length of all arrays allocated during $\varnitems$ $\FuncAppend$ calls.
-I now derive a formula for $\spacefn(\varnitems)$.
+I wish to find the space allocated while appending $n$ items to a dynamic array.
+I denote this quantity $\spacefn(n)$, and define it as the total length of all arrays allocated during $n$ $\FuncAppend$ calls.
+I now derive a formula for $\spacefn(n)$.
 
-From \ref{CapacitySequence} I know the exact capacities $\ListName$ takes on as $\varnitems$ items are appended.
+From \ref{CapacitySequence} I know the exact capacities $\ListName$ takes on as $n$ items are appended.
 Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.
@@
 \begin{align*}
-\spacefn(\varnitems) &= \sum_{i \in S_C} i\\
-&= 0 + \InitCapacity + \GrowthFactor\InitCapacity + \GrowthFactor^2\InitCapacity + \ldots + \GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity\\
-&= \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} \varnitems - \log_{\GrowthFactor} \InitCapacity \rceil + 1} - 1}{\GrowthFactor - 1} \right) \InitCapacity
+\spacefn(n) &= \sum_{i \in S_C} i\\
+&= 0 + \InitCapacity + \GrowthFactor\InitCapacity + \GrowthFactor^2\InitCapacity + \ldots + \GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity\\
+&= \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil + 1} - 1}{\GrowthFactor - 1} \right) \InitCapacity
 \end{align*}
@@
 \begin{align*}
-\left( \frac{\GrowthFactor \frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \leq \spacefn(\varnitems) &< \left( \frac{\GrowthFactor^2 \frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
-P\left( \left( \frac{\GrowthFactor \frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \right) \leq P\left( \spacefn(\varnitems) \right) &< P\left( \left( \frac{\GrowthFactor^2 \frac{\varnitems}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \right)\\
-P\left( \left( \frac{\GrowthFactor}{\GrowthFactor - 1} \right) \varnitems \right) \leq P\left( \spacefn(\varnitems) \right) &< P\left( \left( \frac{\GrowthFactor^2}{\GrowthFactor - 1} \right) \varnitems \right)
+\left( \frac{\GrowthFactor \frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \leq \spacefn(n) &< \left( \frac{\GrowthFactor^2 \frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
+P\left( \left( \frac{\GrowthFactor \frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \right) \leq P\left( \spacefn(n) \right) &< P\left( \left( \frac{\GrowthFactor^2 \frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \right)\\
+P\left( \left( \frac{\GrowthFactor}{\GrowthFactor - 1} \right) n \right) \leq P\left( \spacefn(n) \right) &< P\left( \left( \frac{\GrowthFactor^2}{\GrowthFactor - 1} \right) n \right)
 \end{align*}

### 2017-10-24 Draft2/Appending.Growth.tex
Remove all the \varnitems stuff

@@
 
-I again start off by finding the write cost when $\varnitems$ are appended.
-I give the write cost function a slightly different name, $\nwritesnewfn(\varnitems)$, so I can compare it to $\nwritesfn(\varnitems)$ later.
+I again start off by finding the write cost when $n$ are appended.
+I give the write cost function a slightly different name, $\nwritesnewfn(n)$, so I can compare it to $\nwritesfn(n)$ later.
 I also use $\GrowthFactornew$ and $\InitCapacitynew$ instead of $\GrowthFactor$ and $\InitCapacity$ for the growth factor and initial capacity, respectively.
@@
 $$
-S_R = 0,\ \InitCapacitynew,\ \GrowthFactornew\InitCapacitynew,\ \GrowthFactornew^2\InitCapacitynew,\ \ldots\ \GrowthFactornew^{\lceil \log_{\GrowthFactornew} \varnitems - \log_{\GrowthFactornew} \InitCapacitynew \rceil - 1}\InitCapacitynew
+S_R = 0,\ \InitCapacitynew,\ \GrowthFactornew\InitCapacitynew,\ \GrowthFactornew^2\InitCapacitynew,\ \ldots\ \GrowthFactornew^{\lceil \log_{\GrowthFactornew} n - \log_{\GrowthFactornew} \InitCapacitynew \rceil - 1}\InitCapacitynew
 $$
@@
 Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since $\FuncGrow$ is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\GrowthFactornew} \varnitems - \log_{\GrowthFactornew} \InitCapacitynew \rceil$.
+Since $\FuncGrow$ is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\GrowthFactornew} n - \log_{\GrowthFactornew} \InitCapacitynew \rceil$.
 Then the formula for $\nwritesgrowfn(n)$ is
@@
 \begin{align*}
-k &= \lceil \log_{\GrowthFactornew} \varnitems - \log_{\GrowthFactornew} \InitCapacitynew \rceil\\
-O(k) &= O(\log \varnitems)
+k &= \lceil \log_{\GrowthFactornew} n - \log_{\GrowthFactornew} \InitCapacitynew \rceil\\
+O(k) &= O(\log n)
 \end{align*}
 
-Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\nwritesnewfn(\varnitems)$, leaving just $P(\varnitems)$:
+Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\nwritesnewfn(n)$, leaving just $P(n)$:
 
 \begin{align*}
-P(\nwritesnewfn(\varnitems)) &= P(\varnitems + \nwritesfn(k))\\
-&= P(\varnitems) + P(\nwritesfn(k))\\
-&= P(\varnitems) + O(\log \varnitems)\\
-&= P(\varnitems)
+P(\nwritesnewfn(n)) &= P(n + \nwritesfn(k))\\
+&= P(n) + P(\nwritesfn(k))\\
+&= P(n) + O(\log n)\\
+&= P(n)
 \end{align*}
@@
 % Should this be C(n) instead of C?
-The space function for $\varnitems$ $\FuncAppend$ calls on a growth array is denoted $\spacenewfn(\varnitems)$.
+The space function for $n$ $\FuncAppend$ calls on a growth array is denoted $\spacenewfn(n)$.
 Since growth arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.
-$\spacenewfn(\varnitems)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail.
+$\spacenewfn(n)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail.
 Thus the space the tail allocates must also be determined.
 
-I determined in [...] that if $\varnitems$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\GrowthFactornew} \varnitems - \log_{\GrowthFactornew} \InitCapacitynew \rceil$.
+I determined in [...] that if $n$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\GrowthFactornew} n - \log_{\GrowthFactornew} \InitCapacitynew \rceil$.
 Since the tail is a dynamic array, it allocates $\spacefn(k)$ space, where $\spacefn$ is the space function of the tail.
-Through a similar method to [...] it can be shown $O(\spacefn(k)) = O(k) = O(\log \varnitems)$.
+Through a similar method to [...] it can be shown $O(\spacefn(k)) = O(k) = O(\log n)$.
 Then % TODO: P-analysis should come after the explicit formula.
@@
 \begin{align*}
-\spacenewfn(\varnitems) = P(2^{\lceil \log_2 \varnitems \rceil}) = O(\varnitems)
+\spacenewfn(n) = P(2^{\lceil \log_2 n \rceil}) = O(n)
 \end{align*}

### 2017-10-24 Draft2/BigPNotation.tex
Remove all the \varnitems stuff

@@
 The reason for this is, for certain operations, growth arrays are only better than dynamic arrays by a constant factor.
-For example, dynamic arrays might allocate roughly $2\varnitems$ memory for appending $\varnitems$ items, while growth arrays would allocate roughly $\varnitems$ memory.
-Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $O(\varnitems)$.
+For example, dynamic arrays might allocate roughly $2n$ memory for appending $n$ items, while growth arrays would allocate roughly $n$ memory.
+Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $O(n)$.
 
 My goal is to be able to compare the coefficients of the highest-order terms in both expressions.
-For example, I would like to take the ratio $\frac{2\varnitems}{\varnitems}$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $\varnitems$.
+For example, I would like to take the ratio $\frac{2n}{n}$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $n$.
 However, big-O notation does not support this.
@@
 
-Notice that while $O(2\varnitems) = O(\varnitems)$, $P(2\varnitems) \neq P(\varnitems)$.
-Thus, $P$ makes it possible to distinguish between a function that uses $\varnitems$ space and one that uses $2\varnitems$ space.
+Notice that while $O(2n) = O(n)$, $P(2n) \neq P(n)$.
+Thus, $P$ makes it possible to distinguish between a function that uses $n$ space and one that uses $2n$ space.
 \textbf{Note:} A consequence of this is that bases for logarithms must be specified in big-P notation.

### 2017-10-24 Draft2/Appending.Dynamic.tex
Rename variables

@@
 
-I will first implement appending for dynamic arrays. Let $\ListName$ be a dynamic array. The following definitions are used in the code:
+I will first implement appending for dynamic arrays. Let $\VarList$ be a dynamic array. The following definitions are used in the code:
 
 \begin{description}
-	\item[initial capacity] The capacity of a dynamic a array when one item is appended to it. I denote this $\InitCapacity$.\\
+	\item[initial capacity] The capacity of a dynamic a array when one item is appended to it. I denote this $\VarInitCapacity$.\\
 	(The capacity of any dynamic array with size zero should be zero.)
-	\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\ListName$ grows. I denote this with $\GrowthFactor$.
+	\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows. I denote this with $\VarGrowthFactor$.
 \end{description}
@@
 		\Procedure{$\FuncAppend$}{$L, item$}
-			\If{$\ListName.\FieldFull$}
-				\State $\ListName.\FuncGrow()$
+			\If{$\VarList.\FieldFull$}
+				\State $\VarList.\FuncGrow()$
 			\EndIf
 
-			\State $\ListName.\FieldHead[\ListName.\FieldHeadSize] \gets item$
-			\State $\ListName.\FieldSize \gets \ListName.\FieldSize + 1$
+			\State $\VarList.\FieldHead[\VarList.\FieldHeadSize] \gets item$
+			\State $\VarList.\FieldSize \gets \VarList.\FieldSize + 1$
 		\EndProcedure
@@
 		\Procedure{$\FuncGrow$}{$L$}
-			\If{$\ListName.\FieldEmpty$}
-				\State $\ListName.\FieldBuffer \gets \FuncNewArray(\InitCapacity)$
+			\If{$\VarList.\FieldEmpty$}
+				\State $\VarList.\FieldBuffer \gets \FuncNewArray(\VarInitCapacity)$
 			\Else
-				\State $new\ buf \gets \FuncNewArray(\ListName.\FieldSize \times \GrowthFactor)$
-				\State $\FuncArrayCopy(source: \ListName.\FieldBuffer, dest: new\ buf, len: \ListName.\FieldSize)$
-				\State $\ListName.\FieldBuffer \gets new\ buf$
+				\State $new\ buf \gets \FuncNewArray(\VarList.\FieldSize \times \VarGrowthFactor)$
+				\State $\FuncArrayCopy(source: \VarList.\FieldBuffer, dest: new\ buf, len: \VarList.\FieldSize)$
+				\State $\VarList.\FieldBuffer \gets new\ buf$
 			\EndIf
@@
 How many times is an element stored in an array?
-I will term the answer to this question the \textbf{write cost} of $n$ appends, and denote it $\nwritesfn(n)$.
+I will term the answer to this question the \textbf{write cost} of $n$ appends, and denote it $\FuncWrites(n)$.
 
-In the above code, one write is performed after the conditional, so it is apparent that $\nwritesfn(n) \geq n$ after $n$ appends.
-However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\nwritesfn(n)$, I need to analyze when $\FuncGrow$ is called.
+In the above code, one write is performed after the conditional, so it is apparent that $\FuncWrites(n) \geq n$ after $n$ appends.
+However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\FuncWrites(n)$, I need to analyze when $\FuncGrow$ is called.
 Consider the following lemma:
@@
 \label{CapacitySequence}
-	Let $\ListName$ by a dynamic array.
-As $n$ items are appended, the sequence of capacities $\ListName$ takes on is $$S_C = 0,\ \InitCapacity,\ \GrowthFactor\InitCapacity,\ \GrowthFactor^2\InitCapacity,\ \ldots\ \GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity$$.
+	Let $\VarList$ by a dynamic array.
+As $n$ items are appended, the sequence of capacities $\VarList$ takes on is $$S_C = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$$.
 \end{lemma}
@@
 \begin{proof}
-	The capacity starts out at zero and becomes $\InitCapacity$ once one element is appended.
-From then on, it can only grow by a factor of $\GrowthFactor$ via $\FuncGrow$, so if $\GrowthFactor^i\InitCapacity$ is the current capacity then $\GrowthFactor^{i + 1}\InitCapacity$ must be the next capacity.
-By induction, the rest of the sequence is $$\left\{ \GrowthFactor^i\InitCapacity \right\}_{i = 1}^k$$ for some $k$.
-Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $k$ is the smallest integer for which $\GrowthFactor^k\InitCapacity \geq n$.
+	The capacity starts out at zero and becomes $\VarInitCapacity$ once one element is appended.
+From then on, it can only grow by a factor of $\VarGrowthFactor$ via $\FuncGrow$, so if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity.
+By induction, the rest of the sequence is $$\left\{ \VarGrowthFactor^i\VarInitCapacity \right\}_{i = 1}^k$$ for some $k$.
+Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $k$ is the smallest integer for which $\VarGrowthFactor^k\VarInitCapacity \geq n$.
 Using this property, I now derive $k$.
@@
 	\begin{align*}
-	\GrowthFactor^k\InitCapacity &\geq n\\
-	\GrowthFactor^k &\geq \frac{n}{\InitCapacity}\\
-	k &\geq \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity\\
-	k &\geq \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity > k - 1\\
-	k &= \big\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \big\rceil
+	\VarGrowthFactor^k\VarInitCapacity &\geq n\\
+	\VarGrowthFactor^k &\geq \frac{n}{\VarInitCapacity}\\
+	k &\geq \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity\\
+	k &\geq \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity > k - 1\\
+	k &= \big\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \big\rceil
 	\end{align*}
 
-	Then the final term in the sequence is $\GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity$, completing the proof.
+	Then the final term in the sequence is $\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$, completing the proof.
 \end{proof}
@@
 [make lemma]
-Now, consider that to grow by $\GrowthFactor$, $\FuncGrow$ must be called.
-So $\GrowthFactor^k\InitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\GrowthFactor^{k - 1}\InitCapacity$ for $k \geq 1$.
-Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \InitCapacity,\ \GrowthFactor\InitCapacity,\ \GrowthFactor^2\InitCapacity,\ \ldots\ \GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil - 1}\InitCapacity$$
+Now, consider that to grow by $\VarGrowthFactor$, $\FuncGrow$ must be called.
+So $\VarGrowthFactor^k\VarInitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\VarGrowthFactor^{k - 1}\VarInitCapacity$ for $k \geq 1$.
+Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil - 1}\VarInitCapacity$$
 
@@
 \begin{align*}
-0 + \InitCapacity + \GrowthFactor\InitCapacity + \ldots + \GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil - 1}\InitCapacity &= \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
+0 + \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \ldots + \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil - 1}\VarInitCapacity &= \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 \end{align*}
 
-Finally, counting the writes made for every item in $\FuncAppend$, I finally find an explicit formula for $\nwritesfn(n)$.
+Finally, counting the writes made for every item in $\FuncAppend$, I finally find an explicit formula for $\FuncWrites(n)$.
 
@@
 $$
-\nwritesfn(n) = n + \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
+\FuncWrites(n) = n + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 $$
@@
 To make this expression easier to work with, I will write it in big-P notation to approximate it for large $n$.
-First I note that $\log_{\GrowthFactor} k \leq \lceil \log_{\GrowthFactor} k \rceil < \left( \log_{\GrowthFactor} k \right) + 1$ for any $k > 0$, so $k \leq \GrowthFactor^{\lceil \log_{\GrowthFactor} k \rceil} < \GrowthFactor{k}$.
+First I note that $\log_{\VarGrowthFactor} k \leq \lceil \log_{\VarGrowthFactor} k \rceil < \left( \log_{\VarGrowthFactor} k \right) + 1$ for any $k > 0$, so $k \leq \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k \rceil} < \VarGrowthFactor{k}$.
 Then
@@
 \begin{align*}
-\nwritesfn(n) &= n + \left( \frac{\GrowthFactor^{\big\lceil \log_{\GrowthFactor} \left( \frac {n} {\InitCapacity} \right) \big\rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
-n + \left( \frac{\frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \leq \nwritesfn(n) &< n + \left( \frac{\GrowthFactor\frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
-n + \left( \frac{n - \InitCapacity}{\GrowthFactor - 1} \right) \leq \nwritesfn(n) &< n + \left( \frac{\GrowthFactorn - \InitCapacity}{\GrowthFactor - 1} \right)\\
-P\left( n + \left( \frac{n - \InitCapacity}{\GrowthFactor - 1} \right) \right) \leq P\left( \nwritesfn(n) \right) &< P\left( n + \left( \frac{\GrowthFactorn - \InitCapacity}{\GrowthFactor - 1} \right) \right)\\
-P\left( \left( \frac{\GrowthFactor}{\GrowthFactor - 1} \right) n \right) \leq P\left( \nwritesfn(n) \right) &< P\left( \left( \frac{2\GrowthFactor - 1}{\GrowthFactor - 1} \right) n \right)
+\FuncWrites(n) &= n + \left( \frac{\VarGrowthFactor^{\big\lceil \log_{\VarGrowthFactor} \left( \frac {n} {\VarInitCapacity} \right) \big\rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+n + \left( \frac{\frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \leq \FuncWrites(n) &< n + \left( \frac{\VarGrowthFactor\frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+n + \left( \frac{n - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \leq \FuncWrites(n) &< n + \left( \frac{\VarGrowthFactor{n} - \VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
+P\left( n + \left( \frac{n - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \right) \leq P\left( \FuncWrites(n) \right) &< P\left( n + \left( \frac{\VarGrowthFactor{n} - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \right)\\
+P\left( \left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \right) \leq P\left( \FuncWrites(n) \right) &< P\left( \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n \right)
 \end{align*}
@@
 I wish to find the space allocated while appending $n$ items to a dynamic array.
-I denote this quantity $\spacefn(n)$, and define it as the total length of all arrays allocated during $n$ $\FuncAppend$ calls.
-I now derive a formula for $\spacefn(n)$.
+I denote this quantity $\FuncSpace(n)$, and define it as the total length of all arrays allocated during $n$ $\FuncAppend$ calls.
+I now derive a formula for $\FuncSpace(n)$.
 
-From \ref{CapacitySequence} I know the exact capacities $\ListName$ takes on as $n$ items are appended.
+From \ref{CapacitySequence} I know the exact capacities $\VarList$ takes on as $n$ items are appended.
 Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.
@@
 \begin{align*}
-\spacefn(n) &= \sum_{i \in S_C} i\\
-&= 0 + \InitCapacity + \GrowthFactor\InitCapacity + \GrowthFactor^2\InitCapacity + \ldots + \GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil}\InitCapacity\\
-&= \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} n - \log_{\GrowthFactor} \InitCapacity \rceil + 1} - 1}{\GrowthFactor - 1} \right) \InitCapacity
+\FuncSpace(n) &= \sum_{i \in S_C} i\\
+&= 0 + \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \VarGrowthFactor^2\VarInitCapacity + \ldots + \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity\\
+&= \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil + 1} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 \end{align*}
@@
 \begin{align*}
-\left( \frac{\GrowthFactor \frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \leq \spacefn(n) &< \left( \frac{\GrowthFactor^2 \frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity\\
-P\left( \left( \frac{\GrowthFactor \frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \right) \leq P\left( \spacefn(n) \right) &< P\left( \left( \frac{\GrowthFactor^2 \frac{n}{\InitCapacity} - 1}{\GrowthFactor - 1} \right) \InitCapacity \right)\\
-P\left( \left( \frac{\GrowthFactor}{\GrowthFactor - 1} \right) n \right) \leq P\left( \spacefn(n) \right) &< P\left( \left( \frac{\GrowthFactor^2}{\GrowthFactor - 1} \right) n \right)
+\left( \frac{\VarGrowthFactor \frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \leq \FuncSpace(n) &< \left( \frac{\VarGrowthFactor^2 \frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+P\left( \left( \frac{\VarGrowthFactor \frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \right) \leq P\left( \FuncSpace(n) \right) &< P\left( \left( \frac{\VarGrowthFactor^2 \frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \right)\\
+P\left( \left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \right) \leq P\left( \FuncSpace(n) \right) &< P\left( \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n \right)
 \end{align*}

### 2017-10-24 Draft2/Appending.Growth.tex
Rename variables

@@
 I again start off by finding the write cost when $n$ are appended.
-I give the write cost function a slightly different name, $\nwritesnewfn(n)$, so I can compare it to $\nwritesfn(n)$ later.
-I also use $\GrowthFactornew$ and $\InitCapacitynew$ instead of $\GrowthFactor$ and $\InitCapacity$ for the growth factor and initial capacity, respectively.
+I give the write cost function a slightly different name, $\FuncWritesNew(n)$, so I can compare it to $\FuncWrites(n)$ later.
+I also use $\VarGrowthFactorNew$ and $\VarInitCapacityNew$ instead of $\VarGrowthFactor$ and $\VarInitCapacity$ for the growth factor and initial capacity, respectively.
 
@@
 \begin{lemma}
-	The capacity of a growth array grows by a constant factor $\GrowthFactornew$ after the first time it is called.
+	The capacity of a growth array grows by a constant factor $\VarGrowthFactorNew$ after the first time it is called.
 \end{lemma}
@@
 
-	For the base case, consider the second time $\FuncGrow$ is called: the current capacity is $\InitCapacitynew$, and the next (total) capacity should be $\GrowthFactornew\InitCapacitynew$.
-Then a buffer of size $(\GrowthFactornew - 1)\InitCapacitynew$ should be appended, and that is what the algorithm does.
+	For the base case, consider the second time $\FuncGrow$ is called: the current capacity is $\VarInitCapacityNew$, and the next (total) capacity should be $\VarGrowthFactorNew\VarInitCapacityNew$.
+Then a buffer of size $(\VarGrowthFactorNew - 1)\VarInitCapacityNew$ should be appended, and that is what the algorithm does.
 
 	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time.
-From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\GrowthFactornew^i\InitCapacitynew$ and the head capacity is $(\GrowthFactornew^i - \GrowthFactornew^{i - 1})\InitCapacitynew$.
-The next (total) capacity should be $\GrowthFactornew^{i + 1}\InitCapacitynew$, and the next head capacity should be $(\GrowthFactornew^{i + 1} - \GrowthFactornew^i)\InitCapacitynew$, which is $\GrowthFactornew$ times the current head capacity.
+From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\VarGrowthFactorNew^i\VarInitCapacityNew$ and the head capacity is $(\VarGrowthFactorNew^i - \VarGrowthFactorNew^{i - 1})\VarInitCapacityNew$.
+The next (total) capacity should be $\VarGrowthFactorNew^{i + 1}\VarInitCapacityNew$, and the next head capacity should be $(\VarGrowthFactorNew^{i + 1} - \VarGrowthFactorNew^i)\VarInitCapacityNew$, which is $\VarGrowthFactorNew$ times the current head capacity.
 The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
@@
 
-Let $\nwritesgrowfn(n)$ denote the total number of writes made by $\FuncGrow$. From [make lemma], I know that $\FuncGrow$ is called at the sizes
+Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$. From [make lemma], I know that $\FuncGrow$ is called at the sizes
 
 $$
-S_R = 0,\ \InitCapacitynew,\ \GrowthFactornew\InitCapacitynew,\ \GrowthFactornew^2\InitCapacitynew,\ \ldots\ \GrowthFactornew^{\lceil \log_{\GrowthFactornew} n - \log_{\GrowthFactornew} \InitCapacitynew \rceil - 1}\InitCapacitynew
+S_R = 0,\ \VarInitCapacityNew,\ \VarGrowthFactorNew\VarInitCapacityNew,\ \VarGrowthFactorNew^2\VarInitCapacityNew,\ \ldots\ \VarGrowthFactorNew^{\lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil - 1}\VarInitCapacityNew
 $$
@@
 Let $k$ be the number of times the tail is appended to.
-Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$.
-Since $\FuncGrow$ is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\GrowthFactornew} n - \log_{\GrowthFactornew} \InitCapacitynew \rceil$.
-Then the formula for $\nwritesgrowfn(n)$ is
+Since the tail is a dynamic array, the number of writes it makes is $\FuncWrites(k)$.
+Since $\FuncGrow$ is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil$.
+Then the formula for $\FuncWritesByGrow(n)$ is
 
 $$
-\nwritesgrowfn(n) = k + \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} k - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
+\FuncWritesByGrow(n) = k + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 $$
 
-where $\InitCapacity$ $\GrowthFactor$ are the capacity of the \textit{tail} (not the growth array). I finally conclude that
+where $\VarInitCapacity$ $\VarGrowthFactor$ are the capacity of the \textit{tail} (not the growth array). I finally conclude that
 
 $$
-\nwritesnewfn(n) = n + k + \left( \frac{\GrowthFactor^{\lceil \log_{\GrowthFactor} k - \log_{\GrowthFactor} \InitCapacity \rceil} - 1}{\GrowthFactor - 1} \right) \InitCapacity
+\FuncWritesNew(n) = n + k + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 $$
@@
 \begin{align*}
-k &= \lceil \log_{\GrowthFactornew} n - \log_{\GrowthFactornew} \InitCapacitynew \rceil\\
+k &= \lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil\\
 O(k) &= O(\log n)
@@
 
-Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\nwritesnewfn(n)$, leaving just $P(n)$:
+Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\FuncWritesNew(n)$, leaving just $P(n)$:
 
 \begin{align*}
-P(\nwritesnewfn(n)) &= P(n + \nwritesfn(k))\\
-&= P(n) + P(\nwritesfn(k))\\
+P(\FuncWritesNew(n)) &= P(n + \FuncWrites(k))\\
+&= P(n) + P(\FuncWrites(k))\\
 &= P(n) + O(\log n)\\
@@
 % Should this be C(n) instead of C?
-The space function for $n$ $\FuncAppend$ calls on a growth array is denoted $\spacenewfn(n)$.
+The space function for $n$ $\FuncAppend$ calls on a growth array is denoted $\FuncSpaceNew(n)$.
 Since growth arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.
-$\spacenewfn(n)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail.
+$\FuncSpaceNew(n)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail.
 Thus the space the tail allocates must also be determined.
 
-I determined in [...] that if $n$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\GrowthFactornew} n - \log_{\GrowthFactornew} \InitCapacitynew \rceil$.
-Since the tail is a dynamic array, it allocates $\spacefn(k)$ space, where $\spacefn$ is the space function of the tail.
-Through a similar method to [...] it can be shown $O(\spacefn(k)) = O(k) = O(\log n)$.
+I determined in [...] that if $n$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil$.
+Since the tail is a dynamic array, it allocates $\FuncSpace(k)$ space, where $\FuncSpace$ is the space function of the tail.
+Through a similar method to [...] it can be shown $O(\FuncSpace(k)) = O(k) = O(\log n)$.
 Then % TODO: P-analysis should come after the explicit formula.
@@
 \begin{align*}
-\spacenewfn(n) = P(2^{\lceil \log_2 n \rceil}) = O(n)
+\FuncSpaceNew(n) = P(2^{\lceil \log_2 n \rceil}) = O(n)
 \end{align*}

### 2017-10-24 Draft2/FieldsProperties.tex
Rename variables

@@
 
-If $\ListName$ is a dynamic array, then it is assumed to have the following fields:
+If $\VarList$ is a dynamic array, then it is assumed to have the following fields:
 
 \begin{itemize}
-	\item $\ListName.\FieldBuffer$ - The \textbf{buffer}, or raw array, that $\ListName$ stores its items in.
-	\item $\ListName.\FieldSize$ - The number of items in $\ListName$.
+	\item $\VarList.\FieldBuffer$ - The \textbf{buffer}, or raw array, that $\VarList$ stores its items in.
+	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
 \end{itemize}
 
-As a dynamic array, $\ListName$ is also given the following properties. $:=$ denotes a definition, as opposed to $=$ which checks equivalence. Functions that return boolean values are suffixed with ?.
+As a dynamic array, $\VarList$ is also given the following properties. $:=$ denotes a definition, as opposed to $=$ which checks equivalence. Functions that return boolean values are suffixed with ?.
 
@@
 	\begin{algorithmic}
-		\LineComment{Returns the capacity of $\ListName$}
-		\State $\ListName.\FieldCapacity := \ListName.\FieldBuffer.\FieldLength$
+		\LineComment{Returns the capacity of $\VarList$}
+		\State $\VarList.\FieldCapacity := \VarList.\FieldBuffer.\FieldLength$
 		\State
-		\LineComment{Returns whether $\ListName$ is full}
-		\State $\ListName.\FieldFull := \ListName.\FieldSize = \ListName.\FieldCapacity$
+		\LineComment{Returns whether $\VarList$ is full}
+		\State $\VarList.\FieldFull := \VarList.\FieldSize = \VarList.\FieldCapacity$
 	\end{algorithmic}
@@
 	\begin{algorithmic}
-		\State $\ListName.\FieldBuffer \gets \FuncNewArray(0)$
-		\State $\ListName.\FieldSize \gets 0$
+		\State $\VarList.\FieldBuffer \gets \FuncNewArray(0)$
+		\State $\VarList.\FieldSize \gets 0$
 	\end{algorithmic}
@@
 
-If $\ListName$ is a growth array, then it is assumed to have the following fields:
+If $\VarList$ is a growth array, then it is assumed to have the following fields:
 
 \begin{itemize}
-	\item $\ListName.\FieldHead$ - The \textbf{head} of $\ListName$. It returns the buffer we are currently adding items to.
-	\item $\ListName.\FieldTail$ - The \textbf{tail} of $\ListName$. It returns a dynamic array of buffers that have already been filled. This can be thought of as a two-dimensional array.
-	\item $\ListName.\FieldSize$ - The number of items in $\ListName$.
-	\item $\ListName.\FieldCapacity$ - The \textbf{capacity} of $\ListName$. It returns the maximum number of items $\ListName$ can hold without resizing.
+	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
+	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. It returns a dynamic array of buffers that have already been filled. This can be thought of as a two-dimensional array.
+	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
+	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold without resizing.
 \end{itemize}
 
-As a growth array, $\ListName$ is also given the following properties:
+As a growth array, $\VarList$ is also given the following properties:
 
@@
 	\begin{algorithmic}
-		\LineComment{Returns whether $\ListName$ is empty}
-		\State $\ListName.\FieldEmpty := \ListName.\FieldSize = 0$
+		\LineComment{Returns whether $\VarList$ is empty}
+		\State $\VarList.\FieldEmpty := \VarList.\FieldSize = 0$
 		\State
-		\LineComment{Returns whether $\ListName$ is full}
-		\State $\ListName.\FieldFull := \ListName.\FieldSize = \ListName.\FieldCapacity$
+		\LineComment{Returns whether $\VarList$ is full}
+		\State $\VarList.\FieldFull := \VarList.\FieldSize = \VarList.\FieldCapacity$
 		\State
 		\LineComment{Returns the capacity of $\FieldHead$}
-		\State $\ListName.\FieldHeadCapacity := \ListName.\FieldHead.\FieldLength$
+		\State $\VarList.\FieldHeadCapacity := \VarList.\FieldHead.\FieldLength$
 		\State
@@
 		\LineComment{after depleting the buffers in $\FieldTail$.}
-		\State $\ListName.\FieldHeadSize := \ListName.\FieldSize - \left(\ListName.\FieldCapacity - \ListName.\FieldHeadCapacity\right)$
+		\State $\VarList.\FieldHeadSize := \VarList.\FieldSize - \left(\VarList.\FieldCapacity - \VarList.\FieldHeadCapacity\right)$
 	\end{algorithmic}
@@
 	\begin{algorithmic}
-		\State $\ListName.\FieldHead \gets \FuncNewArray(0)$
-		\State $\ListName.\FieldTail \gets \FuncNewDynamicArray()$
-		\State $\ListName.\FieldSize \gets 0$
-		\State $\ListName.\FieldCapacity \gets 0$
+		\State $\VarList.\FieldHead \gets \FuncNewArray(0)$
+		\State $\VarList.\FieldTail \gets \FuncNewDynamicArray()$
+		\State $\VarList.\FieldSize \gets 0$
+		\State $\VarList.\FieldCapacity \gets 0$
 	\end{algorithmic}

### 2017-10-24 Draft2/AsymptoticNotation.tex
[WIP] Remove P-notation

--- 2017-10-24 Draft2/BigPNotation.tex
@@
 
-In order to highlight the benefit of growth arrays, I will define a new notation for time complexity.
+In order to highlight the benefit of growth arrays, I will use an alternative notation for time complexity.
 The reason for this is, for certain operations, growth arrays are only better than dynamic arrays by a constant factor.
@@
 
-I define an alternative to big-O notation, which I will call \textbf{big-P notation}. I define $P(f(n))$ to be the class of functions $g$ such that $g(n) \to f(n)$ for large $n$. Formally,
+I will use the $\TextTilde$ relation to analyze time complexity. It is defined as follows:
 
-$$
-g \in P(f(n)) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
-$$
+\begin{align*}
+f(n) \TextTilde g(n) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
+\end{align*}
 
-Notice that while $O(2n) = O(n)$, $P(2n) \neq P(n)$.
-Thus, $P$ makes it possible to distinguish between a function that uses $n$ space and one that uses $2n$ space.
-\textbf{Note:} A consequence of this is that bases for logarithms must be specified in big-P notation.
+$f$ and $g$ may be used as shorthand to denote $f(n)$ and $g(n)$, respectively.
+
+Notice that while $O(2n) = O(n)$, $2n \TextTildeNot n$.
+Thus, $\TextTilde$ makes it possible to distinguish between a function that uses $n$ space and one that uses $2n$ space.
+\HdrNote A consequence of this is that bases for logarithms cannot be omitted, like in big-O notation.
 
 \subsection{Properties}
-\label{BigPProperties}
+\label{AsymptoticProperties}
 
-\textbf{Note:} Throughout this paper, when $P(f(n))$ or $O(f(n))$ is used in an arithmetic expression, I am referring to a function in the set and not the set itself.
-For example, the verbal equivalent of $\frac{P(2n)}{P(n)} = P(2)$ states "the quotient of a function in $P(2n)$ and a function in $P(n)$ is equal to a function in $P(2)$."
-
-A useful property $P$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{MergingOverArithmetic}.
+A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{MergingOverArithmetic}.
 
 \begin{theorem}
-	$P$ merges over addition and subtraction. That is,
+	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
 	\begin{align*}
-	P(f(n)) + P(g(n)) &= P(f(n) + g(n))\\
-	P(f(n)) - P(g(n)) &= P(f(n) - g(n))
+	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
+		(\hat{f} + \hat{g}) \TextTilde (f + g)\\
+		(\hat{f} - \hat{g}) \TextTilde (f - g)
+	\end{cases}
 	\end{align*}
@@
 \begin{theorem}
-	$P$ merges over multiplication and division. That is,
+	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
 	\begin{align*}
-	P(f(n))P(g(n)) &= P(f(n)g(n))\\
-	\frac {P(f(n))} {P(g(n))} &= P\left(\frac{f(n)} {g(n)}\right)
+	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
+	\hat{f}\hat{g} \TextTilde fg\\
+	\hat{f} / \hat{g} \TextTilde f / g
+	\end{cases}
 	\end{align*}
@@
 
-Another nice property $P$ and $O$ have in common is that lower-order terms are removed from consideration.
-For example, $P(n) = P(n + \log_2 n)$.
-This is stated by the below theorem, which is proved in \ref{ScrubsLowerOrderTerms}.
+Another nice property $\TextTilde$ and $O$ have in common is that lower-order terms are removed from consideration.
+For example, $n \TextTilde n + \log_2 n$.
+This is stated by the below theorem, which is proved in \ref{RemovesLowerOrderTerms}.
 
 \begin{theorem}
-	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $P(f(n) + g(n)) = P(f(n))$.
+	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $f(n) + g(n) \TextTilde f(n)$.
 \end{theorem}

### 2017-10-24 Draft2/Appendix.tex
[WIP] Remove P-notation
[WIP] Remove P-notation, 2
Remove prime notation

@@
 \begin{theorem}
-	$P$ merges over addition and subtraction. That is,
+	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
 	\begin{align*}
-	P(f(n)) + P(g(n)) &= P(f(n) + g(n))\\
-	P(f(n)) - P(g(n)) &= P(f(n) - g(n))
+	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
+	(\hat{f} + \hat{g}) \TextTilde (f + g)\\
+	(\hat{f} - \hat{g}) \TextTilde (f - g)
+	\end{cases}
 	\end{align*}
@@
 \begin{proof}
-	We will consider the statement about addition first. Recall from the note at \ref{BigPProperties} that this statement is equivalent to:
+	We will consider the statement about addition first. Recall from the note at \ref{AsymptoticProperties} that this statement is equivalent to:
 
-	\textit{Let $f' \in P(f(n))$ and $g' \in P(g(n))$. Then $f' + g' \in P(f(n) + g(n))$.}
+	\textit{Let $\hat{f} \in P(f(n))$ and $\hat{g} \in P(g(n))$. Then $\hat{f} + \hat{g} \in P(f(n) + g(n))$.}
 
@@
 	\begin{align*}
-	\lim_{n \to \infty} \left( \frac{f' + g'}{f + g} \right) &= \lim_{n \to \infty} \left( \frac{f'}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g'}{f + g} \right)\\
-	&= \left( \lim_{n \to \infty} \frac{f'}{f} \right) \left( \lim_{n \to \infty} \left( \frac{f}{f + g} \right) \right) +\\
-	&\ \ \ \ \left( \lim_{n \to \infty} \frac{g'}{g} \right) \left( \lim_{n \to \infty} \left( \frac{g}{f + g} \right) \right)\\
+	\lim_{n \to \infty} \left( \frac{\hat{f} + \hat{g}}{f + g} \right) &= \lim_{n \to \infty} \left( \frac{\hat{f}}{f + g} \right) + \lim_{n \to \infty} \left( \frac{\hat{g}}{f + g} \right)\\
+	&= \left( \lim_{n \to \infty} \frac{\hat{f}}{f} \right) \left( \lim_{n \to \infty} \left( \frac{f}{f + g} \right) \right) +\\
+	&\ \ \ \ \left( \lim_{n \to \infty} \frac{\hat{g}}{g} \right) \left( \lim_{n \to \infty} \left( \frac{g}{f + g} \right) \right)\\
 	&= \lim_{n \to \infty} \left( \frac{f}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g}{f + g} \right)\\
@@
 
-	it follows that $f' + g' \in P(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
+	it follows that $\hat{f} + \hat{g} \in P(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
 \end{proof}
@@
 \begin{proof}
-	We will consider the statement about multiplication first. Recall from the note at \ref{BigPProperties} that this statement is equivalent to:
+	We will consider the statement about multiplication first. Recall from the note at \ref{AsymptoticProperties} that this statement is equivalent to:
 
-	\textit{Let $f' \in P(f(n))$ and $g' \in P(g(n))$. Then $f'g' \in P(f(n)g(n))$.}
+	\textit{Let $\hat{f} \in P(f(n))$ and $\hat{g} \in P(g(n))$. Then $\hat{f}\hat{g} \in P(f(n)g(n))$.}
 
-	We can show this easily by multiplying the limits corresponding to $f'$ and $g'$:
+	We can show this easily by multiplying the limits corresponding to $\hat{f}$ and $\hat{g}$:
 
 	\begin{align*}
-	\lim_{n \to \infty} \frac{f'(n)}{f(n)} &= 1\\
-	\lim_{n \to \infty} \frac{g'(n)}{g(n)} &= 1\\
-	\left( \lim_{n \to \infty} \frac{f'(n)}{f(n)} \right) \left( \lim_{n \to \infty} \frac{g'(n)}{g(n)} \right) &= 1 \cdot 1\\
-	\lim_{n \to \infty} \frac{f'(n)g'(n)}{f(n)g(n)} &= 1
+	\lim_{n \to \infty} \frac{\hat{f}(n)}{f(n)} &= 1\\
+	\lim_{n \to \infty} \frac{\hat{g}(n)}{g(n)} &= 1\\
+	\left( \lim_{n \to \infty} \frac{\hat{f}(n)}{f(n)} \right) \left( \lim_{n \to \infty} \frac{\hat{g}(n)}{g(n)} \right) &= 1 \cdot 1\\
+	\lim_{n \to \infty} \frac{\hat{f}(n)\hat{g}(n)}{f(n)g(n)} &= 1
 	\end{align*}
 
-	it follows that $f'g' \in P(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $g'$ before multiplying, resulting in
+	it follows that $\hat{f}\hat{g} \in P(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $\hat{g}$ before multiplying, resulting in
 
 	\begin{align*}
-	\lim_{n \to \infty} \frac{f'(n) / g'(n)}{f(n) / g(n)} = 1
+	\lim_{n \to \infty} \frac{\hat{f}(n) / \hat{g}(n)}{f(n) / g(n)} = 1
 	\end{align*}
 
-	This implies $f' / g' \in P(f(n) / g(n))$.
+	This implies $\hat{f} / \hat{g} \in P(f(n) / g(n))$.
 \end{proof}
@@
 
-	Now, consider any $g' \in P(g(n))$. Since
+	Now, consider any $\hat{g} \in P(g(n))$. Since
 
 	\begin{align*}
-	\lim_{n \to \infty} \frac {g'(n)} {g(n)} &= 1\\
-	\left( \lim_{n \to \infty} \frac {g'(n)} {g(n)} \right) \left( \lim_{n \to \infty} \frac{g(n)}{h(n)} \right) &= 1\\
-	\lim_{n \to \infty} \frac{g'(n)}{h(n)} &= 1
+	\lim_{n \to \infty} \frac {\hat{g}(n)} {g(n)} &= 1\\
+	\left( \lim_{n \to \infty} \frac {\hat{g}(n)} {g(n)} \right) \left( \lim_{n \to \infty} \frac{g(n)}{h(n)} \right) &= 1\\
+	\lim_{n \to \infty} \frac{\hat{g}(n)}{h(n)} &= 1
 	\end{align*}
 
-	it follows that $g' \in P(h(n))$, and thus $P(g(n)) \subseteq P(h(n))$. By a similar argument, it can be shown $P(h(n)) \subseteq P(g(n))$. Thus it must be true that $P(g(n)) = P(h(n))$.
+	it follows that $\hat{g} \in P(h(n))$, and thus $P(g(n)) \subseteq P(h(n))$. By a similar argument, it can be shown $P(h(n)) \subseteq P(g(n))$. Thus it must be true that $P(g(n)) = P(h(n))$.
 \end{proof}
@@
 \subsection{Removal of Lower-Order Terms}
-\label{ScrubsLowerOrderTerms}
+\label{RemovesLowerOrderTerms}
 

### 2017-10-24 Draft2/Appendix.tex
Labels

@@
 
-\section{Proofs of Properties of Big-P Notation}
+\section{Proofs of $\TextTilde$ Properties}
 
 \subsection{Merging over Arithmetic Operations}
-\label{MergingOverArithmetic}
+\label{pf:MergingOverArithmetic}
 
@@
 \begin{proof}
-	We will consider the statement about addition first. Recall from the note at \ref{AsymptoticProperties} that this statement is equivalent to:
+	We will consider the statement about addition first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:
 
@@
 \begin{proof}
-	We will consider the statement about multiplication first. Recall from the note at \ref{AsymptoticProperties} that this statement is equivalent to:
+	We will consider the statement about multiplication first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:
 
@@
 
-\subsection{Unique Class Lemma}
-\label{UniqueClassOfFunctions}
-
-\begin{lemma}
-	Each function $f(n)$ has a unique class of functions under $P$. That is, suppose $f \in P(g(n))$ and $f \in P(h(n))$. Then $P(g(n)) = P(h(n))$.
-\end{lemma}
-
-\begin{proof}
-	By definition, $\lim_{n \to \infty} \frac{f(n)}{g(n)} = 1$ and $\lim_{n \to \infty} \frac{f(n)}{h(n)} = 1$. Flipping the first equation and multiplying, we receive
-
-	\begin{align*}
-	\left( \lim_{n \to \infty} \frac {g(n)} {f(n)} \right) \left( \lim_{n \to \infty} \frac {f(n)} {h(n)} \right) &= 1\\
-	\lim_{n \to \infty} \frac {g(n)} {h(n)} &= 1\\
-	g &\in P(h(n))
-	\end{align*}
-
-	Now, consider any $\hat{g} \in P(g(n))$. Since
-
-	\begin{align*}
-	\lim_{n \to \infty} \frac {\hat{g}(n)} {g(n)} &= 1\\
-	\left( \lim_{n \to \infty} \frac {\hat{g}(n)} {g(n)} \right) \left( \lim_{n \to \infty} \frac{g(n)}{h(n)} \right) &= 1\\
-	\lim_{n \to \infty} \frac{\hat{g}(n)}{h(n)} &= 1
-	\end{align*}
-
-	it follows that $\hat{g} \in P(h(n))$, and thus $P(g(n)) \subseteq P(h(n))$. By a similar argument, it can be shown $P(h(n)) \subseteq P(g(n))$. Thus it must be true that $P(g(n)) = P(h(n))$.
-\end{proof}
+\subsection{Transitivity}
+\label{pf:Transitivity}
 
 \subsection{Removal of Lower-Order Terms}
-\label{RemovesLowerOrderTerms}
+\label{pf:RemovesLowerOrderTerms}
 
@@
 
-	Then $f(n) + g(n) \in P(f(n))$. Since it is also true that $f(n) + g(n) \in P(f(n) + g(n))$, it follows from \ref{UniqueClassOfFunctions} that $P(f(n)) = P(f(n) + g(n))$.
+	Then $f(n) + g(n) \in P(f(n))$. Since it is also true that $f(n) + g(n) \in P(f(n) + g(n))$, it follows from \ref{pf:Transitivity} that $P(f(n)) = P(f(n) + g(n))$.
 \end{proof}

### 2017-10-24 Draft2/AsymptoticNotation.tex
Labels

@@
 \subsection{Properties}
-\label{AsymptoticProperties}
+\label{subsec:AsymptoticProperties}
 
-A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{MergingOverArithmetic}.
+A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergingOverArithmetic}.
 
@@
 For example, $n \TextTilde n + \log_2 n$.
-This is stated by the below theorem, which is proved in \ref{RemovesLowerOrderTerms}.
+This is stated by the below theorem, which is proved in \ref{pf:RemovesLowerOrderTerms}.
 

### 2017-10-24 Draft2/Appendix.tex
More changes

@@
 \subsection{Merging over Arithmetic Operations}
-\label{pf:MergingOverArithmetic}
+\label{pf:MergesOverArithmetic}
 
-\begin{theorem}
-	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
-	\begin{align*}
-	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
-	(\hat{f} + \hat{g}) \TextTilde (f + g)\\
-	(\hat{f} - \hat{g}) \TextTilde (f - g)
-	\end{cases}
-	\end{align*}
-\end{theorem}
-
-\begin{proof}
+\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticAdd})]
 	We will consider the statement about addition first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:
@@
 
-\begin{theorem}
-	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
-	\begin{align*}
-	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
-	\hat{f}\hat{g} \TextTilde fg\\
-	\hat{f} / \hat{g} \TextTilde f / g
-	\end{cases}
-	\end{align*}
-\end{theorem}
-
-\begin{proof}
+\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticMultiply})]
 	We will consider the statement about multiplication first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:
@@
 
+\begin{theorem}
+	If $f \TextTilde g$ and $g \TextTilde h$, then $f \TextTilde h$.
+\end{theorem}
+
+\begin{proof}
+	By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \TextTilde h$.
+\end{proof}
+
 \subsection{Removal of Lower-Order Terms}

### 2017-10-24 Draft2/AsymptoticNotation.tex
More changes

@@
 
-A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergingOverArithmetic}.
+A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergesOverArithmetic}.
 
 \begin{theorem}
+\label{thm:MergesOverArithmeticAdd}
 	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
@@
 \begin{theorem}
+\label{thm:MergesOverArithmeticMultiply}
 	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,

### 2017-10-24 Draft2/Appending.Growth.tex
Labels
Finish removing P-notation?

@@
 
-\ref{CapacitySequence} still holds, since all of the assumptions made there are also true for growth arrays.
+\ref{lem:CapacitySequence} still holds, since all of the assumptions made there are also true for growth arrays.
 In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:
@@
 
-I now approximate this expression with big-P notation. First, I establish an approximation for $k$ using big-O:
+I now approximate this expression using $\TextTilde$. First, I approximate $k$ using big-O:
 
@@
 
-Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\FuncWritesNew(n)$, leaving just $P(n)$:
+Now, the $k$-term disappears when using $\TextTilde$ to approximate $\FuncWritesNew(n)$, leaving just $n$:
 
 \begin{align*}
-P(\FuncWritesNew(n)) &= P(n + \FuncWrites(k))\\
-&= P(n) + P(\FuncWrites(k))\\
-&= P(n) + O(\log n)\\
-&= P(n)
+\FuncWritesNew(n) &\TextTilde n + \FuncWrites(k)\\
+&= n + O(\log n)\\
+&\TextTilde n
 \end{align*}
@@
 \begin{align*}
-\FuncSpaceNew(n) = P(2^{\lceil \log_2 n \rceil}) = O(n)
+\FuncSpaceNew(n) \TextTilde 2^{\lceil \log_2 n \rceil} = O(n)
 \end{align*}

### 2017-10-24 Draft2/Appendix.tex
Finish removing P-notation?

@@
 \begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticAdd})]
-	We will consider the statement about addition first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:
+\end{proof}
 
-	\textit{Let $\hat{f} \in P(f(n))$ and $\hat{g} \in P(g(n))$. Then $\hat{f} + \hat{g} \in P(f(n) + g(n))$.}
-
-	We can show this by using the limit definition of $P$. For brevity, we will omit the parameter $n$ to each function. Since
+\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticMultiply})]
+	This can be easily shown by multiplying the limits corresponding to $\hat{f}$ and $\hat{g}$:
 
 	\begin{align*}
-	\lim_{n \to \infty} \left( \frac{\hat{f} + \hat{g}}{f + g} \right) &= \lim_{n \to \infty} \left( \frac{\hat{f}}{f + g} \right) + \lim_{n \to \infty} \left( \frac{\hat{g}}{f + g} \right)\\
-	&= \left( \lim_{n \to \infty} \frac{\hat{f}}{f} \right) \left( \lim_{n \to \infty} \left( \frac{f}{f + g} \right) \right) +\\
-	&\ \ \ \ \left( \lim_{n \to \infty} \frac{\hat{g}}{g} \right) \left( \lim_{n \to \infty} \left( \frac{g}{f + g} \right) \right)\\
-	&= \lim_{n \to \infty} \left( \frac{f}{f + g} \right) + \lim_{n \to \infty} \left( \frac{g}{f + g} \right)\\
-	&= \lim_{n \to \infty} \left( \frac{f + g}{f + g} \right)\\
+	\lim_{n \to \infty} \frac{\hat{f}}{f} &= 1\\
+	\lim_{n \to \infty} \frac{\hat{g}}{g} &= 1\\
+	\left( \lim_{n \to \infty} \frac{\hat{f}}{f} \right) \left( \lim_{n \to \infty} \frac{\hat{g}}{g} \right) &= 1 \cdot 1\\
+	\lim_{n \to \infty} \frac{\hat{f}\hat{g}}{fg} &= 1
+	\end{align*}
+
+	it follows that $\hat{f}\hat{g} \TextTilde fg$. The statement about division can be proved by flipping the fraction for $\hat{g}$ before multiplying, resulting in
+
+	\begin{align*}
+	\lim_{n \to \infty} \frac{\hat{f} / \hat{g}}{f / g} = 1
+	\end{align*}
+
+	This shows $\hat{f} / \hat{g} \TextTilde f / g$.
+\end{proof}
+
+\subsection{Removal of Lower-Order Terms}
+\label{pf:RemovesLowerOrderTerms}
+
+\begin{proof}[Proof (Theorem \ref{thm:RemovesLowerOrderTerms})]
+	Since
+
+	\begin{align*}
+	\lim_{n \to \infty} \left( \frac{f + g}{f} \right) &= \lim_{n \to \infty} \frac{f}{f} + \lim_{n \to \infty} \frac{g}{f}\\
+	&= 1 + 0\\
 	&= 1
@@
 
-	it follows that $\hat{f} + \hat{g} \in P(f(n) + g(n))$. The statement about subtraction can be proved in a similar fashion.
-\end{proof}
-
-\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticMultiply})]
-	We will consider the statement about multiplication first. Recall from the note at \ref{subsec:AsymptoticProperties} that this statement is equivalent to:
-
-	\textit{Let $\hat{f} \in P(f(n))$ and $\hat{g} \in P(g(n))$. Then $\hat{f}\hat{g} \in P(f(n)g(n))$.}
-
-	We can show this easily by multiplying the limits corresponding to $\hat{f}$ and $\hat{g}$:
-
-	\begin{align*}
-	\lim_{n \to \infty} \frac{\hat{f}(n)}{f(n)} &= 1\\
-	\lim_{n \to \infty} \frac{\hat{g}(n)}{g(n)} &= 1\\
-	\left( \lim_{n \to \infty} \frac{\hat{f}(n)}{f(n)} \right) \left( \lim_{n \to \infty} \frac{\hat{g}(n)}{g(n)} \right) &= 1 \cdot 1\\
-	\lim_{n \to \infty} \frac{\hat{f}(n)\hat{g}(n)}{f(n)g(n)} &= 1
-	\end{align*}
-
-	it follows that $\hat{f}\hat{g} \in P(f(n)g(n))$. The statement about division can be proved by flipping the fraction for $\hat{g}$ before multiplying, resulting in
-
-	\begin{align*}
-	\lim_{n \to \infty} \frac{\hat{f}(n) / \hat{g}(n)}{f(n) / g(n)} = 1
-	\end{align*}
-
-	This implies $\hat{f} / \hat{g} \in P(f(n) / g(n))$.
+	it follows that $f + g \TextTilde f$.
 \end{proof}
@@
 
-\begin{theorem}
-	If $f \TextTilde g$ and $g \TextTilde h$, then $f \TextTilde h$.
-\end{theorem}
-
-\begin{proof}
+\begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
 By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \TextTilde h$.
 \end{proof}
-
-\subsection{Removal of Lower-Order Terms}
-\label{pf:RemovesLowerOrderTerms}
-
-\begin{theorem}
-	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $P(f(n) + g(n)) = P(f(n))$.
-\end{theorem}
-
-\begin{proof}
-	\begin{align*}
-	\lim_{n \to \infty} \left( \frac{f(n) + g(n)}{f(n)} \right) &= \lim_{n \to \infty} \frac{f(n)}{f(n)} + \lim_{n \to \infty} \frac{g(n)}{f(n)}\\
-	&= 1 + 0\\
-	&= 1
-	\end{align*}
-
-	Then $f(n) + g(n) \in P(f(n))$. Since it is also true that $f(n) + g(n) \in P(f(n) + g(n))$, it follows from \ref{pf:Transitivity} that $P(f(n)) = P(f(n) + g(n))$.
-\end{proof}

### 2017-10-24 Draft2/Abstract.tex
Revise Intro, Abstract

@@
-This paper introduces the \textbf{growth array}, an array-like data structure designed to be efficient at appending elements.
-They offer substantial time and memory savings over dynamic arrays when a large number of elements are appended.
-Growth arrays also support other list operations, such as random access, iteration, and insertion/deletion at an index.
-However, they perform no better, or slightly worse, than dynamic arrays for those methods.
-Also, if the size of the data is known beforehand, allocating a raw array with that size and appending to it is faster than appending to a growth array.
+This paper introduces \textbf{growth arrays}, array-like data structures that are designed for appending elements.
+When the number of items is not known beforehand but is expected to be large, they are more efficient than dynamic arrays by a constant factor.
+Growth arrays support all operations dynamic arrays do, such as random access, iteration, and insertion or deletion at an index.
+However, they perform no better, or slightly worse, than dynamic arrays for operations other than appending.

### 2017-10-24 Draft2/Intro.tex
Remove footnotes
Revise Intro, Abstract

@@
-In imperative languages, the dynamic array is the most common data structure used by programs\footnote{}.
-People often want to add multiple items to a list and then iterate it, which dynamic arrays make simple and efficient.
-But can it be said dynamic arrays have the \textit{most} efficient algorithm for this pattern?
+In imperative languages, the dynamic array is the most common data structure used by programs.
+People often want to add multiple items to a collection and then iterate it, which dynamic arrays make simple and efficient.
+But can it be said they have the \textit{most} efficient algorithm for this pattern?
 
 In this paper, I introduce an alternative data structure to the dynamic array, called the \textbf{growth array}.
-It is more efficient than the dynamic array at appending, particularly for large numbers of items.
-This is due to how it 'grows' once it cannot fit any more items in its buffer.
+It is more efficient than the dynamic array at appending large numbers of items.
+This is due to how it 'grows' once it cannot fit more items in its buffer.
 
@@
 The new buffer they allocate represents a continuation of the items from the old buffer.
-For example, if the old buffer contained items $0-31$, the new buffer would contain items $32$ and beyond.
+For example, if the old buffer contained items $0 - 31$, the new buffer would contain items $32$ and beyond.
 Because of this, growth arrays allocate less memory to store the same number of items, and they do not need to copy items from the old buffer to the new one.
 
-Growth arrays have some caveats, however.
-They perform no better, or slightly worse, than dynamic arrays with respect to other operations.
-In particular, random access involves significantly more instructions than it does for dynamic arrays.
-Additionally, since growth arrays are not contiguous in memory, they may have poorer locality than dynamic arrays, and cannot be passed to external code that accepts contiguous buffers.
+Growth arrays have caveats, however.
+They perform no better, or slightly worse, than dynamic arrays for operations other than appending.
+Random access, in particular, involves many more instructions than it does for dynamic arrays.
+Also, since growth arrays are not contiguous in memory, they may have poorer locality than dynamic arrays, and cannot be passed to external code that accepts contiguous buffers.
 
-It is also worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are completely unnecessary.
-A raw array could simply be allocated with the known size, and items could be appended more quickly to it.
-Thus, growth arrays are only advantageous for scenarios where an unknown amount of data will be appended.
+It is worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are completely unnecessary.
+A raw array could simply be allocated with the known size, and items could be appended to it just as quickly.
+Thus, growth arrays are only beneficial for cases where the amount of data to be appended is unknown, but is expected to be large.

### 2017-10-24 Draft2/AsymptoticNotation.tex
Finish removing P-notation?
Take care of Section 3

@@
 
-I will use the $\TextTilde$ relation to analyze time complexity. It is defined as follows:
+To analyze time complexity, I will use the $\sim$ relation. It is defined as follows:
 
 \begin{align*}
-f(n) \TextTilde g(n) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
+f(n) \sim g(n) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
 \end{align*}
@@
 
-Notice that while $O(2n) = O(n)$, $2n \TextTildeNot n$.
-Thus, $\TextTilde$ makes it possible to distinguish between a function that uses $n$ space and one that uses $2n$ space.
-\HdrNote A consequence of this is that bases for logarithms cannot be omitted, like in big-O notation.
+Notice that while $O(2n) = O(n)$, $2n \not\sim n$.
+Thus, $\sim$ makes it possible to distinguish between a function that uses $n$ space and one that uses $2n$ space.
+{\HdrNote} A consequence of this is that bases for logarithms cannot be omitted, like in big-O notation.
 
@@
 
-A useful property $\TextTilde$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergesOverArithmetic}.
+A useful property $\sim$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergesOverArithmetic}.
 
@@
 	\begin{align*}
-	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
-		(\hat{f} + \hat{g}) \TextTilde (f + g)\\
-		(\hat{f} - \hat{g}) \TextTilde (f - g)
+	(\hat{f} \sim f) \land (\hat{g} \sim g) \rightarrow \begin{cases}
+		(\hat{f} + \hat{g}) \sim (f + g)\\
+		(\hat{f} - \hat{g}) \sim (f - g)
 	\end{cases}
@@
 	\begin{align*}
-	\hat{f} \TextTilde f \land \hat{g} \TextTilde g \rightarrow \begin{cases}
-	\hat{f}\hat{g} \TextTilde fg\\
-	\hat{f} / \hat{g} \TextTilde f / g
+	(\hat{f} \sim f) \land (\hat{g} \sim g) \rightarrow \begin{cases}
+	\hat{f}\hat{g} \sim fg\\
+	\hat{f} / \hat{g} \sim f / g
 	\end{cases}
@@
 
-Another nice property $\TextTilde$ and $O$ have in common is that lower-order terms are removed from consideration.
-For example, $n \TextTilde n + \log_2 n$.
+Another nice property $\sim$ and $O$ have in common is that lower-order terms are removed from consideration.
+For example, $n \sim (n + \log_2 n)$.
 This is stated by the below theorem, which is proved in \ref{pf:RemovesLowerOrderTerms}.
@@
 \begin{theorem}
-	If $\lim_{n \to \infty} \frac{g(n)}{f(n)} = 0$, then $f(n) + g(n) \TextTilde f(n)$.
+\label{thm:RemovesLowerOrderTerms}
+	If $\lim_{n \to \infty} g / f = 0$, then $f + g \sim f$.
 \end{theorem}
+
+Finally, $\sim$ is a transitive operator. That is,
+
+\begin{theorem}
+\label{thm:Transitivity}
+	If $f \sim g$ and $g \sim h$, then $f \sim h$.
+\end{theorem}
+
+This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$. It is proved in \ref{pf:Transitivity}.

### 2017-10-25 Draft2/Appending.Dynamic.tex
Labels
Get the theorems straight?

@@
 
-I will first implement appending for dynamic arrays. Let $\VarList$ be a dynamic array. The following definitions are used in the code:
+I will implement appending for dynamic arrays first. Let $\VarList$ be a dynamic array. The following definitions are used in the code:
 
@@
 \begin{lemma}
-\label{CapacitySequence}
+\label{lem:CapacitySequence}
 	Let $\VarList$ by a dynamic array.
@@
 
-From \ref{CapacitySequence} I know the exact capacities $\VarList$ takes on as $n$ items are appended.
+From \ref{lem:CapacitySequence} I know the exact capacities $\VarList$ takes on as $n$ items are appended.
 Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.

### 2017-10-25 Draft2/AsymptoticNotation.tex
Get the theorems straight?

@@
 \begin{align*}
-f(n) \sim g(n) \leftrightarrow \lim_{n \to \infty} \frac{g(n)}{f(n)} = 1
+f \sim g \leftrightarrow \lim_{n \to \infty} \frac{g}{f} = 1
 \end{align*}
 
-$f$ and $g$ may be used as shorthand to denote $f(n)$ and $g(n)$, respectively.
+This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.
 
@@
 
-A useful property $\sim$ shares with $O$ is that it merges over arithmetic operations. This is stated by the following two theorems, which are proved in \ref{pf:MergesOverArithmetic}.
+Here, I define various properties of the $\sim$ relation that will be used in my proofs. Proofs of these properties can be found in the appendix.
+
+The following two theorems state that $\sim$ can "merge", or un-distribute, over arithmetic operations. This is a property shared with big-O.
 
@@
 
-Another nice property $\sim$ and $O$ have in common is that lower-order terms are removed from consideration.
-For example, $n \sim (n + \log_2 n)$.
-This is stated by the below theorem, which is proved in \ref{pf:RemovesLowerOrderTerms}.
+The following theorem states that lower-order terms may be removed. For example, $(n + \log_2 n) \sim n$.
 
@@
 \label{thm:RemovesLowerOrderTerms}
-	If $\lim_{n \to \infty} g / f = 0$, then $f + g \sim f$.
+	If $\lim_{n \to \infty} g / f = 0$, then $f + O(g) \sim f$.
 \end{theorem}
 
-Finally, $\sim$ is a transitive operator. That is,
+The following theorem shows that $\sim$ is a transitive relation. This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$.
 
@@
 
-This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$. It is proved in \ref{pf:Transitivity}.
+The following theorem states that if two functions are asymptotic, then they belong to the same big-O class.
+
+\begin{theorem}
+\label{thm:SameBigOClass}
+	If $f \sim g$ and $g = O(h)$, then $f = O(h)$.
+\end{theorem}

### 2017-10-25 Draft2/CommonOperations.Blurb.tex
Get the theorems straight?

@@
-In this section, I implement common operations for dynamic and growth arrays, and analyze their time complexity. I also analyze space complexity of operations that allocate memory.
+In this section, I implement the most common operations for dynamic and growth arrays, then analyze their time complexity. If the operation allocates memory, I also analyze its space complexity.

### 2017-10-25 Draft2/FieldsProperties.tex
Tweak "Fields and Properties"
Get the theorems straight?

@@
 	\begin{algorithmic}
+		\Procedure{$\FuncConstructor$}{$\VarList$}
 			\State $\VarList.\FieldBuffer \gets \FuncNewArray(0)$
 			\State $\VarList.\FieldSize \gets 0$
+		\EndProcedure
 	\end{algorithmic}
@@
 	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
-	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. It returns a dynamic array of buffers that have already been filled. This can be thought of as a two-dimensional array.
+	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. It returns a dynamic array of references to buffers that have already been filled. This can be thought of as a two-dimensional array.
+		\subitem It may seem strange for growth arrays to use dynamic arrays internally.
+There is little harm from the extra copying and allocations these dynamic arrays perform, however, since only $O(\log n)$ references are appended to them (proved in [ref3]).
 	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
@@
 	\begin{algorithmic}
+		\Procedure{$\FuncConstructor$}{$\VarList$}
 			\State $\VarList.\FieldHead \gets \FuncNewArray(0)$
@@
 			\State $\VarList.\FieldCapacity \gets 0$
+		\EndProcedure
 	\end{algorithmic}

### 2017-10-25 Draft2/Appending.Dynamic.tex
Lists

@@
 \begin{description}
-	\item[initial capacity] The capacity of a dynamic a array when one item is appended to it. I denote this $\VarInitCapacity$.\\
+	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of a dynamic a array when one item is appended to it.\\
 	(The capacity of any dynamic array with size zero should be zero.)
-	\item[growth factor] The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows. I denote this with $\VarGrowthFactor$.
+	\item[growth factor] Denoted by $\VarGrowthFactor$. The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows.
 \end{description}

### 2017-10-25 Draft2/Appending.Dynamic.tex
Add predefined functions section, more work

@@
 	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of a dynamic a array when one item is appended to it.\\
-	(The capacity of any dynamic array with size zero should be zero.)
+	{\HdrNote} The capacity of any dynamic array with size zero should be zero.
 	\item[growth factor] Denoted by $\VarGrowthFactor$. The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows.
@@
 				\State $new\ buf \gets \FuncNewArray(\VarList.\FieldSize \times \VarGrowthFactor)$
-				\State $\FuncArrayCopy(source: \VarList.\FieldBuffer, dest: new\ buf, len: \VarList.\FieldSize)$
+				\State $\FuncArrayCopy(\VarList.\FieldBuffer, new\ buf, \VarList.\FieldSize)$
 				\State $\VarList.\FieldBuffer \gets new\ buf$
@@
 Before I analyze the time complexity of $\FuncAppend$, I consider a different method for measuring its cost.
-Suppose I start with an empty list and $n$ elements are appended.
+Suppose I start with an empty collection and $n$ elements are appended.
 How many times is an element stored in an array?
@@
 
-In the above code, one write is performed after the conditional, so it is apparent that $\FuncWrites(n) \geq n$ after $n$ appends.
+In the code for $\FuncAppend$, one array store is performed unconditionally, so it is apparent that $\FuncWrites(n) \geq n$ after $n$ appends.
 However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\FuncWrites(n)$, I need to analyze when $\FuncGrow$ is called.
-Consider the following lemma:
+To do this, I use the following lemma:
+
+% Bookmark
 

### 2017-10-25 Draft2/Appending.Dynamic.tex
Work

@@
 
-% Bookmark
-
 \begin{lemma}
 \label{lem:CapacitySequence}
-	Let $\VarList$ by a dynamic array.
-As $n$ items are appended, the sequence of capacities $\VarList$ takes on is $$S_C = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$$.
+	Let $\VarList$ by a dynamic array. Let its \textbf{capacity sequence}, $\VarCapacitySequence$, be the capacities $\VarList$ takes on as $n$ items are appended. Then
+
+	$$
+	\VarCapacitySequence = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
+	$$
 \end{lemma}
+
+% Bookmark
 

### 2017-10-25 Draft2/Appending.Dynamic.tex
Renaming

--- 2017-10-25 Draft2/Appending.Dynamic.tex
@@
 
+\begin{lemma}
+\label{lem:CapacitySeq}
+	Let $\VarList$ by a dynamic array. Let its \textbf{capacity sequence}, $\VarCapacitySeq$, be the capacities $\VarList$ takes on as $n$ items are appended. Then
+
+	$$
+	\VarCapacitySeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
+	$$
+\end{lemma}
+
 % Bookmark
-
-\begin{lemma}
-\label{lem:CapacitySequence}
-	Let $\VarList$ by a dynamic array.
-As $n$ items are appended, the sequence of capacities $\VarList$ takes on is $$S_C = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$$.
-\end{lemma}
 
@@
 
-From \ref{lem:CapacitySequence} I know the exact capacities $\VarList$ takes on as $n$ items are appended.
+From \ref{lem:CapacitySeq} I know the exact capacities $\VarList$ takes on as $n$ items are appended.
 Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.

### 2017-10-25 Draft2/Appending.Growth.tex
Take care of Section 3
Renaming

@@
 
-\ref{lem:CapacitySequence} still holds, since all of the assumptions made there are also true for growth arrays.
+\ref{lem:CapacitySeq} still holds, since all of the assumptions made there are also true for growth arrays.
 In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:
@@
 
-I now approximate this expression using $\TextTilde$. First, I approximate $k$ using big-O:
+I now approximate this expression using $\sim$. First, I approximate $k$ using big-O:
 
@@
 
-Now, the $k$-term disappears when using $\TextTilde$ to approximate $\FuncWritesNew(n)$, leaving just $n$:
+Now, the $k$-term disappears when using $\sim$ to approximate $\FuncWritesNew(n)$, leaving just $n$:
 
 \begin{align*}
-\FuncWritesNew(n) &\TextTilde n + \FuncWrites(k)\\
+\FuncWritesNew(n) &\sim n + \FuncWrites(k)\\
 &= n + O(\log n)\\
-&\TextTilde n
+&\sim n
 \end{align*}
@@
 \begin{align*}
-\FuncSpaceNew(n) \TextTilde 2^{\lceil \log_2 n \rceil} = O(n)
+\FuncSpaceNew(n) \sim 2^{\lceil \log_2 n \rceil} = O(n)
 \end{align*}

### 2017-10-25 Draft2/Appending.Dynamic.tex
Remove $$

@@
 
-	$$
+	\begin{align*}
 	\VarCapacitySeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
-	$$
+	\end{align*}
 \end{lemma}
@@
 From then on, it can only grow by a factor of $\VarGrowthFactor$ via $\FuncGrow$, so if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity.
-By induction, the rest of the sequence is $$\left\{ \VarGrowthFactor^i\VarInitCapacity \right\}_{i = 1}^k$$ for some $k$.
+By induction, the rest of the sequence is
+
+	\begin{align*}
+	\left\{ \VarGrowthFactor^i\VarInitCapacity \right\}_{i = 1}^k
+	\end{align*}
+
+	for some $k$.
 Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $k$ is the smallest integer for which $\VarGrowthFactor^k\VarInitCapacity \geq n$.
@@
 So $\VarGrowthFactor^k\VarInitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\VarGrowthFactor^{k - 1}\VarInitCapacity$ for $k \geq 1$.
-Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil - 1}\VarInitCapacity$$
+Then $\FuncGrow$ was called at the sizes
+
+\begin{align*}
+S_R = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil - 1}\VarInitCapacity
+\end{align*}
 
@@
 [ref1]
-$$
+\begin{align*}
 \FuncWrites(n) = n + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
-$$
+\end{align*}
 

### 2017-10-25 Draft2/Appending.Dynamic.tex
More work

@@
 	Let $\VarList$ by a dynamic array. Let its \textbf{capacity sequence}, $\VarCapacitySeq$, be the capacities $\VarList$ takes on as $n$ items are appended. Then
-
 	\begin{align*}
@@
 From then on, it can only grow by a factor of $\VarGrowthFactor$ via $\FuncGrow$, so if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity.
-By induction, the rest of the sequence is
+By induction, the rest of the sequence is $\left( \VarGrowthFactor^i\VarInitCapacity \right)_{i = 1}^\VarUseful$ for some $\VarUseful$.
 
+	Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $\VarUseful$ is the smallest integer for which $\VarGrowthFactor^\VarUseful\VarInitCapacity \geq n$.
+Using this property, I now derive $\VarUseful$.
 	\begin{align*}
-	\left\{ \VarGrowthFactor^i\VarInitCapacity \right\}_{i = 1}^k
+	\VarGrowthFactor^\VarUseful\VarInitCapacity &\geq n > \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity\\
+	\VarGrowthFactor^\VarUseful &\geq \frac{n}{\VarInitCapacity} > \VarGrowthFactor^{\VarUseful - 1}\\
+	\VarUseful &\geq \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity > \VarUseful - 1\\
 	\end{align*}
-
-	for some $k$.
-Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $k$ is the smallest integer for which $\VarGrowthFactor^k\VarInitCapacity \geq n$.
-Using this property, I now derive $k$.
-
+	Since $\VarUseful$ is an integer,
 	\begin{align*}
-	\VarGrowthFactor^k\VarInitCapacity &\geq n\\
-	\VarGrowthFactor^k &\geq \frac{n}{\VarInitCapacity}\\
-	k &\geq \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity\\
-	k &\geq \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity > k - 1\\
-	k &= \big\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \big\rceil
+	\VarUseful &= \big\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \big\rceil
 	\end{align*}
-
-	Then the final term in the sequence is $\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$, completing the proof.
+	The final term in the sequence is $\VarGrowthFactor^\VarUseful = \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$, completing the proof.
 \end{proof}
@@
 Now, consider that to grow by $\VarGrowthFactor$, $\FuncGrow$ must be called.
-So $\VarGrowthFactor^k\VarInitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\VarGrowthFactor^{k - 1}\VarInitCapacity$ for $k \geq 1$.
+So $\VarGrowthFactor^i\VarInitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\VarGrowthFactor^{i - 1}\VarInitCapacity$ for $i \geq 1$.
 Then $\FuncGrow$ was called at the sizes
-
 \begin{align*}
-S_R = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil - 1}\VarInitCapacity
+\VarGrowSeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity
 \end{align*}
-
-Each time $\FuncGrow$ is called, $i$ items are copied where $i$ is the current size of the dynamic array. Then the total number of items copied for $n$ appends is
-
+Each time $\FuncGrow$ is called, $s$ items are copied where $s$ is the current size of the dynamic array. Then the total number of items copied for $n$ appends is
 \begin{align*}
-0 + \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \ldots + \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil - 1}\VarInitCapacity &= \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
+\sum_{s \in \VarGrowSeq} s &= 0 + \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \ldots + \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity\\
+&= \left( \frac{\VarGrowthFactor^{\VarUseful} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 \end{align*}
-
-Finally, counting the writes made for every item in $\FuncAppend$, I finally find an explicit formula for $\FuncWrites(n)$.
-
+Counting the writes made for every item in $\FuncAppend$, I finally find an explicit formula for $\FuncWrites(n)$.
 [ref1]
 \begin{align*}
-\FuncWrites(n) = n + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
+\FuncWrites(n) = n + \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 \end{align*}
+This expression looks clean at a glance, but $\VarUseful$ implicitly depends on $n$ and uses the ceiling function and logarithms.
+To make it easier to analyze, I will asymptotically bound this expression.
 
 [ref2]
-To make this expression easier to work with, I will write it in big-P notation to approximate it for large $n$.
 First I note that $\log_{\VarGrowthFactor} k \leq \lceil \log_{\VarGrowthFactor} k \rceil < \left( \log_{\VarGrowthFactor} k \right) + 1$ for any $k > 0$, so $k \leq \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k \rceil} < \VarGrowthFactor{k}$.
+Since $\VarUseful = \left\lceil \log_{\VarGrowthFactor} \frac{n}{\VarInitCapacity} \right\rceil$, $\frac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \frac {\VarGrowthFactor{n}} \VarInitCapacity$.
 Then
-
 \begin{align*}
-\FuncWrites(n) &= n + \left( \frac{\VarGrowthFactor^{\big\lceil \log_{\VarGrowthFactor} \left( \frac {n} {\VarInitCapacity} \right) \big\rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-n + \left( \frac{\frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \leq \FuncWrites(n) &< n + \left( \frac{\VarGrowthFactor\frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+\FuncWrites(n) &= n + \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+n + \left( \frac{n / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \leq \FuncWrites(n) &< n + \left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
 n + \left( \frac{n - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \leq \FuncWrites(n) &< n + \left( \frac{\VarGrowthFactor{n} - \VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
-P\left( n + \left( \frac{n - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \right) \leq P\left( \FuncWrites(n) \right) &< P\left( n + \left( \frac{\VarGrowthFactor{n} - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \right)\\
-P\left( \left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \right) \leq P\left( \FuncWrites(n) \right) &< P\left( \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n \right)
+n + \left( \frac{n - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \RelLessEqual \FuncWrites(n) &\RelLess n + \left( \frac{\VarGrowthFactor{n} - \VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \RelLessEqual \FuncWrites(n) &\RelLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
 \end{align*}
@@
 
-I wish to find the space allocated while appending $n$ items to a dynamic array.
-I denote this quantity $\FuncSpace(n)$, and define it as the total length of all arrays allocated during $n$ $\FuncAppend$ calls.
+I wish to find the space allocated when $n$ items are appended to a dynamic array.
+I call this quantity the \textbf{space cost}, denote it $\FuncSpace(n)$, and define it as the total length of arrays allocated by $n$ $\FuncAppend$ calls.
 I now derive a formula for $\FuncSpace(n)$.
 
-From \ref{lem:CapacitySeq} I know the exact capacities $\VarList$ takes on as $n$ items are appended.
-Dynamic arrays also have the property that $i \in S_C$ iff an array of length $i$ was allocated.
+From \ref{lem:CapacitySeq}, I know the capacity sequence of $\VarList$.
+Dynamic arrays also have the property that $c \in \VarCapacitySeq$ iff an array of length $c$ was allocated.
 Then the total length of arrays allocated is
@@
 \begin{align*}
-\FuncSpace(n) &= \sum_{i \in S_C} i\\
-&= 0 + \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \VarGrowthFactor^2\VarInitCapacity + \ldots + \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity\\
-&= \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil + 1} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
+\FuncSpace(n) &= \sum_{c \in \VarCapacitySeq} c\\
+&= 0 + \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \VarGrowthFactor^2\VarInitCapacity + \ldots + \VarGrowthFactor^\VarUseful\VarInitCapacity\\
+&= \left( \frac{\VarGrowthFactor^{\VarUseful + 1} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 \end{align*}
 
-Using the identity in [ref2] again, I bound its big-P complexity:
+Using the identity in [ref2] again, I asymptotically bound $\FuncSpace(n)$:
 
 \begin{align*}
-\left( \frac{\VarGrowthFactor \frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \leq \FuncSpace(n) &< \left( \frac{\VarGrowthFactor^2 \frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-P\left( \left( \frac{\VarGrowthFactor \frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \right) \leq P\left( \FuncSpace(n) \right) &< P\left( \left( \frac{\VarGrowthFactor^2 \frac{n}{\VarInitCapacity} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \right)\\
-P\left( \left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \right) \leq P\left( \FuncSpace(n) \right) &< P\left( \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n \right)
+\left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \leq \FuncSpace(n) &< \left( \frac{\VarGrowthFactor^2{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+\left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \RelLessEqual \FuncSpace(n) &\RelLess \left( \frac{\VarGrowthFactor^2{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \RelLessEqual \FuncSpace(n) &\RelLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n
 \end{align*}

### 2017-11-01 Draft2/Appending.Dynamic.tex
Lots of good stuff

@@
 \label{lem:CapacitySeq}
-	Let $\VarList$ by a dynamic array. Let its \textbf{capacity sequence}, $\VarCapacitySeq$, be the capacities $\VarList$ takes on as $n$ items are appended. Then
+	Let $\VarList$ by a dynamic array.
+Let its \textbf{capacity sequence}, $\VarCapacitySeq$, be the capacities $\VarList$ takes on as $n$ items are appended.
+For $n = 0$, trivially $\VarCapacitySeq = (0)$.
+For $n > 0$,
 	\begin{align*}
-	\VarCapacitySeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
+	\VarCapacitySeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)}\VarInitCapacity
 	\end{align*}
@@
 
-% Bookmark
+\begin{proof}
+	We use the following properties of dynamic arrays:
+	\begin{enumerate}
+		\item The capacity of an empty dynamic array is $0$.
+		\item The capacity of a dynamic array with one item is $\VarInitCapacity$.
+		\item Once it is non-empty, the capacity of a dynamic array can only grow by $\VarGrowthFactor$.
+		\item The capacity is only as large as it needs to be.
+That is, if $\VarCapacitySeq_i$ is the capacity for size $n$, then $n > \VarCapacitySeq_{i - 1}$.
+($i > 1$ since $n > 0$, so $\VarCapacitySeq_{i - 1}$ must be defined.)
+	\end{enumerate}
+	Assumptions (1) and (2) immediately show $\VarCapacitySeq_1 = 0$ and $\VarCapacitySeq_2 = \VarInitCapacity$.
+Assumption (3) shows that if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity, then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity.
+By induction, the rest of the sequence is $\left( \VarGrowthFactor^i\VarInitCapacity \right)_{i = 1}^\VarUseful = \left( \VarCapacitySeq_i \right)_{i = 3}^{\VarUseful + 2}$ for some integer $\VarUseful$.
 
-\begin{proof}
-	The capacity starts out at zero and becomes $\VarInitCapacity$ once one element is appended.
-From then on, it can only grow by a factor of $\VarGrowthFactor$ via $\FuncGrow$, so if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity.
-By induction, the rest of the sequence is $\left( \VarGrowthFactor^i\VarInitCapacity \right)_{i = 1}^\VarUseful$ for some $\VarUseful$.
-
-	Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $\VarUseful$ is the smallest integer for which $\VarGrowthFactor^\VarUseful\VarInitCapacity \geq n$.
-Using this property, I now derive $\VarUseful$.
+	By assumption (4), $\VarCapacitySeq_{\VarUseful + 2} \geq n > \VarCapacitySeq_{\VarUseful + 1}$.
+Supposing $n > \VarInitCapacity$, from (4) again I know that the rest of the sequence contains at least one term.
+Then $\VarUseful \geq 1$, so $\VarCapacitySeq_{\VarUseful + 2} = \VarGrowthFactor^\VarUseful\VarInitCapacity$ and $\VarCapacitySeq_{\VarUseful + 1} = \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity$.
+I can now derive $\VarUseful$:
 	\begin{align*}
@@
 	\end{align*}
-	The final term in the sequence is $\VarGrowthFactor^\VarUseful = \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$, completing the proof.
+	If $n \leq \VarInitCapacity$, then necessarily $\VarCapacitySeq_{\VarUseful + 2} = \VarGrowthFactor^\VarUseful\VarInitCapacity$ is empty and $\VarUseful = 0$.
+Since $\VarUseful \geq 1$ for the previous case, we may obtain a general formula for $\VarUseful$ like so:
+	\begin{align*}
+	\VarUseful &= \max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)
+	\end{align*}
+	The final term in the sequence is $\VarGrowthFactor^\VarUseful\VarInitCapacity = \VarGrowthFactor^{\max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)}\VarInitCapacity$, completing the proof.
 \end{proof}

### 2017-11-01 Draft2/Appending.Growth.tex
Remove $$
Lots of good stuff

@@
 
-I again start off by finding the write cost when $n$ are appended.
-I give the write cost function a slightly different name, $\FuncWritesNew(n)$, so I can compare it to $\FuncWrites(n)$ later.
-I also use $\VarGrowthFactorNew$ and $\VarInitCapacityNew$ instead of $\VarGrowthFactor$ and $\VarInitCapacity$ for the growth factor and initial capacity, respectively.
+I again start off by finding the write cost for $n$ items.
+I will denote mathematical variables and functions associated with growth arrays with a hat on top, to avoid confusion with their dynamic array counterparts.
+For example, $\FuncWritesNew(n)$ will denote growth arrays' write cost function, $\VarInitCapacityNew$ their initial capacity, $\VarGrowthFactorNew$ their growth factor, and so on.
 
-\ref{lem:CapacitySeq} still holds, since all of the assumptions made there are also true for growth arrays.
-In particular, although growth arrays grow differently than dynamic arrays, the following claim is still true:
+\ref{lem:CapacitySeq} still holds, since all of the assumptions made there still hold for growth arrays.
+In particular, although growth arrays use a different growth algorithm than dynamic arrays, the following claim is still true:
 
 \begin{lemma}
-	The capacity of a growth array grows by a constant factor $\VarGrowthFactorNew$ after the first time it is called.
+	The capacity of a non-empty growth array grows by the constant factor $\VarGrowthFactorNew$.
 \end{lemma}
@@
 \begin{proof}
-	I prove that the algorithm ensures this using induction.
+	I prove that the $\FuncGrow$ algorithm always enforces this using induction.
+I induct on the number of times $\FuncGrow$ is called, $k$, showing that for all $k \geq 2$, $\FuncGrow$ behaves correctly when called the $k$th time.
+(At $k = 1$, the growth array is empty, so its behavior is not relevant to this lemma.) I will let $c_i$ and $c_f$ denote the initial and final capacities and $h_i$ and $h_f$ denote the initial and final head capacities for the $k$th call, respectively.
 
-	For the base case, consider the second time $\FuncGrow$ is called: the current capacity is $\VarInitCapacityNew$, and the next (total) capacity should be $\VarGrowthFactorNew\VarInitCapacityNew$.
-Then a buffer of size $(\VarGrowthFactorNew - 1)\VarInitCapacityNew$ should be appended, and that is what the algorithm does.
+	At $k = 2$, $c_i = \VarInitCapacityNew$.
+I wish to show that $c_f = \VarGrowthFactorNew\VarInitCapacityNew$.
+This happens if and only if the next buffer has size $\Delta c = (\VarGrowthFactorNew - 1)\VarInitCapacityNew$, which the algorithm ensures.
 
-	For $i \geq 2$, given the algorithm behaves correctly the $i$th time it is called, I wish to show it behaves correctly the $(i + 1)$th time.
-From the inductive hypothesis, when the algorithm is called the $(i + 1)$th time, the current capacity is $\VarGrowthFactorNew^i\VarInitCapacityNew$ and the head capacity is $(\VarGrowthFactorNew^i - \VarGrowthFactorNew^{i - 1})\VarInitCapacityNew$.
-The next (total) capacity should be $\VarGrowthFactorNew^{i + 1}\VarInitCapacityNew$, and the next head capacity should be $(\VarGrowthFactorNew^{i + 1} - \VarGrowthFactorNew^i)\VarInitCapacityNew$, which is $\VarGrowthFactorNew$ times the current head capacity.
-The algorithm determines the capacity of the next buffer in this manner, proving the inductive step and completing the induction.
+	For $k > 2$, by induction $c_i = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew$ and $h_i = (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew$.
+I wish to show $c_f = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$ and $h_f = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$.
+Because $k > 2$, the algorithm will calculate $h_f$ as $\VarGrowthFactorNew$ times $h_i$.
+Then $h_f = \VarGrowthFactorNew h_i = \VarGrowthFactorNew (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$ as desired, and $c_f = c_i + h_f = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew + (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$, concluding the proof.
 \end{proof}
+
+% Bookmark
 
@@
 
-$$
+\begin{align*}
 S_R = 0,\ \VarInitCapacityNew,\ \VarGrowthFactorNew\VarInitCapacityNew,\ \VarGrowthFactorNew^2\VarInitCapacityNew,\ \ldots\ \VarGrowthFactorNew^{\lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil - 1}\VarInitCapacityNew
-$$
+\end{align*}
 
@@
 
-$$
+\begin{align*}
 \FuncWritesByGrow(n) = k + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
-$$
+\end{align*}
 
@@
 
-$$
+\begin{align*}
 \FuncWritesNew(n) = n + k + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
-$$
+\end{align*}
 

### 2017-11-01 Draft2/Appending.Growth.tex
Spice up a lemma

@@
 I induct on the number of times $\FuncGrow$ is called, $k$, showing that for all $k \geq 2$, $\FuncGrow$ behaves correctly when called the $k$th time.
-(At $k = 1$, the growth array is empty, so its behavior is not relevant to this lemma.) I will let $c_i$ and $c_f$ denote the initial and final capacities and $h_i$ and $h_f$ denote the initial and final head capacities for the $k$th call, respectively.
+(At $k = 1$, the growth array is empty, so its behavior is not relevant to this lemma.) I will let $c_i(k)$ and $c_f(k)$ denote the initial/final capacities and $h_i(k)$ and $h_f(k)$ denote the initial/final head capacities for the $k$th call, respectively.
 
-	At $k = 2$, $c_i = \VarInitCapacityNew$.
-I wish to show that $c_f = \VarGrowthFactorNew\VarInitCapacityNew$.
-This happens if and only if the next buffer has size $\Delta c = (\VarGrowthFactorNew - 1)\VarInitCapacityNew$, which the algorithm ensures.
+	For $k = 2$, $c_i(2) = \VarInitCapacityNew$.
+I wish to show that $c_f(2) = \VarGrowthFactorNew\VarInitCapacityNew$.
+This happens if and only if the next buffer has size ${\Delta c}(2) = (\VarGrowthFactorNew - 1)\VarInitCapacityNew$, which the algorithm ensures.
 
-	For $k > 2$, by induction $c_i = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew$ and $h_i = (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew$.
-I wish to show $c_f = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$ and $h_f = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$.
+	For $k > 2$, by induction $c_i(k) = c_f(k - 1) = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew$ and $h_i(k) = h_f(k - 1) = (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew$.
+I wish to show $c_f(k) = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$ and $h_f(k) = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$.
 Because $k > 2$, the algorithm will calculate $h_f$ as $\VarGrowthFactorNew$ times $h_i$.
-Then $h_f = \VarGrowthFactorNew h_i = \VarGrowthFactorNew (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$ as desired, and $c_f = c_i + h_f = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew + (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$, concluding the proof.
+Then
+	\begin{align*}
+	h_f &= \VarGrowthFactorNew h_i\\
+	&= \VarGrowthFactorNew (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew\\
+	&= (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew
+	\end{align*}
+	and
+	\begin{align*}
+	c_f &= c_i + h_f\\
+	&= \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew + (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew\\
+	&= \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew
+	\end{align*}
+	as desired.
 \end{proof}

### 2017-11-01 Draft2/Appending.Dynamic.tex
More cleanup

@@
 	\end{align*}
-	If $n \leq \VarInitCapacity$, then necessarily $\VarCapacitySeq_{\VarUseful + 2} = \VarGrowthFactor^\VarUseful\VarInitCapacity$ is empty and $\VarUseful = 0$.
-Since $\VarUseful \geq 1$ for the previous case, we may obtain a general formula for $\VarUseful$ like so:
+	If $n \leq \VarInitCapacity$, then necessarily $\left( \VarCapacitySeq_i \right)_{i = 3}^{\VarUseful + 2}$ is empty and $\VarUseful = 0$.
+Since $\VarUseful \geq 1$ for the previous case, and (for this case) if $n \leq \VarInitCapacity$ then $\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil \leq 0$, a general formula for $\VarUseful$ is as follows:
 	\begin{align*}
@@
 
-[make lemma]
-Now, consider that to grow by $\VarGrowthFactor$, $\FuncGrow$ must be called.
-So $\VarGrowthFactor^i\VarInitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\VarGrowthFactor^{i - 1}\VarInitCapacity$ for $i \geq 1$.
-Then $\FuncGrow$ was called at the sizes
+[make corollary]
+Clearly, if $C_i$ is defined for $i > 1$, then $\FuncGrow$ must have been called at the size $C_{i - 1}$.
+Then the \textbf{growth sequence}, the sequence of sizes at which $\FuncGrow$ is called for $n$ appends, must be $\VarCapacitySeq$ with the last element removed:
 \begin{align*}
-\VarGrowSeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity
+\VarGrowSeq = \left( \VarCapacitySeq_i \right)_{i = 1}^{|\VarCapacitySeq| - 1}
 \end{align*}
@@
 \end{align*}
-
 \HdrSpaceComplex
@@
 Then the total length of arrays allocated is
-
 \begin{align*}
@@
 \end{align*}
-
 Using the identity in [ref2] again, I asymptotically bound $\FuncSpace(n)$:

### 2017-11-01 Draft2/Appending.Growth.tex
Even more
More cleanup

@@
 \begin{lemma}
+\label{lem:GrowthArraysGrowthFactor}
 	The capacity of a non-empty growth array grows by the constant factor $\VarGrowthFactorNew$.
@@
 I wish to show $c_f(k) = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$ and $h_f(k) = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$.
-Because $k > 2$, the algorithm will calculate $h_f$ as $\VarGrowthFactorNew$ times $h_i$.
+Because $k > 2$, the algorithm will calculate $h_f(k)$ as $\VarGrowthFactorNew$ times $h_i(k)$.
 Then
 	\begin{align*}
-	h_f &= \VarGrowthFactorNew h_i\\
+	h_f(k) &= \VarGrowthFactorNew h_i(k)\\
 	&= \VarGrowthFactorNew (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew\\
@@
 	\begin{align*}
-	c_f &= c_i + h_f\\
+	c_f(k) &= c_i(k) + h_f(k)\\
 	&= \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew + (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew\\
@@
 
-% Bookmark
+Now that \ref{lem:GrowthArraysGrowthFactor} and consequently \ref{lem:CapacitySeq} are proved for growth arrays, I examine the write cost of $\FuncGrow$.
+Unlike dynamic arrays, $\FuncGrow$ does not make $s$ writes if the current size is $s$.
+In fact, no items are copied; the only source of writes is when a buffer is appended to the tail, since the tail is a dynamic array.
 
-Now I take a look at $\FuncGrow$.
-Unlike dynamic arrays, the number of writes performed does not equal $i$ if the current size is $i$.
-No items are being copied; the only source of writes is appending a buffer to the tail.
-The goal is to find the number of writes that causes.
-
-Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$. From [make lemma], I know that $\FuncGrow$ is called at the sizes
-
+Let $\FuncWritesByGrowNew(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumItemsTail$ be the size of the tail.
+Consider that [make corollary] also holds true for growth arrays, so $\FuncGrow$ is called $|\VarGrowSeq|$ times.
+A buffer is appended to the tail every time except the first, so the size of the tail is
 \begin{align*}
-S_R = 0,\ \VarInitCapacityNew,\ \VarGrowthFactorNew\VarInitCapacityNew,\ \VarGrowthFactorNew^2\VarInitCapacityNew,\ \ldots\ \VarGrowthFactorNew^{\lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil - 1}\VarInitCapacityNew
+\VarNumItemsTail &= |\VarGrowSeq| - 1 = |\VarCapacitySeq| - 2 = \VarUsefulNew
+\end{align*}
+Then the formula for $\FuncWritesByGrowNew(n)$ is simply $\FuncWrites(\VarUsefulNew)$, where $\FuncWrites$ is the write cost function for dynamic arrays.
+Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWritesNew(n)$ is
+\begin{align*}
+\FuncWritesNew(n) = n + \FuncWrites(\VarUsefulNew)
 \end{align*}
 
-Let $k$ be the number of times the tail is appended to.
-Since the tail is a dynamic array, the number of writes it makes is $\FuncWrites(k)$.
-Since $\FuncGrow$ is called $|S_R|$ times and it appends to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil$.
-Then the formula for $\FuncWritesByGrow(n)$ is
-
-\begin{align*}
-\FuncWritesByGrow(n) = k + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
-\end{align*}
-
-where $\VarInitCapacity$ $\VarGrowthFactor$ are the capacity of the \textit{tail} (not the growth array). I finally conclude that
-
-\begin{align*}
-\FuncWritesNew(n) = n + k + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
-\end{align*}
+% Bookmark
 

### 2017-11-01 Draft2/Appending.Growth.tex
[WIP] Remove annoying hats

@@
 I again start off by finding the write cost for $n$ items.
-I will denote mathematical variables and functions associated with growth arrays with a hat on top, to avoid confusion with their dynamic array counterparts.
-For example, $\FuncWritesNew(n)$ will denote growth arrays' write cost function, $\VarInitCapacityNew$ their initial capacity, $\VarGrowthFactorNew$ their growth factor, and so on.
-
 \ref{lem:CapacitySeq} still holds, since all of the assumptions made there still hold for growth arrays.
@@
 \label{lem:GrowthArraysGrowthFactor}
-	The capacity of a non-empty growth array grows by the constant factor $\VarGrowthFactorNew$.
+	The capacity of a non-empty growth array grows by the constant factor $\VarGrowthFactor$.
 \end{lemma}
@@
 
-	For $k = 2$, $c_i(2) = \VarInitCapacityNew$.
-I wish to show that $c_f(2) = \VarGrowthFactorNew\VarInitCapacityNew$.
-This happens if and only if the next buffer has size ${\Delta c}(2) = (\VarGrowthFactorNew - 1)\VarInitCapacityNew$, which the algorithm ensures.
+	For $k = 2$, $c_i(2) = \VarInitCapacity$.
+I wish to show that $c_f(2) = \VarGrowthFactor\VarInitCapacity$.
+This happens if and only if the next buffer has size ${\Delta c}(2) = (\VarGrowthFactor - 1)\VarInitCapacity$, which the algorithm ensures.
 
-	For $k > 2$, by induction $c_i(k) = c_f(k - 1) = \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew$ and $h_i(k) = h_f(k - 1) = (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew$.
-I wish to show $c_f(k) = \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew$ and $h_f(k) = (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew$.
-Because $k > 2$, the algorithm will calculate $h_f(k)$ as $\VarGrowthFactorNew$ times $h_i(k)$.
+	For $k > 2$, by induction $c_i(k) = c_f(k - 1) = \VarGrowthFactor^{k - 2}\VarInitCapacity$ and $h_i(k) = h_f(k - 1) = (\VarGrowthFactor^{k - 2} - \VarGrowthFactor^{k - 3})\VarInitCapacity$.
+I wish to show $c_f(k) = \VarGrowthFactor^{k - 1}\VarInitCapacity$ and $h_f(k) = (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity$.
+Because $k > 2$, the algorithm will calculate $h_f(k)$ as $\VarGrowthFactor$ times $h_i(k)$.
 Then
 	\begin{align*}
-	h_f(k) &= \VarGrowthFactorNew h_i(k)\\
-	&= \VarGrowthFactorNew (\VarGrowthFactorNew^{k - 2} - \VarGrowthFactorNew^{k - 3})\VarInitCapacityNew\\
-	&= (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew
+	h_f(k) &= \VarGrowthFactor h_i(k)\\
+	&= \VarGrowthFactor (\VarGrowthFactor^{k - 2} - \VarGrowthFactor^{k - 3})\VarInitCapacity\\
+	&= (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity
 	\end{align*}
@@
 	c_f(k) &= c_i(k) + h_f(k)\\
-	&= \VarGrowthFactorNew^{k - 2}\VarInitCapacityNew + (\VarGrowthFactorNew^{k - 1} - \VarGrowthFactorNew^{k - 2})\VarInitCapacityNew\\
-	&= \VarGrowthFactorNew^{k - 1}\VarInitCapacityNew
+	&= \VarGrowthFactor^{k - 2}\VarInitCapacity + (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity\\
+	&= \VarGrowthFactor^{k - 1}\VarInitCapacity
 	\end{align*}
@@
 
-Let $\FuncWritesByGrowNew(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumItemsTail$ be the size of the tail.
+Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumItemsTail$ be the size of the tail.
 Consider that [make corollary] also holds true for growth arrays, so $\FuncGrow$ is called $|\VarGrowSeq|$ times.
@@
 \begin{align*}
-\VarNumItemsTail &= |\VarGrowSeq| - 1 = |\VarCapacitySeq| - 2 = \VarUsefulNew
+\VarNumItemsTail &= |\VarGrowSeq| - 1 = |\VarCapacitySeq| - 2 = \VarUseful
 \end{align*}
-Then the formula for $\FuncWritesByGrowNew(n)$ is simply $\FuncWrites(\VarUsefulNew)$, where $\FuncWrites$ is the write cost function for dynamic arrays.
-Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWritesNew(n)$ is
+Then the formula for $\FuncWritesByGrow(n)$ is simply $\hat{\FuncWrites}(\VarUseful)$, where $\hat{\FuncWrites}$ is the write cost function for dynamic arrays.
+Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWrites(n)$ is
 \begin{align*}
-\FuncWritesNew(n) = n + \FuncWrites(\VarUsefulNew)
+\FuncWrites(n) = n + \hat{\FuncWrites}(\VarUseful)
 \end{align*}
@@
 \begin{align*}
-k &= \lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil\\
+k &= \lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil\\
 O(k) &= O(\log n)
@@
 
-Now, the $k$-term disappears when using $\sim$ to approximate $\FuncWritesNew(n)$, leaving just $n$:
+Now, the $k$-term disappears when using $\sim$ to approximate $\FuncWrites(n)$, leaving just $n$:
 
 \begin{align*}
-\FuncWritesNew(n) &\sim n + \FuncWrites(k)\\
+\FuncWrites(n) &\sim n + \FuncWrites(k)\\
 &= n + O(\log n)\\
@@
 % Should this be C(n) instead of C?
-The space function for $n$ $\FuncAppend$ calls on a growth array is denoted $\FuncSpaceNew(n)$.
+The space function for $n$ $\FuncAppend$ calls on a growth array is denoted $\FuncSpace(n)$.
 Since growth arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.
-$\FuncSpaceNew(n)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail.
+$\FuncSpace(n)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail.
 Thus the space the tail allocates must also be determined.
 
-I determined in [...] that if $n$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\VarGrowthFactorNew} n - \log_{\VarGrowthFactorNew} \VarInitCapacityNew \rceil$.
+I determined in [...] that if $n$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil$.
 Since the tail is a dynamic array, it allocates $\FuncSpace(k)$ space, where $\FuncSpace$ is the space function of the tail.
@@
 \begin{align*}
-\FuncSpaceNew(n) \sim 2^{\lceil \log_2 n \rceil} = O(n)
+\FuncSpace(n) \sim 2^{\lceil \log_2 n \rceil} = O(n)
 \end{align*}

### 2017-11-05 Draft2/Appending.Growth.tex
Add stuff
Tweaks

@@
 \end{align*}
-Then the formula for $\FuncWritesByGrow(n)$ is simply $\hat{\FuncWrites}(\VarUseful)$, where $\hat{\FuncWrites}$ is the write cost function for dynamic arrays.
+Then the formula for $\FuncWritesByGrow(n)$ is simply $\hat{\FuncWrites}(\VarUseful)$, where $\hat{\FuncWrites}$ denotes the write cost function for dynamic arrays.
 Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWrites(n)$ is
@@
 \end{align*}
+% Todo: Make this a lemma.
+Now, I approximate this expression using $\sim$. To do this, I will first need to find the big-O complexity of $\VarUseful$:
+\begin{align*}
+\VarUseful &= \max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)\\
+\VarUseful &\sim \max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)\\
+&\sim \lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil\\
+&\sim \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity\\
+&\sim \log_{\VarGrowthFactor} n
+\end{align*}
+
+By [lemma], $O(\VarUseful) = O(\log_{\VarGrowthFactor} n) = O(\log n)$.
 

### 2017-11-05 Draft2/Appending.Dynamic.tex
Work work work

--- 2017-10-25 Draft2/Appending.Dynamic.tex
@@
 \begin{description}
-	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of a dynamic a array when one item is appended to it.\\
-	{\HdrNote} The capacity of any dynamic array with size zero should be zero.
-	\item[growth factor] Denoted by $\VarGrowthFactor$. The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ grows.
+	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of an empty dynamic array.\\
+	{\HdrAssumptions} $\VarInitCapacity$ is an integer, $\VarInitCapacity > 0$
+	\item[growth factor] Denoted by $\VarGrowthFactor$. The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ is non-empty and grows.\\
+	{\HdrAssumptions} $\VarGrowthFactor\VarInitCapacity \geq \VarInitCapacity + 1$
 \end{description}
@@
 		\Procedure{$\FuncGrow$}{$L$}
-			\If{$\VarList.\FieldEmpty$}
-				\State $\VarList.\FieldBuffer \gets \FuncNewArray(\VarInitCapacity)$
-			\Else
 			\State $new\ buf \gets \FuncNewArray(\VarList.\FieldSize \times \VarGrowthFactor)$
@@
 			\State $\VarList.\FieldBuffer \gets new\ buf$
-			\EndIf
 		\EndProcedure
@@
 \label{lem:CapacitySeq}
-	Let $\VarList$ by a dynamic array. Let its \textbf{capacity sequence}, $\VarCapacitySeq$, be the capacities $\VarList$ takes on as $n$ items are appended. Then
+	Let $\VarList$ by a dynamic array.
+Let its \textbf{capacity sequence}, $\VarCapacitySeq$, be the range of values for $\VarList.\FieldCapacity$ as $n$ items are appended.
+For $n = 0$, trivially $\VarCapacitySeq = (\VarInitCapacity)$.
+For $n > 0$,
 	\begin{align*}
-	\VarCapacitySeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
+	\VarCapacitySeq = \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)}\VarInitCapacity
 	\end{align*}
@@
 
-% Bookmark
+\begin{proof}
+	I use the following properties of dynamic arrays:
+	\begin{enumerate}
+		\item The capacity of an empty dynamic array is $\VarInitCapacity$.
+		\item The capacity of a dynamic array can only grow by $\VarGrowthFactor$.
+		\item The capacity is as small as possible.
+Put formally, if $\VarCapacitySeq_i$ is the capacity for $n$ items, then $\VarCapacitySeq_i \geq n$ but $n > \VarCapacitySeq_{i - 1}$.
+(By convention, $\VarCapacitySeq_{-1} = 0$.)
+	\end{enumerate}
+	Assumption (1) immediately shows $\VarCapacitySeq_0 = \VarInitCapacity$.
+Assumption (2) shows that if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity, then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity.
+By induction, $\VarCapacitySeq = \left( \VarGrowthFactor^i\VarInitCapacity \right)_{i = 0}^\VarUseful$ for some whole number $\VarUseful$.
 
-\begin{proof}
-	The capacity starts out at zero and becomes $\VarInitCapacity$ once one element is appended.
-From then on, it can only grow by a factor of $\VarGrowthFactor$ via $\FuncGrow$, so if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity.
-By induction, the rest of the sequence is $\left( \VarGrowthFactor^i\VarInitCapacity \right)_{i = 1}^\VarUseful$ for some $\VarUseful$.
-
-	Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $\VarUseful$ is the smallest integer for which $\VarGrowthFactor^\VarUseful\VarInitCapacity \geq n$.
-Using this property, I now derive $\VarUseful$.
+	The final value of the sequence, $\VarCapacitySeq_\VarUseful$, is the capacity needed for $n$ items.
+By assumption (3), $\VarCapacitySeq_\VarUseful \geq n > \VarCapacitySeq_{\VarUseful - 1}$.
+Consider the case when $n > \VarInitCapacity$: it must be true that $\VarCapacitySeq_\VarUseful > \VarInitCapacity$, so $\VarUseful \geq 1$.
+Since $\VarUseful - 1 \neq 0$, $\VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$ and $\VarCapacitySeq_{\VarUseful - 1} = \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity$.
+Then
 	\begin{align*}
@@
 	\end{align*}
-	The final term in the sequence is $\VarGrowthFactor^\VarUseful = \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$, completing the proof.
+	Now consider the case when $n \leq \VarInitCapacity$.
+By assumption (3), $n > \VarCapacitySeq_{\VarUseful - 1}$.
+$\VarUseful - 1$ must then equal $-1$, since any other value would imply $n > \VarCapacitySeq_{\VarUseful - 1} \geq \VarInitCapacity$.
+Thus $\VarUseful = 0$.
+
+	It was shown $\VarUseful \geq 1 \geq 0$ for the first case, and it can be shown $\left\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil \leq 0$ for the second case.
+Then, a general formula for $\VarUseful$ is as follows:
+	\begin{align*}
+	\VarUseful &= \max(\left\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil, 0)
+	\end{align*}
+	The final term in the sequence is $\VarGrowthFactor^\VarUseful\VarInitCapacity = \VarGrowthFactor^{\max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)}\VarInitCapacity$, completing the proof.
 \end{proof}
 
-[make lemma]
-Now, consider that to grow by $\VarGrowthFactor$, $\FuncGrow$ must be called.
-So $\VarGrowthFactor^i\VarInitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\VarGrowthFactor^{i - 1}\VarInitCapacity$ for $i \geq 1$.
-Then $\FuncGrow$ was called at the sizes
+[make corollary]
+If $\VarCapacitySeq_i$ exists and $i \geq 1$, then clearly $\FuncGrow$ must have been called when the size was $\VarCapacitySeq_{i - 1}$.
+Then the \textbf{growth sequence}, the sizes for which $\FuncGrow$ is called when $n$ items are appended, is $\VarCapacitySeq$ with the last term removed:
 \begin{align*}
-\VarGrowSeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity
+\VarGrowSeq = \VarCapacitySeq \setminus \left\{ \VarCapacitySeq_\VarUseful \right\}
 \end{align*}
-Each time $\FuncGrow$ is called, $s$ items are copied where $s$ is the current size of the dynamic array. Then the total number of items copied for $n$ appends is
+
+When $\FuncGrow$ is called and the current size is $\VarGrowSeq_i$, the algorithm copies $\VarCapacitySeq_i$ items. Then the total number of items copied when $n$ items are appended is:
 \begin{align*}
-\sum_{s \in \VarGrowSeq} s &= 0 + \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \ldots + \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity\\
+\sum_i {\VarGrowSeq_i} &= \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \ldots + \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity\\
 &= \left( \frac{\VarGrowthFactor^{\VarUseful} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 \end{align*}
-Counting the writes made for every item in $\FuncAppend$, I finally find an explicit formula for $\FuncWrites(n)$.
+Counting the writes made for each item by $\FuncAppend$, an explicit formula for $\FuncWrites(n)$ is as follows:
 [ref1]
@@
 \end{align*}
-This expression looks clean at a glance, but $\VarUseful$ implicitly depends on $n$ and uses the ceiling function and logarithms.
-To make it easier to analyze, I will asymptotically bound this expression.
+Now, my goal is to approximate $\FuncWrites(n)$ with $\sim$. To make is easier to do so, I will asymptotically bound $\VarGrowthFactor^\VarUseful$ which depends on $n$.
+
+\begin{lemma}
+	$n / \VarInitCapacity \RelLessEqual \VarGrowthFactor^\VarUseful \RelLess \VarGrowthFactor{n} / \VarInitCapacity$.
+\end{lemma}
+
+\begin{proof}
+	Since $\left\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil > 0$ for sufficiently large $n$, $\VarUseful \sim \left\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil$.
+% Bookmark
+	Since $\log_{\VarGrowthFactor} k \leq \lceil \log_{\VarGrowthFactor} k \rceil < \left( \log_{\VarGrowthFactor} k \right) + 1$ for any $k > 0$, so $k \leq \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k \rceil} < \VarGrowthFactor{k}$.
+Since $\VarUseful = \left\lceil \log_{\VarGrowthFactor} \frac{n}{\VarInitCapacity} \right\rceil$, $\frac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \frac {\VarGrowthFactor{n}} \VarInitCapacity$.
+\end{proof}
 

### 2017-11-06 Draft2/Appending.Dynamic.tex
Rename relations
Lots of work

@@
 	\begin{align*}
-	\VarCapacitySeq = \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)}\VarInitCapacity
+	\VarCapacitySeq = \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\max(\ExprMessy, 0)}\VarInitCapacity
 	\end{align*}
@@
 	\begin{align*}
-	\VarUseful &= \big\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \big\rceil
+	\VarUseful &= \ExprMessy
 	\end{align*}
@@
 
-	It was shown $\VarUseful \geq 1 \geq 0$ for the first case, and it can be shown $\left\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil \leq 0$ for the second case.
-Then, a general formula for $\VarUseful$ is as follows:
+	It was shown $\VarUseful \geq 1 \geq 0$ for the first case, and it can be shown $\ExprMessy \leq 0$ for the second case. Then, a general formula for $\VarUseful$ is as follows:
 	\begin{align*}
-	\VarUseful &= \max(\left\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil, 0)
+	\VarUseful &= \max(\ExprMessy, 0)
 	\end{align*}
-	The final term in the sequence is $\VarGrowthFactor^\VarUseful\VarInitCapacity = \VarGrowthFactor^{\max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)}\VarInitCapacity$, completing the proof.
+	The final term in the sequence is $\VarGrowthFactor^\VarUseful\VarInitCapacity = \VarGrowthFactor^{\max(\ExprMessy, 0)}\VarInitCapacity$, completing the proof.
 \end{proof}
@@
 \begin{lemma}
-	$n / \VarInitCapacity \RelLessEqual \VarGrowthFactor^\VarUseful \RelLess \VarGrowthFactor{n} / \VarInitCapacity$.
+\label{lem:ToVarUsefulPowerBounds}
+	For $n > \VarInitCapacity$, $n / \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \VarGrowthFactor{n} / \VarInitCapacity$.
 \end{lemma}
@@
 \begin{proof}
-	Since $\left\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil > 0$ for sufficiently large $n$, $\VarUseful \sim \left\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil$.
-% Bookmark
-	Since $\log_{\VarGrowthFactor} k \leq \lceil \log_{\VarGrowthFactor} k \rceil < \left( \log_{\VarGrowthFactor} k \right) + 1$ for any $k > 0$, so $k \leq \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k \rceil} < \VarGrowthFactor{k}$.
-Since $\VarUseful = \left\lceil \log_{\VarGrowthFactor} \frac{n}{\VarInitCapacity} \right\rceil$, $\frac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \frac {\VarGrowthFactor{n}} \VarInitCapacity$.
+	It was shown in \ref{lem:CapacitySeq} that if $n > \VarInitCapacity$, $\VarUseful = \ExprMessy \geq 1$.  Now note that $\VarUseful$ may also be written as $\ExprMessyAlt$. Then
+	\begin{align*}
+	\ExprMessyAltInner \leq \VarUseful &< \ExprMessyAltInner + 1\\
+	\frac{n}{\VarInitCapacity} \leq \VarUseful &< \frac{\VarGrowthFactor{n}}{\VarInitCapacity}
+	\end{align*}
+	as desired.
 \end{proof}
 
-[ref2]
-First I note that $\log_{\VarGrowthFactor} k \leq \lceil \log_{\VarGrowthFactor} k \rceil < \left( \log_{\VarGrowthFactor} k \right) + 1$ for any $k > 0$, so $k \leq \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} k \rceil} < \VarGrowthFactor{k}$.
-Since $\VarUseful = \left\lceil \log_{\VarGrowthFactor} \frac{n}{\VarInitCapacity} \right\rceil$, $\frac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \frac {\VarGrowthFactor{n}} \VarInitCapacity$.
-Then
+Now, I proceed to asymptotically bound $\FuncWrites(n)$.
 \begin{align*}
 \FuncWrites(n) &= n + \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-n + \left( \frac{n / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \leq \FuncWrites(n) &< n + \left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-n + \left( \frac{n - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \leq \FuncWrites(n) &< n + \left( \frac{\VarGrowthFactor{n} - \VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
-n + \left( \frac{n - \VarInitCapacity}{\VarGrowthFactor - 1} \right) \RelLessEqual \FuncWrites(n) &\RelLess n + \left( \frac{\VarGrowthFactor{n} - \VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \RelLessEqual \FuncWrites(n) &\RelLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
+n + \left( \frac{n / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLeq \FuncWrites(n) &\FluteLess n + \left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n - \left( \frac{\VarInitCapacity}{\VarGrowthFactor - 1} \right) \FluteLeq \FuncWrites(n) &\FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n - \left( \frac{\VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \FluteLeq \FuncWrites(n) &\FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
 \end{align*}
@@
 I wish to find the space allocated when $n$ items are appended to a dynamic array.
-I call this quantity the \textbf{space cost}, denote it $\FuncSpace(n)$, and define it as the total length of arrays allocated by $n$ $\FuncAppend$ calls.
-I now derive a formula for $\FuncSpace(n)$.
+I call this quantity the \textbf{space cost}, denote it $\FuncSpace(n)$, and define it as the total length of buffers allocated by $n$ $\FuncAppend$ calls.
+Now, I derive a formula for $\FuncSpace(n)$.
 
-From \ref{lem:CapacitySeq}, I know the capacity sequence of $\VarList$.
-Dynamic arrays also have the property that $c \in \VarCapacitySeq$ iff an array of length $c$ was allocated.
-Then the total length of arrays allocated is
+First, from the definition of $\VarList.\FieldCapacity$, note that a dynamic array's capacity is the length of the buffer it stores its items in.
+Then a buffer of length $c$ is allocated at some point if and only if $c \in \VarCapacitySeq$.
+Then the total length of those buffers is
 \begin{align*}
-\FuncSpace(n) &= \sum_{c \in \VarCapacitySeq} c\\
-&= 0 + \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \VarGrowthFactor^2\VarInitCapacity + \ldots + \VarGrowthFactor^\VarUseful\VarInitCapacity\\
+\FuncSpace(n) &= \sum_i {\VarCapacitySeq_i}\\
+&= \VarInitCapacity + \VarGrowthFactor\VarInitCapacity + \VarGrowthFactor^2\VarInitCapacity + \ldots + \VarGrowthFactor^\VarUseful\VarInitCapacity\\
 &= \left( \frac{\VarGrowthFactor^{\VarUseful + 1} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
 \end{align*}
-Using the identity in [ref2] again, I asymptotically bound $\FuncSpace(n)$:
-
+Using Lemma \ref{lem:ToVarUsefulPowerBounds} again, I asymptotically bound $\FuncSpace(n)$:
 \begin{align*}
-\left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \leq \FuncSpace(n) &< \left( \frac{\VarGrowthFactor^2{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-\left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \RelLessEqual \FuncSpace(n) &\RelLess \left( \frac{\VarGrowthFactor^2{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \RelLessEqual \FuncSpace(n) &\RelLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n
+\left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLeq \FuncSpace(n) &\FluteLess \left( \frac{\VarGrowthFactor^2{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n - \left( \frac{\VarInitCapacity}{\VarGrowthFactor - 1} \right) \FluteLeq \FuncSpace(n) &\FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n - \left( \frac{\VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \FluteLeq \FuncSpace(n) &\FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n
 \end{align*}

### 2017-11-06 Draft2/Appending.Dynamic.tex
Reach the bookmark

@@
 
+\begin{corollary}
+\label{coro:GrowthSeq}
+	Let the \textbf{growth sequence}, $\VarGrowSeq$, of $\VarList$ be the sizes for which $\FuncGrow$ is called when $n$ items are appended.
+Then $\VarGrowSeq = \VarCapacitySeq \setminus \left\{ \VarCapacitySeq_\VarUseful \right\}$.
+\end{corollary}
+
+\begin{proof}
+	If $\VarCapacitySeq_i$ exists and $i \geq 1$, then clearly $\FuncGrow$ must have been called when the size was $\VarCapacitySeq_{i - 1}$, so $\VarCapacitySeq_{i - 1} \in \VarGrowSeq$.
+Then $\VarGrowSeq$ contains every term in $\VarCapacitySeq$ except for the last, $\VarCapacitySeq_\VarUseful$, as stated by the corollary.
+\end{proof}
 [make corollary]
@@
 
-When $\FuncGrow$ is called and the current size is $\VarGrowSeq_i$, the algorithm copies $\VarCapacitySeq_i$ items. Then the total number of items copied when $n$ items are appended is:
+When $\FuncGrow$ is called and the current size is $\VarGrowSeq_i$, the algorithm copies $\VarGrowSeq_i$ items. Then the total number of items copied when $n$ items are appended is:
 \begin{align*}

### 2017-11-06 Draft2/Appending.Growth.tex
Reach the bookmark

--- 2017-11-01 Draft2/Appending.Growth.tex
@@
 
-I again start off by finding the write cost for $n$ items.
-\ref{lem:CapacitySeq} still holds, since all of the assumptions made there still hold for growth arrays.
+I start off again by finding the write cost for $n$ items.
+Lemma \ref{lem:CapacitySeq} still holds, since growth arrays satisfy the properties used by that proof.
 In particular, although growth arrays use a different growth algorithm than dynamic arrays, the following claim is still true:
@@
 \label{lem:GrowthArraysGrowthFactor}
-	The capacity of a non-empty growth array grows by the constant factor $\VarGrowthFactor$.
+	The capacity of a growth array grows by the constant factor $\VarGrowthFactor$.
 \end{lemma}
@@
 \begin{proof}
-	I prove that the $\FuncGrow$ algorithm always enforces this using induction.
-I induct on the number of times $\FuncGrow$ is called, $k$, showing that for all $k \geq 2$, $\FuncGrow$ behaves correctly when called the $k$th time.
-(At $k = 1$, the growth array is empty, so its behavior is not relevant to this lemma.) I will let $c_i(k)$ and $c_f(k)$ denote the initial/final capacities and $h_i(k)$ and $h_f(k)$ denote the initial/final head capacities for the $k$th call, respectively.
+	I prove that the $\FuncGrow$ algorithm enforces this using induction.
+I induct on the number of times $\FuncGrow$ is called, $k$, showing that for all natural numbers $k$, $\FuncGrow$ behaves correctly when called the $k$th time.
+I will let $c_i$ and $c_f$ denote the initial/final capacities and $h_i$ and $h_f$ denote the initial/final head capacities for the $k$th call, respectively.
 
-	For $k = 2$, $c_i(2) = \VarInitCapacity$.
-I wish to show that $c_f(2) = \VarGrowthFactor\VarInitCapacity$.
-This happens if and only if the next buffer has size ${\Delta c}(2) = (\VarGrowthFactor - 1)\VarInitCapacity$, which the algorithm ensures.
+	For $k = 1$, $c_i = \VarInitCapacity$.
+I wish to show that $c_f = \VarGrowthFactor\VarInitCapacity$.
+This happens if and only if the next buffer has size $\Delta c = (\VarGrowthFactor - 1)\VarInitCapacity$, which the algorithm ensures.
 
-	For $k > 2$, by induction $c_i(k) = c_f(k - 1) = \VarGrowthFactor^{k - 2}\VarInitCapacity$ and $h_i(k) = h_f(k - 1) = (\VarGrowthFactor^{k - 2} - \VarGrowthFactor^{k - 3})\VarInitCapacity$.
-I wish to show $c_f(k) = \VarGrowthFactor^{k - 1}\VarInitCapacity$ and $h_f(k) = (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity$.
-Because $k > 2$, the algorithm will calculate $h_f(k)$ as $\VarGrowthFactor$ times $h_i(k)$.
+	For $k > 1$, by induction $c_i = \text{previous }c_f = \VarGrowthFactor^{k - 2}\VarInitCapacity$, and $h_i = \text{previous }h_f = (\VarGrowthFactor^{k - 2} - \VarGrowthFactor^{k - 3})\VarInitCapacity$.
+I wish to show $c_f = \VarGrowthFactor^{k - 1}\VarInitCapacity$ and $h_f = (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity$.
+Because $k > 1$, the algorithm will calculate $h_f$ as $\VarGrowthFactor$ times $h_i$.
 Then
 	\begin{align*}
-	h_f(k) &= \VarGrowthFactor h_i(k)\\
-	&= \VarGrowthFactor (\VarGrowthFactor^{k - 2} - \VarGrowthFactor^{k - 3})\VarInitCapacity\\
-	&= (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity
+	h_f &= \VarGrowthFactor h_i = \VarGrowthFactor (\VarGrowthFactor^{k - 2} - \VarGrowthFactor^{k - 3})\VarInitCapacity = (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity
 	\end{align*}
@@
 	\begin{align*}
-	c_f(k) &= c_i(k) + h_f(k)\\
-	&= \VarGrowthFactor^{k - 2}\VarInitCapacity + (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity\\
-	&= \VarGrowthFactor^{k - 1}\VarInitCapacity
+	c_f &= c_i + h_f = \VarGrowthFactor^{k - 2}\VarInitCapacity + (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity = \VarGrowthFactor^{k - 1}\VarInitCapacity
 	\end{align*}
@@
 
-Now that \ref{lem:GrowthArraysGrowthFactor} and consequently \ref{lem:CapacitySeq} are proved for growth arrays, I examine the write cost of $\FuncGrow$.
-Unlike dynamic arrays, $\FuncGrow$ does not make $s$ writes if the current size is $s$.
-In fact, no items are copied; the only source of writes is when a buffer is appended to the tail, since the tail is a dynamic array.
+Since Lemma \ref{lem:GrowthArraysGrowthFactor} has been proven, Lemma \ref{lem:CapacitySeq} and all results based on it must also hold true for growth arrays.
+Now, I am ready to find the write cost of $\FuncGrow$.
+Unlike dynamic arrays, $\FuncGrow$ does not make $\VarGrowSeq_i$ writes when the current size is $\VarGrowSeq_i$.
+In fact, $\FuncGrow$ does not copy \textit{any} items supplied by the user.
+Writes are only made when a buffer is appended to the tail, since the tail is a dynamic array.
 
 Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumItemsTail$ be the size of the tail.
-Consider that [make corollary] also holds true for growth arrays, so $\FuncGrow$ is called $|\VarGrowSeq|$ times.
-A buffer is appended to the tail every time except the first, so the size of the tail is
+Since Corollary \ref{coro:GrowthSeq} also holds true for growth arrays, $\FuncGrow$ is called $|\VarGrowSeq|$ times.
+A buffer is appended to the tail each time $\FuncGrow$ is called.
+Thus, the tail's size is
 \begin{align*}
-\VarNumItemsTail &= |\VarGrowSeq| - 1 = |\VarCapacitySeq| - 2 = \VarUseful
+\VarNumItemsTail &= |\VarGrowSeq| = |\VarCapacitySeq| - 1 = \VarUseful
 \end{align*}
-Then the formula for $\FuncWritesByGrow(n)$ is simply $\hat{\FuncWrites}(\VarUseful)$, where $\hat{\FuncWrites}$ is the write cost function for dynamic arrays.
+Then the formula for $\FuncWritesByGrow(n)$ is simply $\FuncWritesTail(\VarUseful)$, where $\FuncWritesTail$ denotes the tail's write cost function, that is, the write cost function for dynamic arrays.
 Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWrites(n)$ is
 \begin{align*}
-\FuncWrites(n) = n + \hat{\FuncWrites}(\VarUseful)
+\FuncWrites(n) = n + \FuncWritesTail(\VarUseful)
 \end{align*}
+Now, I approximate $\FuncWrites(n)$ using $\sim$. To do this, I will derive the big-O complexity of $\VarUseful$.
+
+\begin{lemma}
+	$\VarUseful = O(\log n)$.
+\end{lemma}
+
+\begin{proof}
+	From \ref{lem:CapacitySeq}, $\VarUseful = \max(\ExprMessy, 0)$. As mentioned in Lemma \ref{lem:ToVarUsefulPowerBounds}, for sufficiently large $n$, $\VarUseful = \ExprMessy$. Then
+	\begin{align*}
+	\VarUseful \sim \ExprMessy \sim \left( \ExprMessyInner \right) \sim \log_{\VarGrowthFactor} n
+	\end{align*}
+	By [lemma], $O(\VarUseful) = O(\log_{\VarGrowthFactor} n) = O(\log n)$ as desired.
+\end{proof}
 

### 2017-11-06 Draft2/Appending.Growth.tex
Some work

@@
 \begin{lemma}
+\label{lem:VarUsefulIsOLogN}
 	$\VarUseful = O(\log n)$.
@@
 
-% Bookmark
-
-I now approximate this expression using $\sim$. First, I approximate $k$ using big-O:
-
+Now when $\FuncWrites(n)$ is approximated with $\sim$, the $\FuncWritesTail(\VarUseful)$ term disappears:
 \begin{align*}
-k &= \lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil\\
-O(k) &= O(\log n)
-\end{align*}
-
-Now, the $k$-term disappears when using $\sim$ to approximate $\FuncWrites(n)$, leaving just $n$:
-
-\begin{align*}
-\FuncWrites(n) &\sim n + \FuncWrites(k)\\
-&= n + O(\log n)\\
-&\sim n
+\FuncWrites(n) &= n + \FuncWritesTail(\VarUseful) = n + O(\VarUseful) = n + O(\log n) \sim n
 \end{align*}
@@
 
-% Should this be C(n) instead of C?
-The space function for $n$ $\FuncAppend$ calls on a growth array is denoted $\FuncSpace(n)$.
-Since growth arrays never throw away item buffers, if the current capacity is $C$ then the total length of item buffers is also $C$.
-$\FuncSpace(n)$ is usually greater than $C$, however; this is because growth arrays not only allocate item buffers, but stores references to them in the tail.
-Thus the space the tail allocates must also be determined.
+Unlike dynamic arrays, growth arrays never throw away buffers.
+This means that if the current capacity is $c$, then the total length of buffers allocated to store items is also $c$.
+Typically, however, $\FuncSpace(n) > c$.
+This is because growth arrays not only store items in buffers, they also store \textbf{references} (or \textbf{pointers}) to the buffers holding the items, in the tail.
+Thus, the space the tail allocates must also be considered.
 
-I determined in [...] that if $n$ are appended then the tail is appended to $k$ times, where $k = \lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil$.
-Since the tail is a dynamic array, it allocates $\FuncSpace(k)$ space, where $\FuncSpace$ is the space function of the tail.
-Through a similar method to [...] it can be shown $O(\FuncSpace(k)) = O(k) = O(\log n)$.
-Then % TODO: P-analysis should come after the explicit formula.
+We established in [lemma] that $\VarNumItemsTail = \VarUseful$.
+Then since $\VarCapacitySeq_\VarUseful$ is the space needed to hold items, and $\FuncSpaceTail(\VarUseful)$ is the space the tail needs to hold references, the formula for $\FuncSpace(n)$ is
+\begin{align*}
+\FuncSpace(n) = \VarCapacitySeq_\VarUseful + \FuncSpaceTail(\VarUseful)
+\end{align*}
+I now wish to approximate this using $\sim$.
+First, note that since $\VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$, it follows from Lemma \ref{lem:ToVarUsefulPowerBounds} that $n \FluteLeq \VarCapacitySeq_\VarUseful \FluteLess \VarGrowthFactor{n}$.
+Since $n$ and $\VarGrowthFactor{n}$ are both $O(n)$, [the squeeze theorem] implies that $\VarCapacitySeq_\VarUseful = O(n)$.
 
+Now, consider the ratio $\lim_{n \to \infty} \left( \FuncSpaceTail(\VarUseful) / \VarCapacitySeq_\VarUseful \right) = O(\log n) / O(n) = O({\log n} / {n}) = 0$.
+Because it is $0$, from \ref{thm:RemovesLowerOrderTerms} we may conclude
 \begin{align*}
-\FuncSpace(n) \sim 2^{\lceil \log_2 n \rceil} = O(n)
+\FuncSpace(n) = \VarCapacitySeq_\VarUseful + \FuncSpaceTail(\VarUseful) \sim \VarCapacitySeq_\VarUseful
 \end{align*}
+
+% Bookmark
+
+Using Lemma \ref{lem:VarUsefulIsOLogN} again, $\FuncSpaceTail(\VarUseful) = O(\VarUseful) = O(\log n)$. Similarly to before, the $\FuncSpaceTail(\VarUseful)$ term vanishes under $\sim$:
+\begin{align*}
+\FuncSpace(n) \sim ... + O(\log n) = ...
+\end{align*}

### 2017-11-06 Draft2/FieldsProperties.tex
Lists
Some work

--- 2017-10-24 Draft2/FieldsProperties.tex
@@
 	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
-	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$. It returns a dynamic array of buffers that have already been filled. This can be thought of as a two-dimensional array.
+	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$.
+\textbf{Important note: The tail is a dynamic array.} It returns a \textit{dynamic array} of references to buffers that are already filled with items.
+The tail can be thought of as a two-dimensional array.\\
+	{\HdrNote} It may seem strange for a growth array to use the very data structure it is replacing.
+As shown in Lemma \ref{lem:VarUsefulIsOLogN}, however, only $O(\log n)$ many references are appended to the tail.
+Thus, the extra copying and allocations the tail performs is minuscule compared to other work done by the growth array.
 	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.

### 2017-11-06 Draft2/Appending.Growth.tex
Use dfrac in a place or 2
Finish the space complexity section

@@
 
-Now, consider the ratio $\lim_{n \to \infty} \left( \FuncSpaceTail(\VarUseful) / \VarCapacitySeq_\VarUseful \right) = O(\log n) / O(n) = O({\log n} / {n}) = 0$.
-Because it is $0$, from \ref{thm:RemovesLowerOrderTerms} we may conclude
+Now, consider the ratio $\lim_{n \to \infty} \dfrac {\FuncSpaceTail(\VarUseful)} {\VarCapacitySeq_\VarUseful} = \dfrac {O(\log n)} {O(n)} = O \left( \dfrac{\log n}{n} \right) = 0$.
+Because it is $0$, from Theorem \ref{thm:RemovesLowerOrderTerms} one can conclude
 \begin{align*}
@@
 \end{align*}
-
-% Bookmark
-
-Using Lemma \ref{lem:VarUsefulIsOLogN} again, $\FuncSpaceTail(\VarUseful) = O(\VarUseful) = O(\log n)$. Similarly to before, the $\FuncSpaceTail(\VarUseful)$ term vanishes under $\sim$:
+Substituting $\FuncSpace(n)$ for $\VarCapacitySeq_\VarUseful$ in the previous inequality,
 \begin{align*}
-\FuncSpace(n) \sim ... + O(\log n) = ...
+n \FluteLeq \FuncSpace(n) \FluteLess \VarGrowthFactor{n}
 \end{align*}

### 2017-11-06 Draft2/AsymptoticNotation.tex
More stuff for today

@@
-\subsection{Motivation}
+\subsection{Introduction}
 
-In order to highlight the benefit of growth arrays, I will use an alternative notation for time complexity.
-The reason for this is, for certain operations, growth arrays are only better than dynamic arrays by a constant factor.
-For example, dynamic arrays might allocate roughly $2n$ memory for appending $n$ items, while growth arrays would allocate roughly $n$ memory.
+Typically, big-O notation is used to analyze the time or space complexity of a function.
+In order to highlight the benefit of growth arrays, however, I will use the $\sim$ relation to analyze complexity.
+This is because for certain operations, growth arrays are only better than dynamic arrays by a constant factor.
+For example, dynamic arrays might use roughly $2n$ space for appending $n$ items, while growth arrays would use roughly $n$ space.
 Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $O(n)$.
@@
 My goal is to be able to compare the coefficients of the highest-order terms in both expressions.
-For example, I would like to take the ratio $\frac{2n}{n}$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $n$.
+For example, I would like to take the ratio $2n / n$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $n$.
 However, big-O notation does not support this.
 
-\subsection{Definition}
+\subsection{Definitions}
 
-To analyze time complexity, I will use the $\sim$ relation. It is defined as follows:
-
+I will mainly use the $\sim$ relation to analyze complexity. It is defined as follows:
 \begin{align*}
-f \sim g \leftrightarrow \lim_{n \to \infty} \frac{g}{f} = 1
+f \sim g \leftrightarrow \lim_{n \to \infty} \frac f g = 1
 \end{align*}
-
 This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.
@@
 
+I will also introduce the cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
+\begin{align*}
+f \FluteLess g \leftrightarrow \lim_{n \to \infty} \frac f g < 1
+\end{align*}
 \subsection{Properties}

### 2017-11-06 Draft2/FieldsProperties.tex
More stuff for today
Modify the ctors
Wording

@@
 
-As a dynamic array, $\VarList$ is also given the following properties. $:=$ denotes a definition, as opposed to $=$ which checks equivalence. Functions that return boolean values are suffixed with ?.
+As a dynamic array, $\VarList$ is also given the following properties.
+{\HdrNote} For pseudocode, I will use $:=$ to denote a definition, and $=$ to denote an equivalence check.
+Functions that return boolean values are suffixed with ?.
 
@@
 		\Procedure{$\FuncConstructor$}{$\VarList$}
-			\State $\VarList.\FieldBuffer \gets \FuncNewArray(0)$
+			\State $\VarList.\FieldBuffer \gets \FuncNewArray(\VarInitCapacity)$
 			\State $\VarList.\FieldSize \gets 0$
@@
 	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
-	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold without resizing.
+	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold before it must grow.
 \end{itemize}
@@
 		\Procedure{$\FuncConstructor$}{$\VarList$}
-			\State $\VarList.\FieldHead \gets \FuncNewArray(0)$
+			\State $\VarList.\FieldHead \gets \FuncNewArray(\VarInitCapacity)$
 			\State $\VarList.\FieldTail \gets \FuncNewDynamicArray()$
 			\State $\VarList.\FieldSize \gets 0$
-			\State $\VarList.\FieldCapacity \gets 0$
+			\State $\VarList.\FieldCapacity \gets \VarInitCapacity$
 		\EndProcedure

### 2017-11-07 Draft2/Appendix.tex
Take care of Section 3
Work

@@
 
-\section{Proofs of $\TextTilde$ Properties}
+\section{Proving $\sim$ Properties}
 
-\subsection{Merging over Arithmetic Operations}
+\subsection{$\sim$ Merges over $+$, $\times$, and $\div$}
 \label{pf:MergesOverArithmetic}
-
-\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticAdd})]
-\end{proof}
-
-\begin{proof}[Proof (Theorem \ref{thm:MergesOverArithmeticMultiply})]
-	This can be easily shown by multiplying the limits corresponding to $\hat{f}$ and $\hat{g}$:
-
+\begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
+	The statement about multiplication can be shown easily by multiplying the limits corresponding to $f$ and $g$:
 	\begin{align*}
-	\lim_{n \to \infty} \frac{\hat{f}}{f} &= 1\\
-	\lim_{n \to \infty} \frac{\hat{g}}{g} &= 1\\
-	\left( \lim_{n \to \infty} \frac{\hat{f}}{f} \right) \left( \lim_{n \to \infty} \frac{\hat{g}}{g} \right) &= 1 \cdot 1\\
-	\lim_{n \to \infty} \frac{\hat{f}\hat{g}}{fg} &= 1
+	\lim_{n \to \infty} \frac{f}{\Tweak{f}} &= 1\\
+	\lim_{n \to \infty} \frac{g}{\Tweak{g}} &= 1\\
+	\left( \lim_{n \to \infty} \frac{f}{\Tweak{f}} \right) \left( \lim_{n \to \infty} \frac{g}{\Tweak{g}} \right) &= 1 \cdot 1\\
+	\lim_{n \to \infty} \frac{fg}{\Tweak{f}\Tweak{g}} &= 1
 	\end{align*}
-
-	it follows that $\hat{f}\hat{g} \TextTilde fg$. The statement about division can be proved by flipping the fraction for $\hat{g}$ before multiplying, resulting in
-
+	it follows that $fg \sim \Tweak{f}\Tweak{g}$. The statement about division can be proved by flipping the limit for $g$ before multiplying, resulting in
 	\begin{align*}
-	\lim_{n \to \infty} \frac{\hat{f} / \hat{g}}{f / g} = 1
+	\lim_{n \to \infty} \frac{f / g}{\Tweak{f} / \Tweak{g}} = 1
 	\end{align*}
-
-	This shows $\hat{f} / \hat{g} \TextTilde f / g$.
+	This shows $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
 \end{proof}
@@
 
-	it follows that $f + g \TextTilde f$.
+	it follows that $f + g \sim f$.
 \end{proof}
@@
 \begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
-By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \TextTilde h$.
+By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \sim h$.
 \end{proof}

### 2017-11-07 Draft2/AsymptoticNotation.tex
Biconds
Work

@@
 \begin{align*}
-f \sim g \leftrightarrow \lim_{n \to \infty} \frac f g = 1
+f \sim g \Biconditional \lim_{n \to \infty} \frac f g = 1
 \end{align*}
@@
 \begin{align*}
-f \FluteLess g \leftrightarrow \lim_{n \to \infty} \frac f g < 1
+f \FluteLess g \Biconditional \lim_{n \to \infty} \frac f g < 1
 \end{align*}
@@
 
-Here, I define various properties of the $\sim$ relation that will be used in my proofs. Proofs of these properties can be found in the appendix.
+Here, I define various properties of the $\sim$ relation that will be used in my proofs. These properties themselves are proved in the appendix.
 
-The following two theorems state that $\sim$ can "merge", or un-distribute, over arithmetic operations. This is a property shared with big-O.
+The following theorem states that $\sim$ can "merge", or un-distribute, over addition, multiplication, and division. This is a property shared with big-O.
 
 \begin{theorem}
-\label{thm:MergesOverArithmeticAdd}
-	$P$ merges over addition and subtraction. That is, for functions $f$ and $g$,
+\label{thm:MergesOverOps}
+	Suppose $f$, $\Tweak{f}$, $g$, and $\Tweak{g}$ are functions. If $f \sim \Tweak{f}$ and $g \sim \Tweak{g}$, then
 	\begin{align*}
-	(\hat{f} \sim f) \land (\hat{g} \sim g) \rightarrow \begin{cases}
-		(\hat{f} + \hat{g}) \sim (f + g)\\
-		(\hat{f} - \hat{g}) \sim (f - g)
-	\end{cases}
+	f + g &\sim \Tweak{f} + \Tweak{g}\\
+	fg &\sim \Tweak{f}\Tweak{g}\\
+	\frac{f}{g} &\sim \frac {\Tweak{f}} {\Tweak{g}}
 	\end{align*}
@@
 
-\begin{theorem}
-\label{thm:MergesOverArithmeticMultiply}
-	$P$ merges over multiplication and division. That is, for functions $f$ and $g$,
-	\begin{align*}
-	(\hat{f} \sim f) \land (\hat{g} \sim g) \rightarrow \begin{cases}
-	\hat{f}\hat{g} \sim fg\\
-	\hat{f} / \hat{g} \sim f / g
-	\end{cases}
-	\end{align*}
-\end{theorem}
-
-The following theorem states that lower-order terms may be removed. For example, $(n + \log_2 n) \sim n$.
+The following theorem states that lower-order terms may be removed: for example, $(n + \log_2 n) \sim n$. This is also a property shared with big-O.
 
@@
 \label{thm:RemovesLowerOrderTerms}
-	If $\lim_{n \to \infty} g / f = 0$, then $f + O(g) \sim f$.
+	If $\lim_{n \to \infty} \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
 \end{theorem}
 
-The following theorem shows that $\sim$ is a transitive relation. This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$.
+The following theorem states that $\sim$ is a transitive relation. This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$.
 

### 2017-11-07 Draft2/Appendix.tex
Cleanup all the limits

@@
 	\begin{align*}
-	\lim_{n \to \infty} \frac{f}{\Tweak{f}} &= 1\\
-	\lim_{n \to \infty} \frac{g}{\Tweak{g}} &= 1\\
-	\left( \lim_{n \to \infty} \frac{f}{\Tweak{f}} \right) \left( \lim_{n \to \infty} \frac{g}{\Tweak{g}} \right) &= 1 \cdot 1\\
-	\lim_{n \to \infty} \frac{fg}{\Tweak{f}\Tweak{g}} &= 1
+	\ExprNToInfty \frac{f}{\Tweak{f}} &= 1\\
+	\ExprNToInfty \frac{g}{\Tweak{g}} &= 1\\
+	\left( \ExprNToInfty \frac{f}{\Tweak{f}} \right) \left( \ExprNToInfty \frac{g}{\Tweak{g}} \right) &= 1 \cdot 1\\
+	\ExprNToInfty \frac{fg}{\Tweak{f}\Tweak{g}} &= 1
 	\end{align*}
@@
 	\begin{align*}
-	\lim_{n \to \infty} \frac{f / g}{\Tweak{f} / \Tweak{g}} = 1
+	\ExprNToInfty \frac{f / g}{\Tweak{f} / \Tweak{g}} = 1
 	\end{align*}
@@
 	\begin{align*}
-	\lim_{n \to \infty} \left( \frac{f + g}{f} \right) &= \lim_{n \to \infty} \frac{f}{f} + \lim_{n \to \infty} \frac{g}{f}\\
+	\ExprNToInfty \left( \frac{f + g}{f} \right) &= \ExprNToInfty \frac{f}{f} + \ExprNToInfty \frac{g}{f}\\
 	&= 1 + 0\\
@@
 \begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
-By definition, $\lim_{n \to \infty} g / f = 1$ and $\lim_{n \to \infty} h / g = 1$. Multiplying the two equations, $\lim_{n \to \infty} h / f = 1$ which implies $f \sim h$.
+By definition, $\ExprNToInfty g / f = 1$ and $\ExprNToInfty h / g = 1$. Multiplying the two equations, $\ExprNToInfty h / f = 1$ which implies $f \sim h$.
 \end{proof}

### 2017-11-07 Draft2/Appendix.tex
More stuff

@@
 \begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
+	% TODO: Prove statement for addition.
+
 	The statement about multiplication can be shown easily by multiplying the limits corresponding to $f$ and $g$:
@@
 
-\subsection{Removal of Lower-Order Terms}
+\subsection{$\sim$ Removes Lower-Order Terms}
 \label{pf:RemovesLowerOrderTerms}
@@
 	Since
-
 	\begin{align*}
-	\ExprNToInfty \left( \frac{f + g}{f} \right) &= \ExprNToInfty \frac{f}{f} + \ExprNToInfty \frac{g}{f}\\
+	\ExprNToInfty \frac{f + g}{f} &= \ExprNToInfty \frac{f}{f} + \ExprNToInfty \frac{g}{f}\\
 	&= 1 + 0\\
@@
 	\end{align*}
-
 	it follows that $f + g \sim f$.
@@
 
-\subsection{Transitivity}
+\subsection{$\sim$ is Transitive}
 \label{pf:Transitivity}
@@
 \begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
-By definition, $\ExprNToInfty g / f = 1$ and $\ExprNToInfty h / g = 1$. Multiplying the two equations, $\ExprNToInfty h / f = 1$ which implies $f \sim h$.
+By definition, $\ExprNToInfty \dfrac f g = 1$ and $\ExprNToInfty \dfrac g h = 1$. Multiplying the two equations, $\ExprNToInfty \dfrac f h = 1$ which implies $f \sim h$.
 \end{proof}

### 2017-11-07 Draft2/AsymptoticNotation.tex
Cleanup all the limits
Add prefix

@@
 \begin{align*}
-f \sim g \Biconditional \lim_{n \to \infty} \frac f g = 1
+f \sim g \Biconditional \ExprNToInfty \frac f g = 1
 \end{align*}
-This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.
+This is read as ``$f$ is asymptotic to $g$'' or ``$f$ and $g$ are asymptotic.'' {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.
 
@@
 \begin{align*}
-f \FluteLess g \Biconditional \lim_{n \to \infty} \frac f g < 1
+f \FluteLess g \Biconditional \ExprNToInfty \frac f g < 1
 \end{align*}
@@
 
-The following theorem states that $\sim$ can "merge", or un-distribute, over addition, multiplication, and division. This is a property shared with big-O.
+The following theorem states that $\sim$ can ``merge,'' or un-distribute, over addition, multiplication, and division. This is a property shared with big-O.
 
@@
 \label{thm:RemovesLowerOrderTerms}
-	If $\lim_{n \to \infty} \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
+	If $\ExprNToInfty \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
 \end{theorem}

### 2017-11-07 Draft2/Appending.Dynamic.tex
Use dfrac in a place or 2
Add prefix
Respond to feedback

@@
 \label{lem:CapacitySeq}
-	Let $\VarList$ by a dynamic array.
+	Let $\VarList$ be a dynamic array.
 Let its \textbf{capacity sequence}, $\VarCapacitySeq$, be the range of values for $\VarList.\FieldCapacity$ as $n$ items are appended.
@@
 	If $\VarCapacitySeq_i$ exists and $i \geq 1$, then clearly $\FuncGrow$ must have been called when the size was $\VarCapacitySeq_{i - 1}$, so $\VarCapacitySeq_{i - 1} \in \VarGrowSeq$.
-Then $\VarGrowSeq$ contains every term in $\VarCapacitySeq$ except for the last, $\VarCapacitySeq_\VarUseful$, as stated by the corollary.
+Then $\VarGrowSeq$ contains every term in $\VarCapacitySeq$ except for the last, $\VarCapacitySeq_\VarUseful$, as the corollary states.
 \end{proof}
@@
 \label{lem:ToVarUsefulPowerBounds}
-	For $n > \VarInitCapacity$, $n / \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \VarGrowthFactor{n} / \VarInitCapacity$.
+	For $n > \VarInitCapacity$, $\dfrac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \dfrac {\VarGrowthFactor{n}} \VarInitCapacity$.
 \end{lemma}
@@
 \begin{proof}
-	It was shown in \ref{lem:CapacitySeq} that if $n > \VarInitCapacity$, $\VarUseful = \ExprMessy \geq 1$.  Now note that $\VarUseful$ may also be written as $\ExprMessyAlt$. Then
+	It was shown in Lemma \ref{lem:CapacitySeq} that if $n > \VarInitCapacity$, $\VarUseful = \ExprMessy \geq 1$.  Now note that $\VarUseful$ may also be written as $\ExprMessyAlt$. Then
 	\begin{align*}

### 2017-11-07 Draft2/Appending.Dynamic.tex
Remove duplicate stuff

@@
 \end{proof}
-[make corollary]
-If $\VarCapacitySeq_i$ exists and $i \geq 1$, then clearly $\FuncGrow$ must have been called when the size was $\VarCapacitySeq_{i - 1}$.
-Then the \textbf{growth sequence}, the sizes for which $\FuncGrow$ is called when $n$ items are appended, is $\VarCapacitySeq$ with the last term removed:
-\begin{align*}
-\VarGrowSeq = \VarCapacitySeq \setminus \left\{ \VarCapacitySeq_\VarUseful \right\}
-\end{align*}
 

### 2017-11-07 Draft2/Appending.Compare.tex
Populate time cmp/space cmp sections

\HdrTimeComplexCmp

Let $\FuncWritesDynamicArray(n)$ and $\FuncWritesGrowthArray(n)$ be the write costs for dynamic and growth arrays, respectively. I derived earlier that
\begin{align*}
\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \FluteLeq \FuncWritesDynamicArray(n) &\FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
\end{align*}
Dividing all sides of this inequality by $n$, I receive
\begin{align*}
\frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \FluteLeq \frac {\FuncWritesDynamicArray(n)} n &\FluteLess \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1}
\end{align*}
Since $\FuncWritesGrowthArray(n) \sim n$, $\dfrac {\FuncWritesDynamicArray(n)} n \sim \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$, thus
\begin{align*}
\frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \FluteLeq \frac {\FuncWritesDynamicArray(n)} {\FuncWritesGrowthArray(n)} &\FluteLess \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1}
\end{align*}

\HdrSpaceComplexCmp

Let $\FuncSpaceDynamicArray(n)$ and $\FuncSpaceGrowthArray(n)$ be the space costs for dynamic and growth arrays, respectively. Recall that
\begin{align*}
\FuncSpaceDynamicArray(n) = \left( \frac{\VarGrowthFactor^{\VarUseful + 1} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
\end{align*}
and $\FuncSpaceGrowthArray(n) \sim \VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$. Taking the ratio of $\FuncSpaceDynamicArray(n)$ to $\FuncSpaceGrowthArray(n)$, I receive
\begin{align*}
\frac{\FuncSpaceDynamicArray(n)}{\FuncSpaceGrowthArray(n)} &\sim \left( \frac{1}{\VarGrowthFactor^\VarUseful} \right) \left( \frac{\VarGrowthFactor^{\VarUseful + 1} - 1}{\VarGrowthFactor - 1} \right)\\
&= \frac{\VarGrowthFactor - 1 / {\VarGrowthFactor^\VarUseful}}{\VarGrowthFactor - 1}\\
&\sim \frac{\VarGrowthFactor}{\VarGrowthFactor - 1}
\end{align*}
The last step comes from the fact that $\VarUseful = \max(\ExprMessy, 0) \to \infty$ as $n \to \infty$.

### 2017-11-08 Draft2/Indexing.Dynamic.tex
Work towards other sections

\HdrDynArrayImpl

The following algorithm implements $\FuncGetItem$ for dynamic arrays. A $\FuncSetItem$ function can be implemented in a similar fashion.

{\HdrNote} I assume all arguments passed to my algorithms are valid. Thus, I do not include argument validation nor error handling in my pseudocode.

\begin{algorithm}
	\begin{algorithmic}[1]
		\Function{$\FuncGetItem$}{$\VarList, index$}
			\State \Return $\VarList.\FieldBuffer[index]$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

Clearly, this function runs in constant time. It also has the benefit of using very few instructions: on architectures like x86, indexing the buffer may take as little as one instruction.

### 2017-11-08 Draft2/Indexing.Growth.tex
Work towards other sections

\HdrGrowthArrayImpl

Indexing a growth array is slower and more complex than indexing a dynamic array. However, this does not mean that accessing data of a growth array has to be slower than accessing that of a dynamic array. Refer to Sections [Iterating] and [Copying to an array] to learn how to quickly access growth arrays' data.

Despite growth arrays' relatively poor indexing performance, I include this section for two reasons. 1) Dynamic arrays are indexed frequently. In order for growth arrays to be a viable replacement for them, it should be possible to index growth arrays too. 2) I wish to show that it is possible to index growth arrays in constant time.

The first algorithm I will demonstrate is a na\"{i}ve implementation that runs in logarithmic time:

\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncGetItem$}{$\VarList, index$}
			\State $\VarIndex \gets index$
			\For{$\VarBuffer \TextIn \VarList.\FieldTail$}
				\If{$\VarIndex < \VarBuffer.\FieldLength$}
					\State \Return $\VarBuffer[\VarIndex]$
				\EndIf
				\State $\VarIndex \gets \VarIndex - \VarBuffer.\FieldLength$
			\EndFor
			\State \Return $\VarList.\FieldHead[\VarIndex]$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

I know that this algorithm runs in $O(\log n)$ time since it was shown earlier that the size of the tail, $\VarNumItemsTail$, equals $\VarUseful$, and (from Lemma \ref{lem:VarUsefulIsOLogN}) that $\VarUseful = O(\log n)$. Aside from iteration over the tail, all statements run in constant time.

% TODO: Explain why you're presenting this algorithm alongside the O(1) algorithm. 1) Simpler 2) 2nd implementation is only fast when g = 2.

### 2017-11-08 Draft2/Indexing.Growth.tex
[WIP] Work towards Indexing.Growth

@@
 
-% TODO: Explain why you're presenting this algorithm alongside the O(1) algorithm. 1) Simpler 2) 2nd implementation is only fast when g = 2.
+TODO: The following needs polish
+
+Although I have an $O(1)$ algorithm, I present this algorithm because 1) it is easier to understand and 2) the other algorithm is only fast for certain values of $\VarGrowthFactor$. [More]
+
+Before I present the constant time algorithm, I must establish [a mathematical foundation for the code].
+I note that every valid index $i$ can also be represented by an ordered pair [TODO: intro vars for these] [beta/varepsilon?] $(I_B, I_E)$, where $I_B$ represents the index of the buffer within the tail, and $I_E$ represents the index of the item within the buffer.
+Once these values are determined, the desired item is easily found via [code or math?] $\VarList.\FieldTail[I_B][I_E]$.
+[I will let $I_B = \VarList.\FieldTail.\FieldSize$ [TODO: Introduce Tsize?] mean that the buffer is $\VarList.\FieldHead$.]
+
+I now derive formulas for $I_B$ and $I_E$ in terms of $i$ [and g and c_0?]. $I_B$ is just the index of the last buffer when $i$ elements are added, or $\VarList.\FieldTail.\FieldSize - 1$

### 2017-11-08 Draft2/Indexing.Growth.tex
Add some polish

--- 2017-11-08 Draft2/Indexing.Growth.tex
@@
 2) I wish to show that it is possible to index growth arrays in constant time.
+
+\HdrLogarithmicImpl
 
@@
 
-% TODO: Explain why you're presenting this algorithm alongside the O(1) algorithm. 1) Simpler 2) 2nd implementation is only fast when g = 2.
+I present this algorithm in addition to the constant time one since 1) it is easier to understand, and 2) the latter is often slower if special circumstances are not met.
+
+\HdrConstantImpl
+
+% TODO: The following needs polish
+
+In this section, I will present the constant time algorithm for indexing a growth array. Before I do so, however, I must establish a mathematical foundation for the algorithm.
+
+I note that every valid index $i$ (``valid'' means $0 \leq i < \VarList.\FieldSize$) can be represented by the ordered pair of integers $(\VarIndexBuffer, \VarIndexElement)$.
+$\VarIndexBuffer$ is called the \textbf{buffer index} and represents the index of the buffer within the tail.
+$\VarIndexElement$ is called the \textbf{element index} and represents the index of the element within the buffer.
+
+% TODO: Even more polish
+
+Once these values are determined, the desired item is easily found via [code or math?] $\VarList.\FieldTail[I_B][I_E]$.
+[I will let $I_B = \VarList.\FieldTail.\FieldSize$ [TODO: Introduce Tsize?] mean that the buffer is $\VarList.\FieldHead$.]
+
+I now derive formulas for $I_B$ and $I_E$ in terms of $i$ [and g and c_0?]. $I_B$ is just the index of the last buffer when $i$ elements are added, or $\VarList.\FieldTail.\FieldSize - 1$

### 2017-11-10 Draft2/Indexing.Growth.tex
More work on Indexing.Growth

--- 2017-11-08 Draft2/Indexing.Growth.tex
@@
 
-% TODO: Explain why you're presenting this algorithm alongside the O(1) algorithm. 1) Simpler 2) 2nd implementation is only fast when g = 2.
+I present this algorithm alongside the constant time one because it is easier to understand, and the latter is often slower if special circumstances are not met.
+
+\HdrConstantImpl
+
+In this section, I will present a constant time algorithm for indexing a growth array. Before I do so, however, I must establish a mathematical justification for it.
+
+Suppose I want to get the $i$th element of a growth array, where $i$ is zero-based.
+I assume that $i$ is a valid index, or that $0 \leq i < \VarList.\FieldSize$.
+In order to locate the desired element, I must find two things: the buffer that holds the item, and the index of the item within that buffer.
+
+Now, consider that every buffer except the head is stored inside the tail.
+Thus, such buffers can be uniquely identified by their index in the tail.
+I will refer to this quantity as the \textbf{buffer index} and denote it $\VarIndexBuffer$.
+I wish to assign the head a buffer index as well, so that each buffer has a unique ID.
+Since the head succeeds the tail's last buffer, which has $\VarIndexBuffer = \VarNumItemsTail - 1$, I will let the head's $\VarIndexBuffer$ be $\VarNumItemsTail$.
+
+I define a helper function, $\FuncGetBuffer$, that gets the buffer associated with a given $\VarIndexBuffer$:
+
+% Todo: Make parameter names for other parts consistent.
+\begin{algorithm}
+	\begin{algorithmic}
+		\Function{$\FuncGetBuffer$}{$\VarList, \VarIndexBuffer$}
+			\If{$\VarIndexBuffer < \VarList.\FieldTail.\FieldSize$}
+				\State \Return $\VarList.\FieldTail[\VarIndexBuffer]$
+			\Else
+				\State \Return $\VarList.\FieldHead$
+			\EndIf
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+I will call the index of the desired element within the buffer the \textbf{element index}, and denote it $\VarIndexElement$.
+
+If I define a helper function $\FuncDecompose$ that returns the $\VarIndexBuffer$ and $\VarIndexElement$ associated with $i$ in an ordered pair, then $\FuncGetItem$ may be written as follows:
+
+\begin{algorithm}
+	\begin{algorithmic}
+		\Function{$\FuncGetItem$}{$\VarList, index$}
+			\State $(\VarIndexBuffer, \VarIndexElement) \gets \FuncDecompose(index)$
+			\State \Return $\VarList.\FuncGetBuffer(\VarIndexBuffer)[\VarIndexElement]$
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+The task is now to find formulae for $\VarIndexBuffer$ and $\VarIndexElement$ in terms of $i$.

### 2017-11-10 Draft2/Indexing.Growth.tex
Replace Var with Lcl for algo local variables
Algos: Variables for param names
Algos: Add spaces between commas
More work (might be a long shot to get this finished on time)

@@
 	\begin{algorithmic}
-		\Function{$\FuncGetItem$}{$\VarList, index$}
-			\State $\VarIndex \gets index$
-			\For{$\VarBuffer \TextIn \VarList.\FieldTail$}
-				\If{$\VarIndex < \VarBuffer.\FieldLength$}
-					\State \Return $\VarBuffer[\VarIndex]$
+		\Function{$\FuncGetItem$}{$\VarList,\ \ParamIndex$}
+			\State $\LclIndex \gets \ParamIndex$
+			\For{$\LclBuffer \TextIn \VarList.\FieldTail$}
+				\If{$\LclIndex < \LclBuffer.\FieldLength$}
+					\State \Return $\LclBuffer[\LclIndex]$
 				\EndIf
-				\State $\VarIndex \gets \VarIndex - \VarBuffer.\FieldLength$
+				\State $\LclIndex \gets \LclIndex - \LclBuffer.\FieldLength$
 			\EndFor
-			\State \Return $\VarList.\FieldHead[\VarIndex]$
+			\State \Return $\VarList.\FieldHead[\LclIndex]$
 		\EndFunction
@@
 
-I define a helper function, $\FuncGetBuffer$, that gets the buffer associated with a given $\VarIndexBuffer$:
+I define a helper function, $\FuncGetBuffer$, that gets the buffer associated with a given $\VarIndexBuffer$.
+$\VarIndexBuffer$ is assumed to be valid; that is, $0 \leq \VarIndexBuffer \leq \VarNumItemsTail$.
 
@@
 	\begin{algorithmic}
-		\Function{$\FuncGetBuffer$}{$\VarList, \VarIndexBuffer$}
-			\If{$\VarIndexBuffer < \VarList.\FieldTail.\FieldSize$}
-				\State \Return $\VarList.\FieldTail[\VarIndexBuffer]$
+		\Function{$\FuncGetBuffer$}{$\VarList,\ \LclIndexBuffer$}
+			\If{$\LclIndexBuffer < \VarList.\FieldTail.\FieldSize$}
+				\State \Return $\VarList.\FieldTail[\LclIndexBuffer]$
 			\Else
@@
 	\begin{algorithmic}
-		\Function{$\FuncGetItem$}{$\VarList, index$}
-			\State $(\VarIndexBuffer, \VarIndexElement) \gets \FuncDecompose(index)$
-			\State \Return $\VarList.\FuncGetBuffer(\VarIndexBuffer)[\VarIndexElement]$
+		\Function{$\FuncGetItem$}{$\VarList,\ \ParamIndex$}
+			\State $(\LclIndexBuffer,\ \LclIndexElement) \gets \FuncDecompose(\ParamIndex)$
+			\State \Return $\VarList.\FuncGetBuffer(\LclIndexBuffer)[\LclIndexElement]$
 		\EndFunction
@@
 
-The task is now to find formulae for $\VarIndexBuffer$ and $\VarIndexElement$ in terms of $i$.
+% Todo: \VarLogicalIndex for i? Introduce "logical index" term above?
+The task is now to find formulae for $\VarIndexBuffer$ and $\VarIndexElement$ in terms of $i$, in order to implement $\FuncDecompose$.
+
+% Todo: There's an awful lot of lemmas. Make some into theorems.
+\begin{lemma}
+	The formulae for $\VarIndexBuffer$ and $\VarIndexElement$ are
+	\begin{align*}
+	\VarIndexBuffer &= \VarUseful|_{n = i + 1}\\
+	\VarIndexElement &= i - \VarGrowSeq_{\VarIndexBuffer - 1}
+	\end{align*}
+\end{lemma}
+
+% Todo: "As shown earlier"
+% Todo: Again, by convention \VarGrowSeq_{-1} = 0. Modify the algorithm accordingly.
+\begin{proof}
+	Appending new items does not change the index of an item that is already in the list. Thus, this problem can be reduced to finding the last element when $n = i + 1$.
+
+	The last element always resides in the head, so $\VarIndexBuffer = \VarNumItemsTail|_{n = i + 1}$. As shown earlier, $\VarNumItemsTail = \VarUseful$, so $\VarIndexBuffer = \VarUseful|_{n = i + 1}$.
+
+	To find $\VarIndexElement$, consider the equation:
+	\begin{align*}
+	n = \text{\# of items in tail} + \text{\# of items in head}
+	\end{align*}
+	From the premise, $n = i + 1$.
+The number of items in the tail is the last size at which $\FuncGrow$ was called, or $\VarGrowSeq_{\VarUseful - 1} = \VarGrowSeq_{\VarIndexBuffer - 1}$.
+Finally, since the desired item is the last item in the growth array, it is also the last item in the head.
+Then the size of the head is $\VarIndexElement + 1$.
+Substituting these values into the above equation, I receive
+	\begin{align*}
+	i + 1 &= \VarGrowSeq_{\VarIndexBuffer - 1} + \VarIndexElement + 1\\
+	\VarIndexElement &= i - \VarGrowSeq_{\VarIndexBuffer - 1}
+	\end{align*}
+	completing the proof.
+\end{proof}
+
+% Todo: Mention formulae for \VarUseful and \VarGrowSeq_{\VarIndexBuffer - 1}.
+Now, the $\FuncDecompose$ function can be implemented as follows:
+
+% Todo: Continue to consider usage of mathematical vs. algorithm vars.
+% Todo: Can ceiling of \log_2 be implemented fast? Also, what if \VarInitCapacity is not a power of 2?
+\begin{algorithm}
+	\begin{algorithmic}
+		\Function{$\FuncDecompose$}{$\ParamIndex$}
+			\State $\LclIndexBuffer \gets \max(\left\lceil \log_{\VarGrowthFactor} (i + 1) - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil, 0)$
+			\State $\LclIndexElement \gets \ParamIndex - \VarGrowthFactor^{\LclIndexBuffer - 1} \times \VarInitCapacity$
+			\State \Return $(\LclIndexBuffer,\ \LclIndexElement)$
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+Clearly, $\FuncDecompose$ runs in constant time. At first glance, however, it appears to be quite expensive since it % Bookmark

### 2017-11-11 Draft2/Indexing.Growth.tex
Correct var name
Argh

@@
 	From the premise, $n = i + 1$.
-The number of items in the tail is the last size at which $\FuncGrow$ was called, or $\VarGrowSeq_{\VarUseful - 1} = \VarGrowSeq_{\VarIndexBuffer - 1}$.
+The number of items in the tail is the last size at which $\FuncGrow$ was called, or $\VarGrowSeq_{\VarUseful - 1} = \VarGrowSeq_{\VarIndexBuffer - 1} = \text{the last term of } \VarGrowSeq$.
 Finally, since the desired item is the last item in the growth array, it is also the last item in the head.
-Then the size of the head is $\VarIndexElement + 1$.
+Thus $\VarIndexElement$ is the head's last valid index, so the size of the head is $\VarIndexElement + 1$.
 Substituting these values into the above equation, I receive
@@
 		\Function{$\FuncDecompose$}{$\ParamIndex$}
-			\State $\LclIndexBuffer \gets \max(\left\lceil \log_{\VarGrowthFactor} (i + 1) - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil, 0)$
+			\State $\LclIndexBuffer \gets \max(\left\lceil \log_{\VarGrowthFactor} (\ParamIndex + 1) - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil, 0)$
 			\State $\LclIndexElement \gets \ParamIndex - \VarGrowthFactor^{\LclIndexBuffer - 1} \times \VarInitCapacity$
@@
 
-Clearly, $\FuncDecompose$ runs in constant time. At first glance, however, it appears to be quite expensive since it % Bookmark
+Clearly, $\FuncDecompose$ runs in constant time.
+Despite that, it still appears to be quite expensive: normally, logarithms and exponentiation utilize costly floating-point instructions.
+However, in the special case where $\VarGrowthFactor = 2$ and $\VarInitCapacity = 2^\VarLogInitCapacity$ for some constant whole number $\VarLogInitCapacity$, I claim that $\VarIndexBuffer$ and $\VarIndexElement$ can be computed without use of floating-point instructions.
+
+To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$.
+There is a constant time algorithm for computing $\left\lceil \log_2 k \right\rceil$ for any $k \in \mathbb{N}$, which uses bitwise operations instead of floating-point instructions.
+(I will not discuss it in this paper due to the length its mathematical justification would require, but the algorithm may be found in [Implementations section].) Thus $\left\lceil \log_2 (i + 1) \right\rceil$ can be computed without floating-point instructions.
+It is easy to see that the rest of the expression for $\VarIndexBuffer$ can be computed without them, too, proving the claim for $\VarIndexBuffer$.
+
+The expression for $\VarIndexElement$ becomes $i - 2^{\VarIndexBuffer + \VarLogInitCapacity - 1}$.
+Since $\VarIndexBuffer$ has already been found, it is trivial to compute $\VarIndexBuffer + \VarLogInitCapacity - 1$.
+$2$ raised to this power can be computed cheaply with a bit shift.
+Finally, subtracting from $i$ does not use floating-point instructions, proving the claim for $\VarIndexElement$.

### 2017-11-11 Draft2/CopyArray.Blurb.tex
Remove all the \varnitems stuff
Respond to feedback
Finally finish the Common Ops section

--- 2017-10-16 Draft2/CopyArray.Blurb.tex
@@
-\descriptn
+% Todo: Is 'n memory' vague?
+After they are done appending to them, users often want to take dynamic arrays and convert them into raw arrays.
+There are multiple possible reasons for this: 1) Raw arrays hold on to exactly $n$ memory to store $n$ elements.
+However, dynamic and growth arrays typically use $> n$ memory so they need not grow every time $\FuncAppend$ is called.
+2) A function in third-party code might only accept a raw array as an argument.
 
-Users often want to take list structures, such as dynamic arrays, and convert them into plain arrays.
-There are multiple reasons why someone would want to do this after they are done adding to the list:
-
-\begin{itemize}
-	\item Plain arrays hold on to exactly the amount of memory needed to hold their elements. However, dynamic and funnel arrays allocate more space than necessary to optimize adding new items.
-	\item The user wants to call a function in third-party code that takes a plain array as an argument.
-	\item
-	\item Plain arrays are contiguous, while funnel arrays are fragmented and have worse locality.
-	\item The indexer of funnel arrays is several times slower than that of plain arrays, whether the $\bigo(1)$ or $\bigo(\log \varnitems)$ implementation is chosen.
-\end{itemize}
+The case is even more compelling for growth arrays: 3) Since they are not entirely contiguous, they have worse data locality (even if the number of discontinuities is $O(\log n)$).
+4) Raw arrays can be indexed much faster than growth arrays.

### 2017-11-11 Draft2/CopyArray.Dynamic.tex
Finally finish the Common Ops section

\HdrDynArrayImpl

The algorithm for converting a dynamic array to a raw array is straightforward:

\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncToArray$}{$\VarList$}
			\State $\LclRawArray \gets \FuncNewArray(\VarList.\FieldSize)$
			\State $\FuncArrayCopy(\VarList.\FieldBuffer,\ \LclRawArray,\ \VarList.\FieldSize)$
			\State \Return $\LclRawArray$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

### 2017-11-11 Draft2/CopyArray.Growth.tex
Finally finish the Common Ops section

\HdrGrowthArrayImpl

The growth array implementation must call $\FuncArrayCopy$ multiple times, since not all elements are contiguous.

\begin{algorithm}
	\begin{algorithmic}
		\Function{$\FuncToArray$}{$\VarList$}
		\State $\LclRawArray \gets \FuncNewArray(\VarList.\FieldSize)$
		\For{$\LclBuffer \TextIn \VarList.\FieldTail$}
			\State $\FuncArrayCopy(\LclBuffer,\ \LclRawArray,\ \LclBuffer.\FieldLength)$
		\EndFor
		\State $\FuncArrayCopy(\VarList.\FieldHead,\ \LclRawArray,\ \VarList.\FieldHeadSize)$
		\State \Return $\LclRawArray$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

### 2017-11-11 Draft2/Iterating.Dynamic.tex
Finally finish the Common Ops section

\HdrDynArrayImpl

The algorithm for iterating dynamic arrays is simple. It loops through all valid indices, and calls the $\FuncGetItem$ method (which is denoted $\VarList[i]$ instead of $\VarList.\FuncGetItem(i)$) for each index.

\begin{algorithm}
	\begin{algorithmic}
		\LineComment{Algorithm for ``$\TextFor \LclItem \TextIn \VarList$'', where $\VarList$ is a dynamic array}
		\For{$\LclIndex = 0,\ \LclIndex < \VarList.\FieldSize,\ \LclIndex \gets \LclIndex + 1$}
			\State $\LclItem \gets \VarList[\LclIndex]$
			\State $\ParamAction(\LclItem)$
		\EndFor
	\end{algorithmic}
\end{algorithm}

### 2017-11-11 Draft2/Iterating.Growth.tex
Finally finish the Common Ops section

\HdrGrowthArrayImpl

The algorithm for growth arrays is not as simple, however, if the user wants optimal performance. As shown in the previous section, the algorithm for indexing growth arrays is very costly compared to its dynamic array counterpart. Thus, I wish to avoid using it in my iteration algorithm.

Fortunately, it turns out that it is possible to avoid its use:

\begin{algorithm}
	\begin{algorithmic}
		\LineComment{Algorithm for ``$\TextFor \LclItem \TextIn \VarList$'', where $\VarList$ is a growth array}
		\For{$\LclBuffer \TextIn \VarList.\FieldTail$}
			\For{$\LclItem \TextIn \LclBuffer$}
				\State $\ParamAction(\LclItem)$
			\EndFor
		\EndFor
		\For{$\LclIndex = 0,\ \LclIndex < \VarList.\FieldHeadSize,\ \LclIndex \gets \LclIndex + 1$}
		\State $\LclItem \gets \VarList.\FieldHead[\LclIndex]$
		\State $\ParamAction(\LclItem)$
		\EndFor
	\end{algorithmic}
\end{algorithm}

### 2017-11-12 Draft2/Indexing.Growth.tex
Fix one thing, agonize over another

--- 2017-11-10 Draft2/Indexing.Growth.tex
@@
 	\end{align*}
+	(By convention, $\VarGrowSeq_{-1} = 0$.)
 \end{lemma}
@@
 
-	To find $\VarIndexElement$, consider the equation:
+	To find $\VarIndexElement$, consider the identity:
 	\begin{align*}
@@
 	\end{align*}
-	From the premise, $n = i + 1$.
-The number of items in the tail is the last size at which $\FuncGrow$ was called, or $\VarGrowSeq_{\VarUseful - 1} = \VarGrowSeq_{\VarIndexBuffer - 1}$.
-Finally, since the desired item is the last item in the growth array, it is also the last item in the head.
-Then the size of the head is $\VarIndexElement + 1$.
-Substituting these values into the above equation, I receive
+	First, I will determine the number of items in the tail.
+In the case where $\VarIndexBuffer = 0$, then because $\VarNumItemsTail = \VarIndexBuffer$, the tail contains $0$ buffers and thus $0 = \VarGrowSeq_{-1}$ items.
+If $\VarIndexBuffer > 0$, the number of items in the tail is the last size at which $\FuncGrow$ was called, or the last term of $\VarGrowSeq$.
+This quantity is $\VarGrowSeq_{\VarUseful - 1} = \VarGrowSeq_{\VarIndexBuffer - 1}$.
+
+	The desired item is the growth array's last element, which implies it is also the head's last element.
+Thus $\VarIndexElement$ is the head's last valid index, so the head size is $\VarIndexElement + 1$.
+Finally, from the premise, $n = i + 1$.
+Substituting all values into the above identity, I receive
 	\begin{align*}
@@
 
-% Todo: Mention formulae for \VarUseful and \VarGrowSeq_{\VarIndexBuffer - 1}.
-Now, the $\FuncDecompose$ function can be implemented as follows:
+Using the formulae for $\VarUseful$ and $\VarGrowSeq_i$, I now implement the $\FuncDecompose$ function:
 
@@
 		\Function{$\FuncDecompose$}{$\ParamIndex$}
-			\State $\LclIndexBuffer \gets \max(\left\lceil \log_{\VarGrowthFactor} (i + 1) - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil, 0)$
+			\State $\LclIndexBuffer \gets \max(\left\lceil \log_{\VarGrowthFactor} (\ParamIndex + 1) - \log_{\VarGrowthFactor} \VarInitCapacity \right\rceil, 0)$
+			\If{$\VarIndexBuffer > 0$}
 				\State $\LclIndexElement \gets \ParamIndex - \VarGrowthFactor^{\LclIndexBuffer - 1} \times \VarInitCapacity$
+			\Else
+				\State $\VarIndexElement \gets \ParamIndex$
+			\EndIf
 			\State \Return $(\LclIndexBuffer,\ \LclIndexElement)$
@@
 
-Clearly, $\FuncDecompose$ runs in constant time. At first glance, however, it appears to be quite expensive since it % Bookmark
+Clearly, $\FuncDecompose$ runs in constant time.
+Despite that, it still appears to be quite expensive: normally, logarithms and exponentiation require use of costly floating-point instructions.
+However, in the special case where $\VarGrowthFactor = 2$ and $\VarInitCapacity = 2^\VarLogInitCapacity$ for some constant whole number $\VarLogInitCapacity$, I claim that $\VarIndexBuffer$ and $\VarIndexElement$ can be computed without use of floating-point instructions.
+
+To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$.
+There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss in this paper due to length concerns.
+(An implementation of the algorithm may be found in [Implementations section].) Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.
+
+In calculating $\VarIndexElement$, the only potential use of floating-point instructions comes from $\VarGrowthFactor^{\VarIndexBuffer - 1}$.
+When $\VarGrowthFactor = 2$, however, this can be calculated with a simple bit shift.
+Thus, it is not necessary to use floating-point instructions to calculate either $\VarIndexBuffer$ or $\VarIndexElement$.

### 2017-11-12 Draft2/Intro.tex
Follow STS guidelines. Polish the intro.

@@
 It is more efficient than the dynamic array at appending large numbers of items.
-This is due to how it 'grows' once it cannot fit more items in its buffer.
+This is due to how it `grows' once it cannot fit more items in its buffer.
 
-When dynamic arrays run out of space, they allocate a new buffer, copy the contents of the old one into it, and throw the old one away.
-However, growth arrays are less wasteful.
-Instead of throwing away the filled buffer, they keep it a part of the data structure.
+When dynamic arrays run out of space, they allocate a new buffer, copy the old one's contents into it, then throw the old one away.
+Growth arrays are less wasteful in this scenario.
+Instead of discarding the filled buffer, they simply archive it.
 The new buffer they allocate represents a continuation of the items from the old buffer.
-For example, if the old buffer contained items $0 - 31$, the new buffer would contain items $32$ and beyond.
-Because of this, growth arrays allocate less memory to store the same number of items, and they do not need to copy items from the old buffer to the new one.
+For example, if the old buffer contained items $0 - 9$, the new buffer would contain items $10$ and beyond.
+Because of this technique, growth arrays allocate less memory to store the same number of items, and do not need to copy the contents of old buffers.
 
 Growth arrays have caveats, however.
-They perform no better, or slightly worse, than dynamic arrays for operations other than appending.
-Random access, in particular, involves many more instructions than it does for dynamic arrays.
-Also, since growth arrays are not contiguous in memory, they may have poorer locality than dynamic arrays, and cannot be passed to external code that accepts contiguous buffers.
+For operations other than appending, they perform no better, or slightly worse, than dynamic arrays.
+In particular, random access is very costly for growth arrays.
+They are also not contiguous in memory, which gives them poorer locality than dynamic arrays, and prevents them from being passed to external code that accepts contiguous buffers.
 
-It is worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are completely unnecessary.
-A raw array could simply be allocated with the known size, and items could be appended to it just as quickly.
+It is worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are redundant.
+One could simply allocate a raw array with the known size, and append items to it just as quickly.
 Thus, growth arrays are only beneficial for cases where the amount of data to be appended is unknown, but is expected to be large.

### 2017-11-12 Draft2/AsymptoticNotation.tex
Respond to feedback
Work

@@
 In order to highlight the benefit of growth arrays, however, I will use the $\sim$ relation to analyze complexity.
-This is because for certain operations, growth arrays are only better than dynamic arrays by a constant factor.
+This is because growth arrays are only better than dynamic ones by a constant factor for certain operations.
 For example, dynamic arrays might use roughly $2n$ space for appending $n$ items, while growth arrays would use roughly $n$ space.
@@
 My goal is to be able to compare the coefficients of the highest-order terms in both expressions.
-For example, I would like to take the ratio $2n / n$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $n$.
+For example, I would like to take the ratio $2n : n$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $n$.
 However, big-O notation does not support this.
@@
 
-I will also introduce the cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
+I will also introduce two cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
 \begin{align*}
@@
 \end{align*}
+When reading these symbols, one says ``$f$ is asymptotically less than $g$'' or ``$f$ is asymptotically less than or equal to $g$''.
+
 \subsection{Properties}
@@
 
-Here, I define various properties of the $\sim$ relation that will be used in my proofs. These properties themselves are proved in the appendix.
+Here, I define various properties of the $\sim$ relation that later proofs will use. The properties themselves are proved in the appendix.
 
@@
 
-The following theorem states that $\sim$ is a transitive relation. This property is used implicitly by proofs that chain multiple $\sim$s in the form $f \sim g \sim h$, then conclude that $f \sim h$.
+The following theorem states that $\sim$ is a transitive relation.
+This property is used implicitly by proofs that chain multiple $\sim$ signs in the form $f \sim g \sim h$, and then conclude that $f \sim h$.
 
 \begin{theorem}
-\label{thm:Transitivity}
+\label{thm:SimIsTransitive}
 	If $f \sim g$ and $g \sim h$, then $f \sim h$.
@@
 \end{theorem}
+
+The following theorem states that if two functions are asymptotic, then they can be used interchangeably in an asymptotic inequality.
+
+\begin{theorem}
+\label{thm:InterchangeableInInequality}
+	If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLess \TweakSecond{f}$, then $f \FluteLess \TweakSecond{f}$.
+If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLess \TweakSecond{g}$, then $\Tweak{g} \FluteLess g$.
+\end{theorem}

### 2017-11-12 Draft2/FieldsProperties.tex
Work

@@
-In subsequent sections, I will implement algorithms for both dynamic and growth arrays.
-In this section, I define fields and properties for these data structures which the algorithms will use.
+In later sections, I will implement algorithms for both dynamic and growth arrays.
+In this section, I will define fields and properties for those algorithms to use.
 \textbf{Fields} are variables associated with an object that may be read from or written to.
-\textbf{Properties} are trivial, constant-time methods that do not change state.
+\textbf{Properties} are trivial, constant time methods that do not change state.
 
-If $\VarList$ is a dynamic array, then it is assumed to have the following fields:
+Let $\VarList$ be a dynamic array. I will give $\VarList$ the following fields:
 
@@
 As a dynamic array, $\VarList$ is also given the following properties.
-{\HdrNote} For pseudocode, I will use $:=$ to denote a definition, and $=$ to denote an equivalence check.
-Functions that return boolean values are suffixed with ?.
+({\HdrNote} For pseudocode, I will use $:=$ to denote a definition, and $=$ to denote an equivalence check.
+Functions that return boolean values are suffixed with ?.)
 
@@
 
-When a dynamic array is instantiated, the following code should run:
+The following code should run when $\VarList$ is instantiated:
 
@@
 
-If $\VarList$ is a growth array, then it is assumed to have the following fields:
+Now, let $\VarList$ be a growth array. I will give it the following fields:
 
 \begin{itemize}
-	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer we are currently adding items to.
+	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer new items are appended to.
 	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$.
-\textbf{Important note: The tail is a dynamic array.} It returns a \textit{dynamic array} of references to buffers that are already filled with items.
+(\textbf{Important note: The tail is a dynamic array.}) It returns a dynamic array of pointers to buffers that are already filled with items.
 The tail can be thought of as a two-dimensional array.\\
-	{\HdrNote} It may seem strange for a growth array to use the very data structure it is replacing.
-As shown in Lemma \ref{lem:VarUsefulIsOLogN}, however, only $O(\log n)$ many references are appended to the tail.
-Thus, the extra copying and allocations the tail performs is minuscule compared to other work done by the growth array.
+	({\HdrRemark} It may seem strange for a growth array to use the very data structure it is replacing.
+Lemma \ref{lem:VarUsefulIsOLogN} shows, however, that only $O(\log n)$ many pointers are appended to the tail.
+Thus, the extra copying and allocations the tail performs is minuscule compared to other work done by the growth array.)
 	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
@@
 	\begin{algorithmic}
-		\LineComment{Returns whether $\VarList$ is empty}
-		\State $\VarList.\FieldEmpty := \VarList.\FieldSize = 0$
-		\State
 		\LineComment{Returns whether $\VarList$ is full}
@@
 		\LineComment{Returns the size of $\FieldHead$}
-		\LineComment{\textbf{Rationale:} $\FieldCapacity - \FieldHeadCapacity$ is the total capacity of the buffers in $\FieldTail$.}
-		\LineComment{Then, $\FieldSize - \left( \FieldCapacity - \FieldHeadCapacity \right)$ is the number of items that were added}
-		\LineComment{after depleting the buffers in $\FieldTail$.}
+		\LineComment{\textbf{Explanation:} $\FieldCapacity - \FieldHeadCapacity$ is the number of items in $\FieldTail$.}
+		\LineComment{$\FieldSize - \left( \FieldCapacity - \FieldHeadCapacity \right)$ is the number of items not in $\FieldTail$ (meaning, in $\FieldHead$).}
 		\State $\VarList.\FieldHeadSize := \VarList.\FieldSize - \left(\VarList.\FieldCapacity - \VarList.\FieldHeadCapacity\right)$
@@
 
-When a growth array is instantiated, the following code should run:
+The following code should run when $\VarList$ is instantiated:
 

### 2017-11-12 Draft2/Appendix.tex
Respond to feedback
Work

@@
+% Todo: Name 'Appendix', not 'Appendices'
 \appendix
@@
 
-\section{Proving $\sim$ Properties}
+\section{Proofs of $\sim$ Properties}
+
+\subsection{$\sim$ is an Equivalence Relation}
+
+\begin{proof}[Proof (Theorem \ref{thm:EquivalenceRelation})]
+	Clearly, $\ExprNToInfty \dfrac{f}{f} = 1$, so $f \sim f$. Thus, $\sim$ is reflexive.
+
+	Suppose $f \sim g$.
+Then $\ExprNToInfty \dfrac{f}{g} = 1$.
+Since both $\ExprNToInfty 1$ and $\ExprNToInfty \dfrac{f}{g}$ exist and the latter is nonzero, $\dfrac{\ExprNToInfty 1}{\ExprNToInfty (f / g)}$ = $\ExprNToInfty \dfrac{g}{f}$.
+Since the left-hand side evaluates to $1$, $g \sim f$.
+Thus, $\sim$ is symmetric.
+
+	Suppose $f \sim g$ and $g \sim h$.
+By definition, $\ExprNToInfty \dfrac{f}{g} = 1$ and $\ExprNToInfty \dfrac{g}{h} = 1$.
+Since both limits exist, their product is $\ExprNToInfty \left( \dfrac{f}{g} \cdot \dfrac{g}{h} \right) = \ExprNToInfty \dfrac{f}{h}$.
+Since this product is $1$, $f \sim h$.
+Thus, $\sim$ is transitive.
+\end{proof}
+
+\subsection{$\sim$ Removes Lower-Order Terms}
+
+\begin{proof}[Proof (Theorem \ref{thm:RemovesLowerOrderTerms})]
+	Since
+	\begin{align*}
+	\ExprNToInfty \frac{f + g}{f} &= \ExprNToInfty \frac{f}{f} + \ExprNToInfty \frac{g}{f}\\
+	&= 1 + 0\\
+	&= 1
+	\end{align*}
+	it follows that $f + g \sim f$.
+\end{proof}
 
 \subsection{$\sim$ Merges over $+$, $\times$, and $\div$}
-\label{pf:MergesOverArithmetic}
+
 \begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
@@
 \end{proof}
-
-\subsection{$\sim$ Removes Lower-Order Terms}
-\label{pf:RemovesLowerOrderTerms}
-
-\begin{proof}[Proof (Theorem \ref{thm:RemovesLowerOrderTerms})]
-	Since
-	\begin{align*}
-	\ExprNToInfty \frac{f + g}{f} &= \ExprNToInfty \frac{f}{f} + \ExprNToInfty \frac{g}{f}\\
-	&= 1 + 0\\
-	&= 1
-	\end{align*}
-	it follows that $f + g \sim f$.
-\end{proof}
-
-\subsection{$\sim$ is Transitive}
-\label{pf:Transitivity}
-
-\begin{proof}[Proof (Theorem \ref{thm:Transitivity})]
-By definition, $\ExprNToInfty \dfrac f g = 1$ and $\ExprNToInfty \dfrac g h = 1$. Multiplying the two equations, $\ExprNToInfty \dfrac f h = 1$ which implies $f \sim h$.
-\end{proof}

### 2017-11-12 Draft2/AsymptoticNotation.tex
Work

@@
 
-The following theorem states that $\sim$ can ``merge,'' or un-distribute, over addition, multiplication, and division. This is a property shared with big-O.
+In the following theorems, variables with the letters $f$, $g$, or $h$ denote arbitrary, non-decreasing functions with positive outputs for sufficiently large $n$.
+
+The following theorem states that $\sim$ meets the requirements of an equivalence relation.
+
+\begin{theorem}
+\label{thm:EquivalenceRelation}
+	$\sim$ is reflexive, transitive, and symmetric.
+\end{theorem}
+
+The following theorem states that lower-order terms may be removed: for example, $(n + \log_2 n) \sim n$. This is a property shared with big-O.
+
+\begin{theorem}
+\label{thm:RemovesLowerOrderTerms}
+	If $\ExprNToInfty \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
+\end{theorem}
+
+\begin{corollary}
+\label{coro:PlusConstant}
+	If $f$ is unbounded, then $f + c \sim f$ for any constant $c$.
+\end{corollary}
+
+The following theorem states that $\sim$ can ``merge,'' or un-distribute, over addition, multiplication, and division. This is also a property shared with big-O.
 
@@
 \label{thm:MergesOverOps}
-	Suppose $f$, $\Tweak{f}$, $g$, and $\Tweak{g}$ are functions. If $f \sim \Tweak{f}$ and $g \sim \Tweak{g}$, then
+	If $f \sim \Tweak{f}$ and $g \sim \Tweak{g}$, then
 	\begin{align*}
@@
 
-The following theorem states that lower-order terms may be removed: for example, $(n + \log_2 n) \sim n$. This is also a property shared with big-O.
-
-\begin{theorem}
-\label{thm:RemovesLowerOrderTerms}
-	If $\ExprNToInfty \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
-\end{theorem}
-
-The following theorem states that $\sim$ is a transitive relation.
-This property is used implicitly by proofs that chain multiple $\sim$ signs in the form $f \sim g \sim h$, and then conclude that $f \sim h$.
-
-\begin{theorem}
-\label{thm:SimIsTransitive}
-	If $f \sim g$ and $g \sim h$, then $f \sim h$.
-\end{theorem}
+\begin{corollary}
+	Both sides of a $\sim$ relation may be added, multiplied, or divided by the same function.
+\end{corollary}
 
@@
 \end{theorem}
+
+\begin{corollary}
+	The same statements hold true for $\FluteLeq$: If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLeq \TweakSecond{f}$, then $f \FluteLeq \TweakSecond{f}$.
+If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLeq \TweakSecond{g}$, then $\Tweak{g} \FluteLeq g$.
+\end{corollary}
+
+\begin{corollary}
+	Both sides of a $\FluteLess$ or $\FluteLeq$ relation may be added, multiplied, or divided by the same function.
+\end{corollary}

### 2017-11-12 Draft2/Appendix.tex
Nightmarish

@@
 \begin{proof}[Proof (Theorem \ref{thm:RemovesLowerOrderTerms})]
-	Since
+	Let $h = O(g)$.
+By definition, $h \leq cg$ for sufficiently large $n$, where $c$ is a positive constant.
+Dividing both sides by $f$ and taking the limit, $\ExprNToInfty \dfrac{h}{f} \leq \ExprNToInfty c \left( \dfrac{g}{f} \right)$.
+Since $\ExprNToInfty \dfrac{g}{f}$ exists and equals $0$, the right-hand side equals $c \cdot 0 = 0$.
+However, $\ExprNToInfty \dfrac{h}{f} \geq 0$ since both $h$ and $f$ are positive.
+By the squeeze theorem, $\ExprNToInfty \dfrac{h}{f} = 0$.
+
+	Since $\ExprNToInfty \dfrac{f}{f}$ and $\ExprNToInfty \dfrac{h}{f}$ both exist,
 	\begin{align*}
-	\ExprNToInfty \frac{f + g}{f} &= \ExprNToInfty \frac{f}{f} + \ExprNToInfty \frac{g}{f}\\
-	&= 1 + 0\\
-	&= 1
+	\ExprNToInfty \dfrac{f + h}{f} = \ExprNToInfty \dfrac{f}{f} + \ExprNToInfty \dfrac{h}{f} = 1 + 0 = 1
 	\end{align*}
-	it follows that $f + g \sim f$.
+	It follows that $f + h = f + O(g) \sim f$.
+\end{proof}
+
+\subsubsection{$f + c \sim f$ for Unbounded $f$}
+
+\begin{proof}[Proof (Corollary \ref{coro:PlusConstant})]
+	If $f$ is unbounded, $\ExprNToInfty \dfrac{c}{f} = 0$. Applying Theorem \ref{thm:RemovesLowerOrderTerms}, $f + c \sim f$.
 \end{proof}
@@
 
-	The statement about multiplication can be shown easily by multiplying the limits corresponding to $f$ and $g$:
+	The statement about multiplication is more easily proven. Since both $\ExprNToInfty \dfrac{f}{\Tweak{f}}$ and $\ExprNToInfty \dfrac{g}{\Tweak{g}}$ exist,
 	\begin{align*}
-	\ExprNToInfty \frac{f}{\Tweak{f}} &= 1\\
-	\ExprNToInfty \frac{g}{\Tweak{g}} &= 1\\
-	\left( \ExprNToInfty \frac{f}{\Tweak{f}} \right) \left( \ExprNToInfty \frac{g}{\Tweak{g}} \right) &= 1 \cdot 1\\
-	\ExprNToInfty \frac{fg}{\Tweak{f}\Tweak{g}} &= 1
+	\ExprNToInfty \frac{fg}{\Tweak{f}\Tweak{g}} = \left( \ExprNToInfty \frac{f}{\Tweak{f}} \right) \left( \ExprNToInfty \frac{g}{\Tweak{g}} \right) = 1 \cdot 1 = 1
 	\end{align*}
-	it follows that $fg \sim \Tweak{f}\Tweak{g}$. The statement about division can be proved by flipping the limit for $g$ before multiplying, resulting in
+	It follows that $fg \sim \Tweak{f}\Tweak{g}$. If the limit for $g$ is flipped before multiplying, the following results:
 	\begin{align*}
@@
 	\end{align*}
-	This shows $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
+	This shows that $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
 \end{proof}
+
+\subsubsection{$\sim$ Relations can be Algebraically Manipulated}
+
+\begin{proof}[Proof (Corollary \ref{coro:BothSides})]
+	Since $\sim$ is reflexive, $g \sim g$. Taking $\Tweak{g} = g$ for Theorem \ref{thm:MergesOverOps}, the corollary statement follows.
+\end{proof}
+
+\subsection{Asymptotic Functions Have the Same Big-O Class}
+
+\begin{proof}[Proof (Theorem \ref{thm:SameBigOClass})]
+	This will be a proof by contradiction.
+Assume $f = O(\Tweak{f})$ where $O(\Tweak{f}) \neq O(\Tweak{g})$.
+Then $\dfrac {O(\Tweak{f})} {O(\Tweak{g})} \neq 1$.
+However, $\ExprNToInfty \dfrac{f}{g} = \dfrac {O(\Tweak{f})} {O(\Tweak{g})}$, so $\ExprNToInfty \dfrac{f}{g} \neq 1$.
+It follows that $f \not\sim g$, which contradicts the given.
+Thus, it must be true that $f = O(\Tweak{g})$.
+\end{proof}
+
+\subsection{Asymptotic Functions may be Swapped in Strict Asymptotic Inequalities}
+
+\begin{proof}[Proof (Theorem \ref{thm:InterchangeableInInequality})]
+	By definition, $\ExprNToInfty \dfrac{f}{\Tweak{f}} = 1$ and $\ExprNToInfty \dfrac{\Tweak{f}}{\TweakSecond{f}} < 1$. Since both limits exist,
+	\begin{align*}
+	\ExprNToInfty \frac{f}{\TweakSecond{f}} = \left( \ExprNToInfty \frac{f}{\Tweak{f}} \right) \left( \ExprNToInfty \frac{\Tweak{f}}{\TweakSecond{f}} \right) < 1 \cdot 1 = 1
+	\end{align*}
+	It follows that $f \FluteLess \TweakSecond{f}$.
+
+	The second statement may be proved in a similar manner. Since $\sim$ is symmetric, $\TweakSecond{g} \sim g$. Applying the same argument as before,
+	\begin{align*}
+	\ExprNToInfty \frac{\Tweak{g}}{g} = \left( \ExprNToInfty \frac{\Tweak{g}}{\TweakSecond{g}} \right) \left( \ExprNToInfty \frac{\TweakSecond{g}}{g} \right) < 1 \cdot 1 = 1
+	\end{align*}
+	Thus, $\Tweak{g} \FluteLess g$.
+\end{proof}
+
+\subsubsection{Asymptotic Functions may be Swapped in Non-Strict Asymptotic Inequalities}
+
+\begin{proof}[Proof (Corollary \ref{coro:InterchangeableInNonStrictInequality})]
+	Suppose $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLeq \TweakSecond{f}$.
+By definition, $\Tweak{f} \FluteLess \TweakSecond{f}$ or $\Tweak{f} \sim \TweakSecond{f}$.
+In the first case, from Theorem \ref{thm:InterchangeableInInequality} $f \FluteLess \TweakSecond{f}$.
+In the second case, since $\sim$ is transitive $f \sim \TweakSecond{f}$.
+In both cases, it is true that $f \FluteLeq \TweakSecond{f}$.
+
+	The second statement is, again, proved in a similar manner.
+If $\Tweak{g} \FluteLeq \TweakSecond{g}$, then $\Tweak{g} \FluteLess \TweakSecond{g}$ or $\Tweak{g} \sim \TweakSecond{g}$.
+In the first case, $\Tweak{g} \FluteLess g$; in the second, $\Tweak{g} \sim g$.
+In both cases, $\Tweak{g} \FluteLeq g$.
+\end{proof}
+
+\subsubsection{$\FluteLess$ and $\FluteLeq$ Relations can be Algebraically Manipulated}
+
+\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequality})]
+	Suppose that $f \FluteLess g$.
+By definition, $\ExprNToInfty \dfrac{f}{g} < 1$.
+For any function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.
+
+	If I suppose $f \FluteLeq g$, then $f \FluteLess g$ or $f \sim g$.
+The first statement implies $fh \FluteLess gh$, and the second implies $fh \sim gh$ (from Corollary \ref{coro:BothSides}).
+In either case, $fh \FluteLeq gh$.
+Using the same logic, it is true that $\dfrac{f}{h} \FluteLeq \dfrac{g}{h}$.
+\end{proof}

### 2017-11-12 Draft2/AsymptoticNotation.tex
Nightmarish

@@
 
-In the following theorems, variables with the letters $f$, $g$, or $h$ denote arbitrary, non-decreasing functions with positive outputs for sufficiently large $n$.
+In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote arbitrary functions that are positive and non-decreasing for sufficiently large $n$.
 
@@
 \begin{corollary}
+\label{coro:BothSides}
 	Both sides of a $\sim$ relation may be added, multiplied, or divided by the same function.
@@
 \label{thm:SameBigOClass}
-	If $f \sim g$ and $g = O(h)$, then $f = O(h)$.
+	If $f \sim g$ and $g = O(\Tweak{g})$, then $f = O(\Tweak{g})$.
 \end{theorem}
@@
 \begin{corollary}
+\label{coro:InterchangeableInNonStrictInequality}
 	The same statements hold true for $\FluteLeq$: If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLeq \TweakSecond{f}$, then $f \FluteLeq \TweakSecond{f}$.
@@
 
-\begin{corollary}
-	Both sides of a $\FluteLess$ or $\FluteLeq$ relation may be added, multiplied, or divided by the same function.
-\end{corollary}
+% Todo: Add note, adding doesn't always work.
+In the same vein as Corollary \ref{coro:BothSides}, the following theorem states that asymptotic inequalities can be algebraically manipulated.
+
+\begin{theorem}
+\label{thm:BothSidesInequality}
+	Both sides of a $\FluteLess$ or $\FluteLeq$ relation may be multiplied or divided by the same function.
+\end{theorem}

### 2017-11-12 Draft2/Appendix.tex
Finish with all the proofs...

@@
 \begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
-	% TODO: Prove statement for addition.
+	Let $\FuncQuotient = \dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, and let $\FuncDenom = \Tweak{g} + \Tweak{g}^2 / \Tweak{f}$. $\FuncQuotient$ may be expressed as
+	\begin{align*}
+	\FuncQuotient &= \frac{(\Tweak{g} / \Tweak{f})(f + g)}{(\Tweak{g} / \Tweak{f})(\Tweak{f} + \Tweak{g})}\\
+	&= \frac{\Tweak{g}(f / \Tweak{f}) + \Tweak{g}g / \Tweak{f}}{\FuncDenom}\\
+	&= \frac{\Tweak{g}(f / \Tweak{f}) + (\Tweak{g}^2 / \Tweak{f})(g / \Tweak{g})}{\FuncDenom}\\
+	&= \frac{\Tweak{g}}{d} \cdot \frac{f}{\Tweak{f}} + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \frac{g}{\Tweak{g}}
+	\end{align*}
+	Now, consider that
+	\begin{align*}
+	\FuncQuotient - 1 &= \FuncQuotient - \frac{\FuncDenom}{\FuncDenom} = \FuncQuotient - \frac{\Tweak{g}}{\FuncDenom} - \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}\\
+	&= \frac{\Tweak{g}}{d} \cdot \frac{f}{\Tweak{f}} + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \frac{g}{\Tweak{g}} - \frac{\Tweak{g}}{\FuncDenom} - \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}\\
+	&= \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right)\\
+	\ExprNToInfty \left( \FuncQuotient - 1 \right) &= \ExprNToInfty \left( \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) + \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right) \right)\\
+	&= \ExprNToInfty \left( \frac{\Tweak{g}}{d} \cdot \left( \frac{f}{\Tweak{f}} - 1 \right) \right) + \ExprNToInfty \left( \frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom} \cdot \left( \frac{g}{\Tweak{g}} - 1 \right) \right)
+	\end{align*}
+	Since $\Tweak{g}$ and $\Tweak{g}^2 / \Tweak{f}$ sum to $\FuncDenom$ and all functions are positive, $\dfrac{\Tweak{g}}{\FuncDenom}$ and $\dfrac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}$ are bounded between $0$ and $1$ as $n \to \infty$.
+From the given, $\ExprNToInfty \left( \dfrac{f}{\Tweak{f}} - 1 \right)$ and $\ExprNToInfty \left( \dfrac{g}{\Tweak{g}} - 1 \right)$ both exist and equal $0$.
+The limit of a bounded expression times one approaching $0$ is $0$; thus, both limits on the right-hand side are $0$.
 
-	The statement about multiplication is more easily proven. Since both $\ExprNToInfty \dfrac{f}{\Tweak{f}}$ and $\ExprNToInfty \dfrac{g}{\Tweak{g}}$ exist,
+	Substituting, I receive $\ExprNToInfty (\FuncQuotient - 1) = 0$, so $\ExprNToInfty \FuncQuotient = 1$.
+Since $\FuncQuotient$ is defined as $\dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, this shows that $f + g \sim \Tweak{f} + \Tweak{g}$, proving the theorem statement for addition.
+
+	The statement is much more easily proven for multiplication. Since both $\ExprNToInfty \dfrac{f}{\Tweak{f}}$ and $\ExprNToInfty \dfrac{g}{\Tweak{g}}$ exist,
 	\begin{align*}
@@
 	\end{align*}
-	This shows that $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
+	This implies that $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
 \end{proof}

### 2017-11-13 Draft2/Appending.Dynamic.tex
Remove [ref1]
Algorithms
Styling for the algos
Work towards other sections
Replace Var with Lcl for algo local variables
Algos: Variables for param names
Algos: Add spaces between commas
Work

@@
 
-I will implement appending for dynamic arrays first. Let $\VarList$ be a dynamic array. The following definitions are used in the code:
-
-\begin{description}
-	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of an empty dynamic array.\\
-	{\HdrAssumptions} $\VarInitCapacity$ is an integer, $\VarInitCapacity > 0$
-	\item[growth factor] Denoted by $\VarGrowthFactor$. The factor by which the current capacity is multiplied to get the new capacity when $\VarList$ is non-empty and grows.\\
-	{\HdrAssumptions} $\VarGrowthFactor\VarInitCapacity \geq \VarInitCapacity + 1$
-\end{description}
+I will implement appending for dynamic arrays first. Let $\VarList$ be a dynamic array. The following constants are used by the algorithm:
 
@@
 	\begin{algorithmic}[1]
-		\Procedure{$\FuncAppend$}{$L, item$}
+		\Procedure{$\FuncAppend$}{$\VarList,\ \ParamItem$}
 			\If{$\VarList.\FieldFull$}
@@
 
-			\State $\VarList.\FieldHead[\VarList.\FieldHeadSize] \gets item$
+			\State $\VarList.\FieldBuffer[\VarList.\FieldSize] \gets \ParamItem$
 			\State $\VarList.\FieldSize \gets \VarList.\FieldSize + 1$
@@
 		\Statex
-		\Procedure{$\FuncGrow$}{$L$}
-			\State $new\ buf \gets \FuncNewArray(\VarList.\FieldSize \times \VarGrowthFactor)$
-			\State $\FuncArrayCopy(\VarList.\FieldBuffer, new\ buf, \VarList.\FieldSize)$
-			\State $\VarList.\FieldBuffer \gets new\ buf$
+		\Procedure{$\FuncGrow$}{$\VarList$}
+			\State $\LclNewBuffer \gets \FuncNewArray(\VarGrowthFactor \times \VarList.\FieldSize)$
+			\State $\FuncArrayCopy(\VarList.\FieldBuffer,\ \LclNewBuffer,\ \VarList.\FieldSize)$
+			\State $\VarList.\FieldBuffer \gets \LclNewBuffer$
 		\EndProcedure
@@
 
-Before I analyze the time complexity of $\FuncAppend$, I consider a different method for measuring its cost.
-Suppose I start with an empty collection and $n$ elements are appended.
+% Todo: CITE
+It is well-known that appending one item to a dynamic array takes amortized $O(1)$ time.
+Thus, appending $n$ items takes $O(n)$ time.
+However, this fact is not very useful for the purpose of comparison--- later, it will be shown that growth arrays also take $O(n)$ time to append $n$ items.
+
+It would be helpful if the ratio $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$ could be determined, where $\FuncTimeDynamicArray(n)$ and $\FuncTimeGrowthArray(n)$ denote the average time needed to append $n$ items for dynamic and growth arrays, respectively.
+However, there is no way to quantify these functions without empirical measurements.
+Thus, I will approximate this ratio through a different technique: Suppose $n$ elements are appended to an empty collection.
 How many times is an element stored in an array?
 I will term the answer to this question the \textbf{write cost} of $n$ appends, and denote it $\FuncWrites(n)$.
+
+I will na\"{i}vely assume that $\FuncTime(n) \propto \FuncWrites(n)$, or that the average time for $n$ appends is proportional to their write cost.
+Then $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)} = \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$, where $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ are respectively the write cost functions for dynamic and growth arrays.
+In this section, I will derive the formula for $\FuncWritesDynamicArray(n)$.
+Because this section concerns dynamic arrays only, I will write it as $\FuncWrites(n)$.
 
@@
 
-	The final value of the sequence, $\VarCapacitySeq_\VarUseful$, is the capacity needed for $n$ items.
+	The final value of the sequence, $\VarCapacitySeq_\VarUseful$, is the capacity needed to store $n$ items.
 By assumption (3), $\VarCapacitySeq_\VarUseful \geq n > \VarCapacitySeq_{\VarUseful - 1}$.
 Consider the case when $n > \VarInitCapacity$: it must be true that $\VarCapacitySeq_\VarUseful > \VarInitCapacity$, so $\VarUseful \geq 1$.
-Since $\VarUseful - 1 \neq 0$, $\VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$ and $\VarCapacitySeq_{\VarUseful - 1} = \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity$.
+Since $\VarUseful - 1 \geq 0$, $\VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$ and $\VarCapacitySeq_{\VarUseful - 1} = \VarGrowthFactor^{\VarUseful - 1}\VarInitCapacity$.
 Then
@@
 	\end{align*}
-	Now consider the case when $n \leq \VarInitCapacity$.
+	Now, consider the case when $n \leq \VarInitCapacity$.
 By assumption (3), $n > \VarCapacitySeq_{\VarUseful - 1}$.
@@
 
-	It was shown $\VarUseful \geq 1 \geq 0$ for the first case, and it can be shown $\ExprMessy \leq 0$ for the second case. Then, a general formula for $\VarUseful$ is as follows:
+	It was shown that $\VarUseful \geq 1 \geq 0$ for the first case, and it can be shown that $\ExprMessy \leq 0$ for the second case. Therefore, a general formula for $\VarUseful$ is as follows:
 	\begin{align*}
@@
 \label{coro:GrowthSeq}
-	Let the \textbf{growth sequence}, $\VarGrowSeq$, of $\VarList$ be the sizes for which $\FuncGrow$ is called when $n$ items are appended.
+	Let the \textbf{growth sequence}, $\VarGrowSeq$, of $\VarList$ be the sizes at which $\FuncGrow$ is called when $n$ items are appended to $\VarList$.
 Then $\VarGrowSeq = \VarCapacitySeq \setminus \left\{ \VarCapacitySeq_\VarUseful \right\}$.
@@
 \begin{proof}
+	% Todo: Better language here? 'exists' is confusing
 	If $\VarCapacitySeq_i$ exists and $i \geq 1$, then clearly $\FuncGrow$ must have been called when the size was $\VarCapacitySeq_{i - 1}$, so $\VarCapacitySeq_{i - 1} \in \VarGrowSeq$.
@@
 \end{align*}
-Counting the writes made for each item by $\FuncAppend$, an explicit formula for $\FuncWrites(n)$ is as follows:
-[ref1]
+Counting the writes made per item by $\FuncAppend$, an explicit formula for $\FuncWrites(n)$ is as follows:
 \begin{align*}
@@
 \end{align*}
-Now, my goal is to approximate $\FuncWrites(n)$ with $\sim$. To make is easier to do so, I will asymptotically bound $\VarGrowthFactor^\VarUseful$ which depends on $n$.
+Now, my goal is to approximate $\FuncWrites(n)$ with $\sim$. To make this easier to do, I will asymptotically bound $\VarGrowthFactor^\VarUseful$ with respect to $n$.
 
@@
 \label{lem:ToVarUsefulPowerBounds}
-	For $n > \VarInitCapacity$, $\dfrac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \dfrac {\VarGrowthFactor{n}} \VarInitCapacity$.
+	$\dfrac n \VarInitCapacity \FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \dfrac {\VarGrowthFactor{n}} \VarInitCapacity$.
+That is, $\dfrac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \dfrac {\VarGrowthFactor{n}} \VarInitCapacity$ for sufficiently large $n$.
 \end{lemma}
@@
 \begin{proof}
-	It was shown in Lemma \ref{lem:CapacitySeq} that if $n > \VarInitCapacity$, $\VarUseful = \ExprMessy \geq 1$.  Now note that $\VarUseful$ may also be written as $\ExprMessyAlt$. Then
+	It was shown in Lemma \ref{lem:CapacitySeq} that if $n > \VarInitCapacity$, $\VarUseful = \ExprMessy \geq 1$.  Now, note that $\VarUseful$ may be written as $\ExprMessyAlt$ for such $n$. Then,
 	\begin{align*}
@@
 
-Now, I proceed to asymptotically bound $\FuncWrites(n)$.
+I now proceed to asymptotically bound $\FuncWrites(n)$:
 \begin{align*}

### 2017-11-13 Draft2/AsymptoticNotation.tex
Work

@@
 
-I will also introduce two cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
+I will also introduce two cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. They are defined as follows:
 \begin{align*}
-f \FluteLess g \Biconditional \ExprNToInfty \frac f g < 1
+f \FluteLess g &\Biconditional \ExprNToInfty \frac f g < 1\\
+f \FluteLeq g &\Biconditional f \FluteLess g \lor f \sim g
 \end{align*}
-When reading these symbols, one says ``$f$ is asymptotically less than $g$'' or ``$f$ is asymptotically less than or equal to $g$''.
+I will call these relations \textbf{asymptotic inequalities}.
+The above inequalities are read ``$f$ is asymptotically less than $g$'' and ``$f$ is asymptotically less than or equal to $g$,'' respectively.
 
@@
 
-Here, I define various properties of the $\sim$ relation that later proofs will use. The properties themselves are proved in the appendix.
+I define various properties of the $\sim$ relation here, which later proofs will use. The properties themselves are proved in the appendix.
 
@@
 \label{coro:BothSides}
-	Both sides of a $\sim$ relation may be added, multiplied, or divided by the same function.
+	A $\sim$ equation holds if both sides are added, multiplied, or divided by the same quantity.
 \end{corollary}
@@
 
-The following theorem states that if two functions are asymptotic, then they can be used interchangeably in an asymptotic inequality.
+The following theorem states that if two functions are asymptotic, then they can be interchanged in an asymptotic inequality.
 
@@
 \label{coro:InterchangeableInNonStrictInequality}
-	The same statements hold true for $\FluteLeq$: If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLeq \TweakSecond{f}$, then $f \FluteLeq \TweakSecond{f}$.
+	This theorem also holds for $\FluteLeq$: If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLeq \TweakSecond{f}$, then $f \FluteLeq \TweakSecond{f}$.
 If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLeq \TweakSecond{g}$, then $\Tweak{g} \FluteLeq g$.
@@
 
-% Todo: Add note, adding doesn't always work.
-In the same vein as Corollary \ref{coro:BothSides}, the following theorem states that asymptotic inequalities can be algebraically manipulated.
+The following theorem states that asymptotic inequalities can be algebraically manipulated, in the same vein as Corollary \ref{coro:BothSides}.
+However, they do not always hold if the same quantity is added to both sides; for example, $1 \FluteLess 2$, but $n + 1 \sim n + 2$.
 
@@
 \label{thm:BothSidesInequality}
-	Both sides of a $\FluteLess$ or $\FluteLeq$ relation may be multiplied or divided by the same function.
+	A $\FluteLess$ or $\FluteLeq$ inequality holds if both sides are multiplied or divided by the same quantity.
 \end{theorem}

### 2017-11-13 Draft2/CommonOperations.Blurb.tex
Work

--- 2017-10-18 Draft2/CommonOperations.Blurb.tex
@@
-In this section, I implement common operations for dynamic and growth arrays, and analyze their time complexity. I also analyze space complexity of operations that allocate memory.
+In this section, I implement commonly used operations for dynamic and growth arrays, then analyze their time complexity. I also analyze the space complexity of operations that allocate memory.

### 2017-11-13 Draft2/ExternalDefinitions.tex
Work

I assume that the following functions are defined by the runtime. Thus, I will use them in my algorithms without providing definitions for them.

\begin{algorithm}
	\begin{algorithmic}
		\LineComment{Copies $len$ items from $source$ to $dest$}
		\State $\FuncArrayCopy(source,\ dest,\ len)$
		\State
		\LineComment{Returns a new array with length $len$}
		\State $\FuncNewArray(len)$
		\State
		\LineComment{Returns a new, empty dynamic array}
		\State $\FuncNewDynamicArray()$
	\end{algorithmic}
\end{algorithm}

I will also use the following constants in my algorithms. Specific values for these constants must be supplied by the person using the algorithms.

\begin{description}
	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of an empty dynamic array.\\
	{\HdrAssumptions} $\VarInitCapacity$ is a natural number
	\item[growth factor] Denoted by $\VarGrowthFactor$. The constant ratio of the new capacity to the old one when $\VarList$ grows.\\
	% Todo
	{\HdrAssumptions} $\VarGrowthFactor\VarInitCapacity \geq \VarInitCapacity + 1$
\end{description}

### 2017-11-13 Draft2/FieldsProperties.tex
Work

@@
 \begin{itemize}
-	\item $\VarList.\FieldBuffer$ - The \textbf{buffer}, or raw array, that $\VarList$ stores its items in.
-	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
+	\item $\VarList.\FieldBuffer$ -- The \textbf{buffer}, or raw array, that $\VarList$ stores its items in.
+	\item $\VarList.\FieldSize$ -- The number of items in $\VarList$.
 \end{itemize}
@@
 \begin{itemize}
-	\item $\VarList.\FieldHead$ - The \textbf{head} of $\VarList$. It returns the buffer new items are appended to.
-	\item $\VarList.\FieldTail$ - The \textbf{tail} of $\VarList$.
+	\item $\VarList.\FieldHead$ -- The \textbf{head} of $\VarList$. It returns the buffer new items are appended to.
+	\item $\VarList.\FieldTail$ -- The \textbf{tail} of $\VarList$.
 (\textbf{Important note: The tail is a dynamic array.}) It returns a dynamic array of pointers to buffers that are already filled with items.
@@
 	({\HdrRemark} It may seem strange for a growth array to use the very data structure it is replacing.
-Lemma \ref{lem:VarUsefulIsOLogN} shows, however, that only $O(\log n)$ many pointers are appended to the tail.
+Lemma \ref{lem:VarUsefulIsOLogN} will show, however, that only $O(\log n)$ many pointers are appended to the tail.
 Thus, the extra copying and allocations the tail performs is minuscule compared to other work done by the growth array.)
-	\item $\VarList.\FieldSize$ - The number of items in $\VarList$.
-	\item $\VarList.\FieldCapacity$ - The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold before it must grow.
+	\item $\VarList.\FieldSize$ -- The number of items in $\VarList$.
+	\item $\VarList.\FieldCapacity$ -- The \textbf{capacity} of $\VarList$. It returns the maximum number of items $\VarList$ can hold before it must grow.
 \end{itemize}

### 2017-11-13 Draft2/Appending.Dynamic.tex
Work
Finish more

@@
 
-I now proceed to asymptotically bound $\FuncWrites(n)$:
+I can build on this inequality to receive asymptotic bounds for $\FuncWrites(n)$:
 \begin{align*}
-\FuncWrites(n) &= n + \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-n + \left( \frac{n / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLeq \FuncWrites(n) &\FluteLess n + \left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n - \left( \frac{\VarInitCapacity}{\VarGrowthFactor - 1} \right) \FluteLeq \FuncWrites(n) &\FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n - \left( \frac{\VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \FluteLeq \FuncWrites(n) &\FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
+\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
+\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful - 1 \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
+\frac n {\VarGrowthFactor - 1} &\FluteLeq \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLess \frac {\VarGrowthFactor{n}} {\VarGrowthFactor - 1}\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
 \end{align*}
@@
 
-I wish to find the space allocated when $n$ items are appended to a dynamic array.
-I call this quantity the \textbf{space cost}, denote it $\FuncSpace(n)$, and define it as the total length of buffers allocated by $n$ $\FuncAppend$ calls.
+I wish to find the space allocated when $n$ items are appended to a collection.
+I call this quantity the \textbf{space cost}, denote it $\FuncSpace(n)$, and define it as the total length of buffers allocated by $n$ appends.
 Now, I derive a formula for $\FuncSpace(n)$.
@@
 \begin{align*}
-\left( \frac{\VarGrowthFactor{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLeq \FuncSpace(n) &\FluteLess \left( \frac{\VarGrowthFactor^2{n} / \VarInitCapacity - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n - \left( \frac{\VarInitCapacity}{\VarGrowthFactor - 1} \right) \FluteLeq \FuncSpace(n) &\FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n - \left( \frac{\VarInitCapacity}{\VarGrowthFactor - 1} \right)\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n \FluteLeq \FuncSpace(n) &\FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n
+\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
+\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity\\
+\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} - 1 \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncSpace(n) \FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n
 \end{align*}

### 2017-11-13 Draft2/Appending.Dynamic.tex
...
Was close...

@@
 It would be helpful if the ratio $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$ could be determined, where $\FuncTimeDynamicArray(n)$ and $\FuncTimeGrowthArray(n)$ denote the average time needed to append $n$ items for dynamic and growth arrays, respectively.
+This represents how much faster growth arrays are than dynamic ones.
 However, there is no way to quantify these functions without empirical measurements.
@@
 \frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
-\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful - 1 \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
-\frac n {\VarGrowthFactor - 1} &\FluteLeq \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLess \frac {\VarGrowthFactor{n}} {\VarGrowthFactor - 1}\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n
+\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful - 1 \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality}, Corollary \ref{coro:InterchangeableInNonStrictInequality})}\\
+\frac n {\VarGrowthFactor - 1} &\FluteLeq \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLess \frac {\VarGrowthFactor{n}} {\VarGrowthFactor - 1} &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n % Bookmark
 \end{align*}

### 2017-11-13 Draft2/Appendix.tex
Was close...

@@
 
-	The statement is much more easily proven for multiplication. Since both $\ExprNToInfty \dfrac{f}{\Tweak{f}}$ and $\ExprNToInfty \dfrac{g}{\Tweak{g}}$ exist,
+	The statement is proven much more easily for multiplication. Since both $\ExprNToInfty \dfrac{f}{\Tweak{f}}$ and $\ExprNToInfty \dfrac{g}{\Tweak{g}}$ exist,
 	\begin{align*}
@@
 
-\subsubsection{$\sim$ Relations can be Algebraically Manipulated}
+\subsubsection{$\sim$ Equations can be Algebraically Manipulated}
 
@@
 
-\subsection{Asymptotic Functions may be Swapped in Strict Asymptotic Inequalities}
+\subsection{Asymptotic Functions may be Interchanged in $\FluteLess$ Inequalities}
 
@@
 
-\subsubsection{Asymptotic Functions may be Swapped in Non-Strict Asymptotic Inequalities}
+\subsubsection{Asymptotic Functions may be Interchanged in $\FluteLeq$ Inequalities}
 
@@
 By definition, $\Tweak{f} \FluteLess \TweakSecond{f}$ or $\Tweak{f} \sim \TweakSecond{f}$.
-In the first case, from Theorem \ref{thm:InterchangeableInInequality} $f \FluteLess \TweakSecond{f}$.
-In the second case, since $\sim$ is transitive $f \sim \TweakSecond{f}$.
+In the first case, from Theorem \ref{thm:InterchangeableInInequality}, $f \FluteLess \TweakSecond{f}$.
+In the second case, since $\sim$ is transitive, $f \sim \TweakSecond{f}$.
 In both cases, it is true that $f \FluteLeq \TweakSecond{f}$.
 
-	The second statement is, again, proved in a similar manner.
-If $\Tweak{g} \FluteLeq \TweakSecond{g}$, then $\Tweak{g} \FluteLess \TweakSecond{g}$ or $\Tweak{g} \sim \TweakSecond{g}$.
+	The second statement is proved similarly.
+It is given that $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLeq \TweakSecond{g}$; the latter implies that either $\Tweak{g} \FluteLess \TweakSecond{g}$ or $\Tweak{g} \sim \TweakSecond{g}$.
 In the first case, $\Tweak{g} \FluteLess g$; in the second, $\Tweak{g} \sim g$.
@@
 
-\subsubsection{$\FluteLess$ and $\FluteLeq$ Relations can be Algebraically Manipulated}
+\subsection{$\FluteLess$ Inequalities can be Algebraically Manipulated}
 
@@
 For any function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.
+\end{proof}
 
+\subsubsection{$\FluteLeq$ Inequalities can be Algebraically Manipulated}
+
+\begin{proof}[Proof (Corollary \ref{coro:BothSidesNonStrictInequality})]
 	If I suppose $f \FluteLeq g$, then $f \FluteLess g$ or $f \sim g$.
-The first statement implies $fh \FluteLess gh$, and the second implies $fh \sim gh$ (from Corollary \ref{coro:BothSides}).
+The first case implies $fh \FluteLess gh$ from Theorem \ref{thm:BothSidesInequality}, and the second implies $fh \sim gh$ from Corollary \ref{coro:BothSides}.
 In either case, $fh \FluteLeq gh$.
@@
 \end{proof}
+
+\subsection{Same-Order Terms may be Added to Both Sides of $\FluteLess$ Inequalities}
+
+\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequalityAdd})]
+	From Theorem \ref{thm:InterchangeableInInequality}, we may substitute $f$ and $g$ in the inequality with $c_1 h$ and $c_2 h$ to receive $c_1 h \FluteLess c_2 h$.
+Then $\ExprNToInfty \dfrac{c_1 h}{c_2 h} = \dfrac{c_1}{c_2} < 1$, so $c_1 < c_2$.
+
+	Now, consider that $c_1 h + h \sim f + h$ and $g + h \sim c_2 h + h$ from Corollary \ref{coro:BothSides}.
+By definition, the limits $\ExprNToInfty \dfrac{(c_1 + 1) h}{f + h}$ and $\ExprNToInfty \dfrac{g + h}{(c_2 + 1) h}$ exist and are equal to $1$.
+Then,
+	\begin{align*}
+	\ExprNToInfty \frac{f + h}{g + h} &= \left( \ExprNToInfty \frac{f + h}{g + h} \right) \left( \ExprNToInfty \dfrac{(c_1 + 1) h}{f + h} \right) \left( \ExprNToInfty \dfrac{g + h}{(c_2 + 1) h} \right)\\
+	&= \ExprNToInfty \frac{(c_1 + 1) h}{(c_2 + 1) h}\\
+	&= \frac{c_1 + 1}{c_2 + 1}
+	\end{align*}
+	Since $c_1 < c_2$, $c_1 + 1 < c_2 + 1$ so $\dfrac{c_1 + 1}{c_2 + 1} < 1$. Thus, $f + h \FluteLess g + h$.
+\end{proof}
+
+\subsubsection{Same-Order Terms may be Added to Both Sides of $\FluteLeq$ Inequalities}
+
+\begin{proof}[Proof (Corollary \ref{coro:BothSidesNonStrictInequalityAdd})]
+	Given $f \FluteLeq g$, it is true that either $f \FluteLess g$ or $f \sim g$.
+In the first case, from Theorem \ref{thm:BothSidesInequalityAdd} it follows that $f + h \FluteLess g + h$.
+In the second case, from Theorem \ref{coro:BothSides} it follows that $f + h \sim g + h$.
+In both cases, $f + h \FluteLeq g + h$.
+\end{proof}

### 2017-11-13 Draft2/AsymptoticNotation.tex
Was close...

@@
 
-I define various properties of the $\sim$ relation here, which later proofs will use. The properties themselves are proved in the appendix.
+I define various properties of the $\sim$ relation here, which proofs in later sections will use. The properties themselves are proved in the appendix.
 
-In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote arbitrary functions that are positive and non-decreasing for sufficiently large $n$.
+In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
 
-The following theorem states that $\sim$ meets the requirements of an equivalence relation.
+The following theorem states that $\sim$ is a valid equivalence relation.
 
@@
 
-The following theorem states that if two functions are asymptotic, then they belong to the same big-O class.
+The following theorem states that asymptotic functions belong to the same big-O class.
 
@@
 
-The following theorem states that if two functions are asymptotic, then they can be interchanged in an asymptotic inequality.
+The following theorem states that asymptotic functions can be interchanged in an asymptotic inequality.
 
@@
 \label{coro:InterchangeableInNonStrictInequality}
-	This theorem also holds for $\FluteLeq$: If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLeq \TweakSecond{f}$, then $f \FluteLeq \TweakSecond{f}$.
-If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLeq \TweakSecond{g}$, then $\Tweak{g} \FluteLeq g$.
+	This theorem also holds for $\FluteLeq$.
 \end{corollary}
@@
 The following theorem states that asymptotic inequalities can be algebraically manipulated, in the same vein as Corollary \ref{coro:BothSides}.
-However, they do not always hold if the same quantity is added to both sides; for example, $1 \FluteLess 2$, but $n + 1 \sim n + 2$.
 
@@
 \label{thm:BothSidesInequality}
-	A $\FluteLess$ or $\FluteLeq$ inequality holds if both sides are multiplied or divided by the same quantity.
+	A $\FluteLess$ inequality holds if both sides are multiplied or divided by the same quantity.
 \end{theorem}
+
+\begin{corollary}
+\label{coro:BothSidesNonStrictInequality}
+	This theorem also holds for $\FluteLeq$.
+\end{corollary}
+
+Notice that the above theorem does not include addition.
+Asymptotic inequalities do not always hold if the same quantity is added to both sides; for example, $1 \FluteLess 2$, but $n + 1 \sim n + 2$.
+In order for them to hold, certain conditions must be met.
+
+\begin{theorem}
+\label{thm:BothSidesInequalityAdd}
+	Suppose $f \FluteLess g$. If $f \sim c_1 h$ and $g \sim c_2 h$ for some $c_1, c_2 > 0$, then $f + h \FluteLess g + h$.
+\end{theorem}
+
+\begin{corollary}
+\label{coro:BothSidesNonStrictInequalityAdd}
+	This theorem also holds for $\FluteLeq$.
+\end{corollary}

### 2017-11-13 Draft2/Implementations.tex
Was close...

% Todo: Use hyperref?
In order to demonstrate empirical evidence that the algorithms described above work, I have implemented them in the programming language C\#. I have written a full test suite for them and benchmarked them extensively. The implementation and the benchmark results can be found here: https://github.com/jamesqo/StsProject

I have previously implemented this algorithm for the open-source project .NET Core, which is run by Microsoft. I submitted two patches that applied this algorithm in order to reduce memory consumption for a commonly-called function. The patches can be found at the following links: https://github.com/dotnet/corefx/pull/11208 and https://github.com/dotnet/corefx/pull/13076. The first patch contains the original implementation of the algorithm. The second patch contains a cleaned-up version of the original implementation.

### 2017-11-13 Draft2/Appendix.tex
Maybe put this to rest at last

@@
 \begin{proof}[Proof (Theorem \ref{thm:BothSidesInequalityAdd})]
-	From Theorem \ref{thm:InterchangeableInInequality}, we may substitute $f$ and $g$ in the inequality with $c_1 h$ and $c_2 h$ to receive $c_1 h \FluteLess c_2 h$.
-Then $\ExprNToInfty \dfrac{c_1 h}{c_2 h} = \dfrac{c_1}{c_2} < 1$, so $c_1 < c_2$.
-
-	Now, consider that $c_1 h + h \sim f + h$ and $g + h \sim c_2 h + h$ from Corollary \ref{coro:BothSides}.
-By definition, the limits $\ExprNToInfty \dfrac{(c_1 + 1) h}{f + h}$ and $\ExprNToInfty \dfrac{g + h}{(c_2 + 1) h}$ exist and are equal to $1$.
-Then,
+	If $\dfrac{f}{h}$ does not approach $0$ as $n \to \infty$, then it is bounded below by some positive constant $c_1$, and $\ExprNToInfty \dfrac{c_1 h}{f} \leq 1$.
+From $f \FluteLess g$, it follows that $\ExprNToInfty \dfrac{f}{g} < 1$.
+Since $g = O(h)$, $\exists c_2 : \ExprNToInfty \dfrac{g}{c_2 h} \leq 1$.
+Multiplying these limits, I receive
 	\begin{align*}
-	\ExprNToInfty \frac{f + h}{g + h} &= \left( \ExprNToInfty \frac{f + h}{g + h} \right) \left( \ExprNToInfty \dfrac{(c_1 + 1) h}{f + h} \right) \left( \ExprNToInfty \dfrac{g + h}{(c_2 + 1) h} \right)\\
-	&= \ExprNToInfty \frac{(c_1 + 1) h}{(c_2 + 1) h}\\
-	&= \frac{c_1 + 1}{c_2 + 1}
+	\left( \ExprNToInfty \frac{c_1 h}{f} \right) \left( \ExprNToInfty \dfrac{f}{g} \right) \left( \ExprNToInfty \dfrac{g}{c_2 h} \right) = \ExprNToInfty \frac{c_1 h}{c_2 h} = \frac{c_1}{c_2}
+	\end{align*}
+	Since at least one limit is less than $1$, and no limit exceeds $1$, the product $\dfrac{c_1}{c_2}$ is less than one. Now, consider that
+	\begin{align*}
+	\ExprNToInfty \frac{f + h}{g + h} \leq \ExprNToInfty \frac{c_1 h + h}{c_2 h + h} = \frac{c_1 + 1}{c_2 + 1}
 	\end{align*}

### 2017-11-13 Draft2/Appending.Dynamic.tex
Work

@@
 \frac n {\VarGrowthFactor - 1} &\FluteLeq \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLess \frac {\VarGrowthFactor{n}} {\VarGrowthFactor - 1} &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n % Bookmark
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequalityAdd}, Corollary \ref{coro:BothSidesNonStrictInequalityAdd})}
 \end{align*}
@@
 \frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
-\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity\\
-\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} - 1 \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncSpace(n) \FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n
+\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}\\
+\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} - 1 \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality}, Corollary \ref{coro:InterchangeableInNonStrictInequality})}\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncSpace(n) \FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}
 \end{align*}

### 2017-11-13 Draft2/Appending.Growth.tex
Cleanup all the limits
Respond to feedback
Algorithms
Styling for the algos
Work towards other sections
Replace Var with Lcl for algo local variables
Algos: Variables for param names
Algos: Add spaces between commas
Fix critical error. Thank god my code caught it.
...
Finalize file layout?
Work

@@
 \HdrGrowthArrayImpl
+
+In this section, $\VarList$ is a growth array. The following algorithm implements appending for growth arrays.
+
+\begin{algorithm}
+	\begin{algorithmic}[1]
+		\Procedure{$\FuncAppend$}{$\VarList,\ \ParamItem$}
+			\If{$\VarList.\FieldFull$}
+				\State $\VarList.\FuncGrow()$
+			\EndIf
+
+			\State $\VarList.\FieldHead[\VarList.\FieldHeadSize] \gets \ParamItem$
+			\State $\VarList.\FieldSize \gets \VarList.\FieldSize + 1$
+		\EndProcedure
+		\Statex
+		\Procedure{$\FuncGrow$}{$\VarList$}
+			\State $\VarList.\FieldTail.Append(\VarList.\FieldHead)$
+			\If{$\VarList.\FieldCapacity = \VarInitCapacity$}
+				\State $\LclNewHeadCapacity \gets (\VarGrowthFactor - 1) \times \VarInitCapacity$
+			\Else
+				\State $\LclNewHeadCapacity \gets \VarGrowthFactor \times \VarList.\FieldHeadCapacity$
+			\EndIf
+			\State $\VarList.\FieldHead \gets \FuncNewArray(\LclNewHeadCapacity)$
+			\State $\VarList.\FieldCapacity \gets \VarList.\FieldCapacity + \LclNewHeadCapacity$
+		\EndProcedure
+	\end{algorithmic}
+\end{algorithm}
 
@@
 
-I start off again by finding the write cost for $n$ items.
-Lemma \ref{lem:CapacitySeq} still holds, since growth arrays satisfy the properties used by that proof.
-In particular, although growth arrays use a different growth algorithm than dynamic arrays, the following claim is still true:
+It takes $O(n)$ time to append $n$ items to a growth array.
+This can be easily seen by noting that every statement in the algorithm has amortized $O(1)$ time complexity (ignoring the call to $\FuncNewArray$, since memory allocation is non-deterministic).
+
+Now, I focus on finding a formula for the write cost function, $\FuncWritesGrowthArray(n)$, which will be written as $\FuncWrites(n)$ in this section.
+I claim that Lemma \ref{lem:CapacitySeq} still holds, since growth arrays satisfy all properties used by that proof.
+In particular, although growth arrays use a different growth algorithm than dynamic arrays, the following statement still holds:
 
@@
 
-	For $k > 1$, by induction $c_i = \text{previous }c_f = \VarGrowthFactor^{k - 2}\VarInitCapacity$, and $h_i = \text{previous }h_f = (\VarGrowthFactor^{k - 2} - \VarGrowthFactor^{k - 3})\VarInitCapacity$.
-I wish to show $c_f = \VarGrowthFactor^{k - 1}\VarInitCapacity$ and $h_f = (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity$.
+	For $k > 1$, by induction $c_i = \text{previous }c_f = \VarGrowthFactor^{k - 1}\VarInitCapacity$, and $h_i = \text{previous }h_f = (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity$.
+I wish to show $c_f = \VarGrowthFactor^{k}\VarInitCapacity$ and $h_f = (\VarGrowthFactor^{k} - \VarGrowthFactor^{k - 1})\VarInitCapacity$.
 Because $k > 1$, the algorithm will calculate $h_f$ as $\VarGrowthFactor$ times $h_i$.
@@
 	\begin{align*}
-	h_f &= \VarGrowthFactor h_i = \VarGrowthFactor (\VarGrowthFactor^{k - 2} - \VarGrowthFactor^{k - 3})\VarInitCapacity = (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity
+	h_f &= \VarGrowthFactor h_i = \VarGrowthFactor (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity = (\VarGrowthFactor^{k} - \VarGrowthFactor^{k - 1})\VarInitCapacity
 	\end{align*}
@@
 	\begin{align*}
-	c_f &= c_i + h_f = \VarGrowthFactor^{k - 2}\VarInitCapacity + (\VarGrowthFactor^{k - 1} - \VarGrowthFactor^{k - 2})\VarInitCapacity = \VarGrowthFactor^{k - 1}\VarInitCapacity
+	c_f &= c_i + h_f = \VarGrowthFactor^{k - 1}\VarInitCapacity + (\VarGrowthFactor^{k} - \VarGrowthFactor^{k - 1})\VarInitCapacity = \VarGrowthFactor^{k}\VarInitCapacity
 	\end{align*}
@@
 In fact, $\FuncGrow$ does not copy \textit{any} items supplied by the user.
-Writes are only made when a buffer is appended to the tail, since the tail is a dynamic array.
+Writes are only made when a buffer pointer is appended to the tail, since the tail is a dynamic array.
 
@@
 \end{align*}
-Then the formula for $\FuncWritesByGrow(n)$ is simply $\FuncWritesTail(\VarUseful)$, where $\FuncWritesTail$ denotes the tail's write cost function, that is, the write cost function for dynamic arrays.
+Then the formula for $\FuncWritesByGrow(n)$ is simply $\FuncWritesTail(\VarUseful)$, where $\FuncWritesTail$ denotes the tail's write cost function (that is, the write cost function for dynamic arrays).
 Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWrites(n)$ is
@@
 \begin{proof}
-	From \ref{lem:CapacitySeq}, $\VarUseful = \max(\ExprMessy, 0)$. As mentioned in Lemma \ref{lem:ToVarUsefulPowerBounds}, for sufficiently large $n$, $\VarUseful = \ExprMessy$. Then
+	From Lemma \ref{lem:CapacitySeq}, $\VarUseful = \max(\ExprMessy, 0)$. As mentioned in Lemma \ref{lem:ToVarUsefulPowerBounds}, for sufficiently large $n$, $\VarUseful = \ExprMessy$. Then
 	\begin{align*}
@@
 \end{align*}
+The last step is true because of Theorem \ref{thm:RemovesLowerOrderTerms}.
 
@@
 
-Now, consider the ratio $\lim_{n \to \infty} \dfrac {\FuncSpaceTail(\VarUseful)} {\VarCapacitySeq_\VarUseful} = \dfrac {O(\log n)} {O(n)} = O \left( \dfrac{\log n}{n} \right) = 0$.
+Now, consider the ratio $\ExprNToInfty \dfrac {\FuncSpaceTail(\VarUseful)} {\VarCapacitySeq_\VarUseful} = \dfrac {O(\log n)} {O(n)} = O \left( \dfrac{\log n}{n} \right) = 0$.
 Because it is $0$, from Theorem \ref{thm:RemovesLowerOrderTerms} one can conclude

### 2017-11-13 Draft2/Appending.Growth.tex
Work

@@
 \end{align*}
-Then the formula for $\FuncWritesByGrow(n)$ is simply $\FuncWritesTail(\VarUseful)$, where $\FuncWritesTail$ denotes the tail's write cost function (that is, the write cost function for dynamic arrays).
+Then the formula for $\FuncWritesByGrow(n)$ is simply $\FuncWritesTail(\VarUseful)$, since $\VarUseful$ pointers are appended to the tail, which is a dynamic array.
 Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWrites(n)$ is
@@
 \begin{proof}
-	From Lemma \ref{lem:CapacitySeq}, $\VarUseful = \max(\ExprMessy, 0)$. As mentioned in Lemma \ref{lem:ToVarUsefulPowerBounds}, for sufficiently large $n$, $\VarUseful = \ExprMessy$. Then
+	From Lemma \ref{lem:CapacitySeq}, $\VarUseful = \max(\ExprMessy, 0)$. For sufficiently large $n$, $\VarUseful = \ExprMessy$. Using $\sim$ to analyze $\VarUseful$, I receive
 	\begin{align*}
@@
 	\end{align*}
-	By [lemma], $O(\VarUseful) = O(\log_{\VarGrowthFactor} n) = O(\log n)$ as desired.
+	(It is trivial to show that $\left\lceil f(n) \right\rceil \sim f(n)$ if $f$ is unbounded, since $\left\lceil f(n) \right\rceil - f(n)$ is bounded by $1$.)
+
+	By Theorem \ref{thm:SameBigOClass}, $O(\VarUseful) = O(\log_{\VarGrowthFactor} n) = O(\log n)$ as desired.
 \end{proof}
 
-Now when $\FuncWrites(n)$ is approximated with $\sim$, the $\FuncWritesTail(\VarUseful)$ term disappears:
+Now when $\FuncWrites(n)$ is approximated with $\sim$, $\FuncWritesTail(\VarUseful)$ disappears:
 \begin{align*}
@@
 \end{align*}
-The last step is true because of Theorem \ref{thm:RemovesLowerOrderTerms}.
+The last step is justified by Theorem \ref{thm:RemovesLowerOrderTerms}.
 
@@
 
-Unlike dynamic arrays, growth arrays never throw away buffers.
+Unlike dynamic arrays, growth arrays do not throw away buffers.
 This means that if the current capacity is $c$, then the total length of buffers allocated to store items is also $c$.
 Typically, however, $\FuncSpace(n) > c$.
-This is because growth arrays not only store items in buffers, they also store \textbf{references} (or \textbf{pointers}) to the buffers holding the items, in the tail.
-Thus, the space the tail allocates must also be considered.
+This is because the tail of growth arrays (which is a dynamic array) also allocates buffers to store buffer pointers.
+The space the tail allocates must be considered in the formula for $\FuncSpace(n)$.
 
-We established in [lemma] that $\VarNumItemsTail = \VarUseful$.
-Then since $\VarCapacitySeq_\VarUseful$ is the space needed to hold items, and $\FuncSpaceTail(\VarUseful)$ is the space the tail needs to hold references, the formula for $\FuncSpace(n)$ is
+In the previous section, I established that $\VarNumItemsTail = \VarUseful$.
+Since $\VarCapacitySeq_\VarUseful$ is the capacity needed to hold $n$ items, and $\FuncSpaceTail(\VarUseful)$ is the space the tail needs to store $\VarUseful$ pointers, I conclude that the formula for $\FuncSpace(n)$ is
 \begin{align*}
@@
 \end{align*}
-I now wish to approximate this using $\sim$.
-First, note that since $\VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$, it follows from Lemma \ref{lem:ToVarUsefulPowerBounds} that $n \FluteLeq \VarCapacitySeq_\VarUseful \FluteLess \VarGrowthFactor{n}$.
+($\FuncSpaceTail$ denotes the space cost function for dynamic arrays.)
+
+% Bookmark
+% The following following paragraph doesn't work.
+
+Now, I wish to approximate this using $\sim$.
+Since $\VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$, it follows from Lemma \ref{lem:ToVarUsefulPowerBounds} that $n \FluteLeq \VarCapacitySeq_\VarUseful \FluteLess \VarGrowthFactor{n}$.
 Since $n$ and $\VarGrowthFactor{n}$ are both $O(n)$, [the squeeze theorem] implies that $\VarCapacitySeq_\VarUseful = O(n)$.

### 2017-11-13 Draft2/Appending.Compare.tex
Polish the Indexing section

@@
 
-Let $\FuncWritesDynamicArray(n)$ and $\FuncWritesGrowthArray(n)$ be the write costs for dynamic and growth arrays, respectively. I derived earlier that
+In this section, $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ will denote the write cost functions for dynamic and growth arrays, respectively. I derived earlier that
 \begin{align*}
@@
 \end{align*}
-Dividing all sides of this inequality by $n$, I receive
+From Theorem \ref{thm:BothSidesInequality} and Corollary \ref{coro:BothSidesNonStrictInequality}, I may divide all sides of this inequality by $n$ to receive
 \begin{align*}
@@
 \end{align*}
-Since $\FuncWritesGrowthArray(n) \sim n$, $\dfrac {\FuncWritesDynamicArray(n)} n \sim \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$, thus
+It was shown earlier that $\FuncWritesGrowthArray(n) \sim n$.
+From Theorem \ref{thm:MergesOverOps}, $\dfrac {\FuncWritesDynamicArray(n)} n \sim \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$.
+From Theorem \ref{thm:InterchangeableInInequality} and Corollary \ref{coro:InterchangeableInNonStrictInequality}, it follows that
 \begin{align*}
@@
 \end{align*}
-
 \HdrSpaceComplexCmp
 
-Let $\FuncSpaceDynamicArray(n)$ and $\FuncSpaceGrowthArray(n)$ be the space costs for dynamic and growth arrays, respectively. Recall that
+Let $\FuncSpaceDynamicArray(n)$ and $\FuncSpaceGrowthArray(n)$ be the space cost functions for dynamic and growth arrays, respectively. Recall that
 \begin{align*}
@@
 \end{align*}
-and $\FuncSpaceGrowthArray(n) \sim \VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$. Taking the ratio of $\FuncSpaceDynamicArray(n)$ to $\FuncSpaceGrowthArray(n)$, I receive
+and that $\FuncSpaceGrowthArray(n) \sim \VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$.
+Taking the ratio of $\FuncSpaceDynamicArray(n)$ to $\FuncSpaceGrowthArray(n)$, I receive
 \begin{align*}
-\frac{\FuncSpaceDynamicArray(n)}{\FuncSpaceGrowthArray(n)} &\sim \left( \frac{1}{\VarGrowthFactor^\VarUseful} \right) \left( \frac{\VarGrowthFactor^{\VarUseful + 1} - 1}{\VarGrowthFactor - 1} \right)\\
+\frac{\FuncSpaceDynamicArray(n)}{\FuncSpaceGrowthArray(n)} &\sim \frac{1}{\VarGrowthFactor^\VarUseful\VarInitCapacity} \cdot \left( \frac{\VarGrowthFactor^{\VarUseful + 1} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity &&\text{(Theorem \ref{thm:MergesOverOps})}\\
 &= \frac{\VarGrowthFactor - 1 / {\VarGrowthFactor^\VarUseful}}{\VarGrowthFactor - 1}\\
-&\sim \frac{\VarGrowthFactor}{\VarGrowthFactor - 1}
+&\sim \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} &&\text{(Theorem \ref{thm:RemovesLowerOrderTerms})}
 \end{align*}
-The last step comes from the fact that $\VarUseful = \max(\ExprMessy, 0) \to \infty$ as $n \to \infty$.

### 2017-11-13 Draft2/Indexing.Dynamic.tex
Algos: Variables for param names
Algos: Add spaces between commas
Polish the Indexing section

@@
 
-The following algorithm implements $\FuncGetItem$ for dynamic arrays. A $\FuncSetItem$ function can be implemented in a similar fashion.
+The following algorithm implements $\FuncGetItem$ for dynamic arrays. (A $\FuncSetItem$ function can be implemented in a similar fashion.)
 
-{\HdrNote} I assume all arguments passed to my algorithms are valid. Thus, I do not include argument validation nor error handling in my pseudocode.
+{\HdrNote} My algorithms do not validate any arguments; all arguments passed to them are assumed to be valid.
 
@@
 	\begin{algorithmic}[1]
-		\Function{$\FuncGetItem$}{$\VarList, index$}
-			\State \Return $\VarList.\FieldBuffer[index]$
+		\Function{$\FuncGetItem$}{$\VarList,\ \ParamIndex$}
+			\State \Return $\VarList.\FieldBuffer[\ParamIndex]$
 		\EndFunction
@@
 
-Clearly, this function runs in constant time. It also has the benefit of using very few instructions: on architectures like x86, indexing the buffer may take as little as one instruction.
+This algorithm runs in $O(1)$ time. It also has the benefit of using very few instructions, which is a benefit that will not be shared with growth arrays.

### 2017-11-13 Draft2/Indexing.Growth.tex
Polish the Indexing section

@@
 Indexing a growth array is slower and more complex than indexing a dynamic array.
-However, this does not mean that accessing data of a growth array has to be slower than accessing that of a dynamic array.
-Refer to Sections [Iterating] and [Copying to an array] to learn how to quickly access growth arrays' data.
+However, this does not mean that accessing data of a growth array is necessarily slower than accessing that of a dynamic array.
+Refer to Sections \ref{sec:Iterating} and \ref{sec:CopyArray} for methods to quickly access growth arrays' data.
 
@@
 I know that this algorithm runs in $O(\log n)$ time since it was shown earlier that the size of the tail, $\VarNumItemsTail$, equals $\VarUseful$, and (from Lemma \ref{lem:VarUsefulIsOLogN}) that $\VarUseful = O(\log n)$.
-Aside from iteration over the tail, all statements run in constant time.
+Aside from iteration over the tail, all statements run in constant time, so the time complexity is precisely $O(\log n)$.
 
@@
 I wish to assign the head a buffer index as well, so that each buffer has a unique ID.
-Since the head succeeds the tail's last buffer, which has $\VarIndexBuffer = \VarNumItemsTail - 1$, I will let the head's $\VarIndexBuffer$ be $\VarNumItemsTail$.
+Since the head follows the tail's last buffer, which has $\VarIndexBuffer = \VarNumItemsTail - 1$, I will let the head's $\VarIndexBuffer$ be $\VarNumItemsTail$.
 
@@
 
-% Todo: Make parameter names for other parts consistent.
 \begin{algorithm}
@@
 
-% Todo: \VarLogicalIndex for i? Introduce "logical index" term above?
-The task is now to find formulae for $\VarIndexBuffer$ and $\VarIndexElement$ in terms of $i$, in order to implement $\FuncDecompose$.
+Now, the task is to find formulae for $\VarIndexBuffer$ and $\VarIndexElement$ in terms of $i$, in order to implement $\FuncDecompose$.
 
@@
 	\end{align*}
-	(By convention, $\VarGrowSeq_{-1} = 0$.)
+	(When $\VarIndexBuffer = 0$, $\VarGrowSeq_{-1} = 0$ by convention.)
 \end{lemma}
@@
 % Todo: "As shown earlier"
-% Todo: Again, by convention \VarGrowSeq_{-1} = 0. Modify the algorithm accordingly.
 \begin{proof}
-	Appending new items does not change the index of an item that is already in the list. Thus, this problem can be reduced to finding the last element when $n = i + 1$.
+	Appending new items does not change the index of an item that is already in the list. Thus, finding the element at index $i$ is equivalent to finding the last element when $n = i + 1$.
 
@@
 
-	To find $\VarIndexElement$, consider the identity:
+	To determine $\VarIndexElement$, consider the identity:
 	\begin{align*}
@@
 	First, I will determine the number of items in the tail.
-In the case where $\VarIndexBuffer = 0$, then because $\VarNumItemsTail = \VarIndexBuffer$, the tail contains $0$ buffers and thus $0 = \VarGrowSeq_{-1}$ items.
+In the case where $\VarIndexBuffer = 0$, then because $\VarNumItemsTail = \VarIndexBuffer$, the tail contains $0$ buffers and thus $0$ items (which equals $\VarGrowSeq_{-1}$).
 If $\VarIndexBuffer > 0$, the number of items in the tail is the last size at which $\FuncGrow$ was called, or the last term of $\VarGrowSeq$.
-This quantity is $\VarGrowSeq_{\VarUseful - 1} = \VarGrowSeq_{\VarIndexBuffer - 1}$.
+This quantity is $\VarGrowSeq_{\VarUseful - 1}$, or $\VarGrowSeq_{\VarIndexBuffer - 1}$.
 
 	The desired item is the growth array's last element, which implies it is also the head's last element.
-Thus $\VarIndexElement$ is the head's last valid index, so the head size is $\VarIndexElement + 1$.
+Thus $\VarIndexElement$ is the head's last valid index, so the head's size is $\VarIndexElement + 1$.
 Finally, from the premise, $n = i + 1$.
@@
 	\begin{align*}
-	i + 1 &= \VarGrowSeq_{\VarIndexBuffer - 1} + \VarIndexElement + 1\\
+	i + 1 &= \VarGrowSeq_{\VarIndexBuffer - 1} + (\VarIndexElement + 1)\\
 	\VarIndexElement &= i - \VarGrowSeq_{\VarIndexBuffer - 1}
@@
 
-% Todo: Continue to consider usage of mathematical vs. algorithm vars.
-% Todo: Can ceiling of \log_2 be implemented fast? Also, what if \VarInitCapacity is not a power of 2?
 \begin{algorithm}
@@
 
+% Todo: CITE!
 Clearly, $\FuncDecompose$ runs in constant time.
-Despite that, it still appears to be quite expensive: normally, logarithms and exponentiation require use of costly floating-point instructions.
+Despite that, it appears to be quite expensive: normally, logarithms and exponentiation require use of floating-point instructions, which are slower than integer-based instructions.
 However, in the special case where $\VarGrowthFactor = 2$ and $\VarInitCapacity = 2^\VarLogInitCapacity$ for some constant whole number $\VarLogInitCapacity$, I claim that $\VarIndexBuffer$ and $\VarIndexElement$ can be computed without use of floating-point instructions.
@@
 To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$.
-There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss in this paper due to length concerns.
-(An implementation of the algorithm may be found in [Implementations section].) Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.
+There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper.
+(An implementation of the algorithm, however, may be found in the links at Section \ref{sec:Implementations}.) Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.
 

### 2017-11-13 Draft2/Abstract.tex
[WIP] Feedback

@@
 This paper introduces \textbf{growth arrays}, array-like data structures that are designed for appending elements.
-When the number of items is not known beforehand but is expected to be large, they are more efficient than dynamic arrays by a constant factor.
-Growth arrays support all operations dynamic arrays do, such as random access, iteration, and insertion or deletion at an index.
-However, they perform no better, or slightly worse, than dynamic arrays for operations other than appending.
+When the number of items is not known beforehand but is expected to be large, growth arrays are more efficient than dynamic arrays by a constant factor.
+They support all operations dynamic arrays do, such as random access, iteration, and insertion or deletion at an index.
+For operations other than appending, however, they perform the same as or slightly worse than dynamic arrays.

### 2017-11-13 Draft2/Appending.Dynamic.tex
Make algorithms not float
[WIP] Feedback

@@
 
-\begin{algorithm}
+\begin{algorithm}[H]
 	\begin{algorithmic}[1]
@@
 
-% Todo: CITE
 It is well-known that appending one item to a dynamic array takes amortized $O(1)$ time.
@@
 \begin{proof}
-	% Todo: Better language here? 'exists' is confusing
 	If $\VarCapacitySeq_i$ exists and $i \geq 1$, then clearly $\FuncGrow$ must have been called when the size was $\VarCapacitySeq_{i - 1}$, so $\VarCapacitySeq_{i - 1} \in \VarGrowSeq$.

### 2017-11-13 Draft2/Intro.tex
Work
[WIP] Feedback

@@
 The new buffer they allocate represents a continuation of the items from the old buffer.
-For example, if the old buffer contained items $0 - 9$, the new buffer would contain items $10$ and beyond.
+For example, if the old buffer contained items $0 -- 9$, the new buffer would contain items $10$ and beyond.
 Because of this technique, growth arrays allocate less memory to store the same number of items, and do not need to copy the contents of old buffers.
@@
 Growth arrays have caveats, however.
-For operations other than appending, they perform no better, or slightly worse, than dynamic arrays.
+Operations other than appending take the same time or longer than for dynamic arrays.
 In particular, random access is very costly for growth arrays.
@@
 
-It is worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are redundant.
+It is worth mentioning that if the size of the data is known in advance, both dynamic and growth arrays are unnecessary.
 One could simply allocate a raw array with the known size, and append items to it just as quickly.

### 2017-11-13 Draft2/Appending.Growth.tex
Make algorithms not float
Rename var

@@
 
-Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumItemsTail$ be the size of the tail.
+Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumPointersTail$ be the size of the tail.
 Since Corollary \ref{coro:GrowthSeq} also holds true for growth arrays, $\FuncGrow$ is called $|\VarGrowSeq|$ times.
@@
 \begin{align*}
-\VarNumItemsTail &= |\VarGrowSeq| = |\VarCapacitySeq| - 1 = \VarUseful
+\VarNumPointersTail &= |\VarGrowSeq| = |\VarCapacitySeq| - 1 = \VarUseful
 \end{align*}
@@
 
-In the previous section, I established that $\VarNumItemsTail = \VarUseful$.
+In the previous section, I established that $\VarNumPointersTail = \VarUseful$.
 Since $\VarCapacitySeq_\VarUseful$ is the capacity needed to hold $n$ items, and $\FuncSpaceTail(\VarUseful)$ is the space the tail needs to store $\VarUseful$ pointers, I conclude that the formula for $\FuncSpace(n)$ is

### 2017-11-13 Draft2/Indexing.Growth.tex
Make algorithms not float
[WIP] Feedback
Rename var

@@
 
-\begin{algorithm}
+\begin{algorithm}[H]
 	\begin{algorithmic}
@@
 
-I know that this algorithm runs in $O(\log n)$ time since it was shown earlier that the size of the tail, $\VarNumItemsTail$, equals $\VarUseful$, and (from Lemma \ref{lem:VarUsefulIsOLogN}) that $\VarUseful = O(\log n)$.
+I know that this algorithm runs in $O(\log n)$ time since it was shown earlier that the size of the tail, $\VarNumPointersTail$, equals $\VarUseful$, and (from Lemma \ref{lem:VarUsefulIsOLogN}) that $\VarUseful = O(\log n)$.
 Aside from iteration over the tail, all statements run in constant time, so the time complexity is precisely $O(\log n)$.
@@
 I wish to assign the head a buffer index as well, so that each buffer has a unique ID.
-Since the head follows the tail's last buffer, which has $\VarIndexBuffer = \VarNumItemsTail - 1$, I will let the head's $\VarIndexBuffer$ be $\VarNumItemsTail$.
+Since the head follows the tail's last buffer, which has $\VarIndexBuffer = \VarNumPointersTail - 1$, I will let the head's $\VarIndexBuffer$ be $\VarNumPointersTail$.
 
 I define a helper function, $\FuncGetBuffer$, that gets the buffer associated with a given $\VarIndexBuffer$.
-$\VarIndexBuffer$ is assumed to be valid; that is, $0 \leq \VarIndexBuffer \leq \VarNumItemsTail$.
+$\VarIndexBuffer$ is assumed to be valid; that is, $0 \leq \VarIndexBuffer \leq \VarNumPointersTail$.
 
-\begin{algorithm}
+\begin{algorithm}[H]
 	\begin{algorithmic}
@@
 
-	The last element always resides in the head, so $\VarIndexBuffer = \VarNumItemsTail|_{n = i + 1}$. As shown earlier, $\VarNumItemsTail = \VarUseful$, so $\VarIndexBuffer = \VarUseful|_{n = i + 1}$.
+	The last element always resides in the head, so $\VarIndexBuffer = \VarNumPointersTail|_{n = i + 1}$.
+As shown earlier, $\VarNumPointersTail = \VarUseful$, so $\VarIndexBuffer = \VarUseful|_{n = i + 1}$.
 
@@
 	First, I will determine the number of items in the tail.
-In the case where $\VarIndexBuffer = 0$, then because $\VarNumItemsTail = \VarIndexBuffer$, the tail contains $0$ buffers and thus $0$ items (which equals $\VarGrowSeq_{-1}$).
+In the case where $\VarIndexBuffer = 0$, then because $\VarNumPointersTail = \VarIndexBuffer$, the tail contains $0$ buffers and thus $0$ items (which equals $\VarGrowSeq_{-1}$).
 If $\VarIndexBuffer > 0$, the number of items in the tail is the last size at which $\FuncGrow$ was called, or the last term of $\VarGrowSeq$.
@@
 
-% Todo: CITE!
 Clearly, $\FuncDecompose$ runs in constant time.

### 2017-11-13 Draft2/ExternalDefinitions.tex
Make algorithms not float
Exterminate more todos

@@
 \begin{description}
-	\item[initial capacity] Denoted by $\VarInitCapacity$. The capacity of an empty dynamic array.\\
-	{\HdrAssumptions} $\VarInitCapacity$ is a natural number
-	\item[growth factor] Denoted by $\VarGrowthFactor$. The constant ratio of the new capacity to the old one when $\VarList$ grows.\\
-	% Todo
-	{\HdrAssumptions} $\VarGrowthFactor\VarInitCapacity \geq \VarInitCapacity + 1$
+	\item[initial capacity] Denoted by $\VarInitCapacity$; the capacity of an empty dynamic array. $\VarInitCapacity$ must be a natural number.
+	\item[growth factor] Denoted by $\VarGrowthFactor$; the constant ratio of the new capacity to the old one when $\VarList$ grows. $\VarGrowthFactor$ must be greater than $1$.
 \end{description}

### 2017-11-14 Draft2/CopyArray.Blurb.tex
Exterminate more todos
Work

@@
-% Todo: Is 'n memory' vague?
-After they are done appending to them, users often want to take dynamic arrays and convert them into raw arrays.
-There are multiple possible reasons for this: 1) Raw arrays hold on to exactly $n$ memory to store $n$ elements.
-However, dynamic and growth arrays typically use $> n$ memory so they need not grow every time $\FuncAppend$ is called.
-2) A function in third-party code might only accept a raw array as an argument.
+Users often want to convert dynamic arrays to raw arrays.
+There are multiple reasons for this: 1) Raw arrays hold on to exactly $n$ memory to store $n$ elements.
+However, dynamic and growth arrays typically use more than $n$ memory, so they need not grow every time an item is appended.
+2) Sometimes, functions in third-party code only accept raw arrays.
 
-The case is even more compelling for growth arrays: 3) Since they are not entirely contiguous, they have worse data locality (even if the number of discontinuities is $O(\log n)$).
+For growth arrays, the case is even more compelling: 3) Since they are not contiguous as a whole, they have worse data locality (even if the number of discontinuities is $O(\log n)$).
 4) Raw arrays can be indexed much faster than growth arrays.
+
+In this section, I will show that growth arrays can be converted to raw arrays not much slower than dynamic arrays.

### 2017-11-14 Draft2/CopyArray.Growth.tex
Make algorithms not float
Work

@@
 
-The growth array implementation must call $\FuncArrayCopy$ multiple times, since not all elements are contiguous.
+The growth array algorithm is slightly slower than the dynamic array one.
+It needs to loop over the tail and call $\FuncArrayCopy$ multiple times, since not all elements are contiguous.
+However, $n$ elements are still copied in total, so the time complexity is still $O(n)$.
 
-\begin{algorithm}
+\begin{algorithm}[H]
 	\begin{algorithmic}

### 2017-11-14 Draft2/Indexing.Dynamic.tex
Make algorithms not float
Add pictures, [WIP] title all the algos
Work

@@
 
-{\HdrNote} My algorithms do not validate any arguments; all arguments passed to them are assumed to be valid.
+{\HdrNote} My algorithms assume all arguments passed to them are valid. Thus, arguments are never checked.
 
-\begin{algorithm}
+{\HdrNote} Although the function is called $\FuncGetItem$, the syntax other algorithms use to call it is $\VarList[\ParamIndex]$.
+
+\begin{algorithm}[H]
+	\caption{Random access \TextDynamicArray}
 	\begin{algorithmic}[1]

### 2017-11-14 Draft2/Iterating.Dynamic.tex
Make algorithms not float
Work

@@
 
-The algorithm for iterating dynamic arrays is simple.
-It loops through all valid indices, and calls the $\FuncGetItem$ method (which is denoted $\VarList[i]$ instead of $\VarList.\FuncGetItem(i)$) for each index.
+The algorithm for iterating dynamic arrays is simple and familiar.
 
-\begin{algorithm}
+\begin{algorithm}[H]
+	\caption{``$\TextFor \LclItem \TextIn \VarList$'' algorithm \TextDynamicArray}
 	\begin{algorithmic}
-		\LineComment{Algorithm for ``$\TextFor \LclItem \TextIn \VarList$'', where $\VarList$ is a dynamic array}
 		\For{$\LclIndex = 0,\ \LclIndex < \VarList.\FieldSize,\ \LclIndex \gets \LclIndex + 1$}
 			\State $\LclItem \gets \VarList[\LclIndex]$
-			\State $\ParamAction(\LclItem)$
+			\State $\TextDoSomethingWith \LclItem$
 		\EndFor

### 2017-11-14 Draft2/Iterating.Growth.tex
Make algorithms not float
Work

@@
 
-The algorithm for growth arrays is not as simple, however, if the user wants optimal performance.
-As shown in the previous section, the algorithm for indexing growth arrays is very costly compared to its dynamic array counterpart.
-Thus, I wish to avoid using it in my iteration algorithm.
+The iteration algorithm for growth arrays is not quite as simple.
+As shown in the previous section, growth arrays' random access algorithm is expensive; thus, it is best avoided.
+The following algorithm implements iteration without using the random access algorithm.
 
-Fortunately, it turns out that it is possible to avoid its use:
-
-\begin{algorithm}
+\begin{algorithm}[H]
+	\caption{``$\TextFor \LclItem \TextIn \VarList$'' algorithm \TextGrowthArray}
 	\begin{algorithmic}
-		\LineComment{Algorithm for ``$\TextFor \LclItem \TextIn \VarList$'', where $\VarList$ is a growth array}
 		\For{$\LclBuffer \TextIn \VarList.\FieldTail$}
 			\For{$\LclItem \TextIn \LclBuffer$}
-				\State $\ParamAction(\LclItem)$
+				\State $\TextDoSomethingWith \LclItem$
 			\EndFor
@@
 			\State $\LclItem \gets \VarList.\FieldHead[\LclIndex]$
-		\State $\ParamAction(\LclItem)$
+			\State $\TextDoSomethingWith \LclItem$
 		\EndFor

### 2017-11-14 Draft2/OtherOperations.Blurb.tex
Other Operations

Growth arrays support other dynamic array operations, such as insertion/deletion at an index, binary search, sorting, etc. I will not give algorithms for these operations in this paper, since they are not as common as the four detailed above. However, I will briefly describe how insertion and deletion can be implemented.

Suppose the user wants to insert an item at index $i$. If $i = n$, then simply append the item. Otherwise ($0 \leq i < n$), capture $\VarList[n - 1]$ in a local variable. Shift all elements with index $\geq i$ forward by one, so that their index increases by one. Append the original value of $\VarList[n - 1]$. Finally, set index $i$ to the provided item.

Suppose the user wants to delete the item at index $i$. Shift all elements with index $> i$ backwards by one, so that their index decreases by one. Decrement $\VarList.\FieldSize$ and $\VarList.\FieldHeadSize$. If this causes $\VarList.\FieldHeadSize$ to become $0$ and $\VarNumPointersTail > 0$, then discard the head and replace it with the last buffer pointed to by the tail. Remove this buffer from the tail.

### 2017-11-15 Draft2/Appendix.tex
Exterminate more todos
Work

@@
-% Todo: Name 'Appendix', not 'Appendices'
 \appendix
@@
 \begin{proof}[Proof (Theorem \ref{thm:RemovesLowerOrderTerms})]
-	Let $h = O(g)$.
-By definition, $h \leq cg$ for sufficiently large $n$, where $c$ is a positive constant.
-Dividing both sides by $f$ and taking the limit, $\ExprNToInfty \dfrac{h}{f} \leq \ExprNToInfty c \left( \dfrac{g}{f} \right)$.
-Since $\ExprNToInfty \dfrac{g}{f}$ exists and equals $0$, the right-hand side equals $c \cdot 0 = 0$.
-However, $\ExprNToInfty \dfrac{h}{f} \geq 0$ since both $h$ and $f$ are positive.
-By the squeeze theorem, $\ExprNToInfty \dfrac{h}{f} = 0$.
-
-	Since $\ExprNToInfty \dfrac{f}{f}$ and $\ExprNToInfty \dfrac{h}{f}$ both exist,
+	Let $g = o(f)$. By definition, $\ExprNToInfty \dfrac{g}{f} = 0$. Since $\ExprNToInfty \dfrac{f}{f}$ and $\ExprNToInfty \dfrac{g}{f}$ both exist,
 	\begin{align*}
-	\ExprNToInfty \dfrac{f + h}{f} = \ExprNToInfty \dfrac{f}{f} + \ExprNToInfty \dfrac{h}{f} = 1 + 0 = 1
+	\ExprNToInfty \dfrac{f + g}{f} = \ExprNToInfty \dfrac{f}{f} + \ExprNToInfty \dfrac{g}{f} = 1 + 0 = 1
 	\end{align*}
-	It follows that $f + h = f + O(g) \sim f$.
+	It follows that $f + g = f + o(f) \sim f$.
 \end{proof}
@@
 \begin{proof}[Proof (Corollary \ref{coro:PlusConstant})]
-	If $f$ is unbounded, $\ExprNToInfty \dfrac{c}{f} = 0$. Applying Theorem \ref{thm:RemovesLowerOrderTerms}, $f + c \sim f$.
+	If $f$ is unbounded, then $c = o(f)$. Applying Theorem \ref{thm:RemovesLowerOrderTerms}, $f + c \sim f$.
 \end{proof}
 
-\subsection{$\sim$ Merges over $+$, $\times$, and $\div$}
+\subsection{$\sim$ Respects $+$, $\times$, and $\div$}
 
@@
 \begin{proof}[Proof (Corollary \ref{coro:BothSides})]
-	Since $\sim$ is reflexive, $g \sim g$. Taking $\Tweak{g} = g$ for Theorem \ref{thm:MergesOverOps}, the corollary statement follows.
+	This immediately follows from Theorem \ref{thm:MergesOverOps} by taking $\Tweak{g} = g$.
 \end{proof}
@@
 \begin{proof}[Proof (Theorem \ref{thm:SameBigOClass})]
-	This will be a proof by contradiction.
-Assume $f = O(\Tweak{f})$ where $O(\Tweak{f}) \neq O(\Tweak{g})$.
-Then $\dfrac {O(\Tweak{f})} {O(\Tweak{g})} \neq 1$.
-However, $\ExprNToInfty \dfrac{f}{g} = \dfrac {O(\Tweak{f})} {O(\Tweak{g})}$, so $\ExprNToInfty \dfrac{f}{g} \neq 1$.
-It follows that $f \not\sim g$, which contradicts the given.
-Thus, it must be true that $f = O(\Tweak{g})$.
+	Let $r = \dfrac{f}{g}$.
+Since $\ExprNToInfty r = 1$, $r \leq 2$ for sufficiently large $n$.
+By definition, $\exists c : g \leq c h$ for sufficiently large $n$, where $c$ is a positive constant.
+Then, $f = rg \leq rc h \leq 2c h$ for sufficiently large $n$.
+Thus, $f = O(h)$.
 \end{proof}
 
-\subsection{Asymptotic Functions may be Interchanged in $\FluteLess$ Inequalities}
+\subsection{Asymptotic Functions may be Interchanged in $\FluteLess$ and $\FluteLeq$ Inequalities}
 
@@
 	Thus, $\Tweak{g} \FluteLess g$.
+
+	From these results and the transitivity of $\sim$, it can trivially be shown that the same statements are true when $\FluteLess$ is replaced with $\FluteLeq$.
 \end{proof}
 
-\subsubsection{Asymptotic Functions may be Interchanged in $\FluteLeq$ Inequalities}
-
-\begin{proof}[Proof (Corollary \ref{coro:InterchangeableInNonStrictInequality})]
-	Suppose $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLeq \TweakSecond{f}$.
-By definition, $\Tweak{f} \FluteLess \TweakSecond{f}$ or $\Tweak{f} \sim \TweakSecond{f}$.
-In the first case, from Theorem \ref{thm:InterchangeableInInequality}, $f \FluteLess \TweakSecond{f}$.
-In the second case, since $\sim$ is transitive, $f \sim \TweakSecond{f}$.
-In both cases, it is true that $f \FluteLeq \TweakSecond{f}$.
-
-	The second statement is proved similarly.
-It is given that $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLeq \TweakSecond{g}$; the latter implies that either $\Tweak{g} \FluteLess \TweakSecond{g}$ or $\Tweak{g} \sim \TweakSecond{g}$.
-In the first case, $\Tweak{g} \FluteLess g$; in the second, $\Tweak{g} \sim g$.
-In both cases, $\Tweak{g} \FluteLeq g$.
-\end{proof}
-
-\subsection{$\FluteLess$ Inequalities can be Algebraically Manipulated}
+\subsection{$\FluteLess$ and $\FluteLeq$ Inequalities can be Algebraically Manipulated}
 
@@
 For any function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.
+
+	From these results and Corollary \ref{coro:BothSides}, it can trivially be shown that the same statement is true when $\FluteLess$ is replaced with $\FluteLeq$.
 \end{proof}
 
-\subsubsection{$\FluteLeq$ Inequalities can be Algebraically Manipulated}
-
-\begin{proof}[Proof (Corollary \ref{coro:BothSidesNonStrictInequality})]
-	If I suppose $f \FluteLeq g$, then $f \FluteLess g$ or $f \sim g$.
-The first case implies $fh \FluteLess gh$ from Theorem \ref{thm:BothSidesInequality}, and the second implies $fh \sim gh$ from Corollary \ref{coro:BothSides}.
-In either case, $fh \FluteLeq gh$.
-Using the same logic, it is true that $\dfrac{f}{h} \FluteLeq \dfrac{g}{h}$.
-\end{proof}
-
-\subsection{Same-Order Terms may be Added to Both Sides of $\FluteLess$ Inequalities}
+\subsection{Same-Order Terms may be Added to Both Sides of $\FluteLess$ and $\FluteLeq$ Inequalities}
 
@@
 	\end{align*}
-	Since at least one limit is less than $1$, and no limit exceeds $1$, the product $\dfrac{c_1}{c_2}$ is less than one. Now, consider that
+	Since at least one limit is less than $1$ and no limit exceeds $1$, the product, $\dfrac{c_1}{c_2}$, is less than $1$. Now, consider that
 	\begin{align*}
@@
 	Since $c_1 < c_2$, $c_1 + 1 < c_2 + 1$ so $\dfrac{c_1 + 1}{c_2 + 1} < 1$. Thus, $f + h \FluteLess g + h$.
+
+	From these results and Corollary \ref{coro:BothSides}, it can trivially be shown that the same statement is true when $\FluteLess$ is replaced with $\FluteLeq$.
 \end{proof}
-
-\subsubsection{Same-Order Terms may be Added to Both Sides of $\FluteLeq$ Inequalities}
-
-\begin{proof}[Proof (Corollary \ref{coro:BothSidesNonStrictInequalityAdd})]
-	Given $f \FluteLeq g$, it is true that either $f \FluteLess g$ or $f \sim g$.
-In the first case, from Theorem \ref{thm:BothSidesInequalityAdd} it follows that $f + h \FluteLess g + h$.
-In the second case, from Theorem \ref{coro:BothSides} it follows that $f + h \sim g + h$.
-In both cases, $f + h \FluteLeq g + h$.
-\end{proof}

### 2017-11-15 Draft2/AsymptoticNotation.tex
Maybe put this to rest at last
Work

@@
 
-Notice that while $O(2n) = O(n)$, $2n \not\sim n$.
+Notice that while $2n = O(n)$, $2n \not\sim n$.
 Thus, $\sim$ makes it possible to distinguish between a function that uses $n$ space and one that uses $2n$ space.
@@
 
-I will also introduce two cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. They are defined as follows:
+I will also introduce two cousins of $\sim$, the relations $\FluteLess$ and $\FluteLeq$.
+The former is normally defined as $f \prec g \Biconditional \ExprNToInfty \dfrac{f}{g} = 0$.
+However, for the purpose of this paper their definitions will be:
 \begin{align*}
@@
 
+I will also use little-o notation in this paper, which is defined as follows:
+\begin{align*}
+f = o(g) \Biconditional \ExprNToInfty \frac{f}{g} = 0
+\end{align*}
 \subsection{Properties}
@@
 
-In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
+{\HdrNote} In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
 
@@
 \label{thm:RemovesLowerOrderTerms}
-	If $\ExprNToInfty \dfrac{g}{f} = 0$, then $f + O(g) \sim f$.
+	$f + o(f) \sim f$.
 \end{theorem}
@@
 
-The following theorem states that $\sim$ can ``merge,'' or un-distribute, over addition, multiplication, and division. This is also a property shared with big-O.
+The following theorem states that $\sim$ respects addition, multiplication, and division. This is also a property shared with big-O.
 
@@
 \label{coro:BothSides}
-	A $\sim$ equation holds if both sides are added, multiplied, or divided by the same quantity.
+	A $\sim$ relation is preserved when both sides are added, multiplied, or divided by the same positive quantity.
 \end{corollary}
@@
 \label{thm:SameBigOClass}
-	If $f \sim g$ and $g = O(\Tweak{g})$, then $f = O(\Tweak{g})$.
+	If $f \sim g$ and $g = O(h)$, then $f = O(h)$.
 \end{theorem}
@@
 	If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLess \TweakSecond{f}$, then $f \FluteLess \TweakSecond{f}$.
-If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLess \TweakSecond{g}$, then $\Tweak{g} \FluteLess g$.
+If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLess \TweakSecond{g}$, then $\Tweak{g} \FluteLess g$.\\
+	These statements also hold for $\FluteLeq$.
 \end{theorem}
-
-\begin{corollary}
-\label{coro:InterchangeableInNonStrictInequality}
-	This theorem also holds for $\FluteLeq$.
-\end{corollary}
 
@@
 \label{thm:BothSidesInequality}
-	A $\FluteLess$ inequality holds if both sides are multiplied or divided by the same quantity.
+	A $\FluteLess$ inequality is preserved when both sides are multiplied or divided by the same positive quantity.\\
+	This statement also holds for $\FluteLeq$.
 \end{theorem}
-
-\begin{corollary}
-\label{coro:BothSidesNonStrictInequality}
-	This theorem also holds for $\FluteLeq$.
-\end{corollary}
 
@@
 \label{thm:BothSidesInequalityAdd}
-	Suppose $f \FluteLess g$. If $f \sim c_1 h$ and $g \sim c_2 h$ for some $c_1, c_2 > 0$, then $f + h \FluteLess g + h$.
+	Suppose $f \FluteLess g$. If $\ExprNToInfty \dfrac{f}{h} > 0$ and $g = O(h)$, then $f + h \FluteLess g + h$.\\
+	This statement also holds for $\FluteLeq$.
 \end{theorem}
-
-\begin{corollary}
-\label{coro:BothSidesNonStrictInequalityAdd}
-	This theorem also holds for $\FluteLeq$.
-\end{corollary}

### 2017-11-15 Draft2/Appendix.tex
Rework A.7

@@
 By definition, $\ExprNToInfty \dfrac{f}{g} < 1$.
-For any function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.
+For any positive function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.
 
@@
 \begin{proof}[Proof (Theorem \ref{thm:BothSidesInequalityAdd})]
-	If $\dfrac{f}{h}$ does not approach $0$ as $n \to \infty$, then it is bounded below by some positive constant $c_1$, and $\ExprNToInfty \dfrac{c_1 h}{f} \leq 1$.
-From $f \FluteLess g$, it follows that $\ExprNToInfty \dfrac{f}{g} < 1$.
-Since $g = O(h)$, $\exists c_2 : \ExprNToInfty \dfrac{g}{c_2 h} \leq 1$.
-Multiplying these limits, I receive
-	\begin{align*}
-	\left( \ExprNToInfty \frac{c_1 h}{f} \right) \left( \ExprNToInfty \dfrac{f}{g} \right) \left( \ExprNToInfty \dfrac{g}{c_2 h} \right) = \ExprNToInfty \frac{c_1 h}{c_2 h} = \frac{c_1}{c_2}
-	\end{align*}
-	Since at least one limit is less than $1$ and no limit exceeds $1$, the product, $\dfrac{c_1}{c_2}$, is less than $1$. Now, consider that
+	Assume that $n$ is arbitrarily large.
+Since $\dfrac{f}{h}$ has a positive limit, it is bounded below by some positive constant $c_1$.
+Rearranging, $c_1 h \leq f$.
+From $f \FluteLess g$, it follows that $f < g$ for sufficiently large $n$.
+Since $g = O(h)$, $\exists c_2 : g \leq c_2 h$.
+Combining these inequalities, I receive $c_1 h \leq f < g \leq c_2 h$.
+From this, it is clear that $c_1 < c_2$.
+
+	Now, consider that
 	\begin{align*}

### 2017-11-15 Draft2/AsymptoticNotation.tex
Duplicate note

@@
 
-{\HdrNote} In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
+{\HdrNote} In the following theorems, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
 

### 2017-11-15 Draft2/Appendix.tex
Duplicate note
Restate the theorems

@@
 
+{\HdrNote} In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
+
 \subsection{$\sim$ is an Equivalence Relation}
 
-\begin{proof}[Proof (Theorem \ref{thm:EquivalenceRelation})]
+\begin{reptheorem}{thm:EquivalenceRelation}
+	$\sim$ is reflexive, transitive, and symmetric.
+\end{reptheorem}
+
+\begin{proof}
 	Clearly, $\ExprNToInfty \dfrac{f}{f} = 1$, so $f \sim f$. Thus, $\sim$ is reflexive.
@@
 
-\begin{proof}[Proof (Theorem \ref{thm:RemovesLowerOrderTerms})]
+\begin{reptheorem}{thm:RemovesLowerOrderTerms}
+	$f + o(f) \sim f$.
+\end{reptheorem}
+
+\begin{proof}
 	Let $g = o(f)$. By definition, $\ExprNToInfty \dfrac{g}{f} = 0$. Since $\ExprNToInfty \dfrac{f}{f}$ and $\ExprNToInfty \dfrac{g}{f}$ both exist,
@@
 
-\begin{proof}[Proof (Corollary \ref{coro:PlusConstant})]
+\begin{repcorollary}{coro:PlusConstant}
+	If $f$ is unbounded, then $f + c \sim f$ for any constant $c$.
+\end{repcorollary}
+
+\begin{proof}
 	If $f$ is unbounded, then $c = o(f)$. Applying Theorem \ref{thm:RemovesLowerOrderTerms}, $f + c \sim f$.
@@
 
-\begin{proof}[Proof (Theorem \ref{thm:MergesOverOps})]
+\begin{reptheorem}{thm:MergesOverOps}
+	If $f \sim \Tweak{f}$ and $g \sim \Tweak{g}$, then
+	\begin{align*}
+	f + g &\sim \Tweak{f} + \Tweak{g}\\
+	fg &\sim \Tweak{f}\Tweak{g}\\
+	\frac{f}{g} &\sim \frac {\Tweak{f}} {\Tweak{g}}
+	\end{align*}
+\end{reptheorem}
+
+\begin{proof}
 	Let $\FuncQuotient = \dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, and let $\FuncDenom = \Tweak{g} + \Tweak{g}^2 / \Tweak{f}$. $\FuncQuotient$ may be expressed as
@@
 
-\begin{proof}[Proof (Corollary \ref{coro:BothSides})]
+\begin{repcorollary}{coro:BothSides}
+	A $\sim$ relation is preserved when both sides are added, multiplied, or divided by the same positive quantity.
+\end{repcorollary}
+
+\begin{proof}
 	This immediately follows from Theorem \ref{thm:MergesOverOps} by taking $\Tweak{g} = g$.
@@
 
-\begin{proof}[Proof (Theorem \ref{thm:SameBigOClass})]
+\begin{reptheorem}{thm:SameBigOClass}
+	If $f \sim g$ and $g = O(h)$, then $f = O(h)$.
+\end{reptheorem}
+
+\begin{proof}
 	Let $r = \dfrac{f}{g}$.
@@
 
-\begin{proof}[Proof (Theorem \ref{thm:InterchangeableInInequality})]
+\begin{reptheorem}{thm:InterchangeableInInequality}
+	If $f \sim \Tweak{f}$ and $\Tweak{f} \FluteLess \TweakSecond{f}$, then $f \FluteLess \TweakSecond{f}$.
+If $g \sim \TweakSecond{g}$ and $\Tweak{g} \FluteLess \TweakSecond{g}$, then $\Tweak{g} \FluteLess g$.\\
+	These statements also hold for $\FluteLeq$.
+\end{reptheorem}
+
+\begin{proof}
 	By definition, $\ExprNToInfty \dfrac{f}{\Tweak{f}} = 1$ and $\ExprNToInfty \dfrac{\Tweak{f}}{\TweakSecond{f}} < 1$. Since both limits exist,
@@
 
-\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequality})]
+\begin{reptheorem}{thm:BothSidesInequality}
+	A $\FluteLess$ inequality is preserved when both sides are multiplied or divided by the same positive quantity.\\
+	This statement also holds for $\FluteLeq$.
+\end{reptheorem}
+
+\begin{proof}
 	Suppose that $f \FluteLess g$.
@@
 
-\begin{proof}[Proof (Theorem \ref{thm:BothSidesInequalityAdd})]
+\begin{reptheorem}{thm:BothSidesInequalityAdd}
+	Suppose $f \FluteLess g$. If $\ExprNToInfty \dfrac{f}{h} > 0$ and $g = O(h)$, then $f + h \FluteLess g + h$.\\
+	This statement also holds for $\FluteLeq$.
+\end{reptheorem}
+
+\begin{proof}
 	Assume that $n$ is arbitrarily large.

### 2017-11-15 Draft2/Appending.Compare.tex
Remove undefined references

@@
 \end{align*}
-From Theorem \ref{thm:BothSidesInequality} and Corollary \ref{coro:BothSidesNonStrictInequality}, I may divide all sides of this inequality by $n$ to receive
+From Theorem \ref{thm:BothSidesInequality}, I may divide all sides of this inequality by $n$ to receive
 \begin{align*}
@@
 From Theorem \ref{thm:MergesOverOps}, $\dfrac {\FuncWritesDynamicArray(n)} n \sim \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$.
-From Theorem \ref{thm:InterchangeableInInequality} and Corollary \ref{coro:InterchangeableInNonStrictInequality}, it follows that
+From Theorem \ref{thm:InterchangeableInInequality}, it follows that
 \begin{align*}

### 2017-11-15 Draft2/Appending.Dynamic.tex
Add pictures, [WIP] title all the algos
Remove undefined references

@@
 \begin{algorithm}[H]
+	\caption{Appending \TextDynamicArray}
 	\begin{algorithmic}[1]
@@
 \frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
-\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful - 1 \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality}, Corollary \ref{coro:InterchangeableInNonStrictInequality})}\\
-\frac n {\VarGrowthFactor - 1} &\FluteLeq \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLess \frac {\VarGrowthFactor{n}} {\VarGrowthFactor - 1} &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequalityAdd}, Corollary \ref{coro:BothSidesNonStrictInequalityAdd})}
+\frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful - 1 \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality})}\\
+\frac n {\VarGrowthFactor - 1} &\FluteLeq \left( \frac{\VarGrowthFactor^\VarUseful - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity \FluteLess \frac {\VarGrowthFactor{n}} {\VarGrowthFactor - 1} &&\text{(Theorem \ref{thm:BothSidesInequality})}\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncWrites(n) \FluteLess \left( \frac{2\VarGrowthFactor - 1}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequalityAdd})}
 \end{align*}
@@
 \frac n \VarInitCapacity &\FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity\\
-\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}\\
-\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} - 1 \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality}, Corollary \ref{coro:InterchangeableInNonStrictInequality})}\\
-\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncSpace(n) \FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequality}, Corollary \ref{coro:BothSidesNonStrictInequality})}
+\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Theorem \ref{thm:BothSidesInequality})}\\
+\frac {\VarGrowthFactor n} \VarInitCapacity &\FluteLeq \VarGrowthFactor^{\VarUseful + 1} - 1 \FluteLess \frac {\VarGrowthFactor^2 n} \VarInitCapacity &&\text{(Corollary \ref{coro:PlusConstant}, Theorem \ref{thm:InterchangeableInInequality})}\\
+\left( \frac{\VarGrowthFactor}{\VarGrowthFactor - 1} \right) n &\FluteLeq \FuncSpace(n) \FluteLess \left( \frac{\VarGrowthFactor^2}{\VarGrowthFactor - 1} \right) n &&\text{(Theorem \ref{thm:BothSidesInequality})}
 \end{align*}

### 2017-11-15 Draft2/Appending.Dynamic.tex
Lots of work

@@
 Thus, appending $n$ items takes $O(n)$ time.
-However, this fact is not very useful for the purpose of comparison--- later, it will be shown that growth arrays also take $O(n)$ time to append $n$ items.
+It will be shown later, however, that growth arrays also take $O(n)$ time for this task, so this does not let us compare time complexities.
 
-It would be helpful if the ratio $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$ could be determined, where $\FuncTimeDynamicArray(n)$ and $\FuncTimeGrowthArray(n)$ denote the average time needed to append $n$ items for dynamic and growth arrays, respectively.
-This represents how much faster growth arrays are than dynamic ones.
-However, there is no way to quantify these functions without empirical measurements.
-Thus, I will approximate this ratio through a different technique: Suppose $n$ elements are appended to an empty collection.
+I wish to find the ratio $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$, where $\FuncTimeDynamicArray(n)$ and $\FuncTimeGrowthArray(n)$ denote the average time needed to append $n$ items for dynamic and growth arrays, respectively.
+This represents how much faster growth arrays are at appending than dynamic ones.
+I will approximate this ratio using the following question: Suppose $n$ elements are appended to an empty collection.
 How many times is an element stored in an array?
@@
 In this section, I will derive the formula for $\FuncWritesDynamicArray(n)$.
-Because this section concerns dynamic arrays only, I will write it as $\FuncWrites(n)$.
+Because this section concerns dynamic arrays only, I will denote it $\FuncWrites(n)$.
 
 In the code for $\FuncAppend$, one array store is performed unconditionally, so it is apparent that $\FuncWrites(n) \geq n$ after $n$ appends.
-However, $\FuncGrow$ also does some writing, so in order to find a precise formula for $\FuncWrites(n)$, I need to analyze when $\FuncGrow$ is called.
+However, $\FuncGrow$ also does some writing via $\FuncArrayCopy$, so in order to find a precise formula for $\FuncWrites(n)$, I need to analyze when $\FuncGrow$ is called.
 To do this, I use the following lemma:
@@
 	\begin{align*}
-	\ExprMessyAltInner \leq \VarUseful &< \ExprMessyAltInner + 1\\
-	\frac{n}{\VarInitCapacity} \leq \VarUseful &< \frac{\VarGrowthFactor{n}}{\VarInitCapacity}
+	\ExprMessyAltInner &\leq \VarUseful < \ExprMessyAltInner + 1\\
+	\frac{n}{\VarInitCapacity} &\leq \VarGrowthFactor^\VarUseful < \frac{\VarGrowthFactor{n}}{\VarInitCapacity}
 	\end{align*}
@@
 \end{align*}
+This means that, for large $n$, the number of items written to append $n$ items is roughly between the two bounds shown.
+For example, suppose $\VarInitCapacity = 4$, $\VarGrowthFactor = 2$, and $32$ items are appended.
+$\FuncGrow$ is called at the sizes $4$, $8$, and $16$, so $4 + 8 + 16 = 28$ items are copied.
+Counting the $32$ writes made by $\FuncAppend$, one per item, the write cost is $\FuncWrites(32) = 28 + 32 = 60$.
+This is approximately equal to the lower bound, $\dfrac{2}{2 - 1} \cdot 32 = 64$.
+
+Now, suppose that one more item is added so that $n = 33$.
+$\FuncGrow$ is called again, so the number of items copied becomes $4 + 8 + 16 + 32 = 60$.
+The write cost becomes $\FuncWrites(33) = 33 + 60 = 93$.
+This is approximately equal to the upper bound, $\dfrac{2 \cdot 2 - 1}{2 - 1} \cdot 33 = 99$.
+
+Intuitively, it makes sense that $\FuncWrites(n)$ should jump from the lower bound to the upper bound when $n = \VarGrowSeq_i + 1$, since at that point $O(n)$ many items are copied from the old to the new buffer.
+(In the previous example, $\VarGrowSeq_i + 1$ is $17$.) As new items are added, however, both $n$ and $\FuncWrites(n)$ only increase by $1$, and the ratio $\dfrac {\FuncWrites(n)} n$ slowly dwindles toward the lower bound until $n$ reaches $\VarGrowSeq_{i + 1} + 1$.
+
 \HdrSpaceComplex
@@
 \end{align*}
+Using the same intuition from the time complexity section, $\FuncSpace(n)$ approaches the lower bound as $n \to \VarGrowSeq_i$, and jumps to the upper bound when $n = \VarGrowSeq_i + 1$.
+If $100$ items were appended to a dynamic array with $\VarInitCapacity = 11$ and $\VarGrowthFactor = 3$, for example, the wasted space $s(100) - 100$ would be approximately $\dfrac{3^2}{3 - 1} \cdot 100 - 100 = 350$.
+If $n$ were $99$, however, it would be approximately $\dfrac{3}{3 - 1} \cdot 99 - 99 = 49.5$.

### 2017-11-15 Draft2/Appending.Growth.tex
Add pictures, [WIP] title all the algos
Lots of work

@@
 
-In this section, $\VarList$ is a growth array. The following algorithm implements appending for growth arrays.
+The following diagrams should provide intuition on how growth arrays work.
+
+\begin{figure}[H]
+	\centering{\includegraphics[width=5in]{GrowthArrayDiagram}}
+	\caption{Appending $30$ items to a growth array with $\VarInitCapacity = 4$, $\VarGrowthFactor = 2$}
+\end{figure}
+
+\begin{figure}[H]
+	\centering{\includegraphics[width=5in]{GrowthArrayDiagram2}}
+	\caption{Appending $16$ items to a growth array with $\VarInitCapacity = 2$, $\VarGrowthFactor = 3$}
+\end{figure}
+
+\begin{figure}[H]
+	\centering{\includegraphics[width=5in]{GrowthArrayDiagram3}}
+	\caption{Appending $1$ item to a growth array with $\VarInitCapacity = 4, \VarGrowthFactor = 2$. Initial size: $8$}
+\end{figure}
+
+In this section, $\VarList$ denotes a growth array. The following algorithm implements appending for growth arrays.
 
 \begin{algorithm}[H]
+	\caption{Appending \TextGrowthArray}
 	\begin{algorithmic}[1]
@@
 
-Now, I focus on finding a formula for the write cost function, $\FuncWritesGrowthArray(n)$, which will be written as $\FuncWrites(n)$ in this section.
-I claim that Lemma \ref{lem:CapacitySeq} still holds, since growth arrays satisfy all properties used by that proof.
-In particular, although growth arrays use a different growth algorithm than dynamic arrays, the following statement still holds:
+Now, I focus on finding a formula for growth arrays' write cost function, $\FuncWritesGrowthArray(n)$, which will be written as $\FuncWrites(n)$ in this section.
+I claim that Lemma \ref{lem:CapacitySeq} also holds for growth arrays, since they satisfy all properties used by that proof.
+In particular, although growth arrays use a different growth algorithm than dynamic arrays, they still have the following property:
 
@@
 Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumPointersTail$ be the size of the tail.
-Since Corollary \ref{coro:GrowthSeq} also holds true for growth arrays, $\FuncGrow$ is called $|\VarGrowSeq|$ times.
+Since Corollary \ref{coro:GrowthSeq} also holds for growth arrays, $\FuncGrow$ is called $|\VarGrowSeq|$ times.
 A buffer is appended to the tail each time $\FuncGrow$ is called.
@@
 \end{align*}
-The last step is justified by Theorem \ref{thm:RemovesLowerOrderTerms}.
+(The last step is justified by Theorem \ref{thm:RemovesLowerOrderTerms}.)
+
+This says that when $n$ items are added, the number of items written is approximately $n$. This is a significant improvement over the asymptotic bounds for $\FuncWritesDynamicArray(n)$.
 

### 2017-11-15 Draft2/ExternalDefinitions.tex
Add pictures, [WIP] title all the algos
Lots of work

@@
 \begin{algorithm}[H]
+	\caption{Runtime-defined functions}
 	\begin{algorithmic}
@@
 
-I will also use the following constants in my algorithms. Specific values for these constants must be supplied by the person using the algorithms.
+\subsection{Constants}
+
+I will use the following constants in my algorithms. These constants govern how the algorithms will behave. Specific values for them must be supplied by the person using the algorithms.
 

### 2017-11-15 Draft2/Intro.tex
add -> append
Lots of work

@@
 In imperative languages, the dynamic array is the most common data structure used by programs.
-People often want to add multiple items to a collection and then iterate it, which dynamic arrays make simple and efficient.
+People often want to append multiple items to a collection and then iterate it, which dynamic arrays make simple and efficient.
 But can it be said they have the \textit{most} efficient algorithm for this pattern?
@@
 The new buffer they allocate represents a continuation of the items from the old buffer.
-For example, if the old buffer contained items $0 -- 9$, the new buffer would contain items $10$ and beyond.
+For example, if the old buffer contained items $0 - 9$, the new buffer would contain items $10$ and beyond.
 Because of this technique, growth arrays allocate less memory to store the same number of items, and do not need to copy the contents of old buffers.

### 2017-11-15 Draft2/Appending.Compare.tex
Many edits

@@
 
-In this section, $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ will denote the write cost functions for dynamic and growth arrays, respectively. I derived earlier that
+In this section, $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ will denote the write cost functions for dynamic and growth arrays, respectively.
+My goal is to approximate the ratio $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$ for large $n$.
+From my assumption near the beginning of Section \ref{subsec:Appending}, this is equal to $\dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$.
+I derived earlier that
 \begin{align*}
@@
 \end{align*}
+For $\VarGrowthFactor = 2$, this can be interpreted as ``For large $n$, dynamic arrays make approximately $2$ to $3$ times as many writes as growth arrays.
+\underline{Thus, for large $n$, they are about $2$ to $3$ times slower than growth arrays.}''
+
 \HdrSpaceComplexCmp
 
-Let $\FuncSpaceDynamicArray(n)$ and $\FuncSpaceGrowthArray(n)$ be the space cost functions for dynamic and growth arrays, respectively. Recall that
+Let $\FuncSpaceDynamicArray(n)$ and $\FuncSpaceGrowthArray(n)$ be the space cost functions for dynamic and growth arrays, respectively.
+I wish to approximate the ratio $\dfrac{\FuncSpaceDynamicArray(n)}{\FuncSpaceGrowthArray(n)}$ for large $n$.
+Recall that
 \begin{align*}
@@
 \end{align*}
-and that $\FuncSpaceGrowthArray(n) \sim \VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$.
-Taking the ratio of $\FuncSpaceDynamicArray(n)$ to $\FuncSpaceGrowthArray(n)$, I receive
+and that $\FuncSpaceGrowthArray(n) \sim \VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$. Dividing $\FuncSpaceDynamicArray(n)$ by $\FuncSpaceGrowthArray(n)$, I receive
 \begin{align*}
@@
 \end{align*}
+For $\VarGrowthFactor = 2$, this can be interpreted as ``\underline{For large $n$, dynamic arrays use approximately twice as much space as growth arrays.}''

### 2017-11-15 Draft2/Appending.Dynamic.tex
Many edits

@@
 
-I will na\"{i}vely assume that $\FuncTime(n) \propto \FuncWrites(n)$, or that the average time for $n$ appends is proportional to their write cost.
+I will assume that $\FuncTime(n) \propto \FuncWrites(n)$, or that the average time for $n$ appends is proportional to their write cost (although this is an oversimplification).
 Then $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)} = \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$, where $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ are respectively the write cost functions for dynamic and growth arrays.

### 2017-11-15 Draft2/Appending.Growth.tex
Many edits

@@
 
-% Bookmark
-% The following following paragraph doesn't work.
-
 Now, I wish to approximate this using $\sim$.
 Since $\VarCapacitySeq_\VarUseful = \VarGrowthFactor^\VarUseful\VarInitCapacity$, it follows from Lemma \ref{lem:ToVarUsefulPowerBounds} that $n \FluteLeq \VarCapacitySeq_\VarUseful \FluteLess \VarGrowthFactor{n}$.
-Since $n$ and $\VarGrowthFactor{n}$ are both $O(n)$, [the squeeze theorem] implies that $\VarCapacitySeq_\VarUseful = O(n)$.
+From Corollary \ref{coro:BothSidesInequalityInvert}, $\dfrac{1}{\VarGrowthFactor n} \FluteLess \dfrac{1}{\VarCapacitySeq_\VarUseful} \FluteLeq \dfrac{1}{n}$.
+From Theorem \ref{thm:BothSidesInequality}, $\dfrac{\FuncSpaceTail(\VarUseful)}{\VarGrowthFactor n} \FluteLess \dfrac{\FuncSpaceTail(\VarUseful)}{\VarCapacitySeq_\VarUseful} \FluteLeq \dfrac{\FuncSpaceTail(\VarUseful)}{n}$.
 
-Now, consider the ratio $\ExprNToInfty \dfrac {\FuncSpaceTail(\VarUseful)} {\VarCapacitySeq_\VarUseful} = \dfrac {O(\log n)} {O(n)} = O \left( \dfrac{\log n}{n} \right) = 0$.
-Because it is $0$, from Theorem \ref{thm:RemovesLowerOrderTerms} one can conclude
+Since $\FuncSpaceTail(\VarUseful) = O(\VarUseful) = O(\log n)$, the limits of the lower and upper bounds are both $0$.
+From the squeeze theorem, it follows that $\ExprNToInfty \dfrac{\FuncSpaceTail(\VarUseful)}{\VarCapacitySeq_\VarUseful} = 0$.
+Thus, $\FuncSpaceTail(\VarUseful) = o(\VarCapacitySeq_\VarUseful)$.
+From Theorem \ref{thm:RemovesLowerOrderTerms}, one can conclude
 \begin{align*}
@@
 \end{align*}
-Substituting $\FuncSpace(n)$ for $\VarCapacitySeq_\VarUseful$ in the previous inequality,
+Using Theorem \ref{thm:InterchangeableInInequality}, I may substitute $\FuncSpace(n)$ for $\VarCapacitySeq_\VarUseful$ in the first inequality to receive
 \begin{align*}
@@
 \end{align*}
+This result is significant since it has smaller lower and upper bounds than $\FuncSpaceDynamicArray(n)$.
+Since the same values of $n$ as for $\FuncSpaceDynamicArray(n)$ correspond to when it is close to the bounds for $\FuncSpace(n)$ (namely, when $n$ is approximately $\VarGrowSeq_i$), $\FuncSpace(n)$ is asymptotically less than $\FuncSpaceDynamicArray(n)$ even though their intervals overlap.
+This will be proven rigorously in the space complexity comparison section.

### 2017-11-15 Draft2/Appendix.tex
Many edits

@@
 
-{\HdrNote} In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
+{\HdrNote} In the following theorems and their proofs, variables with the letters $f$, $g$, or $h$ denote functions that are positive for sufficiently large $n$.
 
@@
 
+\subsubsection{$\FluteLess$ and $\FluteLeq$ Inequalities are Flipped when Both Sides are Inverted}
+
+\begin{repcorollary}{coro:BothSidesInequalityInvert}
+	If $f \FluteLess g$, then $\dfrac{1}{g} \FluteLess \dfrac{1}{f}$.\\
+	This statement also holds for $\FluteLeq$.
+\end{repcorollary}
+
+\begin{proof}
+	This immediately follows from $f \FluteLess g$ or $f \FluteLeq g$ by using Theorem \ref{thm:BothSidesInequality} to divide both sides by $fg$.
+\end{proof}
+
 \subsection{Same-Order Terms may be Added to Both Sides of $\FluteLess$ and $\FluteLeq$ Inequalities}

### 2017-11-15 Draft2/AsymptoticNotation.tex
Many edits

@@
 
-{\HdrNote} In the following theorems, variables with the letters $f$, $g$, or $h$ denote functions that, for sufficiently large $n$, are positive and non-decreasing.
+{\HdrNote} In the following theorems, variables with the letters $f$, $g$, or $h$ denote functions that are positive for sufficiently large $n$.
 
@@
 
+\begin{corollary}
+\label{coro:BothSidesInequalityInvert}
+	If $f \FluteLess g$, then $\dfrac{1}{g} \FluteLess \dfrac{1}{f}$.\\
+	This statement also holds for $\FluteLeq$.
+\end{corollary}
+
 Notice that the above theorem does not include addition.

### 2017-11-15 Draft2/FieldsProperties.tex
Work
Make algorithms not float
Add pictures, [WIP] title all the algos
Many edits

@@
 
-\begin{algorithm}
+\begin{algorithm}[H]
+	\caption{Properties \TextDynamicArray}
 	\begin{algorithmic}
@@
 
-\begin{algorithm}
+\begin{algorithm}[H]
+	\caption{Constructor \TextDynamicArray}
 	\begin{algorithmic}
@@
 	\item $\VarList.\FieldTail$ -- The \textbf{tail} of $\VarList$.
-(\textbf{Important note: The tail is a dynamic array.}) It returns a dynamic array of pointers to buffers that are already filled with items.
+(\underline{{\HdrNote} The tail is a dynamic array.}) It returns a dynamic array of pointers to buffers that are already filled with items.
 The tail can be thought of as a two-dimensional array.\\
@@
 
-\begin{algorithm}
+\begin{algorithm}[H]
+	\caption{Properties \TextGrowthArray}
 	\begin{algorithmic}
@@
 		\State
-		\LineComment{Returns the capacity of $\FieldHead$}
+		\LineComment{Returns the \textbf{head capacity}, or the capacity of $\FieldHead$}
 		\State $\VarList.\FieldHeadCapacity := \VarList.\FieldHead.\FieldLength$
 		\State
-		\LineComment{Returns the size of $\FieldHead$}
+		\LineComment{Returns the \textbf{head size}, or the size of $\FieldHead$}
 		\LineComment{\textbf{Explanation:} $\FieldCapacity - \FieldHeadCapacity$ is the number of items in $\FieldTail$.}
@@
 
-\begin{algorithm}
+\begin{algorithm}[H]
+	\caption{Constructor \TextGrowthArray}
 	\begin{algorithmic}

### 2017-11-15 Draft2/Indexing.Dynamic.tex
Prune indexing section

--- 2017-11-13 Draft2/Indexing.Dynamic.tex
@@
 
-The following algorithm implements $\FuncGetItem$ for dynamic arrays. (A $\FuncSetItem$ function can be implemented in a similar fashion.)
-
-{\HdrNote} My algorithms do not validate any arguments; all arguments passed to them are assumed to be valid.
-
-\begin{algorithm}
-	\begin{algorithmic}[1]
-		\Function{$\FuncGetItem$}{$\VarList,\ \ParamIndex$}
-			\State \Return $\VarList.\FieldBuffer[\ParamIndex]$
-		\EndFunction
-	\end{algorithmic}
-\end{algorithm}
-
-This algorithm runs in $O(1)$ time. It also has the benefit of using very few instructions, which is a benefit that will not be shared with growth arrays.
+The algorithm for indexing a dynamic array is trivial, and will not be shown here.
+It simply reads or writes to the $i$th element of $\VarList.\FieldBuffer$ (where $i$ is zero-based).
+It is well-known that this algorithm runs in $O(1)$ time.
+It also has the benefit of using very few instructions, which will not be the case for growth arrays' algorithm.

### 2017-11-15 Draft2/Indexing.Growth.tex
Exterminate more todos
Exterminate things
Add pictures, [WIP] title all the algos
Prune indexing section

@@
 
-Despite growth arrays' relatively poor indexing performance, I include this section for two reasons.
+Although growth arrays have poor random access performance, I include this section for two reasons.
 1) Dynamic arrays are indexed frequently.
@@
 
-The first algorithm I will demonstrate is a na\"{i}ve implementation that runs in logarithmic time:
+The first algorithm I will demonstrate is a na\"{i}ve implementation that runs in logarithmic time.
+
+{\HdrNote} My algorithms assume all arguments passed to them are valid. Thus, arguments are never checked.
 
 \begin{algorithm}[H]
+	\caption{Random access \TextGrowthArray, logarithmic time}
 	\begin{algorithmic}
@@
 
-I know that this algorithm runs in $O(\log n)$ time since it was shown earlier that the size of the tail, $\VarNumPointersTail$, equals $\VarUseful$, and (from Lemma \ref{lem:VarUsefulIsOLogN}) that $\VarUseful = O(\log n)$.
+I know that this algorithm runs in $O(\log n)$ time since it was shown earlier that the size of the tail, $\VarNumPointersTail$, equals $\VarUseful$, and Lemma \ref{lem:VarUsefulIsOLogN} states that $\VarUseful = O(\log n)$.
 Aside from iteration over the tail, all statements run in constant time, so the time complexity is precisely $O(\log n)$.
 
-I present this algorithm alongside the constant time one because it is easier to understand, and the latter is often slower if special circumstances are not met.
+I present this algorithm alongside the constant time one since it is easier to understand, and the latter is often slower if special circumstances are not met.
 
@@
 In order to locate the desired element, I must find two things: the buffer that holds the item, and the index of the item within that buffer.
+For example, referring to Figure \ref{fig:1}: if $i$ was $10$, I would want the item at index $2$ of the tail's third buffer.
+If $i$ was $20$, I would want the item at index $4$ of the head.
 
@@
 \begin{algorithm}[H]
+	\caption{\TextHelperFunction}
 	\begin{algorithmic}
@@
 
-If I define a helper function $\FuncDecompose$ that returns the $\VarIndexBuffer$ and $\VarIndexElement$ associated with $i$ in an ordered pair, then $\FuncGetItem$ may be written as follows:
+If I define a helper function $\FuncDecompose$ that splits $i$ into the ordered pair $(\VarIndexBuffer,\ \VarIndexElement)$, then $\FuncGetItem$ may be written as follows:
 
 \begin{algorithm}[H]
+	\caption{Random access \TextGrowthArray, constant time}
 	\begin{algorithmic}
@@
 Now, the task is to find formulae for $\VarIndexBuffer$ and $\VarIndexElement$ in terms of $i$, in order to implement $\FuncDecompose$.
+Referring to Figure \ref{fig:1}: $\FuncDecompose(10)$ should return $(2,\ 2)$.
+$\FuncDecompose(20)$ should return $(3,\ 4)$.
 
-% Todo: There's an awful lot of lemmas. Make some into theorems.
 \begin{lemma}
@@
 	\end{align*}
-	(When $\VarIndexBuffer = 0$, $\VarGrowSeq_{-1} = 0$ by convention.)
+	(By convention, $\VarGrowSeq_{-1} = 0$.)
 \end{lemma}
 
-% Todo: "As shown earlier"
 \begin{proof}
@@
 	\end{align*}
-	First, I will determine the number of items in the tail.
-In the case where $\VarIndexBuffer = 0$, then because $\VarNumPointersTail = \VarIndexBuffer$, the tail contains $0$ buffers and thus $0$ items (which equals $\VarGrowSeq_{-1}$).
+	({\HdrNote} The first quantity on the right-hand side is not $\VarNumPointersTail$. $\VarNumPointersTail$ is the number of buffer pointers in the tail.)
+
+	First, I will determine how many items the tail holds.
+In the case where $\VarIndexBuffer = 0$, then because $\VarNumPointersTail = \VarIndexBuffer$, the tail contains $0$ buffer pointers and thus $0$ items (which equals $\VarGrowSeq_{-1}$).
 If $\VarIndexBuffer > 0$, the number of items in the tail is the last size at which $\FuncGrow$ was called, or the last term of $\VarGrowSeq$.
@@
 
-Using the formulae for $\VarUseful$ and $\VarGrowSeq_i$, I now implement the $\FuncDecompose$ function:
+Using the formulae $\VarUseful = \max(\ExprMessy, 0)$ and $\VarGrowSeq_k = \VarGrowthFactor^k \VarInitCapacity$ for $k \geq 0$, I now implement the $\FuncDecompose$ function:
 
 \begin{algorithm}[H]
+	\caption{\TextHelperFunction}
 	\begin{algorithmic}

### 2017-11-15 Draft2/Indexing.Growth.tex
Finish indexing

@@
 
+% Todo: cite.
 To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$.
 There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper.
-(An implementation of the algorithm, however, may be found in the links at Section \ref{sec:Implementations}.) Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.
+Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.
 

### 2017-11-15 Draft2/ConvertRawArray.Blurb.tex
Work

--- 2017-11-14 Draft2/CopyArray.Blurb.tex
@@
 There are multiple reasons for this: 1) Raw arrays hold on to exactly $n$ memory to store $n$ elements.
-However, dynamic and growth arrays typically use more than $n$ memory, so they need not grow every time an item is appended.
-2) Sometimes, functions in third-party code only accept raw arrays.
+However, dynamic and growth arrays typically use more than $n$ memory, so that they need not grow every time an item is appended.
+2) Often, functions in third-party code only accept raw arrays.
 
-For growth arrays, the case is even more compelling: 3) Since they are not contiguous as a whole, they have worse data locality (even if the number of discontinuities is $O(\log n)$).
+For growth arrays, the case is even more compelling: 3) Since they are not contiguous as a whole, they have worse data locality (although the number of discontinuities is only $O(\log n)$).
 4) Raw arrays can be indexed much faster than growth arrays.

### 2017-11-15 Draft2/Iterating.Growth.tex
Work

@@
 The iteration algorithm for growth arrays is not quite as simple.
-As shown in the previous section, growth arrays' random access algorithm is expensive; thus, it is best avoided.
+As shown in Section \ref{subsec:Indexing}, growth arrays' random access algorithm can be expensive; thus, it is best avoided.
 The following algorithm implements iteration without using the random access algorithm.
@@
 		\For{$\LclIndex = 0,\ \LclIndex < \VarList.\FieldHeadSize,\ \LclIndex \gets \LclIndex + 1$}
-			\State $\LclItem \gets \VarList.\FieldHead[\LclIndex]$
-			\State $\TextDoSomethingWith \LclItem$
+			\State $\TextDoSomethingWith \VarList.\FieldHead[\LclIndex]$
 		\EndFor
@@
 \end{algorithm}
+
+Since this algorithm loops over $n$ items, its time complexity is $O(n)$.
+There is nothing to suggest that this algorithm should be substantially slower than dynamic arrays' algorithm.
+Even though the inner loop is occasionally `interrupted' by having to switch buffers, the number of such interruptions is $O(\log n)$, so their cost is minuscule.
+Thus, the only substantial work done by this algorithm is iterating the buffers, which is roughly the same as the work done by dynamic arrays' algorithm.

### 2017-11-15 Draft2/ConvertRawArray.Growth.tex
Work
More work

--- 2017-11-11 Draft2/CopyArray.Growth.tex
@@
 
-The growth array implementation must call $\FuncArrayCopy$ multiple times, since not all elements are contiguous.
+The following algorithm converts a growth array to a raw array:
 
-\begin{algorithm}
+\begin{algorithm}[H]
+	\caption{Converting to a raw array \TextGrowthArray}
 	\begin{algorithmic}
@@
 \end{algorithm}
+
+This algorithm copies $n$ items, so its time complexity is $O(n)$.
+Using the same argument as in Section \ref{subsec:Iterating}, the cost of `interruptions' from switching buffers is minuscule.
+Ignoring $\FuncNewArray$ since it is non-deterministic, the only substantial work done by this function is the multiple $\FuncArrayCopy$ calls.
+They constitute roughly the same work done by dynamic arrays' single $\FuncArrayCopy$ call.
+Thus, $\FuncToArray$ should take roughly as long for growth arrays as it does for dynamic arrays.

### 2017-11-15 Draft2/OtherOperations.Blurb.tex
Change the paper structure

@@
-Growth arrays support other dynamic array operations, such as insertion/deletion at an index, binary search, sorting, etc.
+Growth arrays support other dynamic array operations, such as insertion or deletion at an index, binary search, sorting, etc.
 I will not give algorithms for these operations in this paper, since they are not as common as the four detailed above.
@@
 If $i = n$, then simply append the item.
-Otherwise ($0 \leq i < n$), capture $\VarList[n - 1]$ in a local variable.
-Shift all elements with index $\geq i$ forward by one, so that their index increases by one.
+If $0 \leq i < n$: capture $\VarList[n - 1]$ in a local variable.
+Shift all elements with index $\geq i$ forward, such that their index increases by $1$.
 Append the original value of $\VarList[n - 1]$.
-Finally, set index $i$ to the provided item.
+Finally, store the provided item at index $i$.
 
 Suppose the user wants to delete the item at index $i$.
-Shift all elements with index $> i$ backwards by one, so that their index decreases by one.
-Decrement $\VarList.\FieldSize$ and $\VarList.\FieldHeadSize$.
-If this causes $\VarList.\FieldHeadSize$ to become $0$ and $\VarNumPointersTail > 0$, then discard the head and replace it with the last buffer pointed to by the tail.
+Shift all elements with index $> i$ backwards, such that their index decreases by one.
+(This will overwrite the item at index $i$.) Decrement $\VarList.\FieldSize$ and $\VarList.\FieldHeadSize$.
+If this causes $\VarList.\FieldHeadSize$ to become $0$ and currently $\VarList.\FieldTail.\FieldSize > 0$, then discard the head and replace it with the last buffer pointed to by the tail.
 Remove this buffer from the tail.

### 2017-11-15 Draft2/ClosingRemarks.tex
Add closing remarks

In this paper, I developed the concept of growth arrays and showed that they are a viable replacement for dynamic arrays. I implemented several common dynamic array operations for growth arrays, and showed that for appending, growth arrays outperform dynamic ones both time- and memory-wise. I demonstrated that although growth arrays are slower at random access than dynamic arrays, it is still possible to index them in constant time. Finally, I showed that they perform comparably to dynamic arrays for iteration and conversion to raw arrays.

% Todo: Should have this paragraph?
Today, dynamic arrays are commonly used because they are reasonably efficient at appending. Since growth arrays are even faster at appending, it is possible that they could begin to supplant dynamic arrays if programming languages start adopting them in their standard libraries. It is also possible that the trade-offs growth arrays make to achieve faster appending could hinder their adoption, or have languages offer them as an alternative to dynamic arrays.

I will end this paper with the following open-ended questions, which may serve as inspiration for further research:

\begin{itemize}
	\item Can growth arrays' growth algorithm bring performance improvements to other array-based structures, such as circular queues or array-based stacks?
	\item Is there an efficient, constant time random access algorithm for growth arrays that works for all values of $\VarGrowthFactor$ and $\VarInitCapacity$?
	\item To what extent does growth arrays' fragmented structure result in performance losses due to poorer data locality? Can memory allocators offset these losses by allocating buffers close to each other?
	\item How can algorithms such as binary search and sorting be best implemented for growth arrays? Since growth arrays with $\VarGrowthFactor = 2$ have an evenly-divided structure, is there a better binary search algorithm for them?
\end{itemize}

### 2017-11-15 Draft2/Bibliography.tex
Bogus citation

\begin{thebibliography}{9}

\bibitem{ceillog2}
	Ko, James L. "Algorithm for implementing ceiling of log 2." \textit{GitHub}, 12 Nov. 2017,\\ \texttt{https://github.com/jamesqo/StsProject/blob/master/src/StsProject/Internal/MathHelpers.cs}
\end{thebibliography}

### 2017-11-15 Draft2/Indexing.Growth.tex
Rename labels
Work
Bogus citation

@@
 However, this does not mean that accessing data of a growth array is necessarily slower than accessing that of a dynamic array.
-Refer to Sections \ref{sec:Iterating} and \ref{sec:CopyArray} for methods to quickly access growth arrays' data.
+Refer to Sections \ref{subsec:Iterating} and \ref{subsec:ConvertRawArray} for methods to quickly access growth arrays' data.
 
@@
 
-% Todo: cite.
 To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$.
-There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper.
+There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper \cite{ceillog2}.
 Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.

### 2017-11-15 Draft2/ClosingRemarks.tex
Delete the unsure para

@@
 Finally, I showed that they perform comparably to dynamic arrays for iteration and conversion to raw arrays.
-
-% Todo: Should have this paragraph?
-Today, dynamic arrays are commonly used because they are reasonably efficient at appending.
-Since growth arrays are even faster at appending, it is possible that they could begin to supplant dynamic arrays if programming languages start adopting them in their standard libraries.
-It is also possible that the trade-offs growth arrays make to achieve faster appending could hinder their adoption, or have languages offer them as an alternative to dynamic arrays.
 

### 2017-11-16 Draft2/Appending.Compare.tex
Thank god

@@
 In this section, $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ will denote the write cost functions for dynamic and growth arrays, respectively.
-My goal is to approximate the ratio $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$ for large $n$.
-From my assumption near the beginning of Section \ref{subsec:Appending}, this is equal to $\dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$.
+My goal is to approximate the ratio $\frac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$ for large $n$.
+From my assumption near the beginning of Section \ref{subsec:Appending}, this is equal to $\frac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$.
 I derived earlier that
@@
 It was shown earlier that $\FuncWritesGrowthArray(n) \sim n$.
-From Theorem \ref{thm:MergesOverOps}, $\dfrac {\FuncWritesDynamicArray(n)} n \sim \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$.
+From Theorem \ref{thm:MergesOverOps}, $\frac {\FuncWritesDynamicArray(n)} n \sim \frac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$.
 From Theorem \ref{thm:InterchangeableInInequality}, it follows that
@@
 Let $\FuncSpaceDynamicArray(n)$ and $\FuncSpaceGrowthArray(n)$ be the space cost functions for dynamic and growth arrays, respectively.
-I wish to approximate the ratio $\dfrac{\FuncSpaceDynamicArray(n)}{\FuncSpaceGrowthArray(n)}$ for large $n$.
+I wish to approximate the ratio $\frac{\FuncSpaceDynamicArray(n)}{\FuncSpaceGrowthArray(n)}$ for large $n$.
 Recall that

### 2017-11-16 Draft2/Appending.Dynamic.tex
Thank god

@@
 
-I wish to find the ratio $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$, where $\FuncTimeDynamicArray(n)$ and $\FuncTimeGrowthArray(n)$ denote the average time needed to append $n$ items for dynamic and growth arrays, respectively.
+I wish to find the ratio $\frac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)}$, where $\FuncTimeDynamicArray(n)$ and $\FuncTimeGrowthArray(n)$ denote the average time needed to append $n$ items for dynamic and growth arrays, respectively.
 This represents how much faster growth arrays are at appending than dynamic ones.
@@
 I will assume that $\FuncTime(n) \propto \FuncWrites(n)$, or that the average time for $n$ appends is proportional to their write cost (although this is an oversimplification).
-Then $\dfrac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)} = \dfrac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$, where $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ are respectively the write cost functions for dynamic and growth arrays.
+Then $\frac{\FuncTimeDynamicArray(n)}{\FuncTimeGrowthArray(n)} = \frac{\FuncWritesDynamicArray(n)}{\FuncWritesGrowthArray(n)}$, where $\FuncWritesDynamicArray$ and $\FuncWritesGrowthArray$ are respectively the write cost functions for dynamic and growth arrays.
 In this section, I will derive the formula for $\FuncWritesDynamicArray(n)$.
@@
 \label{lem:ToVarUsefulPowerBounds}
-	$\dfrac n \VarInitCapacity \FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \dfrac {\VarGrowthFactor{n}} \VarInitCapacity$.
-That is, $\dfrac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \dfrac {\VarGrowthFactor{n}} \VarInitCapacity$ for sufficiently large $n$.
+	$\frac n \VarInitCapacity \FluteLeq \VarGrowthFactor^\VarUseful \FluteLess \frac {\VarGrowthFactor{n}} \VarInitCapacity$.
+That is, $\frac n \VarInitCapacity \leq \VarGrowthFactor^\VarUseful < \frac {\VarGrowthFactor{n}} \VarInitCapacity$ for sufficiently large $n$.
 \end{lemma}
@@
 Counting the $32$ writes made by $\FuncAppend$, one per item, the write cost is $\FuncWrites(32) = 28 + 32 = 60$.
-This is approximately equal to the lower bound, $\dfrac{2}{2 - 1} \cdot 32 = 64$.
+This is approximately equal to the lower bound, $\frac{2}{2 - 1} \cdot 32 = 64$.
 
@@
 The write cost becomes $\FuncWrites(33) = 33 + 60 = 93$.
-This is approximately equal to the upper bound, $\dfrac{2 \cdot 2 - 1}{2 - 1} \cdot 33 = 99$.
+This is approximately equal to the upper bound, $\frac{2 \cdot 2 - 1}{2 - 1} \cdot 33 = 99$.
 
 Intuitively, it makes sense that $\FuncWrites(n)$ should jump from the lower bound to the upper bound when $n = \VarGrowSeq_i + 1$, since at that point $O(n)$ many items are copied from the old to the new buffer.
-(In the previous example, $\VarGrowSeq_i + 1$ is $17$.) As new items are added, however, both $n$ and $\FuncWrites(n)$ only increase by $1$, and the ratio $\dfrac {\FuncWrites(n)} n$ slowly dwindles toward the lower bound until $n$ reaches $\VarGrowSeq_{i + 1} + 1$.
+(In the previous example, $\VarGrowSeq_i + 1$ is $17$.) As new items are added, however, both $n$ and $\FuncWrites(n)$ only increase by $1$, and the ratio $\frac {\FuncWrites(n)} n$ slowly dwindles toward the lower bound until $n$ reaches $\VarGrowSeq_{i + 1} + 1$.
 
@@
 Using the same intuition from the time complexity section, $\FuncSpace(n)$ approaches the lower bound as $n \to \VarGrowSeq_i$, and jumps to the upper bound when $n = \VarGrowSeq_i + 1$.
-If $100$ items were appended to a dynamic array with $\VarInitCapacity = 11$ and $\VarGrowthFactor = 3$, for example, the wasted space $s(100) - 100$ would be approximately $\dfrac{3^2}{3 - 1} \cdot 100 - 100 = 350$.
-If $n$ were $99$, however, it would be approximately $\dfrac{3}{3 - 1} \cdot 99 - 99 = 49.5$.
+If $100$ items were appended to a dynamic array with $\VarInitCapacity = 11$ and $\VarGrowthFactor = 3$, for example, the wasted space $s(100) - 100$ would be approximately $\frac{3^2}{3 - 1} \cdot 100 - 100 = 350$.
+If $n$ were $99$, however, it would be approximately $\frac{3}{3 - 1} \cdot 99 - 99 = 49.5$.

### 2017-11-16 Draft2/Appendix.tex
Thank god

@@
 \begin{proof}
-	Clearly, $\ExprNToInfty \dfrac{f}{f} = 1$, so $f \sim f$. Thus, $\sim$ is reflexive.
+	Clearly, $\ExprNToInfty \frac{f}{f} = 1$, so $f \sim f$. Thus, $\sim$ is reflexive.
 
 	Suppose $f \sim g$.
-Then $\ExprNToInfty \dfrac{f}{g} = 1$.
-Since both $\ExprNToInfty 1$ and $\ExprNToInfty \dfrac{f}{g}$ exist and the latter is nonzero, $\dfrac{\ExprNToInfty 1}{\ExprNToInfty (f / g)}$ = $\ExprNToInfty \dfrac{g}{f}$.
+Then $\ExprNToInfty \frac{f}{g} = 1$.
+Since both $\ExprNToInfty 1$ and $\ExprNToInfty \frac{f}{g}$ exist and the latter is nonzero, $\frac{\ExprNToInfty 1}{\ExprNToInfty (f / g)}$ = $\ExprNToInfty \frac{g}{f}$.
 Since the left-hand side evaluates to $1$, $g \sim f$.
@@
 	Suppose $f \sim g$ and $g \sim h$.
-By definition, $\ExprNToInfty \dfrac{f}{g} = 1$ and $\ExprNToInfty \dfrac{g}{h} = 1$.
-Since both limits exist, their product is $\ExprNToInfty \left( \dfrac{f}{g} \cdot \dfrac{g}{h} \right) = \ExprNToInfty \dfrac{f}{h}$.
+By definition, $\ExprNToInfty \frac{f}{g} = 1$ and $\ExprNToInfty \frac{g}{h} = 1$.
+Since both limits exist, their product is $\ExprNToInfty \left( \frac{f}{g} \cdot \frac{g}{h} \right) = \ExprNToInfty \frac{f}{h}$.
 Since this product is $1$, $f \sim h$.
@@
 \begin{proof}
-	Let $g = o(f)$. By definition, $\ExprNToInfty \dfrac{g}{f} = 0$. Since $\ExprNToInfty \dfrac{f}{f}$ and $\ExprNToInfty \dfrac{g}{f}$ both exist,
+	Let $g = o(f)$. By definition, $\ExprNToInfty \frac{g}{f} = 0$. Since $\ExprNToInfty \frac{f}{f}$ and $\ExprNToInfty \frac{g}{f}$ both exist,
 	\begin{align*}
-	\ExprNToInfty \dfrac{f + g}{f} = \ExprNToInfty \dfrac{f}{f} + \ExprNToInfty \dfrac{g}{f} = 1 + 0 = 1
+	\ExprNToInfty \frac{f + g}{f} = \ExprNToInfty \frac{f}{f} + \ExprNToInfty \frac{g}{f} = 1 + 0 = 1
 	\end{align*}
@@
 \begin{proof}
-	Let $\FuncQuotient = \dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, and let $\FuncDenom = \Tweak{g} + \Tweak{g}^2 / \Tweak{f}$. $\FuncQuotient$ may be expressed as
+	Let $\FuncQuotient = \frac{f + g}{\Tweak{f} + \Tweak{g}}$, and let $\FuncDenom = \Tweak{g} + \Tweak{g}^2 / \Tweak{f}$. $\FuncQuotient$ may be expressed as
 	\begin{align*}
@@
 	\end{align*}
-	Since $\Tweak{g}$ and $\Tweak{g}^2 / \Tweak{f}$ sum to $\FuncDenom$ and all functions are positive, $\dfrac{\Tweak{g}}{\FuncDenom}$ and $\dfrac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}$ are bounded between $0$ and $1$ as $n \to \infty$.
-From the given, $\ExprNToInfty \left( \dfrac{f}{\Tweak{f}} - 1 \right)$ and $\ExprNToInfty \left( \dfrac{g}{\Tweak{g}} - 1 \right)$ both exist and equal $0$.
+	Since $\Tweak{g}$ and $\Tweak{g}^2 / \Tweak{f}$ sum to $\FuncDenom$ and all functions are positive, $\frac{\Tweak{g}}{\FuncDenom}$ and $\frac{\Tweak{g}^2 / \Tweak{f}}{\FuncDenom}$ are bounded between $0$ and $1$ as $n \to \infty$.
+From the given, $\ExprNToInfty \left( \frac{f}{\Tweak{f}} - 1 \right)$ and $\ExprNToInfty \left( \frac{g}{\Tweak{g}} - 1 \right)$ both exist and equal $0$.
 The limit of a bounded expression times one approaching $0$ is $0$; thus, both limits on the right-hand side are $0$.
@@
 	Substituting, I receive $\ExprNToInfty (\FuncQuotient - 1) = 0$, so $\ExprNToInfty \FuncQuotient = 1$.
-Since $\FuncQuotient$ is defined as $\dfrac{f + g}{\Tweak{f} + \Tweak{g}}$, this shows that $f + g \sim \Tweak{f} + \Tweak{g}$, proving the theorem statement for addition.
+Since $\FuncQuotient$ is defined as $\frac{f + g}{\Tweak{f} + \Tweak{g}}$, this shows that $f + g \sim \Tweak{f} + \Tweak{g}$, proving the theorem statement for addition.
 
-	The statement is proven much more easily for multiplication. Since both $\ExprNToInfty \dfrac{f}{\Tweak{f}}$ and $\ExprNToInfty \dfrac{g}{\Tweak{g}}$ exist,
+	The statement is proven much more easily for multiplication. Since both $\ExprNToInfty \frac{f}{\Tweak{f}}$ and $\ExprNToInfty \frac{g}{\Tweak{g}}$ exist,
 	\begin{align*}
@@
 	\end{align*}
-	This implies that $\dfrac f g \sim \dfrac {\Tweak{f}} {\Tweak{g}}$.
+	This implies that $\frac f g \sim \frac {\Tweak{f}} {\Tweak{g}}$.
 \end{proof}
@@
 \begin{proof}
-	Let $r = \dfrac{f}{g}$.
+	Let $r = \frac{f}{g}$.
 Since $\ExprNToInfty r = 1$, $r \leq 2$ for sufficiently large $n$.
@@
 \begin{proof}
-	By definition, $\ExprNToInfty \dfrac{f}{\Tweak{f}} = 1$ and $\ExprNToInfty \dfrac{\Tweak{f}}{\TweakSecond{f}} < 1$. Since both limits exist,
+	By definition, $\ExprNToInfty \frac{f}{\Tweak{f}} = 1$ and $\ExprNToInfty \frac{\Tweak{f}}{\TweakSecond{f}} < 1$. Since both limits exist,
 	\begin{align*}
@@
 	Suppose that $f \FluteLess g$.
-By definition, $\ExprNToInfty \dfrac{f}{g} < 1$.
-For any positive function $h$, $\ExprNToInfty \dfrac{fh}{gh} < 1$ and $\ExprNToInfty \dfrac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\dfrac{f}{h} \FluteLess \dfrac{g}{h}$.
+By definition, $\ExprNToInfty \frac{f}{g} < 1$.
+For any positive function $h$, $\ExprNToInfty \frac{fh}{gh} < 1$ and $\ExprNToInfty \frac{f / h}{g / h} < 1$, so respectively $fh \FluteLess gh$ and $\frac{f}{h} \FluteLess \frac{g}{h}$.
 
@@
 \begin{repcorollary}{coro:BothSidesInequalityInvert}
-	If $f \FluteLess g$, then $\dfrac{1}{g} \FluteLess \dfrac{1}{f}$.\\
+	If $f \FluteLess g$, then $\frac{1}{g} \FluteLess \frac{1}{f}$.\\
 	This statement also holds for $\FluteLeq$.
@@
 \begin{reptheorem}{thm:BothSidesInequalityAdd}
-	Suppose $f \FluteLess g$. If $\ExprNToInfty \dfrac{f}{h} > 0$ and $g = O(h)$, then $f + h \FluteLess g + h$.\\
+	Suppose $f \FluteLess g$. If $\ExprNToInfty \frac{f}{h} > 0$ and $g = O(h)$, then $f + h \FluteLess g + h$.\\
 	This statement also holds for $\FluteLeq$.
@@
 	Assume that $n$ is arbitrarily large.
-Since $\dfrac{f}{h}$ has a positive limit, it is bounded below by some positive constant $c_1$.
+Since $\frac{f}{h}$ has a positive limit, it is bounded below by some positive constant $c_1$.
 Rearranging, $c_1 h \leq f$.
@@
 	\end{align*}
-	Since $c_1 < c_2$, $c_1 + 1 < c_2 + 1$ so $\dfrac{c_1 + 1}{c_2 + 1} < 1$. Thus, $f + h \FluteLess g + h$.
+	Since $c_1 < c_2$, $c_1 + 1 < c_2 + 1$ so $\frac{c_1 + 1}{c_2 + 1} < 1$. Thus, $f + h \FluteLess g + h$.
 

### 2017-11-16 Draft2/AsymptoticNotation.tex
Thank god

@@
 I will also introduce two cousins of $\sim$, the relations $\FluteLess$ and $\FluteLeq$.
-The former is normally defined as $f \prec g \Biconditional \ExprNToInfty \dfrac{f}{g} = 0$.
+The former is normally defined as $f \prec g \Biconditional \ExprNToInfty \frac{f}{g} = 0$.
 However, for the purpose of this paper their definitions will be:
@@
 \label{coro:BothSidesInequalityInvert}
-	If $f \FluteLess g$, then $\dfrac{1}{g} \FluteLess \dfrac{1}{f}$.\\
+	If $f \FluteLess g$, then $\frac{1}{g} \FluteLess \frac{1}{f}$.\\
 	This statement also holds for $\FluteLeq$.
@@
 \label{thm:BothSidesInequalityAdd}
-	Suppose $f \FluteLess g$. If $\ExprNToInfty \dfrac{f}{h} > 0$ and $g = O(h)$, then $f + h \FluteLess g + h$.\\
+	Suppose $f \FluteLess g$. If $\ExprNToInfty \frac{f}{h} > 0$ and $g = O(h)$, then $f + h \FluteLess g + h$.\\
 	This statement also holds for $\FluteLeq$.

### 2017-12-11 Draft2/Indexing.Growth.tex
Painful pondering

@@
 
-Clearly, $\FuncDecompose$ runs in constant time.
-Despite that, it appears to be quite expensive: normally, logarithms and exponentiation require use of floating-point instructions, which are slower than integer-based instructions.
+At first glance, $\FuncDecompose$ appears to be expensive: logarithms and exponentiation normally imply use of floating-point instructions, which tend to be slower than integer-based ones.
 However, in the special case where $\VarGrowthFactor = 2$ and $\VarInitCapacity = 2^\VarLogInitCapacity$ for some constant whole number $\VarLogInitCapacity$, I claim that $\VarIndexBuffer$ and $\VarIndexElement$ can be computed without use of floating-point instructions.
 
-To see this, first note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$.
-There is a constant time algorithm to compute $\left\lceil \log_2 k \right\rceil$ without using floating-point for any $k \in \mathbb{N}$, which I will not discuss because it involves concepts outside the scope of this paper \cite{ceillog2}.
-Equipped with such an algorithm, it is easy to see that the whole expression can be computed without use of floating-point.
-
-In calculating $\VarIndexElement$, the only potential use of floating-point instructions comes from $\VarGrowthFactor^{\VarIndexBuffer - 1}$.
-When $\VarGrowthFactor = 2$, however, this can be calculated with a simple bit shift.
-Thus, it is not necessary to use floating-point instructions to calculate either $\VarIndexBuffer$ or $\VarIndexElement$.
+To see this, note that $\VarIndexBuffer$ becomes $\max(\left\lceil \log_2 (i + 1) \right\rceil - \VarLogInitCapacity, 0)$.
+Using the concept of de Bruijn sequences, one can index the leftmost $1$ in the binary representation of $i$ in constant time \cite{ceillog2}.
+(For example, if $i = 9 = 1001\text{ in binary}$, the index of the leftmost $1$ starting from the right is $3$.) This index is the same as $\left\lfloor \log_2 i \right\rfloor$.
+Using the fact that $\left\lceil \log_2 (i + 1) \right\rceil = \left\lfloor \log_2 i \right\rfloor + 1$ (as there cannot be natural numbers between $\log_2 i$ and $\log_2 (i + 1)$), one can easily find $\VarIndexBuffer$.
+Finally, calculating $\VarGrowthFactor^{\VarIndexBuffer - 1}$ becomes a simple bit shift when $\VarGrowthFactor = 2$.

### 2017-12-11 Draft2/Bibliography.tex
Take care of the bib!

@@
+\begin{flushleft}
 \begin{thebibliography}{9}
 
+\bibitem{tildedef}
+	de Bruijn, Nicolaas G. \textit{Asymptotic Methods in Analysis}. Dover Publications, 1981.
+
+\bibitem{littleodef}
+	Cormen et al. \textit{Introduction to Algorithms, Second Edition}. The MIT Press, 2001.
+
+\bibitem{amortized}
+	Fiebrink, Rebecca. \textit{Amortized Analysis Explained}. Princeton University, 2007. Available at \texttt{https://www.cs.princeton.edu/~fiebrink/423/AmortizedAnalysisExplained\_Fiebrink.pdf}.
+
+\bibitem{fptables}
+	Fog, Agner.
+\textit{Lists of instruction latencies, throughputs and micro-operation breakdowns for Intel, AMD and VIA CPUs}.
+Technical University of Denmark, 2017.
+Available at \texttt{http://www.agner.org/optimize/instruction\_tables.pdf}.
+
 \bibitem{ceillog2}
-	Ko, James L. "Algorithm for implementing ceiling of log 2." \textit{GitHub}, 12 Nov. 2017,\\ \texttt{https://github.com/jamesqo/StsProject/blob/master/src/StsProject/Internal/MathHelpers.cs}
+	Leiserson et al.
+\textit{Using de Bruijn sequences to Index a 1 in a Computer Word}.
+MIT Laboratory for Computer Science, 1998.
+Available at \texttt{http://supertech.csail.mit.edu/papers/debruijn.pdf}.
+
 \end{thebibliography}
+\end{flushleft}

### 2017-12-11 Draft2/Indexing.Growth.tex
Take care of the bib!

@@
 
-At first glance, $\FuncDecompose$ appears to be expensive: logarithms and exponentiation normally imply use of floating-point instructions, which tend to be slower than integer-based ones.
+At first glance, $\FuncDecompose$ appears to be expensive: logarithms and exponentiation normally imply use of floating-point instructions, which tend to be slower than integer-based ones \cite{fptables}.
 However, in the special case where $\VarGrowthFactor = 2$ and $\VarInitCapacity = 2^\VarLogInitCapacity$ for some constant whole number $\VarLogInitCapacity$, I claim that $\VarIndexBuffer$ and $\VarIndexElement$ can be computed without use of floating-point instructions.
@@
 Using the fact that $\left\lceil \log_2 (i + 1) \right\rceil = \left\lfloor \log_2 i \right\rfloor + 1$ (as there cannot be natural numbers between $\log_2 i$ and $\log_2 (i + 1)$), one can easily find $\VarIndexBuffer$.
-Finally, calculating $\VarGrowthFactor^{\VarIndexBuffer - 1}$ becomes a simple bit shift when $\VarGrowthFactor = 2$.
+Finally, calculating $\VarGrowthFactor^{\VarIndexBuffer - 1}$ to find $\VarIndexElement$ becomes a simple bit shift when $\VarGrowthFactor = 2$.

### 2017-12-11 Draft2/Abstract.tex
Make a bunch more changes for NYCSEF

@@
 This paper introduces \textbf{growth arrays}, array-like data structures that are designed for appending elements.
-When the number of items is not known beforehand but is expected to be large, growth arrays are more efficient than dynamic arrays by a constant factor.
+When the number of items is not known beforehand but is expected to be large, growth arrays perform better than dynamic arrays by a constant factor.
 They support all operations dynamic arrays do, such as random access, iteration, and insertion or deletion at an index.
 For operations other than appending, however, they perform the same as or slightly worse than dynamic arrays.
+
+Growth arrays have the potential to make a major impact on the field of computer science.
+If dynamic arrays are replaced with growth arrays across various programming languages and frameworks, it is likely that many programs will see significant performance boosts.
+Also, other array-based data structures such as circular queues and stacks stand to benefit from the efficiency improvements of growth arrays.

### 2017-12-11 Draft2/ClosingRemarks.tex
Add back the thing.
Make a bunch more changes for NYCSEF

@@
-In this paper, I developed the concept of growth arrays and showed that they are a viable replacement for dynamic arrays.
-I implemented several common dynamic array operations for growth arrays, and showed that for appending, growth arrays outperform dynamic ones both time- and memory-wise.
-I demonstrated that although growth arrays are slower at random access than dynamic arrays, it is still possible to index them in constant time.
+In this paper, I formally developed the concept of growth arrays.
+By implementing several common dynamic array operations for them, I showed that they are a viable replacement for dynamic arrays.
+I proved that growth arrays outperform dynamic ones both time- and memory-wise when a large number of elements are appended.
+I exhibited logarithmic and constant time random access algorithms for growth arrays.
 Finally, I showed that they perform comparably to dynamic arrays for iteration and conversion to raw arrays.
 
-I will end this paper with the following open-ended questions, which may serve as inspiration for further research:
+Dynamic arrays are used frequently today because they are efficient at appending.
+Since growth arrays are even more efficient at it, they should be used in place of dynamic arrays when appending is performance-critical.
+Programming languages and frameworks should strongly consider adding support for growth arrays to improve program performance.
+
+I will conclude this paper with several open-ended questions, which may serve as inspiration for further research.
 
 \begin{itemize}
-	\item Can growth arrays' growth algorithm bring performance improvements to other array-based structures, such as circular queues or array-based stacks?
-	\item Is there an efficient, constant time random access algorithm for growth arrays that works for all values of $\VarGrowthFactor$ and $\VarInitCapacity$?
-	\item To what extent does growth arrays' fragmented structure result in performance losses due to poorer data locality?
-Can memory allocators offset these losses by allocating buffers close to each other?
-	\item How can algorithms such as binary search and sorting be best implemented for growth arrays?
-Since growth arrays with $\VarGrowthFactor = 2$ have an evenly-divided structure, is there a better binary search algorithm for them?
+	\item Can other array-based data structures, such as stacks or circular queues, also benefit from using growth arrays' algorithm for growth?
+	\item Is there a constant time random access algorithm for growth arrays that does not use floating-point and works for all values of $\VarGrowthFactor$ and $\VarInitCapacity$?
+	\item To what extent does growth arrays' poorer data locality result in performance losses? (Can tuning memory allocators offset these losses?)
+	\item How can binary search and sorting algorithms be best implemented for growth arrays?
+(In particular, growth arrays with $\VarGrowthFactor = 2$ have an evenly-divided structure: if $2^k$ items are appended, $2^{k - 1}$ will be in the head and $2^{k - 1}$ in the tail.
+Does this lend itself to a better binary search algorithm?)
 \end{itemize}

### 2018-02-06 Draft2/DataCollection.tex
Add DataCollection section

To test my claims, I measured the performance of the above operations in a real programming language and runtime. My computing environment consisted of a Windows 10 desktop with an Intel Core i5-4460T 1.90GHz Haswell processor for the appending benchmarks, and a Windows 10 laptop with an Intel Core i5-7200U 2.50GHz Kaby Lake processor for the other benchmarks. On both computers, I used C\# 7.0 with the .NET Core 2.1.4 runtime. I used the excellent BenchmarkDotNet library to obtain performance metrics and plotted them with the R package ggplot2.

I compared the performance of a growth array implementation I had written in C\# to that of a heavily-optimized dynamic array that was part of the C\# standard library, \texttt{System.Collections.Generic.List}. The \texttt{List} type had parameters $\VarInitCapacity = 4$ and $\VarGrowthFactor = 2$, while my growth array implementation had $\VarInitCapacity = 8$ and $\VarGrowthFactor = 2$. (The different values of $\VarInitCapacity$ were not significant since $\frac{8}{4}$ was a multiple of $\VarGrowthFactor$, causing the two collections to exhibit similar trends for large $n$.) I used 57 unique values of $n$ for the appending benchmarks, and 15 different values of $n$ for the other benchmarks. In both cases, input values included increasing powers of $2$ up to $32768$. For the appending benchmarks, I also included numbers that were one more than a power of $2$, numbers that were the average of two consecutive powers of $2$, and all numbers less than $10$ in my input data. Here are my results:

\begin{figure}[H]
	\begin{minipage}{0.45\textwidth}
		\label{plot:1}
		\centering{\includegraphics[width=3.25in]{Append-timeline}}
		\caption{Time measurements for appending}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\label{plot:2}
		\centering{\includegraphics[width=3.25in]{Append-allocations}}
		\caption{Space measurements for appending}
	\end{minipage}
\end{figure}

\begin{figure}[H]
	\begin{minipage}{0.45\textwidth}
		\label{plot:3}
		\centering{\includegraphics[width=3.25in]{GetItem-timeline}}
		\caption{Time measurements for indexing}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\label{plot:4}
		\centering{\includegraphics[width=3.25in]{Iteration-timeline}}
		\caption{Time measurements for iterating}
	\end{minipage}
\end{figure}

\begin{figure}[H]
	\begin{minipage}{\textwidth}
		\label{plot:5}
		\centering{\includegraphics[width=3.25in]{Copying-timeline}}
		\caption{Time measurements for copying to raw arrays}
	\end{minipage}
\end{figure}

%% TODO: Why isn't \ref working?
Figures 4 and 5 show that growth arrays consistently outperform dynamic arrays at appending. Past $n = 4$, the blue line remains about one unit square below the red line for both graphs. Since the graphs are logarithmically scaled with one unit square representing a factor of $2$, I conclude that growth arrays use approximately half the time and half the space to append the same number of items as dynamic arrays for values of $n$ past $4$.

It misleadingly looks like the lines are touching for values of $n$ near powers of $2$. At these points, the blue and red lines appear to make vertical ``jumps.'' That is not what is really happening. The bottom end of each jump corresponds to when $n$ is a power of $2$, and the top end corresponds to when $n$ is one more than a power of $2$. The top end of each blue jump is close to the bottom end of each red jump, but it is incorrect to compare them since both points correspond to different values of $n$.

As you might guess, these jumps are where full capacity is reached and growth must occur. The sudden increase in time is mainly caused by the $O(n)$ memory allocation and (in dynamic arrays' case) the copying that happens when $\FuncGrow$ is called. Notice that the blue jumps are much less drastic than the red ones; this is because growth arrays do not make a copy of $n$ elements when they grow.

Figure 6 illustrates the graphs of 3 different random access algorithms, 2 of them for growth arrays. The constant time algorithms flat-line as they should, while the logarithmic time algorithm traces out a logarithmic curve. The dynamic array algorithm clearly beats both of the growth array algorithms: it appears to be approximately $8$ times faster than the constant time algorithm I introduced, and around $4$ times faster than the logarithmic time one at the point they are closest. An interesting observation is that the logarithmic time algorithm appears to outperform the blue constant time algorithm for values of $n$ that are $128$ or less.

Figures 7 and 8 show an interesting trend: the blue line converges towards the red line as $n$ gets very large. This supports the claim that I made in Sections \ref{subsec:Iterating} and \ref{subsec:ConvertRawArray} that not only do iteration and copying have the same time complexity for dynamic and growth arrays, their respective algorithms also have negligible time difference across data structures as $n$ gets very large. Also worth noting is the large gap that opens between the red and blue lines in Figure 8 for values of $n$ between $8$ and $4096$. This suggests that for small values of $n$, the extra overhead growth arrays introduce by iterating the tail's buffers is very significant.

### 2018-03-11 Draft2/DataCollection.tex
Changes for NYCSEF finals round

@@
 To test my claims, I measured the performance of the above operations in a real programming language and runtime.
-My computing environment consisted of a Windows 10 desktop with an Intel Core i5-4460T 1.90GHz Haswell processor for the appending benchmarks, and a Windows 10 laptop with an Intel Core i5-7200U 2.50GHz Kaby Lake processor for the other benchmarks.
-On both computers, I used C\# 7.0 with the .NET Core 2.1.4 runtime.
+My computing environment consisted of a Windows 10 desktop with an Intel Core i5-4460T 1.90GHz Haswell processor.
+I used C\# 7.0 with the .NET Core 2.1.4 runtime.
 I used the excellent BenchmarkDotNet library to obtain performance metrics and plotted them with the R package ggplot2.
 
-I compared the performance of a growth array implementation I had written in C\# to that of a heavily-optimized dynamic array that was part of the C\# standard library, \texttt{System.Collections.Generic.List}.
+I compared the performance of a growth array implementation I had written in C\# to that of a heavily-optimized dynamic array provided by the C\# standard library, \texttt{System.Collections.Generic.List}.
 The \texttt{List} type had parameters $\VarInitCapacity = 4$ and $\VarGrowthFactor = 2$, while my growth array implementation had $\VarInitCapacity = 8$ and $\VarGrowthFactor = 2$.
@@
 In both cases, input values included increasing powers of $2$ up to $32768$.
-For the appending benchmarks, I also included numbers that were one more than a power of $2$, numbers that were the average of two consecutive powers of $2$, and all numbers less than $10$ in my input data.
+For the appending benchmarks, I also tested with values of $n$ that were one more than a power of $2$, values that were the average of two consecutive powers of $2$, and values from $1$ to $10$.
 Here are my results:
@@
 This suggests that for small values of $n$, the extra overhead growth arrays introduce by iterating the tail's buffers is very significant.
+
+For all benchmarks, BenchmarkDotNet consistently reported margins of error and standard deviation values on the order of $\frac{1}{100}$th of the measurement values.
